### 2019-09-04 paper.tex
inicio del paper de fuerza de compresion

%% Copyright 2007, 2008, 2009 Elsevier Ltd

\documentclass[preprint,12pt]{elsarticle}

\usepackage{verbatim} % comentarios
\usepackage{epsfig}
\usepackage{amssymb}

\usepackage{mathtools}

\usepackage{lineno}

\usepackage{tikz}        %permite rellenar las figuras (circulos)
\usepackage{etoolbox}
%\usepackage[backend=biber,citestyle=authoryear]{biblatex}

%\usepackage{epstopdf}

\usepackage[caption=false]{subfig}

\begin{document}

\newcommand*{\hwplotB}{\raisebox{3pt}{\tikz{\draw[red,dashed,line 
width=3.2pt](0,0) -- 
(5mm,0);}}}

\newrobustcmd*{\mydiamond}[1]{\tikz{\filldraw[black,fill=#1] (0,0) -- 
(0.1cm,0.2cm) --
(0.2cm,0) -- (0.1cm,-0.2cm);}}

\newrobustcmd*{\mytriangleleft}[1]{\tikz{\filldraw[black,fill=#1] (0,0.15cm) -- 
(-0.3cm,0) -- (0,-0.15cm);}}
\definecolor{Blue}{cmyk}{1.,1.,0,0}

\begin{frontmatter}

\title{Effects of body force on the original Social Force Model}

\begin{abstract}

\end{abstract}

\begin{keyword}

Pedestrian Dynamics \sep Social Force Model \sep 
Jamaraat Pilgrimage

\PACS 45.70.Vn \sep 89.65.Lm

\end{keyword}

\end{frontmatter}

%\linenumbers

\section{\label{introduction}Introduction}

\section{\label{background}Background}

\subsection{\label{sfm}The Social Force Model}

\section{\label{simulations}Setting and parameters}

\subsection{\label{software} Simulation software}

\section{\label{results}Results}

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./vd_vs_te_N225.eps}
\caption{\label{} }
\end{figure}

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./vd_vs_te_ck.eps}
\caption{\label{} }
\end{figure}

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./flow-density_vd1_multi_kn.eps}
\caption{\label{} }
\end{figure}

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./histo_grado_density5_width22_kn0.eps}
\caption{\label{} }
\end{figure}

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./histo_grado_density7_width22_kn0.eps}
\caption{\label{} }
\end{figure}

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./histo_grado_density9_width22_kn0.eps}
\caption{\label{} }
\end{figure}

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./histo_grado_density5_width22_knE5.eps}
\caption{\label{} }
\end{figure}

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./histo_grado_density7_width22_knE5.eps}
\caption{\label{} }
\end{figure}

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./histo_grado_density9_width22_knE5.eps}
\caption{\label{} }
\end{figure}

\section{\label{conclusions}Conclusions}

\section*{Acknowledgments}
This work was supported by the National Scientific and Technical 
Research Council (spanish: Consejo Nacional de Investigaciones Cient\'\i ficas 
y T\'ecnicas - CONICET, Argentina) grant Programaci\'on Cient\'\i fica 2018 (UBACYT) Number 20020170100628BA.

\appendix

%/////////////////////////////////////////////////
\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

%\bibitem{helbing3}
%Helbing, D., Johansson, A., and Al-Abideen, H. Z., 2007. ``Dynamics of crowd 
%disasters: An empirical study." Physical review E 75 (4), 046109.
%{\path{https://doi.org/10.1103/PhysRevE.75.046109}}

\end{thebibliography}
\end{document}
\endinput

### 2019-09-04 plots/distribucion_grado/kn0/plot_histo.py

@@ -1,0 +1,113 @@
+# Sacado de https://scipy.github.io/old-wiki/pages/Cookbook/Matplotlib/LaTeX_Examples.html
+'''
+Grafica histogramas 
+'''
+
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+#import numarray
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+########################  MAIN  ########################
+def main():
+
+	##### PARAMETERS ##### 
+	density = 5
+	kn = "0"
+	clase = "density{}_width22_kn{}".format(density,kn)
+	distribucion = np.genfromtxt("distrib_grado_{}".format(clase),delimiter = ' ')    
+	title_plot= "Corridor $w=$22~m - $k_n$={} - Density={}".format(kn,density)
+	out_name = "histo_grado_{}".format(clase)
+	binwidth = 0.007
+	min_comp = 0.0
+	max_comp = 0.17
+
+	min_grado = 0
+	max_grado = 7
+	plot_histo_norm_discreta(distribucion,title_plot,out_name,min_grado,max_grado)
+	#plot_histo_normalized(distribucion,title_plot,out_name,binwidth,min_comp,max_comp)
+
+
+
+
+def plot_histo_ocurrence(distribucion,titulo,out_name):
+     plt.figure()
[…]

### 2019-09-04 plots/distribucion_grado/knE5/plot_histo.py

@@ -1,0 +1,113 @@
+# Sacado de https://scipy.github.io/old-wiki/pages/Cookbook/Matplotlib/LaTeX_Examples.html
+'''
+Grafica histogramas 
+'''
+
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+#import numarray
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+########################  MAIN  ########################
+def main():
+
+	##### PARAMETERS ##### 
+	density = 9
+	kn = "E5"
+	clase = "density{}_width22_kn{}".format(density,kn)
+	distribucion = np.genfromtxt("distrib_grado_{}".format(clase),delimiter = ' ')    
+	title_plot= "Corridor $w=$22~m - $k_n$={} - Density={}".format(kn,density)
+	out_name = "histo_grado_{}".format(clase)
+	binwidth = 0.007
+	min_comp = 0.0
+	max_comp = 0.17
+
+	min_grado = 0
+	max_grado = 7
+	plot_histo_norm_discreta(distribucion,title_plot,out_name,min_grado,max_grado)
+	#plot_histo_normalized(distribucion,title_plot,out_name,binwidth,min_comp,max_comp)
+
+
+
+
+def plot_histo_ocurrence(distribucion,titulo,out_name):
+     plt.figure()
[…]

### 2019-09-04 plots/fis225/plot_fis.py

@@ -1,0 +1,90 @@
+# Sacado de https://scipy.github.io/old-wiki/pages/Cookbook/Matplotlib/LaTeX_Examples.html
+
+'''
+Grafica tiempo de evacuacion vs vd usando Pandas
+'''
+
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+import pandas as pd 
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+### DATA ###
+
+
+
+data_kcomp_E4 = pd.read_csv("tevsvd_N225_kcom_E4.txt", header=None,delimiter=' ') 
+data_kcomp_E4.columns=['vd','iter','te','N_quedaron','nan']
+vd_kcomp_E4 = list(data_kcomp_E4.vd.unique())
+avg_te_kcomp_E4 = data_kcomp_E4.groupby(data_kcomp_E4['vd'])['te'].mean().values.tolist()
+std_te_kcomp_E4 = data_kcomp_E4.groupby(data_kcomp_E4['vd'])['te'].std().values.tolist()
+
+data_kcomp_E5 = pd.read_csv("tevsvd_N225_kcom_E5.txt", header=None,delimiter=' ') 
[…]

### 2019-09-04 plots/fisck/plot_fis.py

@@ -1,0 +1,90 @@
+# Sacado de https://scipy.github.io/old-wiki/pages/Cookbook/Matplotlib/LaTeX_Examples.html
+
+'''
+Grafica tiempo de evacuacion vs vd usando Pandas
+'''
+
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+import pandas as pd 
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+### DATA ###
+
+
+
+data_kcomp_E4 = pd.read_csv("tevsvd_ck_kcomp_E4.txt", header=None,delimiter=' ') 
+data_kcomp_E4.columns=['vd','iter','te','N_quedaron','nan']
+vd_kcomp_E4 = list(data_kcomp_E4.vd.unique())
+avg_te_kcomp_E4 = data_kcomp_E4.groupby(data_kcomp_E4['vd'])['te'].mean().values.tolist()
+std_te_kcomp_E4 = data_kcomp_E4.groupby(data_kcomp_E4['vd'])['te'].std().values.tolist()
+
+data_kcomp_E5 = pd.read_csv("tevsvd_ck_kcomp_E5.txt", header=None,delimiter=' ') 
[…]

### 2019-09-04 plots/fundamental_diagram_kn/flow_density.py

@@ -1,0 +1,84 @@
+# Sacado de https://scipy.github.io/old-wiki/pages/Cookbook/Matplotlib/LaTeX_Examples.html
+
+'''
+
+'''
+
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+#import numarray
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+### DATA ###
+data_kn0 = np.genfromtxt("flow-density_vd1_pasillo22m_kn0.txt",delimiter = ' ') 
+density_kn0 = data_kn0[:,0]
+flow_kn0 = data_kn0[:,1]
+
+data_knE4 = np.genfromtxt("flow-density_vd1_pasillo22m_knE4.txt",delimiter = ' ') 
+density_knE4 = data_knE4[:,0]
+flow_knE4 = data_knE4[:,1]
+
+data_knE5 = np.genfromtxt("flow-density_vd1_pasillo22m_knE5.txt",delimiter = ' ') 
+density_knE5 = data_knE5[:,0]
+flow_knE5 = data_knE5[:,1]
+
+
+###  PLOT  ###
+
+fig, ax1 = plt.subplots()
+
+#plt.plot(density_kn0,flow_kn0,'k--+',mew=0.7,markersize=4,label='width = 2m') 
[…]

### 2019-11-26 paper.tex
borre todo lo viejo y puse el grafico de te vs vd

@@
 
-\title{Effects of body force on the original Social Force Model}
+\title{Effects of the body force on the evacuation dynamics}
 
@@
 
-Pedestrian Dynamics \sep Social Force Model \sep 
-Jamaraat Pilgrimage
+Pedestrian Dynamics \sep Social Force Model \sep Body Force
 
@@
 
-\section{\label{simulations}Setting and parameters}
-
-\subsection{\label{software} Simulation software}
+\section{\label{simulations}Numerical simulations}
 
 \section{\label{results}Results}
+
+\subsection{\label{bottleneck} Bottleneck}
 
@@
 
-\begin{figure}[htbp!]
-\centering
-\includegraphics[width=0.7\columnwidth]
-{./vd_vs_te_ck.eps}
-\caption{\label{} }
-\end{figure}
+\subsection{\label{corridor} Corridor}
 
-\begin{figure}[htbp!]
-\centering
-\includegraphics[width=0.7\columnwidth]
-{./flow-density_vd1_multi_kn.eps}
-\caption{\label{} }
-\end{figure}
-
-\begin{figure}[htbp!]
-\centering
-\includegraphics[width=0.7\columnwidth]
-{./histo_grado_density5_width22_kn0.eps}
-\caption{\label{} }
-\end{figure}
-
-\begin{figure}[htbp!]
-\centering
-\includegraphics[width=0.7\columnwidth]
-{./histo_grado_density7_width22_kn0.eps}
-\caption{\label{} }
-\end{figure}
-
-\begin{figure}[htbp!]
-\centering
-\includegraphics[width=0.7\columnwidth]
-{./histo_grado_density9_width22_kn0.eps}
-\caption{\label{} }
-\end{figure}
-
-\begin{figure}[htbp!]
-\centering
-\includegraphics[width=0.7\columnwidth]
-{./histo_grado_density5_width22_knE5.eps}
-\caption{\label{} }
-\end{figure}
-
-\begin{figure}[htbp!]
-\centering
-\includegraphics[width=0.7\columnwidth]
-{./histo_grado_density7_width22_knE5.eps}
-\caption{\label{} }
-\end{figure}
-
-\begin{figure}[htbp!]
-\centering
-\includegraphics[width=0.7\columnwidth]
-{./histo_grado_density9_width22_knE5.eps}
-\caption{\label{} }
-\end{figure}
+\subsection{\label{reduced-in-units} Reduced-in-units equation of motion}
 

### 2019-11-26 plots/bottleneck/compresion/plot_histo.py

@@ -1,0 +1,113 @@
+# Sacado de https://scipy.github.io/old-wiki/pages/Cookbook/Matplotlib/LaTeX_Examples.html
+'''
+Grafica histogramas 
+'''
+
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+#import numarray
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+########################  MAIN  ########################
+def main():
+
+     ##### PARAMETERS ##### 
+     vd = 10
+     kn = "120000"
+     clase = "bottleneck_vd{}_k{}".format(vd,kn)
+     distribucion = np.genfromtxt("distrib_comp_{}".format(clase),delimiter = ' ')    
+     title_plot= "Bottleneck - $k_n$={} - $v_d$={}".format(kn,vd)
+     out_name = "histo_grado_{}".format(clase)
+     binwidth = 0.005
+     min_comp = 0.0
+     max_comp = 0.20
+     min_grado = 0
+     max_grado = 7
+     print("media= ",np.mean(distribucion))
+     #plot_histo_norm_discreta(distribucion,title_plot,out_name,min_grado,max_grado)
+     plot_histo_normalized(distribucion,title_plot,out_name,binwidth,min_comp,max_comp)
+
+
+
+
[…]

### 2019-11-26 plots/bottleneck/te/plot_fis.py

@@ -1,0 +1,105 @@
+# Sacado de https://scipy.github.io/old-wiki/pages/Cookbook/Matplotlib/LaTeX_Examples.html
+
+'''
+Grafica tiempo de evacuacion vs vd usando Pandas
+'''
+
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+import pandas as pd 
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+### DATA ###
+
+
+data_kcomp_E4 = pd.read_csv("tevsvd_N225_k12000.txt", header=None,delimiter=' ') 
+data_kcomp_E4.columns=['vd','iter','te','N_quedaron','nan']
+vd_kcomp_E4 = list(data_kcomp_E4.vd.unique())
+avg_te_kcomp_E4 = data_kcomp_E4.groupby(data_kcomp_E4['vd'])['te'].mean().values.tolist()
+std_te_kcomp_E4 = data_kcomp_E4.groupby(data_kcomp_E4['vd'])['te'].std().values.tolist()
+
+data_kcomp_E5 = pd.read_csv("tevsvd_N225_k120000.txt", header=None,delimiter=' ') 
[…]

### 2019-11-26 plots/distribucion_grado/kn0/plot_histo.py

@@ -1,113 +1,0 @@
-# Sacado de https://scipy.github.io/old-wiki/pages/Cookbook/Matplotlib/LaTeX_Examples.html
-'''
-Grafica histogramas 
-'''
-
-import pylab
-import numpy as np
-import matplotlib.pyplot as plt
-import math
-#import numarray
-
-# a dos columnas: 3+3/8 (ancho, in)
-# a una columna : 6.5   (ancho  in)
-
-golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
-fig_width = 3+3/8 			    # width  in inches
-fig_height = fig_width*golden_mean          # height in inches
-fig_size =  [fig_width,fig_height]
-
-params = {'backend': 'ps',
-          'axes.titlesize': 8,
-          'axes.labelsize': 9,
-          'axes.linewidth': 0.5, 
-          'axes.grid': True,
-          'axes.labelweight': 'normal',  
-          'font.family': 'serif',
-          'font.size': 8.0,
-          'font.weight': 'normal',
-          'text.color': 'black',
-          'xtick.labelsize': 8,
-          'ytick.labelsize': 8,
-          'text.usetex': True,
-          'legend.fontsize': 8,
-          'figure.dpi': 300,
-          'figure.figsize': fig_size,
-          'savefig.dpi': 300,
-         }
-
-pylab.rcParams.update(params)
-
-########################  MAIN  ########################
-def main():
-
-	##### PARAMETERS ##### 
-	density = 5
-	kn = "0"
-	clase = "density{}_width22_kn{}".format(density,kn)
-	distribucion = np.genfromtxt("distrib_grado_{}".format(clase),delimiter = ' ')    
-	title_plot= "Corridor $w=$22~m - $k_n$={} - Density={}".format(kn,density)
-	out_name = "histo_grado_{}".format(clase)
-	binwidth = 0.007
-	min_comp = 0.0
-	max_comp = 0.17
-
-	min_grado = 0
-	max_grado = 7
-	plot_histo_norm_discreta(distribucion,title_plot,out_name,min_grado,max_grado)
-	#plot_histo_normalized(distribucion,title_plot,out_name,binwidth,min_comp,max_comp)
-
-
-
-
-def plot_histo_ocurrence(distribucion,titulo,out_name):
-     plt.figure()
[…]

### 2019-11-26 plots/distribucion_grado/knE5/plot_histo.py

@@ -1,113 +1,0 @@
-# Sacado de https://scipy.github.io/old-wiki/pages/Cookbook/Matplotlib/LaTeX_Examples.html
-'''
-Grafica histogramas 
-'''
-
-import pylab
-import numpy as np
-import matplotlib.pyplot as plt
-import math
-#import numarray
-
-# a dos columnas: 3+3/8 (ancho, in)
-# a una columna : 6.5   (ancho  in)
-
-golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
-fig_width = 3+3/8 			    # width  in inches
-fig_height = fig_width*golden_mean          # height in inches
-fig_size =  [fig_width,fig_height]
-
-params = {'backend': 'ps',
-          'axes.titlesize': 8,
-          'axes.labelsize': 9,
-          'axes.linewidth': 0.5, 
-          'axes.grid': True,
-          'axes.labelweight': 'normal',  
-          'font.family': 'serif',
-          'font.size': 8.0,
-          'font.weight': 'normal',
-          'text.color': 'black',
-          'xtick.labelsize': 8,
-          'ytick.labelsize': 8,
-          'text.usetex': True,
-          'legend.fontsize': 8,
-          'figure.dpi': 300,
-          'figure.figsize': fig_size,
-          'savefig.dpi': 300,
-         }
-
-pylab.rcParams.update(params)
-
-########################  MAIN  ########################
-def main():
-
-	##### PARAMETERS ##### 
-	density = 9
-	kn = "E5"
-	clase = "density{}_width22_kn{}".format(density,kn)
-	distribucion = np.genfromtxt("distrib_grado_{}".format(clase),delimiter = ' ')    
-	title_plot= "Corridor $w=$22~m - $k_n$={} - Density={}".format(kn,density)
-	out_name = "histo_grado_{}".format(clase)
-	binwidth = 0.007
-	min_comp = 0.0
-	max_comp = 0.17
-
-	min_grado = 0
-	max_grado = 7
-	plot_histo_norm_discreta(distribucion,title_plot,out_name,min_grado,max_grado)
-	#plot_histo_normalized(distribucion,title_plot,out_name,binwidth,min_comp,max_comp)
-
-
-
-
-def plot_histo_ocurrence(distribucion,titulo,out_name):
-     plt.figure()
[…]

### 2019-11-26 plots/fis225/plot_fis.py

@@ -1,90 +1,0 @@
-# Sacado de https://scipy.github.io/old-wiki/pages/Cookbook/Matplotlib/LaTeX_Examples.html
-
-'''
-Grafica tiempo de evacuacion vs vd usando Pandas
-'''
-
-import pylab
-import numpy as np
-import matplotlib.pyplot as plt
-import math
-import pandas as pd 
-
-# a dos columnas: 3+3/8 (ancho, in)
-# a una columna : 6.5   (ancho  in)
-
-golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
-fig_width = 3+3/8 			    # width  in inches
-fig_height = fig_width*golden_mean          # height in inches
-fig_size =  [fig_width,fig_height]
-
-params = {'backend': 'ps',
-          'axes.titlesize': 8,
-          'axes.labelsize': 9,
-          'axes.linewidth': 0.5, 
-          'axes.grid': True,
-          'axes.labelweight': 'normal',  
-          'font.family': 'serif',
-          'font.size': 8.0,
-          'font.weight': 'normal',
-          'text.color': 'black',
-          'xtick.labelsize': 8,
-          'ytick.labelsize': 8,
-          'text.usetex': True,
-          'legend.fontsize': 8,
-          'figure.dpi': 300,
-          'figure.figsize': fig_size,
-          'savefig.dpi': 300,
-         }
-
-pylab.rcParams.update(params)
-
-### DATA ###
-
-
-
-data_kcomp_E4 = pd.read_csv("tevsvd_N225_kcom_E4.txt", header=None,delimiter=' ') 
-data_kcomp_E4.columns=['vd','iter','te','N_quedaron','nan']
-vd_kcomp_E4 = list(data_kcomp_E4.vd.unique())
-avg_te_kcomp_E4 = data_kcomp_E4.groupby(data_kcomp_E4['vd'])['te'].mean().values.tolist()
-std_te_kcomp_E4 = data_kcomp_E4.groupby(data_kcomp_E4['vd'])['te'].std().values.tolist()
-
-data_kcomp_E5 = pd.read_csv("tevsvd_N225_kcom_E5.txt", header=None,delimiter=' ') 
[…]

### 2019-11-26 plots/fisck/plot_fis.py

@@ -1,90 +1,0 @@
-# Sacado de https://scipy.github.io/old-wiki/pages/Cookbook/Matplotlib/LaTeX_Examples.html
-
-'''
-Grafica tiempo de evacuacion vs vd usando Pandas
-'''
-
-import pylab
-import numpy as np
-import matplotlib.pyplot as plt
-import math
-import pandas as pd 
-
-# a dos columnas: 3+3/8 (ancho, in)
-# a una columna : 6.5   (ancho  in)
-
-golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
-fig_width = 3+3/8 			    # width  in inches
-fig_height = fig_width*golden_mean          # height in inches
-fig_size =  [fig_width,fig_height]
-
-params = {'backend': 'ps',
-          'axes.titlesize': 8,
-          'axes.labelsize': 9,
-          'axes.linewidth': 0.5, 
-          'axes.grid': True,
-          'axes.labelweight': 'normal',  
-          'font.family': 'serif',
-          'font.size': 8.0,
-          'font.weight': 'normal',
-          'text.color': 'black',
-          'xtick.labelsize': 8,
-          'ytick.labelsize': 8,
-          'text.usetex': True,
-          'legend.fontsize': 8,
-          'figure.dpi': 300,
-          'figure.figsize': fig_size,
-          'savefig.dpi': 300,
-         }
-
-pylab.rcParams.update(params)
-
-### DATA ###
-
-
-
-data_kcomp_E4 = pd.read_csv("tevsvd_ck_kcomp_E4.txt", header=None,delimiter=' ') 
-data_kcomp_E4.columns=['vd','iter','te','N_quedaron','nan']
-vd_kcomp_E4 = list(data_kcomp_E4.vd.unique())
-avg_te_kcomp_E4 = data_kcomp_E4.groupby(data_kcomp_E4['vd'])['te'].mean().values.tolist()
-std_te_kcomp_E4 = data_kcomp_E4.groupby(data_kcomp_E4['vd'])['te'].std().values.tolist()
-
-data_kcomp_E5 = pd.read_csv("tevsvd_ck_kcomp_E5.txt", header=None,delimiter=' ') 
[…]

### 2019-11-26 plots/fundamental_diagram_kn/flow_density.py

@@ -1,84 +1,0 @@
-# Sacado de https://scipy.github.io/old-wiki/pages/Cookbook/Matplotlib/LaTeX_Examples.html
-
-'''
-
-'''
-
-import pylab
-import numpy as np
-import matplotlib.pyplot as plt
-import math
-#import numarray
-
-# a dos columnas: 3+3/8 (ancho, in)
-# a una columna : 6.5   (ancho  in)
-
-golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
-fig_width = 3+3/8 			    # width  in inches
-fig_height = fig_width*golden_mean          # height in inches
-fig_size =  [fig_width,fig_height]
-
-params = {'backend': 'ps',
-          'axes.titlesize': 8,
-          'axes.labelsize': 9,
-          'axes.linewidth': 0.5, 
-          'axes.grid': True,
-          'axes.labelweight': 'normal',  
-          'font.family': 'serif',
-          'font.size': 8.0,
-          'font.weight': 'normal',
-          'text.color': 'black',
-          'xtick.labelsize': 8,
-          'ytick.labelsize': 8,
-          'text.usetex': True,
-          'legend.fontsize': 8,
-          'figure.dpi': 300,
-          'figure.figsize': fig_size,
-          'savefig.dpi': 300,
-         }
-
-pylab.rcParams.update(params)
-
-### DATA ###
-data_kn0 = np.genfromtxt("flow-density_vd1_pasillo22m_kn0.txt",delimiter = ' ') 
-density_kn0 = data_kn0[:,0]
-flow_kn0 = data_kn0[:,1]
-
-data_knE4 = np.genfromtxt("flow-density_vd1_pasillo22m_knE4.txt",delimiter = ' ') 
-density_knE4 = data_knE4[:,0]
-flow_knE4 = data_knE4[:,1]
-
-data_knE5 = np.genfromtxt("flow-density_vd1_pasillo22m_knE5.txt",delimiter = ' ') 
-density_knE5 = data_knE5[:,0]
-flow_knE5 = data_knE5[:,1]
-
-
-###  PLOT  ###
-
-fig, ax1 = plt.subplots()
-
-#plt.plot(density_kn0,flow_kn0,'k--+',mew=0.7,markersize=4,label='width = 2m') 
[…]

### 2019-11-26 paper.tex
agregue el diagrama fundamental

@@
 
+\begin{figure}[!htbp]
+\centering
+    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_bottleneck_vd2_k0.eps}\label{size_distribution_w22_density4.5}}\ 
+    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_bottleneck_vd2_k120000.eps}\label{size_distribution_w22_density4.5_kx10}}\\
+    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_bottleneck_vd4_k0.eps}\label{size_distribution_w22_density5}}\
+    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_bottleneck_vd4_k120000.eps}\label{size_distribution_w22_density5_kx10}}\\
+    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_bottleneck_vd10_k0.eps}\label{size_distribution_w22_density5_5}}\
+    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_bottleneck_vd10_k120000.eps}\label{size_distribution_w22_density5_5_kx10}}
+\caption[width=0.47\columnwidth]{}
+\label{compresion_distribution}
+\end{figure}
+
 \subsection{\label{corridor} Corridor}
+
+\begin{figure}[!htbp]
+\centering
+    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./flow-density_multifric_nocomp.eps}\label{flow_density_nocomp}}\ 
+    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./flow-density_multifric_comp.eps}\label{flow_density_comp}}\\
+\caption[width=0.47\columnwidth]{}
+\label{flow_density}
+\end{figure}
 

### 2019-11-26 plots/bottleneck/compresion/plot_histo.py

@@ -43,7 +43,7 @@ def main():
 
      ##### PARAMETERS ##### 
      vd = 10
-     kn = "120000"
+     kn = "0"
      clase = "bottleneck_vd{}_k{}".format(vd,kn)
      distribucion = np.genfromtxt("distrib_comp_{}".format(clase),delimiter = ' ')    
      title_plot= "Bottleneck - $k_n$={} - $v_d$={}".format(kn,vd)

### 2019-11-26 plots/corridor/fundamental_diagram/flow_density_multi.py

@@ -1,0 +1,107 @@
+'''
+Grafica multiples densidades vs flujo
+'''
+
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+import pandas as pd
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+### DATA ###
+
+data_kn_kt = pd.read_csv("flow_density_kn_kt.txt",sep=" ")
+density_kn_kt = data_kn_kt["density"].tolist()
+flow_kn_kt = data_kn_kt["flow"].tolist()
+speed_kn_kt=np.divide(flow_kn_kt,density_kn_kt)
+
+data_kn_ktx3 = pd.read_csv("flow_density_kn_ktx3.txt",sep=" ")
+density_kn_ktx3 = data_kn_ktx3["density"].tolist()
+flow_kn_ktx3 = data_kn_ktx3["flow"].tolist()
+speed_kn_ktx3=np.divide(flow_kn_ktx3,density_kn_ktx3)
+
+data_kn_ktx5 = pd.read_csv("flow_density_kn_ktx5.txt",sep=" ")
[…]

### 2019-11-26 paper.tex
incorporacion de mas graficos

@@
 
+\begin{figure}[!htbp]
+\centering
+    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_density7_width22_kn0.eps}\label{flow_density_nocomp}}\ 
+    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_density7_width22_knE5.eps}\label{flow_density_comp}}\\
+        \subfloat[]{\includegraphics[width=0.40\columnwidth]{./tesselation_d7_t30_kn0.eps}\label{tesselation_d7_t30_kn0}}\
+    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./tesselation_d7_t30_knE5.eps}\label{tesselation_d7_t30_knE5}}\\
+            \subfloat[]{\includegraphics[width=0.40\columnwidth]{./g(r)_d7_kn0.eps}\label{g(r)_d7_kn0}}\
+    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./g(r)_d7_knE5.eps}\label{g(r)_d7_knE5}}\\
+\caption[width=0.47\columnwidth]{}
+\label{flow_density}
+\end{figure}
+
+\begin{figure}[htbp!]
+\centering
+\includegraphics[width=0.7\columnwidth]
+{./triangles.eps}
+\caption{\label{} }
+\end{figure}
+
 \subsection{\label{reduced-in-units} Reduced-in-units equation of motion}

### 2019-11-26 plots/corridor/degree_distribution/plot_histo.py

@@ -1,0 +1,114 @@
+# Sacado de https://scipy.github.io/old-wiki/pages/Cookbook/Matplotlib/LaTeX_Examples.html
+'''
+Grafica histogramas 
+'''
+
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+#import numarray
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+########################  MAIN  ########################
+def main():
+
+	##### PARAMETERS ##### 
+	density = 7
+	kn = "E5"
+	clase = "density{}_width22_kn{}".format(density,kn)
+	distribucion = np.genfromtxt("distrib_grado_{}".format(clase),delimiter = ' ')    
+	title_plot= "Corridor $w=$22~m - $k_n$={} - Density={}".format(kn,density)
+	out_name = "histo_grado_{}".format(clase)
+	binwidth = 0.007
+	min_comp = 0.0
+	max_comp = 0.17
+
+	min_grado = 0
+	max_grado = 7
+	plot_histo_norm_discreta(distribucion,title_plot,out_name,min_grado,max_grado)
+	#plot_histo_normalized(distribucion,title_plot,out_name,binwidth,min_comp,max_comp)
+
+
+
+
+def plot_histo_ocurrence(distribucion,titulo,out_name):
+     plt.figure()
[…]

### 2019-11-26 plots/corridor/g_r/plot_gr.py

@@ -1,0 +1,61 @@
+'''
+Calcula la funcion de correlacion radial g(r)
+'''
+import pylab
+import numpy as np
+import math
+import matplotlib.pyplot as plt
+import pandas as pd
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8                            # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 600,
+         }
+
+pylab.rcParams.update(params)
+
+density = "7"
+output_name_histo = "g(r)_d{}_knE5".format(density)
+titulo = "Global density ={}".format(density)+" p.m$^{-2}$"
+
+data_kn0_d7 = pd.read_csv("r_g_density{}_width22_kn0_r28x22".format(density),sep="\t")
+r_kn0_d7 =  data_kn0_d7["bins"].tolist()
+g_kn0_d7 =  data_kn0_d7["g"].tolist()
+
+data_knE5_d7 = pd.read_csv("r_g_density{}_width22_knE5_r28x22".format(density),sep="\t")
+r_knE5_d7 =  data_knE5_d7["bins"].tolist()
+g_knE5_d7 =  data_knE5_d7["g"].tolist()
+
+
+#plt.plot(r_kn0_d7, g_kn0_d7, '-r',lw=1,label="$k_n=$0")
+plt.plot(r_knE5_d7, g_knE5_d7, '-b',lw=1,label="$k_n=$1.2 E5")
+
+pylab.grid(False)
+pylab.xlabel('$r$(m)',fontsize=10)
+pylab.ylabel('$g~(r)$',fontsize=10)
+pylab.title('{}'.format(titulo),fontsize=10)
+pylab.xlim(0.0, 2)
[…]

### 2019-11-26 plots/corridor/triangles/plot_network_parameters.py

@@ -1,0 +1,149 @@
+import sys
+import os
+import pandas as pd
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+
+
+def main():
+
+
+     df = pd.read_csv('network_data_knE5_t100s.txt',delimiter = '\t') 
+     global_density = df['0.density'].tolist()
+     f_in_giant = df['2.fraction nodes in giant'].tolist()
+     shortest_path = df['5.average shortest path length'].tolist()
+     diameter = df['6.diameter'].tolist()
+     mean_degree = df['7.mean degree'].tolist()
+     std_degree = df['8.std degree'].tolist()
+     traingles = df['9.triangles per node'].tolist()
+     simbol ='-o'
+     color = 'b'
+     label = "With body force"
+     #plot_degree(global_density,mean_degree,std_degree,color,simbol,label)
+     #plot_fraction_in_giant(global_density,f_in_giant,color,simbol,label)
+     #plot_shortest_path(global_density,shortest_path,color,simbol,label)
+     #plot_diameter(global_density,diameter,color,simbol,label)
+     plot_triangles(global_density,traingles,color,simbol,label)
+
+
[…]

### 2019-11-26 plots/corridor/voronoi/plot_voronoi_tessellation_color.py

@@ -1,0 +1,165 @@
+import pylab
+import numpy as np
+import math
+import matplotlib.pyplot as plt
+import pandas as pd
+from   scipy.spatial import Voronoi, voronoi_plot_2d
+from   scipy.spatial import ConvexHull
+import matplotlib.patches as patches
+import matplotlib as mpl
+import matplotlib.cm as cm
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8                            # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 600,
+         }
+
+pylab.rcParams.update(params)
+
+
+################## PRAMETERS ######################### 
+selected_time = 30
+global_density = 7
+output_name = "tesselation_d{}_time{}_color_relative_kn0".format(global_density,selected_time)
+data_config = "config_density{}_width22_kn0".format(global_density)
+xmin = 1.0
+xmax = 27.0
+ymin = 1
+ymax = 21.0
+
+
+######################## Functions ##################### 
+
+def extract_config(data,t):
+     '''
+     t is the selected time
+     this function extracts the configuration for the time t
+     only one timestep is extracted
+     '''
+     ESCALA_TIME = 10000
+
+     str_selected_timestep='{}\n'.format(int(t*ESCALA_TIME))
+     f=open(data, 'r')
+     lines=f.readlines()
+     x=[]
+     y=[]
+     i=0
+     flag=True
+     while i<len(lines) and flag:
+          line = lines[i].rstrip('\n')
+          if(line=='ITEM: TIMESTEP'):
+               iter_time=lines[i+1]
+               if(iter_time==str_selected_timestep):
+                    number_pedestrians=int(lines[i+3])
+                    first_line_table=i+9
[…]

### 2019-11-26 plots/reduced-in-units/venn.py

@@ -1,0 +1,43 @@
+import pylab as plt
+from matplotlib_venn import venn3, venn3_circles
+import math
+import pylab
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+v = venn3(subsets=(1,1,1,1,1,1,1),set_labels = ('$\mathcal{A}$', '$\mathcal{K}$', '$\mathcal{K}_c$'))
+v.get_label_by_id('100').set_text(' $\\frac{A \\tau}{m v_d}$')
+v.get_label_by_id('010').set_text('$\\frac{\\kappa B \\tau}{m}$')
+v.get_label_by_id('001').set_text('$\\frac{k B \\tau}{m v_d}$')
+v.get_label_by_id('111').set_text('$m/\\tau$')
+v.get_label_by_id('101').set_text('$\\frac{\\tau}{m v_d}$')
+v.get_label_by_id('110').set_text('')
+v.get_label_by_id('011').set_text('$\\frac{B\\tau}{m}$')
+
+
+pylab.savefig('venn_parameters.png', format='png', dpi=300, bbox_inches='tight')
+pylab.savefig('venn_parameters.eps', format='eps', dpi=300, bbox_inches='tight')

### 2019-12-04 plots/reduced-in-units/venn.py
arregle el diagrama de venn

@@ -33,7 +33,7 @@ v = venn3(subsets=(1,1,1,1,1,1,1),set_labels = ('$\mathcal{A}$', '$\mathcal{K}$'
 v.get_label_by_id('100').set_text(' $\\frac{A \\tau}{m v_d}$')
 v.get_label_by_id('010').set_text('$\\frac{\\kappa B \\tau}{m}$')
 v.get_label_by_id('001').set_text('$\\frac{k B \\tau}{m v_d}$')
-v.get_label_by_id('111').set_text('$m/\\tau$')
+v.get_label_by_id('111').set_text('$\\tau/m$')
 v.get_label_by_id('101').set_text('$\\frac{\\tau}{m v_d}$')
 v.get_label_by_id('110').set_text('')
 v.get_label_by_id('011').set_text('$\\frac{B\\tau}{m}$')

### 2019-12-11 plots/corridor/triangles/plot_network_parameters.py
agregue el diagrama de venn con dos parametros

@@ -155,6 +155,7 @@ def plot_triangles(global_density,triangles,color,simbol,label):
      plt.legend(frameon=False,loc='best',labelspacing=-0.1,borderpad=0.3,handletextpad=0.5,fontsize=6,numpoints=1) 
 
      pylab.savefig('triangles.png', format='png', dpi=300, bbox_inches='tight')
+     pylab.savefig('triangles.eps', format='eps', dpi=300, bbox_inches='tight')
 
 
 def plot_shortest_path(global_density,shortest_path,color,simbol,label):
@@ -181,6 +182,7 @@ def plot_diameter(global_density,diameter,color,simbol,label):
      plt.legend(frameon=False,loc='best',labelspacing=-0.1,borderpad=0.3,handletextpad=0.5,fontsize=6,numpoints=1) 
 
      pylab.savefig('diameter.png', format='png', dpi=300, bbox_inches='tight')
+     pylab.savefig('diameter.eps', format='eps', dpi=300, bbox_inches='tight')
 
 
 

### 2019-12-11 plots/reduced-in-units/venn.py

@@ -1,5 +1,5 @@
 import pylab as plt
-from matplotlib_venn import venn3, venn3_circles
+from matplotlib_venn import venn3, venn3_circles,venn2
 import math
 import pylab
 
@@ -29,6 +29,8 @@ params = {'backend': 'ps',
 
 pylab.rcParams.update(params)
 
+'''
+##### 3 parametros reducidos #####
 v = venn3(subsets=(1,1,1,1,1,1,1),set_labels = ('$\mathcal{A}$', '$\mathcal{K}$', '$\mathcal{K}_c$'))
 v.get_label_by_id('100').set_text(' $\\frac{A \\tau}{m v_d}$')
 v.get_label_by_id('010').set_text('$\\frac{\\kappa B \\tau}{m}$')
@@ -37,7 +39,13 @@ v.get_label_by_id('111').set_text('$\\tau/m$')
 v.get_label_by_id('101').set_text('$\\frac{\\tau}{m v_d}$')
 v.get_label_by_id('110').set_text('')
 v.get_label_by_id('011').set_text('$\\frac{B\\tau}{m}$')
+'''
 
+##### 2 parametros reducidos #####
+v = venn2(subsets=(1,1,1),set_labels = ('$\mathcal{A}$', '$\mathcal{K}$'))
+v.get_label_by_id('10').set_text(' $\\frac{A \\tau}{m v_d}$')
+v.get_label_by_id('01').set_text('$\\frac{\\kappa B \\tau}{m}$')
+v.get_label_by_id('11').set_text('$\\tau/m$')
 
-pylab.savefig('venn_parameters.png', format='png', dpi=300, bbox_inches='tight')
-pylab.savefig('venn_parameters.eps', format='eps', dpi=300, bbox_inches='tight')
+pylab.savefig('venn_2parameters.png', format='png', dpi=300, bbox_inches='tight')
+pylab.savefig('venn_2parameters.eps', format='eps', dpi=300, bbox_inches='tight')

### 2019-12-15 plots/corridor/triangles/plot_network_parameters.py
commit para hacer pull

@@ -57,8 +57,6 @@ def main():
      #plot_diameter(global_density,diameter,color,simbol,label)
      plot_triangles(global_density,triangles,color,simbol,label)
 
-
-
      df = pd.read_csv('network_data_knE5_t30s.txt',delimiter = '\t') 
      global_density = df['0.density'].tolist()
      f_in_giant = df['2.fraction nodes in giant'].tolist()
@@ -93,8 +91,6 @@ def main():
      #plot_shortest_path(global_density,shortest_path,color,simbol,label)
      #plot_diameter(global_density,diameter,color,simbol,label)
      plot_triangles(global_density,triangles,color,simbol,label)
-
-
 
      df = pd.read_csv('network_data_kn0_t30s.txt',delimiter = '\t') 
      global_density = df['0.density'].tolist()
@@ -153,7 +149,7 @@ def plot_triangles(global_density,triangles,color,simbol,label):
      plt.xlim(4.5,9.1)
      lgd=plt.legend(numpoints=1,handlelength=0.8) 
      plt.legend(frameon=False,loc='best',labelspacing=-0.1,borderpad=0.3,handletextpad=0.5,fontsize=6,numpoints=1) 
-
+     pylab.savefig('triangles.eps', format='eps', dpi=300, bbox_inches='tight')
      pylab.savefig('triangles.png', format='png', dpi=300, bbox_inches='tight')
 
 
@@ -181,8 +177,6 @@ def plot_diameter(global_density,diameter,color,simbol,label):
      plt.legend(frameon=False,loc='best',labelspacing=-0.1,borderpad=0.3,handletextpad=0.5,fontsize=6,numpoints=1) 
 
      pylab.savefig('diameter.png', format='png', dpi=300, bbox_inches='tight')
-
-
 
 
 if __name__=='__main__':

### 2019-12-15 paper.tex
puse el diagrama de venn en formato png
agregue el diagrama de venn con dos parametros

@@
 
-\section{\label{background}Background}
+The Social Force Model (SFM) addresses two physical forces as 
+\textit{essential}: the ``body force'' and the ``sliding friction''. Both are 
+inspired by granular interactions and were claimed to be necessary  
+for attaining the particular effects in panicking crowds \cite{helbing_2000}. 
+The ``sliding friction'' actually proved to be an essential feature of the 
+``faster-is-slower'' effect, although the role of the ``body force'' appears, 
+at a first instance, not so clear \cite{dorso_2005,dorso_2007,dorso_2011}. \\
+
+The existence of a ``body force'' in the context of highly dense crowds (say, 5 
+to 10$\,$people/m$^2$) is a commonsense matter \cite{henein_2007,fruin_1993}. 
+Researchers, however, question the numerical setting for this force in 
+the SFM context \cite{lakoba_2005}. As a matter of fact, the usual setting by 
+Helbing prevents the overlapping among pedestrians, but it is known to 
+accomplish artificially high force levels 
+\cite{helbing_2000,lakoba_2005,langston_2006,lin_2017}. The force estimates 
+from the SFM appear to be remarkably higher with respect to the reported real 
+life data (say, an order of magnitude). The crowd motion simulations, however, 
+present quite realistic results \cite{lakoba_2005,langston_2006,dorso_2017}. 
+The 
+point seems to be that the SFM focuses on the ``incoordination phenomenon'' due 
+to clogging, missing the ``individualistic'' perspective  of single pedestrians 
+or very small groups \cite{helbing_2000,henein_2007,narain_2009}.  \\
+
+Many researchers realized that modifying the SFM may (partially) surpass the 
+misleading parameter setting. It was proposed that the pedestrians' 
+psychological force (say, the ``social force'') should be suppressed in the 
+context of highly dense crowds 
+\cite{pelechano_2007,moussaid_2011,alonso_2014,bottinelli_2017}, or smoothly 
+quenched according to the crowd density \cite{song_2019}. The authors in 
+Refs.~\cite{kabalan_2017,jebrane_2019} further proposed a rigid body model in 
+order to completely avoid the overlapping phenomenon. This perspective 
+dismisses 
+any connection to a ``sliding friction''. Conversely, other authors tried to 
+limit the pedestrians acceleration by introducing ``static friction'' between 
+the pedestrians and the floor \cite{wang_2019}. This kind of friction, however, 
+reduces the effective willings of the pedestrians.  \\
+
+A meaningful (individualistic) numerical setting appears not available yet (to 
+our knowledge). The reason is that different numerical settings can lead to 
+the same crowd dynamics. Actually, only a small set of dimensionless 
+``numbers'' control the crowd dynamics \cite{dorso_2019}. These are similar to 
+those encountered in other active matter systems (P\'eclet number, etc.)  
+\cite{marchetti_2014}. We may hypothesize that while the dimensionless 
+``numbers'' provide some kind of control on the ``incoordination phenomenon'' 
+in 
+crowds, only a few numerical settings can attain an ``individualistic'' 
+meaning. 
+ \\
+
+The numerical setting for the ``faster is slower'' effect presented by 
+Helbing and co-workers is somewhat cumbersome 
+Ref.~\cite{helbing_2000,dorso_2017,dorso_2019}. Although a single 
+parameter (say, the desired velocity $v_d$) is numerically varied to 
+explain the phenomenon, the researcher looses sight of the dimensionless 
+``numbers'' that truly control the crowd dynamics. The setting in 
+Ref.~\cite{helbing_2000} also misses the ``faster is faster'' effect reported 
+to occur at very high pedestrian densities \cite{dorso_2017,haghani_2019}. 
+Alternatively, the empirical fundamental diagram raises as a point of reference 
+for the SFM control parameters \cite{helbing_2007,dorso_2017}. \\
+
+The fundamental diagram exhibits the flux behavior for either low dense crowds 
+(with seldom contacts between pedestrians) and highly dense crowds (dominated 
+by 
+body forces and sliding friction). The latter usually experiences a flux 
+slowing 
+down, but other behaviors are also possible \cite{helbing_2007,lohner_2018}. In 
+light of our previous hypothesis, we may suspect that the  modeling of the 
+``flux slowing down'' within the context of the SFM will require the proper 
+setting of the (dimensionless) controlling parameters. We examined this working 
+hypothesis in Ref.~\cite{dorso_2019}, but limiting the parameter exploration to 
+the sliding friction, disregarding the body force. \\
+
+We now widen the investigation on the parameter settings to include the one 
+associated to the body force. We will focus on the complex interplay between 
+the body force and the sliding friction among pedestrians. Recall that the 
+interplay dynamics is not directly controlled by the numerical setting, but 
+through dimensionless ``numbers'', where the model parameters appear mixed 
+between each other. Thus, this step up offers a challenge to the 
+``individualistic'' meaning of the parameter's setting.
+
+The investigation is organized as follows. We first recall the available 
+experimental values on the body force and the sliding friction (see Section 
+\ref{experimental}). Secondly, we introduce the reduced-in-units SFM and the 
+three dimensionless numbers that control the crowd dynamics (see Section 
+\ref{background}). We present our numerical simulations in Section 
+\ref{results}. For the sake of clarity, this Section is 
+separated into two major parts: the bottleneck scenario and the corridor 
+scenario in Sections \ref{bottleneck} and \ref{corridor}, respectively. 
+Section \ref{discussion} opens a detailed discussion raising from of the results 
+in Section \ref{results}. The last Section closes the investigation with our 
+main conclusions.
+
+\section{\label{experimental}Experimental background}
+
+\section{\label{background}Theoretical background}
 
 \subsection{\label{sfm}The Social Force Model}
-
-\section{\label{simulations}Numerical simulations}
 
@@
 
+\begin{figure}[!htbp]
+\centering
+    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./venn_2parameters.png}\label{venn_2parameters}}\ 
+    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./venn_3parameters.png}\label{venn_3parameters}}\\
+\caption[width=0.47\columnwidth]{}
+\label{flow_density}
+\end{figure}
+
+\section{\label{discussion}Discussion}
+
 \section{\label{conclusions}Conclusions}
@@
 %/////////////////////////////////////////////////
-\begin{thebibliography}{10}
-\expandafter\ifx\csname url\endcsname\relax
-  \def\url#1{\texttt{#1}}\fi
-\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
-\expandafter\ifx\csname href\endcsname\relax
-  \def\href#1#2{#2} \def\path#1{#1}\fi
+%\begin{thebibliography}{10}
+%\expandafter\ifx\csname url\endcsname\relax
+%  \def\url#1{\texttt{#1}}\fi
+%\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
+%\expandafter\ifx\csname href\endcsname\relax
+%  \def\href#1#2{#2} \def\path#1{#1}\fi
 
@@
 
-\end{thebibliography}
+%\end{thebibliography}
+
+\bibliographystyle{unsrt}
+\bibliography{paper}% Produces the bibliography via BibTeX.
+
 \end{document}

### 2019-12-17 plots/bottleneck/overlap_distribution/plot_histo.py
cambie el nombre de la carpeta de graficos de distribucion de overlap

@@ -1,0 +1,113 @@
+# Sacado de https://scipy.github.io/old-wiki/pages/Cookbook/Matplotlib/LaTeX_Examples.html
+'''
+Grafica histogramas 
+'''
+
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+#import numarray
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+########################  MAIN  ########################
+def main():
+
+     ##### PARAMETERS ##### 
+     vd = 10
+     kn = "0"
+     clase = "bottleneck_vd{}_k{}".format(vd,kn)
+     distribucion = np.genfromtxt("distrib_comp_{}".format(clase),delimiter = ' ')    
+     title_plot= "Bottleneck - $k_n$={} - $v_d$={}".format(kn,vd)
+     out_name = "histo_grado_{}".format(clase)
+     binwidth = 0.005
+     min_comp = 0.0
+     max_comp = 0.20
+     min_grado = 0
+     max_grado = 7
+     print("media= ",np.mean(distribucion))
+     #plot_histo_norm_discreta(distribucion,title_plot,out_name,min_grado,max_grado)
+     plot_histo_normalized(distribucion,title_plot,out_name,binwidth,min_comp,max_comp)
+
+
+
+
[…]

### 2019-12-17 plots/bottleneck/degree_vs_vd/plot_degree_vs.py
agregue degree vs vd y overlap vs vd

@@ -1,0 +1,63 @@
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+import pandas as pd
+#import numarray
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+###  DATA  ###
+data_kn0 = pd.read_csv("degree_vs_vd_kn0.txt",sep="\t")
+vd_kn0 = data_kn0["vd"].tolist()
+mean_comp_kn0 = data_kn0["list_mean_degree"].tolist()
+std_comp_kn0 = data_kn0["list_std_degree"].tolist()
+
+data_kn = pd.read_csv("degree_vs_vd_kn120000.txt",sep="\t")
+vd_kn = data_kn["vd"].tolist()
+mean_comp_kn = data_kn["list_mean_degree"].tolist()
+std_comp_kn = data_kn["list_std_degree"].tolist()
+
+###  PLOT  ###
+fig, ax1 = plt.subplots()
+
+plt.plot(vd_kn0,mean_comp_kn0,'-cs',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k=0$') 
+plt.plot(vd_kn,mean_comp_kn,'-bx',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k=1.2$ E5') 
+
+
+pylab.grid(False)
+pylab.xlabel('$v_d$~(m~s$^{-1})$')
[…]

### 2019-12-17 plots/bottleneck/overlap_vs_vd/plot_comp_vs_vd.py

@@ -1,0 +1,101 @@
+'''
+Grafica compresion vs vd para muchos kn diferentes
+'''
+
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+import pandas as pd
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+### DATA ###
+
+data_kn0 = pd.read_csv("comp_vs_vd_k0.txt",sep="\t")
+vd_kn0 = data_kn0["vd"].tolist()
+mean_comp_kn0 = data_kn0["mean_comp"].tolist()
+std_comp_kn0 = data_kn0["std_comp"].tolist()
+
+data_knE4 = pd.read_csv("comp_vs_vd_kn1.2E4.txt",sep="\t")
+vd_knE4 = data_knE4["vd"].tolist()
+mean_comp_knE4 = data_knE4["mean_comp"].tolist()
+std_comp_knE4 = data_knE4["std_comp"].tolist()
+
+data_knx5 = pd.read_csv("comp_vs_vd_k60000.txt",sep="\t")
+vd_knx5 = data_knx5["vd"].tolist()
+mean_comp_knx5 = data_knx5["mean_comp"].tolist()
[…]

### 2019-12-17 paper.tex
Update paper.tex
agregue los captions a las primeras figuras

@@
 between each other. Thus, this step up offers a challenge to the 
-``individualistic'' meaning of the parameter's setting.
+``individualistic'' meaning of the parameter's setting. \\
 
@@
 {./vd_vs_te_N225.eps}
-\caption{\label{} }
+\caption{\label{vd_vs_te}Mean evacuation time (s) vs.
+the pedestrian’s desired velocity (m/s) for a bottleneck.
+The room was 20 m x 20 m size.
+The door was 0.92 m width.
+Mean values were computed from 10 evacuation processes.
+225 pedestrians were initially placed in a square lattice with a random initial velocity.
+Each process was finished when 158 pedestrians left the room.
+The different symbols indicate the $k$ value corresponding to the body force (see the label).
+}
+\end{figure}
+
+\begin{figure}[!htbp]
+\centering
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./degree_vs_vd_multi_kn.eps}\label{degree_te}}\ 
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./overlap_vs_vd_multi_kn.eps}\label{overlap_te}}\\
+\caption[width=0.47\columnwidth]{(a) Mean degree as a function of the pedestrian’s desired velocity (m/s).
+(b) Mean overlap as a function of the pedestrian’s desired velocity (m/s).
+Each symbol indicates the $k$ value corresponding to the body force (see the labels).
+The data corresponds to a bottleneck with periodic boundary conditions (reinjecting pedestrians).
+The average was taken every two seconds once the crowd reaches the stationary state ($t=$20~s) until the end of the simulation ($t=$110~s).}
+\label{degree_overlap_te}
 \end{figure}

### 2019-12-17 plots/bottleneck/degree_vs_vd/plot_degree_vs.py
update de archivos y epigrafes

@@ -40,17 +40,34 @@ vd_kn0 = data_kn0["vd"].tolist()
 mean_comp_kn0 = data_kn0["list_mean_degree"].tolist()
 std_comp_kn0 = data_kn0["list_std_degree"].tolist()
 
+data_knE4 = pd.read_csv("degree_vs_vd_kn12000.txt",sep="\t")
+vd_knE4 = data_knE4["vd"].tolist()
+mean_comp_knE4 = data_knE4["list_mean_degree"].tolist()
+std_comp_knE4 = data_knE4["list_std_degree"].tolist()
+
+data_kn6E4 = pd.read_csv("degree_vs_vd_kn60000.txt",sep="\t")
+vd_kn6E4 = data_kn6E4["vd"].tolist()
+mean_comp_kn6E4 = data_kn6E4["list_mean_degree"].tolist()
+std_comp_kn6E4 = data_kn6E4["list_std_degree"].tolist()
+
 data_kn = pd.read_csv("degree_vs_vd_kn120000.txt",sep="\t")
 vd_kn = data_kn["vd"].tolist()
 mean_comp_kn = data_kn["list_mean_degree"].tolist()
 std_comp_kn = data_kn["list_std_degree"].tolist()
 
+data_knE6 = pd.read_csv("degree_vs_vd_k1200000.txt",sep="\t")
+vd_knE6 = data_knE6["vd"].tolist()
+mean_comp_knE6 = data_knE6["list_mean_degree"].tolist()
+std_comp_knE6 = data_knE6["list_std_degree"].tolist()
+
 ###  PLOT  ###
 fig, ax1 = plt.subplots()
 
 plt.plot(vd_kn0,mean_comp_kn0,'-cs',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k=0$') 
-plt.plot(vd_kn,mean_comp_kn,'-bx',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k=1.2$ E5') 
-
+plt.plot(vd_knE4,mean_comp_knE4,'-y^',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$k=1.2$ E4') 
+plt.plot(vd_kn6E4,mean_comp_kn6E4,'-rv',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$k=6$ E4') 
[…]

### 2019-12-17 plots/bottleneck/overlap_vs_vd/plot_comp_vs_vd.py

@@ -39,30 +39,30 @@ pylab.rcParams.update(params)
 
 ### DATA ###
 
-data_kn0 = pd.read_csv("comp_vs_vd_k0.txt",sep="\t")
+data_kn0 = pd.read_csv("overlap_vs_vd_kn0.txt",sep="\t")
 vd_kn0 = data_kn0["vd"].tolist()
-mean_comp_kn0 = data_kn0["mean_comp"].tolist()
-std_comp_kn0 = data_kn0["std_comp"].tolist()
+mean_comp_kn0 = data_kn0["list_mean_overlap"].tolist()
+std_comp_kn0 = data_kn0["list_std_overlap"].tolist()
 
-data_knE4 = pd.read_csv("comp_vs_vd_kn1.2E4.txt",sep="\t")
+data_knE4 = pd.read_csv("overlap_vs_vd_kn1.2E4.txt",sep="\t")
 vd_knE4 = data_knE4["vd"].tolist()
-mean_comp_knE4 = data_knE4["mean_comp"].tolist()
-std_comp_knE4 = data_knE4["std_comp"].tolist()
+mean_comp_knE4 = data_knE4["list_mean_overlap"].tolist()
+std_comp_knE4 = data_knE4["list_std_overlap"].tolist()
 
-data_knx5 = pd.read_csv("comp_vs_vd_k60000.txt",sep="\t")
+data_knx5 = pd.read_csv("overlap_vs_vd_kn6E4.txt",sep="\t")
 vd_knx5 = data_knx5["vd"].tolist()
-mean_comp_knx5 = data_knx5["mean_comp"].tolist()
-std_comp_knx5 = data_knx5["std_comp"].tolist()
+mean_comp_knx5 = data_knx5["list_mean_overlap"].tolist()
+std_comp_knx5 = data_knx5["list_std_overlap"].tolist()
 
-data_knE5 = pd.read_csv("comp_vs_vd_kn1.2E5.txt",sep="\t")
+data_knE5 = pd.read_csv("overlap_vs_vd_kn1.2E5.txt",sep="\t")
 vd_knE5 = data_knE5["vd"].tolist()
-mean_comp_knE5 = data_knE5["mean_comp"].tolist()
-std_comp_knE5 = data_knE5["std_comp"].tolist()
+mean_comp_knE5 = data_knE5["list_mean_overlap"].tolist()
[…]

### 2019-12-17 plots/bottleneck/te/plot_fis.py

@@ -54,11 +54,11 @@ vd_kcomp_E5 = list(data_kcomp_E5.vd.unique())
 avg_te_kcomp_E5 = data_kcomp_E5.groupby(data_kcomp_E5['vd'])['te'].mean().values.tolist()
 std_te_kcomp_E5 = data_kcomp_E5.groupby(data_kcomp_E5['vd'])['te'].std().values.tolist()
 
-data_kx5 = pd.read_csv("tevsvd_N225_k600000.txt", header=None,delimiter=' ') 
-data_kx5.columns=['vd','iter','te','N_quedaron','nan']
-vd_kx5 = list(data_kx5.vd.unique())
-avg_te_kx5 = data_kx5.groupby(data_kx5['vd'])['te'].mean().values.tolist()
-std_te_kx5 = data_kx5.groupby(data_kx5['vd'])['te'].std().values.tolist()
+data_kE6 = pd.read_csv("tevsvd_N225_k1200000.txt", header=None,delimiter=' ') 
+data_kE6.columns=['vd','iter','te','N_quedaron','nan']
+vd_kE6 = list(data_kE6.vd.unique())
+avg_te_kE6 = data_kE6.groupby(data_kE6['vd'])['te'].mean().values.tolist()
+std_te_kE6 = data_kE6.groupby(data_kE6['vd'])['te'].std().values.tolist()
 
 data_6E4 = pd.read_csv("tevsvd_N225_k60000.txt", header=None,delimiter=' ') 
 data_6E4.columns=['vd','iter','te','N_quedaron','nan']
@@ -89,8 +89,8 @@ plt.errorbar(vd_6E4,avg_te_6E4,std_te_6E4,linestyle='none',fmt='none',color='non
 plt.plot(vd_kcomp_E5,avg_te_kcomp_E5,'-bx',mew=0.7,mec='k',markersize=4,label='$k_n =$ 1.2 E5') 
 plt.errorbar(vd_kcomp_E5,avg_te_kcomp_E5,std_te_kcomp_E5,linestyle='none',fmt='none',color='none',ecolor='b') 
 
-plt.plot(vd_kx5,avg_te_kx5,'-ko',mew=0.7,mec='k',markersize=4,label='$k_n =$ 6 E5') 
-plt.errorbar(vd_kx5,avg_te_kx5,std_te_kx5,linestyle='none',fmt='none',color='none',ecolor='k') 
[…]

### 2019-12-18 paper.tex
escribi texto que explica el primer grafico

@@
 
+In this section, we present the results corresponding to the bottleneck geometry.
+We show how the overall dynamic of the system changes depending on the $k$ value associated to the body force in the original SFM.\\
+
+Fig.
+\ref{vd_vs_te} shows the evacuation time as a function of the pedestrian's desired velocity.
+The evacuation time was defined as the time until 70\% of the pedestrians left the room.
+The different markers correspond to different $k$ values ($i.e$ different body force stiffness).
+The crosses correspond to the Helbing original SFM parameter, the up triangles correspond to the value measured in Ref ..
+and Increasing the $k$ reduced the evacuation time, squares correspond to an absent body force and circles correspond to an extreme value of stiffness (one order of magnitude higher than the original SFM).
+The down triangles correspond to an intermediate value between the empirical value presented in Ref...
+and the chosen by Helbing in Ref...\\
+
+There is a noticeable difference in the evacuation time depending on the $k$ value of the body force.
+The higher the $k$ the smaller the evacuation time, meaning that if pedestrians are stiffer the overall speed increases (hence the evacuation time).\\
+
+Notice that the faster-is-slower (FIS) effect and the faster-is-faster (FIF) effect are both dependent on the value of $k$.
+If $k$ is high enough, the FIF effect does not show for the explored desired velocity values ($v_d \leq 10$~m/s).\\
+
 \begin{figure}[htbp!]

### 2019-12-19 paper.tex
agregue mas texto en la parte de resultados (bottleneck)

@@
 
-Notice that the faster-is-slower (FIS) effect and the faster-is-faster (FIF) effect are both dependent on the value of $k$.
-If $k$ is high enough, the FIF effect does not show for the explored desired velocity values ($v_d \leq 10$~m/s).\\
+The Faster-is-Faster (FIF) is the phenomenon in which under certain conditions, increasing the desired velocity yields to a reduction of the evacuation time.
+While the Faster-is-Faster is the opposite (the higher $v_d$ the lower the evacuation time).
+Notice that the presence of the faster-is-faster (FIF) effect and the faster-is-slower are dependent on the value of $k$.
+In Fig.~\ref{vd_vs_te} we can see that $k=1.2$~E5 only exhibits FIS effect for $v_d>$2~m/s.
+$k=1.2$~E6 only shows FIF effect and the explored values of $k$ that satisfy $k \leq 6$~E4 exhibit both the FIS and the FIF effect.
+\\
 
@@
 \end{figure}
+
+Network analysis is a set of techniques that characterize the structures in a given graph.
+We defined the graph of contacts among individuals.
+In this graph, each node represents a pedestrian and the link between a pair of nodes is settled if this pair of pedestrians are in physical contact ($i.e.$ $r_{ij}<d_{ij}$).\\
+
+Fig.~\ref{degree_te}
 

### 2019-12-19 paper.tex
agregue un poco mas de texto para explicar la figura 2 de bottleneck

@@
 The Faster-is-Faster (FIF) is the phenomenon in which under certain conditions, increasing the desired velocity yields to a reduction of the evacuation time.
-While the Faster-is-Faster is the opposite (the higher $v_d$ the lower the evacuation time).
+The Faster-is-Faster is the opposite effect (the higher $v_d$ the lower the evacuation time).
 Notice that the presence of the faster-is-faster (FIF) effect and the faster-is-slower are dependent on the value of $k$.
@@
 
-Network analysis is a set of techniques that characterize the structures in a given graph.
+Network analysis is a set of techniques that characterize the structures in a graph.
 We defined the graph of contacts among individuals.
@@
 
-Fig.~\ref{degree_te}
+Fig.~\ref{degree_vd} shows the mean degree of the contact graph as a function of the desired velocity.
+The degree of a node is defined as the amount of edges assigned to the node.
+This means, the number of pedestrians that are in contact with a given pedestrian.
+The mean degree is the average of the degree over all the nodes (pedestrians) and over the whole time from the stationary state until the end of the simulation.\\
+
+Increasing $v_d$ increases the mean degree in all cases.
+This happens because increasing $v_d$ produces higher densities that force individuals to touch each other.
+For a given $v_d$ the mean degree reduces as the $k$ value increases.
+In other words, the stiffer the pedestrians the less they touch each other.
+We will later discuss that this phenomenon is a characteristic of the bottleneck geometry that cannot be extrapolated to the corridor geometry.\\
+
+Fig.~\ref{overlap_vd} shows the overlap as a function of $v_d$.
+The overlap is defined as $d_{ij}-r_{ij}$ where $d_{ij}$ is the sum of radius of particle $i$ and particle $j$ and $r_{ij}$  is the distance between both particles.
+In the range $v_d \geq 2$~m/s we can see that increasing $v_d$ increases the overlap (for all the $k$ values studied).
+For a given $v_d$, the overlap increases as the $k$ value decreases.
+Reducing $k$ means reducing the normal body force which allows a greater invasion of the personal space of the particles.\\
 
@@
 \centering
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./degree_vs_vd_multi_kn.eps}\label{degree_te}}\ 
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./overlap_vs_vd_multi_kn.eps}\label{overlap_te}}\\
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./degree_vs_vd_multi_kn.eps}\label{degree_vd}}\ 
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./overlap_vs_vd_multi_kn.eps}\label{overlap_vd}}\\
 \caption[width=0.47\columnwidth]{(a) Mean degree as a function of the pedestrian’s desired velocity (m/s).
@@
 Each symbol indicates the $k$ value corresponding to the body force (see the labels).
-The data corresponds to a bottleneck with periodic boundary conditions (reinjecting pedestrians).
+The data corresponds to a bottleneck with periodic boundary conditions (re-injecting pedestrians).
 The average was taken every two seconds once the crowd reaches the stationary state ($t=$20~s) until the end of the simulation ($t=$110~s).}
-\label{degree_overlap_te}
+\label{degree_overlap_vd}
 \end{figure}

### 2019-12-20 paper.tex
modificacion delos diagramas de venn

@@
 \centering
-    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./venn_2parameters.png}\label{venn_2parameters}}\ 
-    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./venn_3parameters.png}\label{venn_3parameters}}\\
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./venn_2parameters.png}\label{venn_2parameters}}\ 
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./venn_3parameters.png}\label{venn_3parameters}}\\
 \caption[width=0.47\columnwidth]{}

### 2019-12-20 plots/reduced-in-units/venn.py

@@ -31,21 +31,21 @@ pylab.rcParams.update(params)
 
 '''
 ##### 3 parametros reducidos #####
-v = venn3(subsets=(1,1,1,1,1,1,1),set_labels = ('$\mathcal{A}$', '$\mathcal{K}$', '$\mathcal{K}_c$'))
-v.get_label_by_id('100').set_text(' $\\frac{A \\tau}{m v_d}$')
-v.get_label_by_id('010').set_text('$\\frac{\\kappa B \\tau}{m}$')
-v.get_label_by_id('001').set_text('$\\frac{k B \\tau}{m v_d}$')
-v.get_label_by_id('111').set_text('$\\tau/m$')
-v.get_label_by_id('101').set_text('$\\frac{\\tau}{m v_d}$')
+v = venn3(subsets=(1,1,1,1,1,1,1),set_labels = ('$\mathcal{A} =\\frac{A \\tau}{v_d m}$', '$\mathcal{K} = \\frac{\\kappa B \\tau}{m}$', '$\mathcal{K}_c = \\frac{k B \\tau}{v_d m}$'))
+v.get_label_by_id('100').set_text('$A$')
+v.get_label_by_id('010').set_text('$\\kappa$')
+v.get_label_by_id('001').set_text('$k$')
+v.get_label_by_id('111').set_text('$\\frac{\\tau}{m}$')
+v.get_label_by_id('101').set_text('$\\frac{1}{v_d}$')
 v.get_label_by_id('110').set_text('')
-v.get_label_by_id('011').set_text('$\\frac{B\\tau}{m}$')
+v.get_label_by_id('011').set_text('$B$')
 '''
 
 ##### 2 parametros reducidos #####
-v = venn2(subsets=(1,1,1),set_labels = ('$\mathcal{A}$', '$\mathcal{K}$'))
-v.get_label_by_id('10').set_text(' $\\frac{A \\tau}{m v_d}$')
-v.get_label_by_id('01').set_text('$\\frac{\\kappa B \\tau}{m}$')
-v.get_label_by_id('11').set_text('$\\tau/m$')
+v = venn2(subsets=(1,1,1),set_labels = ('$\mathcal{A} = \\frac{A \\tau}{v_d m}$', '$\mathcal{K} = \\frac{\\kappa B \\tau}{m}$'))
+v.get_label_by_id('10').set_text(' $\\frac{A}{v_d}$')
+v.get_label_by_id('01').set_text('$\\kappa B$')
[…]

### 2019-12-20 paper.tex
creacion de graficos de configuraciones con network (escala de colores para el grado)

@@
 \centering
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_d6_kn0.eps}\label{network_d6_kn0}}\ 
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_d6_knE5.eps}\label{network_d6_knE5}}\\
+\caption[width=0.47\columnwidth]{}
+\label{network_corridor}
+\end{figure}
+
+\begin{figure}[!htbp]
+\centering
     \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_density7_width22_kn0.eps}\label{flow_density_nocomp}}\ 
     \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_density7_width22_knE5.eps}\label{flow_density_comp}}\\
-        \subfloat[]{\includegraphics[width=0.40\columnwidth]{./tesselation_d7_t30_kn0.eps}\label{tesselation_d7_t30_kn0}}\
-    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./tesselation_d7_t30_knE5.eps}\label{tesselation_d7_t30_knE5}}\\
             \subfloat[]{\includegraphics[width=0.40\columnwidth]{./g(r)_d7_kn0.eps}\label{g(r)_d7_kn0}}\

### 2019-12-20 plots/bottleneck/network_config/plot_config_graph.py

@@ -1,0 +1,176 @@
+'''
+Genera un grafico con nodos y links a partir de una configuracion
+Las posiciones de los nodos corresponden a las posiciones de los
+individuos en el recinto. 
+'''
+import numpy as np
+import networkx as nx
+import matplotlib.pyplot as plt
+import matplotlib.colors as mcolors
+import pylab
+import math
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8                           # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+
+
+def extract_config(data,t):
+     '''
+     t is the selected time
+     this function extracts the configuration for the time t
+     only one timestep is extracted
+     '''
+     ESCALA_TIME = 10000
+
+     str_selected_timestep='{}\n'.format(int(t*ESCALA_TIME))
+     f=open(data, 'r')
+     lines=f.readlines()
+     index = []
+     x=[]
+     y=[]
+     i=0
+     flag=True
+     while i<len(lines) and flag:
+          line = lines[i].rstrip('\n')
+          if(line=='ITEM: TIMESTEP'):
+               iter_time=lines[i+1]
+               if(iter_time==str_selected_timestep):
+                    number_pedestrians=int(lines[i+3])
+                    first_line_table=i+9
+                    for j in range(first_line_table, first_line_table+number_pedestrians):
+                         row=lines[j].split(' ')
+                         index+=[int(row[0])]
[…]

### 2019-12-20 plots/corridor/network_config/plot_config_graph.py

@@ -1,0 +1,175 @@
+'''
+Genera un grafico con nodos y links a partir de una configuracion
+Las posiciones de los nodos corresponden a las posiciones de los
+individuos en el recinto. 
+'''
+import numpy as np
+import networkx as nx
+import matplotlib.pyplot as plt
+import matplotlib.colors as mcolors
+import pylab
+import math
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8                           # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+
+
+def extract_config(data,t):
+     '''
+     t is the selected time
+     this function extracts the configuration for the time t
+     only one timestep is extracted
+     '''
+     ESCALA_TIME = 10000
+
+     str_selected_timestep='{}\n'.format(int(t*ESCALA_TIME))
+     f=open(data, 'r')
+     lines=f.readlines()
+     index = []
+     x=[]
+     y=[]
+     i=0
+     flag=True
+     while i<len(lines) and flag:
+          line = lines[i].rstrip('\n')
+          if(line=='ITEM: TIMESTEP'):
+               iter_time=lines[i+1]
+               if(iter_time==str_selected_timestep):
+                    number_pedestrians=int(lines[i+3])
+                    first_line_table=i+9
+                    for j in range(first_line_table, first_line_table+number_pedestrians):
+                         row=lines[j].split(' ')
+                         index+=[int(row[0])]
[…]

### 2019-12-20 paper.tex
Update paper.tex

@@
 \section{\label{experimental}Experimental background}
+
+The complex behavior of pedestrians feature either his (her) feelings and 
+the environmental conditions. The former is expressed, for example, by his 
+(her) moving ``attitude'' (say, self-assuredness). The latter brings out the 
+observed separation between pedestrians. Also, the ``contacts'' between 
+individuals address some kind of ``unwanted'' slowing down. All these 
+observed patterns are commonly quantified in the literature into a a set of 
+characteristic  parameters. The experimental meaning of these parameters is as 
+follows.
+
+\begin{itemize}
+\item[(i)] The walking attitude of a pedestrian may appear somewhat 
+``assertive'' if he (she) reacts actively to unexpected behaviors 
+\cite{lakoba_2005,helbing_1995}. The smaller the reaction time, the more 
+assertive or aggresive observed posture. The associated parameter to this 
+behavior is the relaxation or characteristic time $\tau$ 
+\cite{johansson_2009,helbing_2000}.
+
+\item[(ii)] Despite the reactive attitude $\tau$, the pedestrian addresses a 
+``free'' (undisturbed) walking speed $\v_0$. This speed expresses his (her) 
+motivation or intention to reach a certain destination (as comfortable as 
+possible). Observations commonly associate $0.6\,$m/s, $1\,$m/s or $1.5\,$m/s 
+to relaxed, normal or nervous walking speeds, respectively  
+\cite{helbing_1995,helbing_2000,li_2015}.
+
+\item[(iii)] The walking speed of pedestrians appears to be lower in a 
+crowded walkway with respect to their usually expected ``free'' walking speeds 
+\cite{weidmann_1992,lakoba_2005}. Pedestrians tend to reduce their speed within 
+crowded environments because they perceive not enough space for taking a 
+step  \cite{johansson_2009}. This (perceived) step distance is therefore an 
+influential parameter on the pedestrians behavior. It is known as the 
+characteristic length $B$.
+
+\item[(iv)] Physical interactions occur in very crowded environments. The 
+``body force''  and ``sliding friction'' can be introduced straight forward. 
+This will be done in Section \ref{background}. But it is worth noting that 
+both are associated to the moving difficulties (say, slowing down and 
+obstructions) observed in contacting pedestrians.
+
+\end{itemize}
+
+Table~\ref{table_data} shows a few empirical figures for the most common 
+parameters. More data is available throughout the literature (see, for example, 
+Refs.~\cite{hoogendoorn_2007,seyfried_2007,johansson_2007,moussaid_2009,
+luber_2010,seer_2014,li_2015} ). We intentionally omitted data that assumes a 
+specific mathematical model. The exhibited values should also be considered as a 
+general purpose approach, since no distinction has been made on age, gender or 
+cultural habits. \\
+
+\begin{table}
+\begin{tabular}{cccccc}
+ \hline
+ $\tau$[s]   & $m$[kg]     & $v_d$[m/s]  &  $B$[m]  & $k$[kg/s$^2$] &  Refs. \\
+ \hline
+0.61         & ---         & 1.24 & $0.36+1.06\,v$ &  ---                 &  
+ \cite{seyfried_2007} \\
+0.50$^*$     & 80$^*$      & 1.34 & 0.50           &  ---                 &  
+\cite{weidmann_1992,lakoba_2005}\\
+---          & $67.5$      & 1.39 &  ---           &  $96.1 + 12694.1\,x$ & 
+\cite{song_2019}\\
+---          & $67.0$      & 1.39 &  ---           &  $97.0 + 29378.9\,x$ & 
+\cite{song_2019}\\
+
+\hline
+\end{tabular}
+\caption{The experimental data for the pedestrian parameters, as explained in 
+Section~\ref{experimental}. The magnitude $v$ means de pedestrian velocity 
+(m/s). The magnitude $x$ means the compression length (m). The upper row for 
+Ref.~\cite{song_2019} corresponds data acquired in winter and the lower row to 
+datas acquiquired in summer. The asterisk ($^*$) corresponds to reasonable 
+estimates. }
+\label{table_data}
+\end{table}
+
+A first examination of the figures in Table~\ref{table_data} shows that the 
+choise $\tau\simeq0.6\,$s seems to be a reasonable estimation for the 
+relaxation time, although this may vary with respect to gender or culture 
+\cite{siddharth_2018}. Additionally, we confirm that normal pedestrians attain 
+desired velocties around $1.3\,$m/s. \\
+
+No body contacts were reported in Refs.~\cite{seyfried_2007,weidmann_1992} 
+since these experiments correspond to the low density regime. At this instance, 
+the pedestrian does not feel to be too close to the others....    \\
 

### 2019-12-20 paper.tex
modificaciones de redaccion en results bottleneck

--- 2019-12-20 paper.tex
@@
 The evacuation time was defined as the time until 70\% of the pedestrians left the room.
-The different markers correspond to different $k$ values ($i.e$ different body force stiffness).
-The crosses correspond to the Helbing original SFM parameter, the up triangles correspond to the value measured in Ref ..
-and Increasing the $k$ reduced the evacuation time, squares correspond to an absent body force and circles correspond to an extreme value of stiffness (one order of magnitude higher than the original SFM).
+The different markers correspond to different $k$ values ($i.e$ different body ``stiffness'').
+The crosses correspond to the Helbing original SFM parameter, the up-triangles correspond to the value measured in Ref ..., squares correspond to an absent body force and circles correspond to an extreme value of stiffness (one order of magnitude higher than the original SFM).
 The down triangles correspond to an intermediate value between the empirical value presented in Ref...
@@
 There is a noticeable difference in the evacuation time depending on the $k$ value of the body force.
-The higher the $k$ the smaller the evacuation time, meaning that if pedestrians are stiffer the overall speed increases (hence the evacuation time).\\
+The higher the $k$ the smaller the evacuation time, meaning that if pedestrians are stiffer, the overall speed increases (hence the evacuation time decreases).\\
 
@@
 The Faster-is-Faster is the opposite effect (the higher $v_d$ the lower the evacuation time).
-Notice that the presence of the faster-is-faster (FIF) effect and the faster-is-slower are dependent on the value of $k$.
+Notice that the presence of the Faster-is-Faster (FIF) effect and the Faster-is-Slower are dependent on the value of $k$.
 In Fig.~\ref{vd_vs_te} we can see that $k=1.2$~E5 only exhibits FIS effect for $v_d>$2~m/s.
-$k=1.2$~E6 only shows FIF effect and the explored values of $k$ that satisfy $k \leq 6$~E4 exhibit both the FIS and the FIF effect.
-\\
+When $k=1.2$~E6, the evacuation time reduces as $v_d$ increases, meaning that only FIF is reported.
+The explored values of $k$ that satisfy $k \leq 6$~E4 exhibit both the FIS and the FIF effect depending on the range of desired velocities.
+Notice that the behavior of the case in which $k = 0$ is very similar to the case in which $k = 1.2$~E4.\\
+% se puede discutir que este resultado es importante porque k=1.2E4 es un valor empirico y k=1.2E5 tambien lo es, osea que el FIF podria estar o no estar dependiendo de cual es el verdadero valor de k.
+Habria que chequear en unidades reducidas como queda.
 
@@
 The degree of a node is defined as the amount of edges assigned to the node.
-This means, the number of pedestrians that are in contact with a given pedestrian.
-The mean degree is the average of the degree over all the nodes (pedestrians) and over the whole time from the stationary state until the end of the simulation.\\
+This means, the number of pedestrians that are in physical contact with a given pedestrian.
+The mean degree is the average of the degree over all the nodes (pedestrians) and over the whole sampled time (from the time the system reaches the stationary state to the end of the simulation).\\
 

### 2019-12-20 paper.tex
mas correcciones de gramatica
correcciones de gramatica

@@
 \item[(ii)] Despite the reactive attitude $\tau$, the pedestrian addresses a 
-``free'' (undisturbed) walking speed $\v_0$. This speed expresses his (her) 
+``free'' (undisturbed) walking speed $v_0$. This speed expresses his (her) 
 motivation or intention to reach a certain destination (as comfortable as 
@@
 We defined the graph of contacts among individuals.
-In this graph, each node represents a pedestrian and the link between a pair of nodes is settled if this pair of pedestrians are in physical contact ($i.e.$ $r_{ij}<d_{ij}$).\\
+In this graph, each node represents a pedestrian and the link between a pair of nodes is settled if the pedestrians are in physical contact ($i.e.$ $r_{ij}<d_{ij}$).\\
 
@@
 
-Increasing $v_d$ increases the mean degree in all cases.
+Increasing $v_d$ increases the mean degree in all the cases.
 This happens because increasing $v_d$ produces higher densities that force individuals to touch each other.
@@
 In other words, the stiffer the pedestrians the less they touch each other.
-We will later discuss that this phenomenon is a characteristic of the bottleneck geometry that cannot be extrapolated to the corridor geometry.\\
+We will later discuss that this phenomenon is restricted to the bottleneck geometry that cannot be extrapolated to the corridor geometry.\\
 
@@
 For a given $v_d$, the overlap increases as the $k$ value decreases.
-Reducing $k$ means reducing the normal body force which allows a greater invasion of the personal space of the particles.\\
+Reducing $k$ means reducing the normal body force which allows a greater invasion of the personal space of the individuals.\\
 

### 2019-12-23 paper.tex
quite graficos que no van a estar en el paper

@@
 
-\begin{figure}[!htbp]
-\centering
-    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_bottleneck_vd2_k0.eps}\label{size_distribution_w22_density4.5}}\ 
-    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_bottleneck_vd2_k120000.eps}\label{size_distribution_w22_density4.5_kx10}}\\
-    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_bottleneck_vd4_k0.eps}\label{size_distribution_w22_density5}}\
-    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_bottleneck_vd4_k120000.eps}\label{size_distribution_w22_density5_kx10}}\\
-    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_bottleneck_vd10_k0.eps}\label{size_distribution_w22_density5_5}}\
-    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_bottleneck_vd10_k120000.eps}\label{size_distribution_w22_density5_5_kx10}}
-\caption[width=0.47\columnwidth]{}
-\label{compresion_distribution}
-\end{figure}
-
 \subsection{\label{corridor} Corridor}
@@
 \centering
-    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./flow-density_multifric_nocomp.eps}\label{flow_density_nocomp}}\ 
-    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./flow-density_multifric_comp.eps}\label{flow_density_comp}}\\
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_nocomp.eps}\label{flow_density_nocomp}}\ 
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_comp.eps}\label{flow_density_comp}}\\
 \caption[width=0.47\columnwidth]{}
@@
 \label{network_corridor}
-\end{figure}
-
-\begin{figure}[!htbp]
-\centering
-    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_density7_width22_kn0.eps}\label{flow_density_nocomp}}\ 
-    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./histo_grado_density7_width22_knE5.eps}\label{flow_density_comp}}\\
-            \subfloat[]{\includegraphics[width=0.40\columnwidth]{./g(r)_d7_kn0.eps}\label{g(r)_d7_kn0}}\
-    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./g(r)_d7_knE5.eps}\label{g(r)_d7_knE5}}\\
-\caption[width=0.47\columnwidth]{}
-\label{flow_density}
 \end{figure}

### 2019-12-23 paper.tex
corregi y agregue el grafico de grado y configuracion

@@
 
+\begin{figure}[!htbp]
+\centering
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn0.eps}\label{flow_density_nocomp}}\ 
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn0.eps}\label{flow_density_comp}}\\
+        \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn120000.eps}\label{flow_density_nocomp}}\ 
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn120000.eps}\label{flow_density_comp}}\\
+\caption[width=0.47\columnwidth]{}
+\label{flow_density}
+\end{figure}
+
 \subsection{\label{corridor} Corridor}

### 2019-12-23 plots/bottleneck/network_config/plot_config_graph.py

@@ -132,7 +132,8 @@ def plot_network(G,output_filename):
      fig, ax = plt.subplots()
      pos=nx.get_node_attributes(G,'pos')
      sc = nx.draw(G,pos,width=0.5,node_color=n_color,cmap='viridis',node_size=5,with_labels=False,edge_color='black')
-     plt.axis([13,20,4,16])
+     #plt.axis([13,20,4,16])
+     plt.axis([10,20,4,16])
      plt.axis('on')
      plt.grid('false')
      #plt.text(15.5, 5.5, "16", fontsize=10)
@@ -155,8 +156,8 @@ def plot_network(G,output_filename):
 def main():
 
      ############# PARAMETERS #############
-     input_filename = 'config_bottleneck_vd10_k120000'
-     output_filename = 'network_vd10_kn120000'
+     input_filename = 'config_bottleneck_vd2_k0'
+     output_filename = 'network_vd2_kn0'
      time = 100
      sum_rads = 0.46
      ######################################

### 2019-12-23 paper.tex
Update paper.tex

@@
 \begin{table}
-\begin{tabular}{cccccc}
+\begin{tabular}{c@{\hspace{6mm}}c@{\hspace{6mm}}c@{\hspace{6mm}}c@{\hspace{6mm}}
+c@{\hspace{14mm}}l}
  \hline
@@
 \cite{siddharth_2018}. Additionally, we confirm that normal pedestrians attain 
-desired velocties around $1.3\,$m/s. \\
+desired velocities around $1.3\,$m/s. \\
+
+The reports from Refs.~\cite{seyfried_2007,weidmann_1992} do not include any 
+values for the compressibility $k$ since these experiments were carried out 
+under low density conditions. Notice that the minimum (perceived) step distance 
+is $0.36\,$m \cite{seyfried_2007}, but the pedestrians seem to require larger 
+distances when they walk faster. The commonly accepted value $B\simeq 
+0.5\,$m is somewhat valid for walking speeds under $0.5\,$m/s 
+\cite{seyfried_2007}. Higher walking speeds (say, $1\,$m/s) will require 
+a step distance of $1.3\,$m for the pedestrians to feel that there is enough 
+space to move along.     \\
 

### 2019-12-26 paper.tex
agregue el diagrama fundamental actualizado

@@
 \centering
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_nocomp.eps}\label{flow_density_nocomp}}\ 
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_comp.eps}\label{flow_density_comp}}\\
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_nobodyforce.eps}\label{flow_density_nocomp}}\ 
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_bodyforce.eps}\label{flow_density_comp}}\\
 \caption[width=0.47\columnwidth]{}

### 2019-12-26 plots/corridor/fundamental_diagram/kn0/flow_density_multi.py

@@ -1,0 +1,121 @@
+'''
+Grafica multiples densidades vs flujo
+'''
+
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+import pandas as pd
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+### DATA ###
+
+data_kn0_kt = pd.read_csv("fd_kt_kn0.txt",sep="\t")
+global_density_kn0_kt = data_kn0_kt["mean_global_dens"].tolist()
+density_kn0_kt = data_kn0_kt["mean_local_dens"].tolist()
+flow_kn0_kt = data_kn0_kt["mean_local_flowx"].tolist()
+std_flow_kn0_kt = data_kn0_kt["std_local_flowx"].tolist()
+speed_kn0_kt = np.divide(flow_kn0_kt,density_kn0_kt)
+
+'''
+data_kn0_ktx3 = pd.read_csv("flow_density_kn0_ktx3.txt",sep=" ")
+density_kn0_ktx3 = data_kn0_ktx3["density"].tolist()
[…]

### 2019-12-26 plots/corridor/fundamental_diagram/knE5/flow_density_multi.py

@@ -39,11 +39,14 @@ pylab.rcParams.update(params)
 
 ### DATA ###
 
-data_kn_kt = pd.read_csv("flow_density_kn_kt.txt",sep=" ")
-density_kn_kt = data_kn_kt["density"].tolist()
-flow_kn_kt = data_kn_kt["flow"].tolist()
-speed_kn_kt=np.divide(flow_kn_kt,density_kn_kt)
+data_kn_kt = pd.read_csv("fd_kt_kn.txt",sep="\t")
+global_density_kn_kt = data_kn_kt["mean_global_dens"].tolist()
+density_kn_kt = data_kn_kt["mean_local_dens"].tolist()
+flow_kn_kt = data_kn_kt["mean_local_flowx"].tolist()
+std_flow_kn_kt = data_kn_kt["std_local_flowx"].tolist()
+speed_kn_kt = np.divide(flow_kn_kt,density_kn_kt)
 
+'''
 data_kn_ktx3 = pd.read_csv("flow_density_kn_ktx3.txt",sep=" ")
 density_kn_ktx3 = data_kn_ktx3["density"].tolist()
 flow_kn_ktx3 = data_kn_ktx3["flow"].tolist()
@@ -63,32 +66,48 @@ data_kn_ktx9 = pd.read_csv("flow_density_kn_ktx9.txt",sep=" ")
 density_kn_ktx9 = data_kn_ktx9["density"].tolist()
 flow_kn_ktx9 = data_kn_ktx9["flow"].tolist()
 speed_kn_ktx9=np.divide(flow_kn_ktx9,density_kn_ktx9)
+'''
+data_ktx5_kn = pd.read_csv("fd_ktx5_kn.txt",sep="\t")
+global_density_ktx5_kn = data_ktx5_kn["mean_global_dens"].tolist()
+density_ktx5_kn = data_ktx5_kn["mean_local_dens"].tolist()
+flow_ktx5_kn = data_ktx5_kn["mean_local_flowx"].tolist()
+std_flow_ktx5_kn = data_ktx5_kn["std_local_flowx"].tolist()
+speed_ktx5_kn = np.divide(flow_ktx5_kn,density_ktx5_kn)
 
-data_kn_ktx10 = pd.read_csv("flow_density_kn_ktx10.txt",sep=" ")
-density_kn_ktx10 = data_kn_ktx10["density"].tolist()
-flow_kn_ktx10 = data_kn_ktx10["flow"].tolist()
[…]

### 2019-12-26 paper.tex
Update paper.tex

@@
 individuals address some kind of ``unwanted'' slowing down. All these 
-observed patterns are commonly quantified in the literature into a a set of 
+observed patterns are commonly quantified in the literature into a set of 
 characteristic  parameters. The experimental meaning of these parameters is as 
@@
 datas acquiquired in summer. The asterisk ($^*$) corresponds to reasonable 
-estimates. }
+estimates from the authors. }
 \label{table_data}

### 2019-12-26 paper.tex
Update paper.tex

@@
 
-No body contacts were reported in Refs.~\cite{seyfried_2007,weidmann_1992} 
-since these experiments correspond to the low density regime. At this instance, 
-the pedestrian does not feel to be too close to the others....    \\
+The reported data from Ref.~\cite{song_2019} correspond to the crowded 
+environment of the Beijing subway. This environment was not suitable for 
+providing information on the step distance $B$, but estimates for the 
+desired speed and the body compresibility could be achieved. The reported 
+magnitude $k$ assesses either the clothes and the body compressibility. The 
+final value, though, is linearly related to the compression $x$. \\
+
+We measured the maximum forces attainable at the subway in Buenos Aires, 
+Argentina. Our preliminary results show that pedestrians feel uncomfortable 
+whenever a body force ranging from $5$ to $20\,$N is applied for at least ten 
+minutes. Short lasting forces (say, less than 4 minutes) may also be perceived 
+as uncomfortable for values ranging from $10$ to $30\,$N. We also recorded body 
+forces up to $60\,$N during very short ``hits''. The comparison with the 
+fittings provided by Ref.~\cite{song_2019} shows that these magnitudes 
+accomplish densities around 5 people/m$^2$.     \\
+
+The maximum (realistic) compressions may be computed from the relation 
+$F=k(x)\,x$ and the compressibility $k(x)$ reported in Table~\ref{table_data}. 
+An ``uncomfortable'' body force of $30\,$N can address compressions in the 
+range of $0.030-0.055\,$m. Also, a ``hitting'' force of $60\,$N can address 
+compressions between $0.045$ and $0.065\,$m. Thus, according to 
+Table~\ref{table_data}, we may expect experimental values for $k(x)$ up to 
+$1000\,$kg/s$^2$ (for $30\,$N), or, up to $1400\,$kg/s$^2$ (for $60\,$N). \\
+
+Besides, no realiable values for the sliding friction $\kappa$ appears to be 
+available in the literature (to our knowledge). We may pressume, however, that 
+the sliding friction approaches a fraction of the body force. We will come back 
+to this issue in Section~\ref{background}. \\
 

### 2019-12-26 paper.tex
Update paper.tex

@@
 Table~\ref{table_data}, we may expect experimental values for $k(x)$ up to 
-$1000\,$kg/s$^2$ (for $30\,$N), or, up to $1400\,$kg/s$^2$ (for $60\,$N). \\
+$1000\,$kg/s$^2$ (for $F=30\,$N), or, up to $1400\,$kg/s$^2$ (for $F=60\,$N). \\
 

### 2019-12-26 paper.tex
Update paper.tex

@@
 
-We measured the maximum forces attainable at the subway in Buenos Aires, 
-Argentina. Our preliminary results show that pedestrians feel uncomfortable 
+We measured the maximum attainable forces at the subway in Buenos Aires, 
+Argentina. Our preliminary results show that pedestrians feel ``uncomfortable'' 
 whenever a body force ranging from $5$ to $20\,$N is applied for at least ten 
 minutes. Short lasting forces (say, less than 4 minutes) may also be perceived 
-as uncomfortable for values ranging from $10$ to $30\,$N. We also recorded body 
+as ``uncomfortable'' for values ranging from $10$ to $30\,$N. We also recorded body 
 forces up to $60\,$N during very short ``hits''. The comparison with the 

### 2019-12-27 plots/bottleneck/network_config/plot_config_graph.py
cambie la relacion de aspecto de los graficos de network en bottleneck

@@ -15,7 +15,7 @@ import math
 
 golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
 fig_width = 3+3/8                           # width  in inches
-fig_height = fig_width*golden_mean          # height in inches
+fig_height = fig_width#fig_width*golden_mean          # height in inches
 fig_size =  [fig_width,fig_height]
 
 params = {'backend': 'ps',
@@ -156,8 +156,8 @@ def plot_network(G,output_filename):
 def main():
 
      ############# PARAMETERS #############
-     input_filename = 'config_bottleneck_vd2_k0'
-     output_filename = 'network_vd2_kn0'
+     input_filename = 'config_bottleneck_vd10_k120000'
+     output_filename = 'network_vd10_kn120000'
      time = 100
      sum_rads = 0.46
      ######################################

### 2019-12-27 plots/corridor/degree_vs_density/plot_degree_vs.py
agregue las figuras de overlap vs densidad y degree vs densidad

@@ -1,0 +1,74 @@
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+import pandas as pd
+#import numarray
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+###  DATA  ###
+data_kn0 = pd.read_csv("degree_vs_dens_kn0.txt",sep="\t")
+vd_kn0 = data_kn0["dens"].tolist()
+mean_degree_kn0 = data_kn0["list_mean_degree"].tolist()
+std_degree_kn0 = data_kn0["list_std_degree"].tolist()
+
+data_knE4 = pd.read_csv("degree_vs_dens_kn1.2E4.txt",sep="\t")
+vd_knE4 = data_knE4["dens"].tolist()
+mean_degree_knE4 = data_knE4["list_mean_degree"].tolist()
+std_degree_knE4 = data_knE4["list_std_degree"].tolist()
+
+data_kn = pd.read_csv("degree_vs_dens_kn1.2E5.txt",sep="\t")
+vd_kn = data_kn["dens"].tolist()
+mean_degree_kn = data_kn["list_mean_degree"].tolist()
+std_degree_kn = data_kn["list_std_degree"].tolist()
+
[…]

### 2019-12-27 plots/corridor/overlap_vs_density/plot_overlap_vs.py

@@ -1,0 +1,75 @@
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+import pandas as pd
+#import numarray
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+###  DATA  ###
+data_kn0 = pd.read_csv("overlap_vs_dens_kn0.txt",sep="\t")
+dens_kn0 = data_kn0["dens"].tolist()
+mean_overlap_kn0 = data_kn0["list_mean_overlap"].tolist()
+std_overlap_kn0 = data_kn0["list_std_overlap"].tolist()
+
+data_knE4 = pd.read_csv("overlap_vs_dens_knE4.txt",sep="\t")
+dens_knE4 = data_knE4["dens"].tolist()
+mean_overlap_knE4 = data_knE4["list_mean_overlap"].tolist()
+std_overlap_knE4 = data_knE4["list_std_overlap"].tolist()
+
+data_kn = pd.read_csv("overlap_vs_dens_knE5.txt",sep="\t")
+dens_kn = data_kn["dens"].tolist()
+mean_overlap_kn = data_kn["list_mean_overlap"].tolist()
+std_overlap_kn = data_kn["list_std_overlap"].tolist()
+
[…]

### 2019-12-27 paper.tex
agregue las figuras de overlap vs densidad y degree vs densidad
Update paper.tex

@@
 
+The Social Force Model (SFM) provides the necessary framework for simulating 
+the collective dynamics of self-driven particles (\textit{i.e.} pedestrians). 
+The pedestrians are considered to follow an equation of motion involving 
+either ``socio-psychological'' forces and physical forces (say, granular 
+forces). The equation of motion for any pedestrian $i$ (of mass $m_i$) reads
+
+\begin{equation}
+ m_i\,\displaystyle\frac{d\mathbf{v}_i}{dt}=\mathbf{f}_d^{(i)}+
+ \displaystyle\sum_{j=1}^N\mathbf{f}_s^{(ij)}+
+ \displaystyle\sum_{j=1}^N\mathbf{f}_g^{(ij)}\label{eqn_motion}
+\end{equation}
+
+\noindent where the subscript $j$ corrresponds to any neighboring pedestrian or 
+the walls. The three forces $\mathbf{f}_d$, $\mathbf{f}_s$ and $\mathbf{f}_g$ 
+are different in nature. The desire force $\mathbf{f}_d$ represents the 
+acceleration (or deceleration) of the pedestrian due to his (her) own willings. 
+The social force $\mathbf{f}_s$, intead, describes the tendency of the 
+pedestrians to stay away from each other. The granular force $\mathbf{f}_g$ 
+stands for either the sliding friction and the compression between 
+pedestrians. \\
+
+Notice that these forces are supposed to influence the behavior of the 
+pedestrians in a similar fashion as mentioned in Section~\ref{experimental}. 
+Thus, the set of (empirical) parameters described in Section~\ref{experimental} 
+is expected to be also present in the SFM. These will appear in connection to 
+the forces, although their meaning may be somewhat different. \\
+
+The pedestrians' own willing is modeled by the desire force $\mathbf{f}_d$. 
+This force stands for the acceleration (deceleration) required to reach a 
+certain position at the desired walking speed $v_d$. This involves, however, a 
+personal attitude that makes him (her) appear more or less ``assertive''. As 
+mentioned in Section~\ref{experimental}, the reaction time $\tau$  attains for 
+this attitude. Thus, the desire force is modeled as follows
+
+\begin{equation}
+\mathbf{f}_d^{(i)}=m\,\displaystyle\frac{v_d^{(i)}\,
+\hat{\mathbf{e}}_d^{(i)}(t)-
+ \mathbf{v}^{(i)}(t)}{\tau}
+\end{equation}
+
+\noindent where $\hat{\mathbf{e}}(t)$ represents the unit vector pointing to 
+the target position. $\mathbf{v}(t)$ stands for the pedestrian velocity at time 
+$t$. \\
+
+The tendency of any individual to preserve his (her) ``private sphere'' is 
+accomplished by the social force $\mathbf{f}_s$. This force is expected to 
+prevent the pedestrians from getting too close to each other (or to the walls) 
+in a crowded environment. If he (she) perceives that there is not enough space 
+to move, he (she) will decelerate or even move back. The model for this kind of 
+``socio-psychological'' behavior is as follows
+
+\begin{equation}
+ \mathbf{f}_s^{(i)}=A\,e^{(R_{ij}-r_{ij})/B}\hat{\mathbf{n}}_{ij}
+ \label{eqn_social}
+\end{equation}
+
+\noindent where $r_{ij}$ means the distance between the center of mass of the 
+pedestrians $i$ and $j$, and $R_{ij}=R_i+R_j$ is the sum of the pedestrians 
+radius. The unit vector $\hat{\mathbf{n}}_{ij}$ points from pedestrian $j$ to 
+pedestrian $i$, meaning a repulsive interaction.\\
+
+The net distance $|R_{ij}-r_{ij}|$ scales to the parameter $B$ in the 
+expression (\ref{eqn_social}). This parameter plays the role of a fall-off 
+length within the model, and thus, it may be somewhat connected to the 
+(perceived) step distance mentioned in Section~\ref{experimental}. The 
+parameter $A$, however, does not provide any direct link to other parameters 
+mentioned there. \\
+
+The granular force (say, the sliding friction plus the body force) attain to 
+the moving difficulties encountered in very crowded environments. The 
+expression for the granular force is has been borrowed from other granular 
+matter fields, as follows
+
+\begin{equation}
+ \mathbf{f}_g^{(ij)}=\kappa\,(R_{ij}-r_{ij})\,\Theta(R_{ij}-r_{ij})
+\,(\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij})\,\hat{\mathbf{t}}_{ij}+
+k\,(R_{ij}-r_{ij})\,\Theta(R_{ij}\,\hat{\mathbf{n}}_{ij}
+-r_{ij})\label{eqn_friction}
+\end{equation}
+
+\noindent where $\Theta(R_{ij}-r_{ij})$ equals unity if $R_{ij}>r_{ij}$ and 
+vanished otherwise. $\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij}$ 
+represents the difference between the tangential velocities of the sliding 
+bodies (or between the individual and the walls).    \\
+
+The sliding friction occurs in the tangential direction while the body force 
+occurs in the normal direction. Both are assumed to be linear with respect to 
+the net distance between contacting pedestrians. The sliding friction is also 
+linearly related to the difference between the (tangential) velocities. The 
+coefficients $\kappa$ (for the sliding friction) and $k$ (for the 
+body force) are supposed to be related to the areas of contact and the clothes 
+material, among others. \\
+
+We stress that the expression (\ref{eqn_friction}) assumes fixed values for 
+$\kappa$ and $k$. This may not be completely true according to 
+Table~\ref{table_data}. The local density (and thus, the pedestrians' 
+compression) may affect the compressibility parameter $k$ by more than an order 
+of magnitude. We will vary $k$ (and $\kappa$) in order to explore this 
+phenomenon. \\
+
+\subsection{\label{sfm}The parameters setting}
+
 \section{\label{results}Results}
@@
 
+\begin{figure}[!htbp]
+\centering
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./degree_vs_dens_multi_kn.eps}\label{degree_dens}}\ 
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./overlap_vs_dens_multi_kn.eps}\label{overlap_dens}}\\
+\caption[width=0.47\columnwidth]{}
+\label{network_corridor}
+\end{figure}
+
 \begin{figure}[htbp!]

### 2019-12-27 paper.tex
Update paper.tex

@@
 \begin{equation}
- \mathbf{f}_s^{(i)}=A\,e^{(R_{ij}-r_{ij})/B}\hat{\mathbf{n}}_{ij}
+ \mathbf{f}_s^{(i)}=A\,e^{(R_{ij}-r_{ij})/B}\,\hat{\mathbf{n}}_{ij}
  \label{eqn_social}
@@
 \begin{equation}
- \mathbf{f}_g^{(ij)}=\kappa\,(R_{ij}-r_{ij})\,\Theta(R_{ij}-r_{ij})
-\,(\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij})\,\hat{\mathbf{t}}_{ij}+
-k\,(R_{ij}-r_{ij})\,\Theta(R_{ij}\,\hat{\mathbf{n}}_{ij}
--r_{ij})\label{eqn_friction}
+ \mathbf{f}_g^{(ij)}=\kappa\,g(R_{ij}-r_{ij})\,
+(\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij})\,\hat{\mathbf{t}}_{ij}+
+k\,g(R_{ij}-r_{ij})\,
+\,\hat{\mathbf{n}}_{ij}\label{eqn_friction}
 \end{equation}
 
-\noindent where $\Theta(R_{ij}-r_{ij})$ equals unity if $R_{ij}>r_{ij}$ and 
-vanished otherwise. $\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij}$ 
-represents the difference between the tangential velocities of the sliding 
-bodies (or between the individual and the walls).    \\
+\noindent where $g(R_{ij}-r_{ij})$. $\Theta(R_{ij}-r_{ij})$ equals R_{ij}-r_{ij} 
+if $R_{ij}>r_{ij}$ and vanished otherwise. 
+$\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij}$ represents the difference 
+between the tangential velocities of the sliding bodies (or between the 
+individual and the walls).    \\
 
@@
 \subsection{\label{sfm}The parameters setting}
+
+\begin{figure}[!htbp]
+\centering
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./venn_2parameters.png}\label{venn_2parameters}}\ 
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./venn_3parameters.png}\label{venn_3parameters}}\\
+\caption[width=0.47\columnwidth]{}
+\label{flow_density}
+\end{figure}
 
@@
 
-\begin{figure}[!htbp]
-\centering
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./venn_2parameters.png}\label{venn_2parameters}}\ 
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./venn_3parameters.png}\label{venn_3parameters}}\\
-\caption[width=0.47\columnwidth]{}
-\label{flow_density}
-\end{figure}
-
 \section{\label{discussion}Discussion}

### 2019-12-29 plots/corridor/triangles/plot_density_triangles.py
agregue carpeta con data de los triangulos vs densidad con estadistica

@@ -1,0 +1,94 @@
+import sys
+import os
+import pandas as pd
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+
+
+def main():
+
+     file_name = 'network_data_corridor_avgt_kn0.txt'
+     simbol ='-s'
+     color = 'c'
+     label = "$k_n=$~0"
+     plot_triangles(file_name,simbol,color,label)
+
+     file_name= 'network_data_corridor_avgt_kn1.2E4.txt' 
+     simbol ='-^'
+     color = 'y'
+     label = "$k_n=1.2$~E4"
+     plot_triangles(file_name,simbol,color,label)
+
+     file_name = 'network_data_corridor_avgt_kn1.2E5.txt' 
+     simbol ='-x'
+     color = 'b'
+     label = "$k_n=1.2$~E5"
+     plot_triangles(file_name,simbol,color,label)
+
+     file_name = 'network_data_corridor_avgt_kn1.2E6.txt'
+     simbol ='-o'
+     color = 'k'
+     label = "$k_n=1.2$~E6"
+     plot_triangles(file_name,simbol,color,label)
+
+
+
+def plot_triangles(file_name,simbol,color,label):
+     '''
+     Importa un archivo con las caracteristicas de la red 
+     y grafica triangulos vs densidad
+     '''
[…]

### 2019-12-29 plots/corridor/triangles/plot_network_parameters.py

@@ -40,103 +40,60 @@ pylab.rcParams.update(params)
 def main():
 
 
-     df = pd.read_csv('network_data_kn1.2E6_t30s.txt',delimiter = '\t') 
-     global_density = df['0.density'].tolist()
-     f_in_giant = df['2.fraction nodes in giant'].tolist()
-     shortest_path = df['5.average shortest path length'].tolist()
-     diameter = df['6.diameter'].tolist()
-     mean_degree = df['7.mean degree'].tolist()
-     std_degree = df['8.std degree'].tolist()
-     triangles = df['9.triangles per node'].tolist()
+     df = pd.read_csv('network_data_corridor_avgt_kn1.2E6.txt',delimiter = '\t') 
+     global_density = df['0.Global dens'].tolist()
+     f_in_giant = df['1.fraction nodes in giant'].tolist()
+     diameter = df['3.diameter'].tolist()
+     mean_degree = df['4.mean degree'].tolist()
+     std_degree = df['5.std degree'].tolist()
+     triangles = df['6.triangles per node'].tolist()
+     triangles_std = df['7.std triangles per node'].tolist()
      simbol ='-o'
      color = 'k'
      label = "$k_n=1.2$~E6"
-     #plot_degree(global_density,mean_degree,std_degree,color,simbol,label)
-     #plot_fraction_in_giant(global_density,f_in_giant,color,simbol,label)
-     #plot_shortest_path(global_density,shortest_path,color,simbol,label)
-     #plot_diameter(global_density,diameter,color,simbol,label)
      plot_triangles(global_density,triangles,color,simbol,label)
 
-     df = pd.read_csv('network_data_knE5_t30s.txt',delimiter = '\t') 
-     global_density = df['0.density'].tolist()
-     f_in_giant = df['2.fraction nodes in giant'].tolist()
-     shortest_path = df['5.average shortest path length'].tolist()
-     diameter = df['6.diameter'].tolist()
-     mean_degree = df['7.mean degree'].tolist()
-     std_degree = df['8.std degree'].tolist()
-     triangles = df['9.triangles per node'].tolist()
+     df = pd.read_csv('network_data_corridor_avgt_kn1.2E5.txt',delimiter = '\t') 
+     global_density = df['0.Global dens'].tolist()
+     f_in_giant = df['1.fraction nodes in giant'].tolist()
[…]

### 2019-12-29 plots/corridor/triangles/plot_network_parameters.py
pequena correccion

@@ -1,114 +1,0 @@
-import sys
-import os
-import pandas as pd
-import pylab
-import numpy as np
-import matplotlib.pyplot as plt
-import math
-
-# a dos columnas: 3+3/8 (ancho, in)
-# a una columna : 6.5   (ancho  in)
-
-golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
-fig_width = 3+3/8 			    # width  in inches
-fig_height = fig_width*golden_mean          # height in inches
-fig_size =  [fig_width,fig_height]
-
-params = {'backend': 'ps',
-          'axes.titlesize': 8,
-          'axes.labelsize': 9,
-          'axes.linewidth': 0.5, 
-          'axes.grid': True,
-          'axes.labelweight': 'normal',  
-          'font.family': 'serif',
-          'font.size': 8.0,
-          'font.weight': 'normal',
-          'text.color': 'black',
-          'xtick.labelsize': 8,
-          'ytick.labelsize': 8,
-          'text.usetex': True,
-          'legend.fontsize': 8,
-          'figure.dpi': 300,
-          'figure.figsize': fig_size,
-          'savefig.dpi': 300,
-         }
-
-pylab.rcParams.update(params)
-
-
-
-def main():
-
-
-     df = pd.read_csv('network_data_corridor_avgt_kn1.2E6.txt',delimiter = '\t') 
-     global_density = df['0.Global dens'].tolist()
-     f_in_giant = df['1.fraction nodes in giant'].tolist()
-     diameter = df['3.diameter'].tolist()
-     mean_degree = df['4.mean degree'].tolist()
-     std_degree = df['5.std degree'].tolist()
-     triangles = df['6.triangles per node'].tolist()
-     triangles_std = df['7.std triangles per node'].tolist()
-     simbol ='-o'
-     color = 'k'
-     label = "$k_n=1.2$~E6"
-     plot_triangles(global_density,triangles,color,simbol,label)
-
-     df = pd.read_csv('network_data_corridor_avgt_kn1.2E5.txt',delimiter = '\t') 
-     global_density = df['0.Global dens'].tolist()
-     f_in_giant = df['1.fraction nodes in giant'].tolist()
-     diameter = df['3.diameter'].tolist()
-     mean_degree = df['4.mean degree'].tolist()
-     std_degree = df['5.std degree'].tolist()
[…]

### 2019-12-29 paper.tex
Update paper.tex

@@
 
-\noindent where $g(R_{ij}-r_{ij})$. $\Theta(R_{ij}-r_{ij})$ equals R_{ij}-r_{ij} 
-if $R_{ij}>r_{ij}$ and vanished otherwise. 
-$\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij}$ represents the difference 
-between the tangential velocities of the sliding bodies (or between the 
-individual and the walls).    \\
+\noindent where $g(R_{ij}-r_{ij})$ equals $R_{ij}-r_{ij}$ if $R_{ij}>r_{ij}$ and 
+vanished otherwise. $\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij}$ 
+represents the difference between the tangential velocities of the sliding 
+bodies (or between the individual and the walls).    \\
 
@@
 
-\subsection{\label{sfm}The parameters setting}
+\subsection{\label{parameters}The parameters setting}
+
+The numerical setting of the parameters may affect the dynamics of the 
+pedestrians. Some settings, however, yield similar collective dynamics. In 
+order to investigate the similarities, we can introduce unit-less magnitudes 
+and proceed straightforward as indicated in Appendix~\ref{appendix_1}. We 
+realize from Appendix~\ref{appendix_1} that only three (unit-less) 
+parameters  are the true ``control'' parameters for the collective dynamics. 
+These are $\mathcal{A}$, $\mathcal{K}$, $\mathcal{K}_c$ as defined in 
+Appendix~\ref{appendix_1}. Recall that $\mathcal{A}$ and $\mathcal{K}$ are 
+precisely the same as in Ref.~\cite{dorso_2019}, but a novel $\mathcal{K}_c$ 
+has been introduced due to the body force.   \\
+
+The logical relations between the unit-less parameters and the ``individual'' 
+parameters can be studied by means of the Venn diagrams exhibited in 
+Fig.~\ref{venn_diagram}. The parameters $\mathcal{A}$, $\mathcal{K}$ and 
+$\mathcal{K}_c$ are represented as intersecting sets, and the ``individual'' 
+parameters are represented as elements within each set. The shared elements 
+between $\mathcal{A}$, $\mathcal{K}$ and $\mathcal{K}_c$ are placed inside de 
+intersecting regions. \\
 
@@
 \centering
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./venn_2parameters.png}\label{venn_2parameters}}\ 
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./venn_3parameters.png}\label{venn_3parameters}}\\
-\caption[width=0.47\columnwidth]{}
-\label{flow_density}
+
+\subfloat[(a)]{\includegraphics[width=0.45\columnwidth]{./venn_2parameters.png}
+\label{venn_2parameters}}\
+
+\subfloat[(b)]{\includegraphics[width=0.45\columnwidth]{./venn_3parameters.png}
+\label{venn_3parameters}}\\
+\caption[width=0.47\columnwidth]{Venn diagrams for the unit-less parameters
+appearing in the equation of motion (\ref{eqn_motion}) (see 
+Appendix~\ref{appendix_1} for details). The sets correspond to 
+$\mathcal{A}=\{\tau/m,1/v_d,A\}$, $\mathcal{K}=\{\tau/m,B,\kappa\}$ and 
+$\mathcal{K}_c=\{\tau/m,1/v_d,B,k\}$ (a) The Venn diagram representation if no 
+body force is introduced in the SFM (only sets $\mathcal{A}$ and $\mathcal{K}$, 
+as in Ref.~\cite{dorso_2019}). (b) The Venn diagram representation for the sets 
+$\mathcal{A}$, $\mathcal{K}$ and $\mathcal{K}_c$. }
+\label{venn_diagram}
 \end{figure}
+
+The set of parameters introduced within the context of the SFM (see 
+Section~\ref{background}) affects the collective dynamics. The setting for 
+these parameters may change...\\
 
@@
 
+\section{appendix_1}
+
+The SFM description in Section~\ref{sfm} introduces seven parameters ($m$, 
+$\tau$, $v_d$, $B$, $A$, $\kappa$ and $k$) attaining for the ``individual'' 
+behavior of each pedestrian. The collective dynamic, however, requires a 
+smaller set of parameters. In order to identify this smaller set, we introduce 
+the following unit-less magnitudes\\
+
+\begin{equation}
+ \left\{\begin{array}{lcl}
+         t' & = & t/\tau \\
+         r' & = & r/B \\
+         v' & = & v/v_d \\
+        \end{array}\right.
+\end{equation}
+
+The equation of motion (\ref{eqn_motion}) can be written in terms of these 
+(unit-less) magnitudes, while only three (reduced) parameters are needed.\\
+
+\begin{equation}
+ \displaystyle\frac{d\mathbf{v}'}{dt'}=
+ \hat{\mathbf{e}}_d-\mathbd{v}'+\mathcal{A}\,e^{R'-r'}\,
+ \hat{\mathbf{n}}+g(R'-r')\,\bigg[\mathcal{K}\,(\Delta\mathbf{v}'\cdot
+ \hat{\mathbf{t}})\,\hat{\mathbf{t}}+\mathbf{K}_c\,\hat{\mathbf{n}}\bigg]
+\end{equation}
+
+\noindent where the smaller set ($\mathcal{A}$,$\mathcal{K}$,$\mathcal{K}_c$) 
+means\\
+
+\begin{equation}
+ \mathcal{A}=\displaystyle\frac{A\,\tau}{m\,v_d}\ \ \ \ , \ \ \ \ 
+ \mathcal{K}=\displaystyle\frac{\kappa\,B\,\tau}{m}\ \ \ \ , \ \ \ \
+ \mathcal{K}_c=\displaystyle\frac{k\,B\,\tau}{m}
+\end{equation}
+
+Notice that the SFM will arrive to similar collective dynamics whenever the 
+reduced set ($\mathcal{A}$,$\mathcal{K}$,$\mathcal{K}_c$) remains unchanged 
+(although some ``individual'' parameters are allowed to change). For a deep 
+explanation on the meaning  of the set 
+($\mathcal{A}$,$\mathcal{K}$,$\mathcal{K}_c$) see Section~\ref{parameters}. \\
+
 %/////////////////////////////////////////////////

### 2019-12-29 paper.tex
Add files via upload
Update de Guillermo Frank.

@@
 \title{Effects of the body force on the evacuation dynamics}
+
+\author[add1]{I.M.~Sticco}
+ \address[add1]{Departamento de F\'\i sica, Facultad de Ciencias 
+Exactas y Naturales, Universidad de Buenos Aires,\\
+ Pabell\'on I, Ciudad Universitaria, 1428 Buenos Aires, Argentina.}
+ %Lines break automatically or can be forced with \\
+ \author[add2]{G.A.~Frank}
+ \address[add2]{Unidad de Investigaci\'on y Desarrollo de las 
+Ingenier\'\i as, Universidad Tecnol\'ogica Nacional, Facultad Regional Buenos 
+Aires, Av. Medrano 951, 1179 Buenos Aires, Argentina.}
+ %Lines break automatically or can be forced with \\
+\author[add1,add3]{C.O.~Dorso\corref{cor1}}%
+ \cortext[cor1]{codorso@df.uba.ar}
+%\affiliation{Departamento de F\'\i sica, Facultad de Ciencias Exactas y 
+%Naturales, Universidad de Buenos Aires,\\
+% Pabell\'on I, Ciudad Universitaria, 1428 Buenos Aires, Argentina.}%
+% \altaffiliation[Also at ]{Instituto de F\'\i sica de Buenos Aires, Pabell\'on 
+%I, Ciudad Universitaria, 1428 Buenos Aires, Argentina.}
+\address[add3]{Instituto de F\'\i sica de Buenos Aires,
+Pabell\'on I, Ciudad Universitaria, 1428 Buenos Aires, Argentina.}
+ %\affiliation{Departamento de F\'\i sica, Facultad de Ciencias 
+%Exactas y Naturales, Universidad de Buenos Aires,\\
+% Pabell\'on I, Ciudad Universitaria, 1428 Buenos Aires, Argentina.}
 
@@
 
-\subfloat[(a)]{\includegraphics[width=0.45\columnwidth]{./venn_2parameters.png}
-\label{venn_2parameters}}\
-
-\subfloat[(b)]{\includegraphics[width=0.45\columnwidth]{./venn_3parameters.png}
-\label{venn_3parameters}}\\
+\subfloat[\label{venn_2parameters}]
+{\includegraphics[width=0.45\columnwidth]{./venn_2parameters.png}}
+\hfill    
+\subfloat[\label{venn_3parameters}]
+{\includegraphics[width=0.45\columnwidth]{./venn_3parameters.png}
+}\\
 \caption[width=0.47\columnwidth]{Venn diagrams for the unit-less parameters
@@
 $\mathcal{A}=\{\tau/m,1/v_d,A\}$, $\mathcal{K}=\{\tau/m,B,\kappa\}$ and 
-$\mathcal{K}_c=\{\tau/m,1/v_d,B,k\}$ (a) The Venn diagram representation if no 
+$\mathcal{K}_c=\{\tau/m,1/v_d,B,k\}$. (a) The Venn diagram representation if no 
 body force is introduced in the SFM (only sets $\mathcal{A}$ and $\mathcal{K}$, 
@@
 
-\subsection{\label{reduced-in-units} Reduced-in-units equation of motion}
-
 \section{\label{discussion}Discussion}
@@
 
-\section{appendix_1}
+\section{\label{appendix_1} Reduced-in-units equation of motion}
 
@@
  \displaystyle\frac{d\mathbf{v}'}{dt'}=
- \hat{\mathbf{e}}_d-\mathbd{v}'+\mathcal{A}\,e^{R'-r'}\,
+ \hat{\mathbf{e}}_d-\mathbf{v}'+\mathcal{A}\,e^{R'-r'}\,
  \hat{\mathbf{n}}+g(R'-r')\,\bigg[\mathcal{K}\,(\Delta\mathbf{v}'\cdot
- \hat{\mathbf{t}})\,\hat{\mathbf{t}}+\mathbf{K}_c\,\hat{\mathbf{n}}\bigg]
+ \hat{\mathbf{t}})\,\hat{\mathbf{t}}+\mathcal{K}_c\,\hat{\mathbf{n}}\bigg]
 \end{equation}

### 2019-12-29 paper.tex
Update paper.tex

@@
 pedestrians. Some settings, however, yield similar collective dynamics. In 
-order to investigate the similarities, we can introduce unit-less magnitudes 
-and proceed straightforward as indicated in Appendix~\ref{appendix_1}. We 
-realize from Appendix~\ref{appendix_1} that only three (unit-less) 
-parameters  are the true ``control'' parameters for the collective dynamics. 
-These are $\mathcal{A}$, $\mathcal{K}$, $\mathcal{K}_c$ as defined in 
-Appendix~\ref{appendix_1}. Recall that $\mathcal{A}$ and $\mathcal{K}$ are 
-precisely the same as in Ref.~\cite{dorso_2019}, but a novel $\mathcal{K}_c$ 
-has been introduced due to the body force.   \\
+order to investigate these similarities, we can introduce unit-less magnitudes 
+and proceed straightforward as indicated in \ref{appendix_1}. We realize from 
+Appendix~\ref{appendix_1} that only three (unit-less) parameters  are the true 
+``control'' parameters for the collective dynamics. These are $\mathcal{A}$, 
+$\mathcal{K}$, $\mathcal{K}_c$ as defined in \ref{appendix_1}. Recall that 
+$\mathcal{A}$ and $\mathcal{K}$ are precisely the same as in 
+Ref.~\cite{dorso_2019}, but a novel $\mathcal{K}_c$ parameter has been 
+introduced due to the body force.   \\
 
@@
 
-The set of parameters introduced within the context of the SFM (see 
-Section~\ref{background}) affects the collective dynamics. The setting for 
-these parameters may change...\\
+An inspection of the diagrams in Fig.~\ref{venn_diagram} shows that the 
+relaxation time (per unit mass) $\tau/m$ is always a common parameter, whether 
+or not the body force is included in the model. \\
 

### 2019-12-30 paper.tex
comente un par de cosas en el apendice porque no compilaba
Update paper.tex
agregue texto que explica el diagrama fundamental

--- 2019-12-29 paper.tex
@@
 
+In this section, we present the results corresponding to the corridor geometry.
+We show how the overall dynamic of the system changes depending on the $k$ value associated to the body force in the original SFM.\\
+
+In Fig ...
+we show the flow as a function of the global density (fundamental diagram).
+\ref{flow_density_no_body_force} corresponds to non body force ($i.e k_n=0$), \label{flow_density_body_force} corresponds to a body force with $k_n$=1.2~E5.
+Each curve correspond to a different friction value.
+The circles correspond to the value of the original SFM ($\\kappa = 2.4~E5$), the "+" symbol correspond to the original value increased by a factor of five and triangles correspond to the original value increased by a factor of ten.
+\\
+
+According to most of the empirical measurements, the flow decreases for high enough values of density because the motion becomes jammed.
+Notice that the original friction does not produce a reduction of the flow when there is no body force but when the body force is included (with the original value), the flow reduces from  5 p m$^{-2}$ to 7 p m$^{-2}$ and increases for higher values of density.
+When the density is five times the original value, the flow reduces for densities higher than 5 p m$^{-2}$ in both cases (with body force and without body force).
+The main qualitative difference is that including the body force produces a subtle increment in the flow for densities higher than 7 p m$^{-2}$.
+When the friction is increased by a factor of ten, the flow reduces or remains constant when the density is higher than 5 p m$^{-2}$ for both cases (with body force and without body force).
+\\
+
+This result suggests that even including the body force, the original SFM requires an increment of the friction in order to reproduce the flow reduction reported in empirical measurements.
+
 \begin{figure}[!htbp]
 \centering
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_nobodyforce.eps}\label{flow_density_nocomp}}\ 
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_bodyforce.eps}\label{flow_density_comp}}\\
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_nobodyforce.eps}\label{flow_density_no_body_force}}\ 
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_bodyforce.eps}\label{flow_density_body_force}}\\
 \caption[width=0.47\columnwidth]{}

### 2019-12-30 paper.tex
agregue texto que explica mean degree vs density

@@
 When the friction is increased by a factor of ten, the flow reduces or remains constant when the density is higher than 5 p m$^{-2}$ for both cases (with body force and without body force).
-\\
+This result suggests that even including the body force, the original SFM requires an increment of the friction in order to reproduce the flow reduction reported in empirical measurements.\\
 
-This result suggests that even including the body force, the original SFM requires an increment of the friction in order to reproduce the flow reduction reported in empirical measurements.
+It is worth mentioning that increasing the body force reduces the flow, for a given density and a given friction value (compare \ref{flow_density_no_body_force} with \ref{flow_density_body_force} ).
+In other words, pedestrians walk slower along the corridor if the $k$ value increases ($i.e$ if they are stiffer).
+This result is the opposite of what we get in bottleneck geometry since the stiffer the pedestrians the faster they walk.\\
 
@@
 
+To understand why in corridor geometry pedestrians walk slower as they become stiffer it is important to take into account that pedestrians walk slower if the friction increases.
+In corridors, the friction increases when pedestrians become stiffer because the crowd tends to cluster more.
+The clusterization means that more pedestrians are touching each other.
+\\
+
+One way to analyze the clusterization is by creating a network out of the (x,y) positions of the pedestrians.
+In this network, each node represents a pedestrian and there is a link between a pair of nodes $i,j$ if the pair of pedestrians represented by the nodes are touching each other ($i.e.
+d_{ij} \leq R_{ij}$).
+Once the network is created, it is possible to use the analytical tools that allow describing the configuration such as the mean degree, the distribution of clusters, the shortest path length, etc.\\
+
+In Fig \ref{degree_dens} we show the mean degree as a function of the global density for different $k$ values.
+When the density is low,  the degree is zero because the pedestrians do not touch each other.
+When the density is around 4.5, a few pedestrians start to touch each other increasing the mean degree.
+As the density increases, the mean degree increases too until reaching an asymptotic behavior in degree six.
+When the degree is six, it corresponds to the densest packing possible for identical hard circles, the result is a hexagonal packing arrangement.\\
+
+It is important to notice in Fig \ref{degree_dens} that for a given value of density, the stiffer the pedestrians, the higher the degree.
+A higher degree means more friction force which is the cause of the reduction of the flow.
+In the bottleneck geometry, the opposite thing happens, the stiffer the pedestrians the lower the mean degree.
+This is the reason why in bottleneck pedestrians evacuate faster as they become stiffer while in corridor pedestrian's flow is lower as they become stiffer.\\
+
 \begin{figure}[!htbp]
 \centering
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_d6_kn0.eps}\label{network_d6_kn0}}\ 
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_d6_knE5.eps}\label{network_d6_knE5}}\\
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./degree_vs_dens_multi_kn.eps}\label{degree_dens}}\ 
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./overlap_vs_dens_multi_kn.eps}\label{overlap_dens}}\\
 \caption[width=0.47\columnwidth]{}
@@
 \centering
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./degree_vs_dens_multi_kn.eps}\label{degree_dens}}\ 
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./overlap_vs_dens_multi_kn.eps}\label{overlap_dens}}\\
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_d6_kn0.eps}\label{network_d6_kn0}}\ 
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_d6_knE5.eps}\label{network_d6_knE5}}\\
 \caption[width=0.47\columnwidth]{}

### 2019-12-30 plots/bottleneck/network_config/plot_config_graph.py
mejore las figuras de network config para bottleneck

@@ -120,7 +120,7 @@ def crea_dict_pos(index,x,y):
           pos.update( {'{}'.format(indice) : xy} )
      return pos
 
-def plot_network(G,output_filename):
+def plot_network(G,output_filename,title):
      '''
      Grafica nodos y links ubicados en la posicion correspondiente
      del recinto. El color de cada nodo esta en funcion del grado. 
@@ -130,23 +130,26 @@ def plot_network(G,output_filename):
      nodes = G.nodes()
      n_color = np.asarray([degrees[n] for n in nodes])
      fig, ax = plt.subplots()
-     pos=nx.get_node_attributes(G,'pos')
-     sc = nx.draw(G,pos,width=0.5,node_color=n_color,cmap='viridis',node_size=5,with_labels=False,edge_color='black')
-     #plt.axis([13,20,4,16])
+     pos = nx.get_node_attributes(G,'pos')
+     sc = nx.draw(G,pos,width=0.5,cmap='jet',vmax=6,node_color=n_color,node_size=5,with_labels=False,edge_color='black')
+     plt.axis([13,20,4,16])
      plt.axis([10,20,4,16])
      plt.axis('on')
-     plt.grid('false')
-     #plt.text(15.5, 5.5, "16", fontsize=10)
-     #plt.text(8, 5.5, "8", fontsize=10)
-     #plt.text(7.5, 6, "6", fontsize=10)
-     #plt.text(7.5, 13.5, "14", fontsize=10)
+     plt.grid('off')
      ax.set_xlabel('$x$-position',fontsize=8)
      ax.set_ylabel('$y$-position',fontsize=8)
-     cmap=plt.cm.viridis
-     sm = plt.cm.ScalarMappable(cmap=cmap, norm=plt.Normalize(vmin = min(n_color), vmax=max(n_color)))
+     ax.set_title("{}".format(title),fontsize=10)
+     cmap=plt.cm.jet
+     sm = plt.cm.ScalarMappable(cmap=cmap, norm=plt.Normalize(vmin = min(n_color), vmax=6))
      sm._A = []
-     plt.colorbar(sm)
-     #sm.set_clim(0, 100)
+     plt.colorbar(sm,values=np.linspace(0, 6, 7))
+     plt.text(21.5, 4.5, "0", fontsize=12,color="k")
+     plt.text(21.5, 6.5, "1", fontsize=12,color="k")
[…]

### 2019-12-30 paper.tex
agregue los nuevos graficos de network en bottleneck al archivo tex

@@
     \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn0.eps}\label{flow_density_comp}}\\
-        \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn120000.eps}\label{flow_density_nocomp}}\ 
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn120000.eps}\label{flow_density_comp}}\\
+        \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn1200000.eps}\label{flow_density_nocomp}}\ 
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn1200000.eps}\label{flow_density_comp}}\\
 \caption[width=0.47\columnwidth]{}
@@
 
-It is important to notice in Fig \ref{degree_dens} that for a given value of density, the stiffer the pedestrians, the higher the degree.
+It is important to notice that in Fig.
+\ref{degree_dens} for a given value of density, the stiffer the pedestrians, the higher the degree.
 A higher degree means more friction force which is the cause of the reduction of the flow.
@@
 This is the reason why in bottleneck pedestrians evacuate faster as they become stiffer while in corridor pedestrian's flow is lower as they become stiffer.\\
+
+The mean overlap increases as the global density increases (see Fig...) and the higher the stiffness the lower the overlap.
+This result is similar to the overlap vs.
+the desired velocity obtained for bottleneck geometry.
+The higher the value of $k$ the higher the repulsion of pedestrian-pedestrian interaction since the body force is acting in the normal direction $n_{ij}$.\\
 
@@
 \end{figure}
+
+As was mentioned above, increasing the $k$ value of the body force increases the stiffness of pedestrians.
+Increasing the stiffness reduces the overlap (both in bottleneck and corridor) and reduces the mean degree in a bottleneck and increases the mean degree in a corridor.
+In fig.
+...
+it shown the network associated with the corridor at a particular timestep ($t=$) and a particular global density.
+Fig.
+...
+corresponds to $k=0$ while Fig.
+...
+corresponds to $k=1.2$~E5.
+This is an example to show how increasing the stiffness increases the number of contacts between pedestrians.
+Notice that there are many more pedestrians with degree 6 in the case of $k=1.2$~E5 than the case of $k=0$.
+\\
 

### 2019-12-31 paper.tex
Add files via upload
Compilado por G. Frank y por I. Sticco. Compila bien.

@@
 \title{Effects of the body force on the evacuation dynamics}
+
+\author[add1]{I.M.~Sticco}
+ \address[add1]{Departamento de F\'\i sica, Facultad de Ciencias 
+Exactas y Naturales, \\ Universidad de Buenos Aires,\\
+ Pabell\'on I, Ciudad Universitaria, 1428 Buenos Aires, Argentina.}
+
+ \author[add2]{G.A.~Frank}
+ \address[add2]{Unidad de Investigaci\'on y Desarrollo de las 
+Ingenier\'\i as, Universidad Tecnol\'ogica Nacional, Facultad Regional Buenos 
+Aires, Av. Medrano 951, 1179 Buenos Aires, Argentina.}
+
+\author[add1,add3]{C.O.~Dorso\corref{cor1}}%
+ \cortext[cor1]{codorso@df.uba.ar}
+
+ \address[add3]{Instituto de F\'\i sica de Buenos Aires,\\
+Pabell\'on I, Ciudad Universitaria, 1428 Buenos Aires, Argentina.}
 
@@
 pedestrians. Some settings, however, yield similar collective dynamics. In 
-order to investigate the similarities, we can introduce unit-less magnitudes 
-and proceed straightforward as indicated in Appendix~\ref{appendix_1}. We 
-realize from Appendix~\ref{appendix_1} that only three (unit-less) 
-parameters  are the true ``control'' parameters for the collective dynamics. 
-These are $\mathcal{A}$, $\mathcal{K}$, $\mathcal{K}_c$ as defined in 
-Appendix~\ref{appendix_1}. Recall that $\mathcal{A}$ and $\mathcal{K}$ are 
-precisely the same as in Ref.~\cite{dorso_2019}, but a novel $\mathcal{K}_c$ 
-has been introduced due to the body force.   \\
+order to investigate these similarities, we introduce unit-less magnitudes 
+and proceed straightforward as indicated in \ref{appendix1}. We realize from 
+\ref{appendix1} that only three (unit-less) parameters  are the true 
+``control'' parameters for the collective dynamics. These are $\mathcal{A}$, 
+$\mathcal{K}$, $\mathcal{K}_c$ as defined in \ref{appendix1}. Recall that 
+$\mathcal{A}$ and $\mathcal{K}$ are precisely the same as in 
+Ref.~\cite{dorso_2019}, but a novel $\mathcal{K}_c$ parameter has been 
+introduced due to the body force.   \\
 
@@
 
-\subfloat[(a)]{\includegraphics[width=0.45\columnwidth]{./venn_2parameters.png}
-\label{venn_2parameters}}\
-
-\subfloat[(b)]{\includegraphics[width=0.45\columnwidth]{./venn_3parameters.png}
-\label{venn_3parameters}}\\
+\subfloat[\label{venn_2parameters}]
+{\includegraphics[width=0.45\columnwidth]{./venn_2parameters.png}}
+\hfill    
+\subfloat[\label{venn_3parameters}]
+{\includegraphics[width=0.45\columnwidth]{./venn_3parameters.png}
+}\\
 \caption[width=0.47\columnwidth]{Venn diagrams for the unit-less parameters
 appearing in the equation of motion (\ref{eqn_motion}) (see 
-Appendix~\ref{appendix_1} for details). The sets correspond to 
+Appendix~\ref{appendix1} for details). The sets correspond to 
 $\mathcal{A}=\{\tau/m,1/v_d,A\}$, $\mathcal{K}=\{\tau/m,B,\kappa\}$ and 
-$\mathcal{K}_c=\{\tau/m,1/v_d,B,k\}$ (a) The Venn diagram representation if no 
+$\mathcal{K}_c=\{\tau/m,1/v_d,B,k\}$. (a) The Venn diagram representation if no 
 body force is introduced in the SFM (only sets $\mathcal{A}$ and $\mathcal{K}$, 
@@
 
-The set of parameters introduced within the context of the SFM (see 
-Section~\ref{background}) affects the collective dynamics. The setting for 
-these parameters may change...\\
+A first inspection of the diagrams in Fig.~\ref{venn_diagram} shows that the 
+relaxation time (per unit mass) $\tau/m$ is always a common parameter to all 
+sets, regardless of the body force. This means that the ``assertive'' attitude 
+of the pedestrian, addressed by the reaction time (see 
+Section~\ref{experimental}), applies to all stimuli and the own willings. The 
+role of $\tau$ has already been discussed in 
+Refs.~\cite{johansson_2009,dorso_2019}.    \\
+
+Fig.~\ref{venn_2parameters} represents the situation when $\mathcal{K}_c$ is 
+absent. Notice that $A/v_d$ or $\kappa B$ may control the collective 
+dynamic, in spite of the ``assertive'' attitude. The individual character of 
+$v_d$ or $B$ appears somehow ``loosely'' in the crowd dynamic. We mean by 
+``loosely'' that any numerical setting of these parameters may be 
+counterbalanced by the right setting of $A$ or $\kappa$, keeping the 
+colletive dynamic (qualitatively) unchanged.  \\
+
+Fig.~\ref{venn_3parameters} provides a picture of the parameters' relations 
+after introducing $\mathcal{K}_c$. Surprisingly, $\mathcal{K}_c$ appears as a
+wider set (say, a four elements set) than $\mathcal{A}$ or $\mathcal{K}$ (three 
+elements' sets). It shares the parameter $v_d$ with $\mathcal{A}$ and the 
+parameter $B$ with $\mathcal{K}$. The practical consequence to these (logical)
+relations is that $v_d$ or $B$ affect simultaneously two ``control'' parameters 
+of the collective dynamics. Conversely, either $v_d$ and $B$ may counterbalance 
+$\mathcal{K}_c$ in order to keep the colletive dynamic (qualitatively) 
+unchanged.  \\
+
+We confirm from these diagrams that no univocal relations can be established 
+between the individual parameters and the collective dynamics (in a crowded 
+environment). The presence of the body force moves the dynamics to a more 
+complex context. We will investigate this context in Section~\ref{results}. \\
 
@@
 
-\section{appendix_1}
+\section{\label{appendix1}Reduced-in-units equation of motion}
 
@@
  \mathcal{K}=\displaystyle\frac{\kappa\,B\,\tau}{m}\ \ \ \ , \ \ \ \
- \mathcal{K}_c=\displaystyle\frac{k\,B\,\tau}{m}
+ \mathcal{K}_c=\displaystyle\frac{k\,B\,\tau}{m\,v_d}
 \end{equation}

### 2019-12-31 paper.tex
agregue un pedazo de texto a network bottleneck

--- 2019-12-30 paper.tex
@@
 
+Increasing the stiffness has a significative impact on the evacuation dynamics.
+It reduces the overlap and reduces the mean degree between pedestrians.
+Both effects tend to reduce the friction in the crowd and the immediate consequence of this is a reduction of the evacuation time (pedestrians escape faster).
+The body force has a notorious impact in the number of pedestrians that each pedestrians touch (degree).
+This is clearly depicted in Fig.
+\ref{network_bottleneck} where four different configurations of the evacuation dynamics are shown.
+The configurations represent 225 pedestrians trying to escape through a 0.92 m door which center is located at $(x,y)=(20,10)$~m.
+The colors correspond to the degree of each node (pedestrian) and the lines between pedestrians represent the contacts among them.\\
+
 \begin{figure}[!htbp]
 \centering
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn0.eps}\label{flow_density_nocomp}}\ 
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn0.eps}\label{flow_density_comp}}\\
-        \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn1200000.eps}\label{flow_density_nocomp}}\ 
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn1200000.eps}\label{flow_density_comp}}\\
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn0.eps}\label{network_vd2_kn0}}\ 
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn0.eps}\label{network_vd10_kn0}}\\
+        \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn1200000.eps}\label{network_vd2_kn1200000}}\ 
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn1200000.eps}\label{network_vd10_kn1200000}}\\
 \caption[width=0.47\columnwidth]{}
-\label{flow_density}
+\label{network_bottleneck}
 \end{figure}
@@
 
-\section{appendix_1}
+%\section{appendix_1}
 
@@
 
-\begin{equation}
- \displaystyle\frac{d\mathbf{v}'}{dt'}=
- \hat{\mathbf{e}}_d-\mathbd{v}'+\mathcal{A}\,e^{R'-r'}\,
- \hat{\mathbf{n}}+g(R'-r')\,\bigg[\mathcal{K}\,(\Delta\mathbf{v}'\cdot
- \hat{\mathbf{t}})\,\hat{\mathbf{t}}+\mathbf{K}_c\,\hat{\mathbf{n}}\bigg]
-\end{equation}
+%\begin{equation}
+% \displaystyle\frac{d\mathbf{v}'}{dt'}=
+% \hat{\mathbf{e}}_d-\mathbd{v}'+\mathcal{A}\,e^{R'-r'}\,
+% \hat{\mathbf{n}}+g(R'-r')\,\bigg[\mathcal{K}\,(\Delta\mathbf{v}'\cdot
+% \hat{\mathbf{t}})\,\hat{\mathbf{t}}+\mathbf{K}_c\,\hat{\mathbf{n}}\bigg]
+%\end{equation}
 

### 2019-12-31 paper.tex
complete un poco el texto de network en bottleneck

@@
 
+The four configurations corresponds to two different $v_d$ and two different $k$ values.
+Fig.
+\ref{network_vd2_kn0} represents $v_d=$2 and $k=0$, Fig.
+\ref{network_vd10_kn0} corresponds to $v_d=$10 and $k=0$ while \ref{network_vd2_kn1200000} and \ref{network_vd10_kn1200000} correspond to $v_d=$2 and $v_d=$10 respectively and both have the same body force coefficient $k=$1.2~E6.
+As expected, increasing the desired velocity compress the crowd towards the exit.
+\\
+
+Comparing Fig.
+\ref{network_vd2_kn0} against Fig.
+\ref{network_vd2_kn1200000} and Fig \ref{network_vd10_kn0} against Fig.
+\ref{network_vd10_kn1200000} it is clear that increasing the stiffness reduces the degree.
+The most notorious case is the pictures corresponding to $v_d=$10 in which, despite having the same $v_d$, the size of the bulk increases when the pedestrians are stiffer.
+Moreover, when pedestrians are stiffer they have fewer contacts in general (less degree).
+Notice that there are no pedestrians with degree 6 when $k=1.2$~E6 and there are a lot of pedestrians with degree 6 when $k$=0.
+
 \begin{figure}[!htbp]

### 2019-12-31 paper.tex
agregue texto para la parte de triangulos por nodo

@@
 
+The increment of the clusterization is responsible for the reduction of the flow.
+In the corridor geometry, the crowd gets more clusterized if the pedestrians become stiffer.
+We studied the network properties of the contact graph arising from the positions $(x,y)$ of every the pedestrians.
+We found that a good descriptor to exhibit the clusterization is the number of triangles per node.
+A triangle is defined as a structure composed of three nodes all in contact with each other.
+In Fig.
+\ref{triangles} we show the triangles per node as a function of the global density for different stiffness values $k$.
+This descriptor allows to distinguish states with the same global density but different stiffness levels.
+In other words, it is a descriptor very sensitive to changes in stiffness that allow expressing the degree of clustering of the system even better than the mean degree.
+\\
+
+This result is consistent with the results obtained in Ref.
+\cite{pugnaloni_2013} where they explore several topological and geometric descriptors capable of properly describing granular systems with different stiffness.
+While our study system is self-propelled, there are analogies with the system studied in Ref.
+Like the authors, we recommend using topological descriptors (in particular triangles per node) to describe systems with equal global density and different stiffness levels.\\
+
 \begin{figure}[htbp!]
@@
 {./triangles.eps}
-\caption{\label{} }
+\caption{\label{triangles} }
 \end{figure}

### 2019-12-31 plots/corridor/network_config/plot_config_graph.py
mejore los graficos de network en corridor

@@ -120,31 +120,40 @@ def crea_dict_pos(index,x,y):
           pos.update( {'{}'.format(indice) : xy} )
      return pos
 
-def plot_network(G,output_filename):
+def plot_network(G,output_filename,title):
      '''
      Grafica nodos y links ubicados en la posicion correspondiente
      del recinto. El color de cada nodo esta en funcion del grado. 
      '''
-
-     degrees = G.degree() 
+     
+     # Add a ghost node in a ghost position to have one node
+     # with zero degree (same scale than bottleneck)
+     G.add_node(4000) 
+     G.nodes[4000]['pos'] = [100,100]
+     
+     degrees = G.degree()
      nodes = G.nodes()
      n_color = np.asarray([degrees[n] for n in nodes])
      fig, ax = plt.subplots()
      pos=nx.get_node_attributes(G,'pos')
-     sc = nx.draw(G,pos,width=0.5,node_color=n_color,cmap='viridis',node_size=5,ax=ax,with_labels=False,edge_color='black')
+     sc = nx.draw(G,pos,width=0.5,node_color=n_color,cmap='jet',node_size=5,ax=ax,with_labels=False,edge_color='black')
      plt.axis([8,16,6,14])
      plt.axis('on')
      plt.grid('false')
-     plt.text(15.5, 5.5, "16", fontsize=10)
-     plt.text(8, 5.5, "8", fontsize=10)
-     plt.text(7.5, 6, "6", fontsize=10)
-     plt.text(7.5, 13.5, "14", fontsize=10)
      ax.set_xlabel('$x$-position',fontsize=8)
      ax.set_ylabel('$y$-position',fontsize=8)
-     cmap=plt.cm.viridis
-     sm = plt.cm.ScalarMappable(cmap=cmap, norm=plt.Normalize(vmin = 2, vmax=6))
+     ax.set_title("{}".format(title),fontsize=10)
+     cmap=plt.cm.jet
+     sm = plt.cm.ScalarMappable(cmap=cmap, norm=plt.Normalize(vmin = 0, vmax=6))
      sm._A = []
-     plt.colorbar(sm)
+     plt.colorbar(sm,values=np.linspace(0, 6, 7))
+     plt.text(17, 6.3, "0", fontsize=12,color="k")
+     plt.text(17, 7.3, "1", fontsize=12,color="k")
+     plt.text(17, 8.5, "2", fontsize=12,color="k")
+     plt.text(17, 9.7, "3", fontsize=12,color="k")
[…]

### 2019-12-31 paper.tex
hice algunas correcciones de estilo

@@
 The evacuation time was defined as the time until 70\% of the pedestrians left the room.
-The different markers correspond to different $k$ values ($i.e$ different body ``stiffness'').
+The different markers correspond to different $k$ values (\textit{i.e.} different body ``stiffness'').
 The crosses correspond to the Helbing original SFM parameter, the up-triangles correspond to the value measured in Ref ..., squares correspond to an absent body force and circles correspond to an extreme value of stiffness (one order of magnitude higher than the original SFM).
@@
 We defined the graph of contacts among individuals.
-In this graph, each node represents a pedestrian and the link between a pair of nodes is settled if the pedestrians are in physical contact ($i.e.$ $r_{ij}<d_{ij}$).\\
+In this graph, each node represents a pedestrian and the link between a pair of nodes is settled if the pedestrians are in physical contact (\textit{i.e.} $r_{ij}<R{ij}$).\\
 
@@
 Fig.~\ref{overlap_vd} shows the overlap as a function of $v_d$.
-The overlap is defined as $d_{ij}-r_{ij}$ where $d_{ij}$ is the sum of radius of particle $i$ and particle $j$ and $r_{ij}$  is the distance between both particles.
+The overlap is defined as $R_{ij}-r_{ij}$ where $R_{ij}$ is the sum of radius of particle $i$ and particle $j$ and $r_{ij}$  is the distance between both particles.
 In the range $v_d \geq 2$~m/s we can see that increasing $v_d$ increases the overlap (for all the $k$ values studied).
@@
 
-In Fig ...
-we show the flow as a function of the global density (fundamental diagram).
-\ref{flow_density_no_body_force} corresponds to non body force ($i.e k_n=0$), \label{flow_density_body_force} corresponds to a body force with $k_n$=1.2~E5.
+In Fig.
+\ref{flow_density} we show the flow as a function of the global density (fundamental diagram).
+\ref{flow_density_no_body_force} corresponds to non body force (\textit{i.e.} $k_n=0$), \label{flow_density_body_force} corresponds to a body force with $k_n$=1.2~E5.
 Each curve correspond to a different friction value.
-The circles correspond to the value of the original SFM ($\\kappa = 2.4~E5$), the "+" symbol correspond to the original value increased by a factor of five and triangles correspond to the original value increased by a factor of ten.
+The circles correspond to the value of the original SFM ($\kappa = 2.4$~E5), the "+" symbol correspond to the original value increased by a factor of five and triangles correspond to the original value increased by a factor of ten.
 \\
@@
 It is worth mentioning that increasing the body force reduces the flow, for a given density and a given friction value (compare \ref{flow_density_no_body_force} with \ref{flow_density_body_force} ).
-In other words, pedestrians walk slower along the corridor if the $k$ value increases ($i.e$ if they are stiffer).
+In other words, pedestrians walk slower along the corridor if the $k$ value increases (\textit{i.e.} if they are stiffer).
 This result is the opposite of what we get in bottleneck geometry since the stiffer the pedestrians the faster they walk.\\
@@
 One way to analyze the clusterization is by creating a network out of the (x,y) positions of the pedestrians.
-In this network, each node represents a pedestrian and there is a link between a pair of nodes $i,j$ if the pair of pedestrians represented by the nodes are touching each other ($i.e.
-d_{ij} \leq R_{ij}$).
+In this network, each node represents a pedestrian and there is a link between a pair of nodes $i,j$ if the pair of pedestrians represented by the nodes are touching each other (\textit{i.e.} $r_{ij} \leq R_{ij}$).
 Once the network is created, it is possible to use the analytical tools that allow describing the configuration such as the mean degree, the distribution of clusters, the shortest path length, etc.\\
@@
 
-The mean overlap increases as the global density increases (see Fig...) and the higher the stiffness the lower the overlap.
+The mean overlap increases as the global density increases (see Fig.
+\ref{overlap_dens}) and the higher the stiffness the lower the overlap.
 This result is similar to the overlap vs.
@@
 As was mentioned above, increasing the $k$ value of the body force increases the stiffness of pedestrians.
-Increasing the stiffness reduces the overlap (both in bottleneck and corridor) and reduces the mean degree in a bottleneck and increases the mean degree in a corridor.
-In fig.
-...
-it shown the network associated with the corridor at a particular timestep ($t=$) and a particular global density.
+Increasing the stiffness reduces the overlap (both in bottleneck and corridor) and reduces the mean degree in a bottleneck but increases the mean degree in a corridor.
+In Fig.\ref{network_corridor} it shown the network associated with the corridor at a particular timestep and a particular global density.
 Fig.
-...
-corresponds to $k=0$ while Fig.
-...
-corresponds to $k=1.2$~E5.
+\ref{network_d6_kn0} corresponds to $k=0$ while Fig.
+\ref{network_d6_knE5} corresponds to $k=1.2$~E5.
 This is an example to show how increasing the stiffness increases the number of contacts between pedestrians.

### 2019-12-31 paper.tex
agregue todos los captions

@@
     \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn1200000.eps}\label{network_vd10_kn1200000}}\\
-\caption[width=0.47\columnwidth]{}
+\caption[width=0.47\columnwidth]{Contact networks of a 225 pedestrian evacuation through a bottleneck.
+The door is placed at $(x,y)=(20,10)$~m, the width of the door is 0.92~m (equivalent to 2 pedestrian's diameter).
+The lines that connect the nodes (pedestrians) represent the contact between them.
+The color represents the degree (the number of pedestrians with which it is connected).
+\ref{network_vd2_kn0} and \ref{network_vd10_kn0} correspond to a simulation without body force with $v_d=$2 and $v_d=$10 respectively.
+\ref{network_vd2_kn1200000} and \ref{network_vd10_kn1200000} correspond to simulations with $k$=1.2~E6 with $v_d=$2 and $v_d=$10 respectively.}
 \label{network_bottleneck}
@@
     \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_bodyforce.eps}\label{flow_density_body_force}}\\
-\caption[width=0.47\columnwidth]{}
+\caption[width=0.47\columnwidth]{Flow vs.
+global density.
+The flow is calculated in a circular area of R=1~m at the center of the corridor.
+The circle corresponds to the original friction of the SFM, the "+" symbol corresponds to the friction increased by a factor of five and the triangles correspond to the friction increased by a factor of ten.
+The desired velocity was $v_d=1$ in all the cases.
+Fig.
+\ref{flow_density_no_body_force} corresponds to simulations without body force and Fig.
+\ref{flow_density_body_force} corresponds to a body force with $k=$1.2~E5.}
 \label{flow_density}
@@
     \subfloat[]{\includegraphics[width=0.45\columnwidth]{./overlap_vs_dens_multi_kn.eps}\label{overlap_dens}}\\
-\caption[width=0.47\columnwidth]{}
+\caption[width=0.47\columnwidth]{\ref{degree_dens} mean degree as a function of the global density for different $k$ values.
+\label{overlap_dens} mean overlap as a function of the global density.
+The mean values are averages over all the pedestrians and over time once the system reaches the stationary state.
+Both measurements correspond to corridor geometry with desired velocity $v_d=1$.}
 \label{network_corridor}
@@
     \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_d6_knE5.eps}\label{network_d6_knE5}}\\
-\caption[width=0.47\columnwidth]{}
+\caption[width=0.47\columnwidth]{Contact network of the pedestrians along the corridor.
+The lines that connect the nodes (pedestrians) represent the contact between them.
+The colors stand for the degree of the node (the number of pedestrians that are in contact with him/her).
+The corridor was 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
+\ref{network_d6_kn0} corresponds to a simulation without body force and \label{network_d6_knE5} corresponds to a simulation with $k=1.2$~E5.}
 \label{network_corridor}
@@
 {./triangles.eps}
-\caption{\label{triangles} }
+\caption{\label{triangles} Triangles per node as a function of the global density.
+A triangle in a network is defined as three nodes all connected.
+Each marker corresponds to a different stiffness $k$ (see the label in the plot).
+The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
+}
 \end{figure}

### 2020-01-01 paper.tex
algunas correcciones de gramatica

@@
 In this section, we present the results corresponding to the bottleneck geometry.
-We show how the overall dynamic of the system changes depending on the $k$ value associated to the body force in the original SFM.\\
+We show the effects of modifying the body force coefficient $k$ in the evacuation dynamics.
+This coefficient is associated with the stiffness of the pedestrians.
+\\
 
 Fig.
-\ref{vd_vs_te} shows the evacuation time as a function of the pedestrian's desired velocity.
-The evacuation time was defined as the time until 70\% of the pedestrians left the room.
+\ref{vd_vs_te} shows the evacuation time as a function of the pedestrian\textsc{\char13}s desired velocity.
+The evacuation time was defined as the time until 80\% of the pedestrians left the room.
 The different markers correspond to different $k$ values (\textit{i.e.} different body ``stiffness'').
-The crosses correspond to the Helbing original SFM parameter, the up-triangles correspond to the value measured in Ref ..., squares correspond to an absent body force and circles correspond to an extreme value of stiffness (one order of magnitude higher than the original SFM).
+The crosses correspond to the Helbing original SFM parameter, the up-triangles correspond to the value measured in Ref ..., squares correspond to zero body force and circles correspond to an extreme value of stiffness (one order of magnitude higher than the original SFM).
 The down triangles correspond to an intermediate value between the empirical value presented in Ref...
@@
 There is a noticeable difference in the evacuation time depending on the $k$ value of the body force.
-The higher the $k$ the smaller the evacuation time, meaning that if pedestrians are stiffer, the overall speed increases (hence the evacuation time decreases).\\
+The higher is $k$ the smaller the evacuation time, meaning that if pedestrians are stiffer, the overall speed increases (hence the evacuation time decreases).\\
 
 The Faster-is-Faster (FIF) is the phenomenon in which under certain conditions, increasing the desired velocity yields to a reduction of the evacuation time.
-The Faster-is-Faster is the opposite effect (the higher $v_d$ the lower the evacuation time).
+The Faster-is-Slower is the opposite effect (the higher $v_d$, the higher the evacuation time).
 Notice that the presence of the Faster-is-Faster (FIF) effect and the Faster-is-Slower are dependent on the value of $k$.
@@
 Network analysis is a set of techniques that characterize the structures in a graph.
-We defined the graph of contacts among individuals.
-In this graph, each node represents a pedestrian and the link between a pair of nodes is settled if the pedestrians are in physical contact (\textit{i.e.} $r_{ij}<R{ij}$).\\
+We defined the contact network where each node represents a pedestrian and the link between a pair of nodes is settled if the pedestrians are in physical contact (\textit{i.e.} $r_{ij} \leq R{ij}$).\\
 
-Fig.~\ref{degree_vd} shows the mean degree of the contact graph as a function of the desired velocity.
+Fig.~\ref{degree_vd} shows the mean degree of the contact network as a function of the desired velocity.
 The degree of a node is defined as the amount of edges assigned to the node.
@@
 For a given $v_d$ the mean degree reduces as the $k$ value increases.
-In other words, the stiffer the pedestrians the less they touch each other.
+In other words, the stiffer the pedestrians are, the less they touch each other.
 We will later discuss that this phenomenon is restricted to the bottleneck geometry that cannot be extrapolated to the corridor geometry.\\
@@
 \caption[width=0.47\columnwidth]{(a) Mean degree as a function of the pedestrian’s desired velocity (m/s).
-(b) Mean overlap as a function of the pedestrian’s desired velocity (m/s).
+(b) Mean overlap as a function of the pedestrians desired velocity.
 Each symbol indicates the $k$ value corresponding to the body force (see the labels).
@@
 \ref{network_vd10_kn1200000} it is clear that increasing the stiffness reduces the degree.
-The most notorious case is the pictures corresponding to $v_d=$10 in which, despite having the same $v_d$, the size of the bulk increases when the pedestrians are stiffer.
+The most notorious case is exhibit in the pictures corresponding to $v_d=$10 in which, despite having the same $v_d$, the size of the bulk increases when the pedestrians are stiffer.
 Moreover, when pedestrians are stiffer they have fewer contacts in general (less degree).
@@
 \caption[width=0.47\columnwidth]{Contact networks of a 225 pedestrian evacuation through a bottleneck.
-The door is placed at $(x,y)=(20,10)$~m, the width of the door is 0.92~m (equivalent to 2 pedestrian's diameter).
+The door is placed at $(x,y)=(20,10)$~m, the width of the door is 0.92~m (equivalent to 2 pedestrian\textsc{\char13}s diameter).
 The lines that connect the nodes (pedestrians) represent the contact between them.
@@
 
-In this section, we present the results corresponding to the corridor geometry.
-We show how the overall dynamic of the system changes depending on the $k$ value associated to the body force in the original SFM.\\
+In this section, we present the results corresponding to the corridor geometry. We show the effects of modifying the body force coefficient $k$ in the dynamics.\\
 
@@
 \ref{flow_density} we show the flow as a function of the global density (fundamental diagram).
-\ref{flow_density_no_body_force} corresponds to non body force (\textit{i.e.} $k_n=0$), \label{flow_density_body_force} corresponds to a body force with $k_n$=1.2~E5.
+\ref{flow_density_no_body_force} corresponds to zero body force (\textit{i.e.} $k_n=0$), \ref{flow_density_body_force} corresponds to a body force with $k_n$=1.2~E5.
 Each curve correspond to a different friction value.
@@
 
-According to most of the empirical measurements, the flow decreases for high enough values of density because the motion becomes jammed.
-Notice that the original friction does not produce a reduction of the flow when there is no body force but when the body force is included (with the original value), the flow reduces from  5 p m$^{-2}$ to 7 p m$^{-2}$ and increases for higher values of density.
-When the density is five times the original value, the flow reduces for densities higher than 5 p m$^{-2}$ in both cases (with body force and without body force).
+According to most of the empirical measurements, the flow decreases for high enough values of density because pedestrians become jammed.
+Notice that the original friction does not produce a reduction of the flow when there is zero body force but when the body force is included (with the original SFM value), the flow reduces from  5 p m$^{-2}$ to 7 p m$^{-2}$ and increases for higher values of density.
+When the friction is five times the original value, the flow reduces for densities higher than 5 p m$^{-2}$ in both cases (with body force and without body force).
 The main qualitative difference is that including the body force produces a subtle increment in the flow for densities higher than 7 p m$^{-2}$.
@@
 In other words, pedestrians walk slower along the corridor if the $k$ value increases (\textit{i.e.} if they are stiffer).
-This result is the opposite of what we get in bottleneck geometry since the stiffer the pedestrians the faster they walk.\\
+This result is the opposite of what we get in bottleneck geometry since in bottleneck, the stiffer the pedestrians are, the faster they walk (and evacuate).\\
 
@@
 The flow is calculated in a circular area of R=1~m at the center of the corridor.
-The circle corresponds to the original friction of the SFM, the "+" symbol corresponds to the friction increased by a factor of five and the triangles correspond to the friction increased by a factor of ten.
+The circular markers correspond to the original friction of the SFM, the "+" symbol corresponds to the friction increased by a factor of five and the triangles correspond to the friction increased by a factor of ten.
 The desired velocity was $v_d=1$ in all the cases.
-Fig.
-\ref{flow_density_no_body_force} corresponds to simulations without body force and Fig.
+Fig.~\ref{flow_density_no_body_force} corresponds to simulations without body force and Fig.
 \ref{flow_density_body_force} corresponds to a body force with $k=$1.2~E5.}
@@
 To understand why in corridor geometry pedestrians walk slower as they become stiffer it is important to take into account that pedestrians walk slower if the friction increases.
-In corridors, the friction increases when pedestrians become stiffer because the crowd tends to cluster more.
-The clusterization means that more pedestrians are touching each other.
+In corridors, the friction increases when pedestrians become stiffer because the crowd tends to be more connected.
+To be more connected means that more pedestrians are touching each other.
 \\
 
-One way to analyze the clusterization is by creating a network out of the (x,y) positions of the pedestrians.
+One way to analyze the increment of connectivity is by creating a network out of the (x,y) positions of the pedestrians.
 In this network, each node represents a pedestrian and there is a link between a pair of nodes $i,j$ if the pair of pedestrians represented by the nodes are touching each other (\textit{i.e.} $r_{ij} \leq R_{ij}$).
-Once the network is created, it is possible to use the analytical tools that allow describing the configuration such as the mean degree, the distribution of clusters, the shortest path length, etc.\\
+Once the network is created, it is possible to use the analytical tools that allow describing the network such as the mean degree, the distribution of clusters, the shortest path length, etc.\\
 
@@
 In the bottleneck geometry, the opposite thing happens, the stiffer the pedestrians the lower the mean degree.
-This is the reason why in bottleneck pedestrians evacuate faster as they become stiffer while in corridor pedestrian's flow is lower as they become stiffer.\\
+This is the reason why in bottleneck pedestrians evacuate faster as they become stiffer while in corridor pedestrian\textsc{\char13}s flow is lower as they become stiffer.\\
 

### 2020-01-01 paper.tex
mas correcciones de gramatica en la parte de resultados

@@
 
-In Fig \ref{degree_dens} we show the mean degree as a function of the global density for different $k$ values.
+Fig.~\ref{degree_dens} shows the mean degree as a function of the global density for different $k$ values.
 When the density is low,  the degree is zero because the pedestrians do not touch each other.
@@
 In the bottleneck geometry, the opposite thing happens, the stiffer the pedestrians the lower the mean degree.
-This is the reason why in bottleneck pedestrians evacuate faster as they become stiffer while in corridor pedestrian\textsc{\char13}s flow is lower as they become stiffer.\\
+This is the reason why in a bottleneck, pedestrians evacuate faster as they become stiffer while in a corridor the pedestrian\textsc{\char13}s flow is lower as they become stiffer.\\
 
@@
 This result is similar to the overlap vs.
-the desired velocity obtained for bottleneck geometry.
-The higher the value of $k$ the higher the repulsion of pedestrian-pedestrian interaction since the body force is acting in the normal direction $n_{ij}$.\\
+desired velocity obtained for bottleneck geometry.
+The higher the value of $k$ the higher the repulsion of the pedestrian-pedestrian interaction since the body force is acting in the normal direction $n_{ij}$.\\
 
@@
     \subfloat[]{\includegraphics[width=0.45\columnwidth]{./overlap_vs_dens_multi_kn.eps}\label{overlap_dens}}\\
-\caption[width=0.47\columnwidth]{\ref{degree_dens} mean degree as a function of the global density for different $k$ values.
-\label{overlap_dens} mean overlap as a function of the global density.
+\caption[width=0.47\columnwidth]{(a) Mean degree as a function of the global density for different $k$ values.
+(b) mean overlap as a function of the global density.
 The mean values are averages over all the pedestrians and over time once the system reaches the stationary state.
@@
 Increasing the stiffness reduces the overlap (both in bottleneck and corridor) and reduces the mean degree in a bottleneck but increases the mean degree in a corridor.
-In Fig.\ref{network_corridor} it shown the network associated with the corridor at a particular timestep and a particular global density.
-Fig.
-\ref{network_d6_kn0} corresponds to $k=0$ while Fig.
+In Fig.~\ref{network_corridor} it shown the contact network corresponding to the corridor at a particular timestep and a particular global density.
+Fig.~\ref{network_d6_kn0} corresponds to $k=0$ while Fig.
 \ref{network_d6_knE5} corresponds to $k=1.2$~E5.
-This is an example to show how increasing the stiffness increases the number of contacts between pedestrians.
+This is an example to show that increasing the stiffness increases the number of contacts between pedestrians (the network connectivity).
 Notice that there are many more pedestrians with degree 6 in the case of $k=1.2$~E5 than the case of $k=0$.
@@
 The corridor was 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
-\ref{network_d6_kn0} corresponds to a simulation without body force and \label{network_d6_knE5} corresponds to a simulation with $k=1.2$~E5.}
+(a) corresponds to a simulation without body force and (b) corresponds to a simulation with $k=1.2$~E5.}
 \label{network_corridor}
@@
 In the corridor geometry, the crowd gets more clusterized if the pedestrians become stiffer.
-We studied the network properties of the contact graph arising from the positions $(x,y)$ of every the pedestrians.
-We found that a good descriptor to exhibit the clusterization is the number of triangles per node.
+We studied the network properties of the contact graph arising from the positions $(x,y)$ of every pedestrian.
+We found that a good descriptor to exhibit the connectivity is the number of triangles per node.
 A triangle is defined as a structure composed of three nodes all in contact with each other.
-In Fig.
-\ref{triangles} we show the triangles per node as a function of the global density for different stiffness values $k$.
+Fig.~\ref{triangles} shows the triangles per node as a function of the global density for different stiffness values $k$.
 This descriptor allows to distinguish states with the same global density but different stiffness levels.
-In other words, it is a descriptor very sensitive to changes in stiffness that allow expressing the degree of clustering of the system even better than the mean degree.
+In other words, it is a descriptor very sensitive to changes in stiffness that allow expressing the connectivity of the system even better than the mean degree.
 \\
 
-This result is consistent with the results obtained in Ref.
-\cite{pugnaloni_2013} where they explore several topological and geometric descriptors capable of properly describing granular systems with different stiffness.
-While our study system is self-propelled, there are analogies with the system studied in Ref.
-Like the authors, we recommend using topological descriptors (in particular triangles per node) to describe systems with equal global density and different stiffness levels.\\
+This result is consistent with the results obtained in Ref.~\cite{pugnaloni_2013} where the authors explore several topological and geometric descriptors capable of properly describing granular systems with different stiffness.
+While our study system is self-propelled, there are analogies with the system studied in Ref.~\cite{pugnaloni_2013} Like the authors, we recommend using topological descriptors (in particular triangles per node) to describe systems with equal global density and different stiffness levels.\\
 

### 2020-01-01 paper.tex
mejore el grafico de degree vs dens y agregue un parrafo en resultados

@@
 The color represents the degree (the number of pedestrians with which it is connected).
-\ref{network_vd2_kn0} and \ref{network_vd10_kn0} correspond to a simulation without body force with $v_d=$2 and $v_d=$10 respectively.
-\ref{network_vd2_kn1200000} and \ref{network_vd10_kn1200000} correspond to simulations with $k$=1.2~E6 with $v_d=$2 and $v_d=$10 respectively.}
+(a) and (b) correspond to a simulation without body force with $v_d=$2 and $v_d=$10 respectively.
+(c) and (d) correspond to simulations with $k$=1.2~E6 with $v_d=$2 and $v_d=$10 respectively.}
 \label{network_bottleneck}
@@
 The desired velocity was $v_d=1$ in all the cases.
-Fig.~\ref{flow_density_no_body_force} corresponds to simulations without body force and Fig.
-\ref{flow_density_body_force} corresponds to a body force with $k=$1.2~E5.}
+(a) corresponds to simulations without body force and (b) corresponds to a body force with $k=$1.2~E5.}
 \label{flow_density}
@@
 As was mentioned above, increasing the $k$ value of the body force increases the stiffness of pedestrians.
-Increasing the stiffness reduces the overlap (both in bottleneck and corridor) and reduces the mean degree in a bottleneck but increases the mean degree in a corridor.
+Increasing the stiffness reduces the overlap (both in bottleneck and corridor).
+Regarding the network connectivity, increasing the stiffness reduces the mean degree in a bottleneck but increases the mean degree in a corridor.
 In Fig.~\ref{network_corridor} it shown the contact network corresponding to the corridor at a particular timestep and a particular global density.
@@
 Notice that there are many more pedestrians with degree 6 in the case of $k=1.2$~E5 than the case of $k=0$.
+\\
+
+This result is exactly the opposite of what we get in the bottleneck.
+This happens because, in the corridor, the lateral walls act like containers that force the pedestrian to increase their contacts.
+Whereas in the bottleneck there are no lateral walls.
+Thus, when increasing the stiffness they have more space to detach from each other, reducing the connectedness (hence reducing the mean degree).
 \\
@@
 
-The increment of the clusterization is responsible for the reduction of the flow.
-In the corridor geometry, the crowd gets more clusterized if the pedestrians become stiffer.
+The increment of the connectedness is responsible for the reduction of the flow.
+In the corridor geometry, the crowd gets more connected if the pedestrians become stiffer.
 We studied the network properties of the contact graph arising from the positions $(x,y)$ of every pedestrian.

### 2020-01-03 paper.tex
quite el titulo de reduced in units
correcciones en bottleneck

@@
 
-In this section, we present the results corresponding to the bottleneck geometry.
-We show the effects of modifying the body force coefficient $k$ in the evacuation dynamics.
-This coefficient is associated with the stiffness of the pedestrians.
+We present in this Section the results corresponding to the bottleneck geometry.
+We show the consequences of modifying the body force coefficient $k$ in the evacuation dynamics.
+Recall that this coefficient is associated with the stiffness of the pedestrians.
 \\
@@
 Fig.
-\ref{vd_vs_te} shows the evacuation time as a function of the pedestrian\textsc{\char13}s desired velocity.
-The evacuation time was defined as the time until 80\% of the pedestrians left the room.
-The different markers correspond to different $k$ values (\textit{i.e.} different body ``stiffness'').
-The crosses correspond to the Helbing original SFM parameter, the up-triangles correspond to the value measured in Ref ..., squares correspond to zero body force and circles correspond to an extreme value of stiffness (one order of magnitude higher than the original SFM).
-The down triangles correspond to an intermediate value between the empirical value presented in Ref...
-and the chosen by Helbing in Ref...\\
-
-There is a noticeable difference in the evacuation time depending on the $k$ value of the body force.
-The higher is $k$ the smaller the evacuation time, meaning that if pedestrians are stiffer, the overall speed increases (hence the evacuation time decreases).\\
-
-The Faster-is-Faster (FIF) is the phenomenon in which under certain conditions, increasing the desired velocity yields to a reduction of the evacuation time.
-The Faster-is-Slower is the opposite effect (the higher $v_d$, the higher the evacuation time).
-Notice that the presence of the Faster-is-Faster (FIF) effect and the Faster-is-Slower are dependent on the value of $k$.
-In Fig.~\ref{vd_vs_te} we can see that $k=1.2$~E5 only exhibits FIS effect for $v_d>$2~m/s.
-When $k=1.2$~E6, the evacuation time reduces as $v_d$ increases, meaning that only FIF is reported.
-The explored values of $k$ that satisfy $k \leq 6$~E4 exhibit both the FIS and the FIF effect depending on the range of desired velocities.
-Notice that the behavior of the case in which $k = 0$ is very similar to the case in which $k = 1.2$~E4.\\
-% se puede discutir que este resultado es importante porque k=1.2E4 es un valor empirico y k=1.2E5 tambien lo es, osea que el FIF podria estar o no estar dependiendo de cual es el verdadero valor de k.
-Habria que chequear en unidades reducidas como queda.
+\ref{vd_vs_te} shows the evacuation time as a function of the pedestrian's desired velocity.
+The evacuation time is defined as the time until 80\% of the pedestrians left the room.
+The different markers correspond to different $k$ values (\textit{i.e.} different body ``stiffness''; see caption for details).
+We will focus on the evacuation time for $v_d>2\,$m/s.\\
 
@@
 The different symbols indicate the $k$ value corresponding to the body force (see the label).
-}
+The crosses correspond to the Helbing original SFM parameter, the up-triangles correspond to the value measured in Ref ..., squares correspond to zero body force and circles correspond to an extreme value of stiffness (one order of magnitude higher than the original SFM).
+The down triangles correspond to an intermediate value between the empirical value presented in Ref...
+and the chosen by Helbing in Ref.~\cite{helbing_2000} }
 \end{figure}
 
-Network analysis is a set of techniques that characterize the structures in a graph.
-We defined the contact network where each node represents a pedestrian and the link between a pair of nodes is settled if the pedestrians are in physical contact (\textit{i.e.} $r_{ij} \leq R{ij}$).\\
+Two behavioral patterns can be seen in Fig.~\ref{vd_vs_te}.
+Whenever the slope is positive it means that the harder the pedestrians try to get out (higher $v_d$), the higher it takes them to evacuate.
+This is the Faster-is-slower (FIS) regime.
+Conversely, the negative slope corresponds to a Faster-is-Faster (FIF) phenomenon (the harder they try, the quicker they leave).
+Fig.~\ref{vd_vs_te} shows a change in the slope sign only for stiffness values below $k=1.2$~E5.
+This mean that ``soft'' individuals are required to attain this behavioral change.
+Notice that for  $k=1.2$~E6 (the stiffest explored pedestrians) no FIS can be seen at all.
+Besides, the evacuation pattern for $k = 0$ and $k = 1.2$~E4 are very similar since the body force is comparable to the social force for these stiffness values.
+\\
+
+Despite the presence of the FIS or FIF phenomenon, the evacuation time at a fixed value of $v_d$ decreases for increasing values of $k$.
+This means that stiffer pedestrians evacuate faster than soft pedestrians.
+In order to investigate this issue, we computed the mean velocity of the whole crowd as a function of the stiffens $k$.
+\textcolor{red}{agregar figura velocidad (k)}.
+\\
+
+The presence of a FIF phenomenon for only (soft individuals) open many questions on the microscopic dynamics of pedestrians.
+We may presume that contacts between pedestrians are quite different for soft individuals than for stiff individuals.
+In order to study the contacts dynamics, regardless of the compression effects, we assimilate the pedestrians as nodes and the whole crowd as a network.
+We set a link between any two individuals if both are in physical contact (\textit{i.e.} $r_{ij} \leq R{ij}$).\\
 
 Fig.~\ref{degree_vd} shows the mean degree of the contact network as a function of the desired velocity.
-The degree of a node is defined as the amount of edges assigned to the node.
+The degree of a node is defined as the number of links that connecting this node to any other node.
 This means, the number of pedestrians that are in physical contact with a given pedestrian.
-The mean degree is the average of the degree over all the nodes (pedestrians) and over the whole sampled time (from the time the system reaches the stationary state to the end of the simulation).\\
+The mean degree is the average of the degree over all the nodes (pedestrians) and over the whole sampled time.
+We report mean values after the system has reached the stationary state, that is, after a well formed bulk has been established.\\
 
-Increasing $v_d$ increases the mean degree in all the cases.
-This happens because increasing $v_d$ produces higher densities that force individuals to touch each other.
-For a given $v_d$ the mean degree reduces as the $k$ value increases.
-In other words, the stiffer the pedestrians are, the less they touch each other.
-We will later discuss that this phenomenon is restricted to the bottleneck geometry that cannot be extrapolated to the corridor geometry.\\
+Increasing $v_d$ increases the mean degree, as expected.
+This occurs because increasing $v_d$ produces higher densities that force individuals to touch each other.
+But surprisingly.
+for a given $v_d$ the mean degree reduces as the $k$ value increases.
+A noticeable decrease of the mean degree can be seen for the highest explored value of $k$.
+We may expect a significant change in the sliding friction due to this fact.\\
 
-Fig.~\ref{overlap_vd} shows the overlap as a function of $v_d$.
-The overlap is defined as $R_{ij}-r_{ij}$ where $R_{ij}$ is the sum of radius of particle $i$ and particle $j$ and $r_{ij}$  is the distance between both particles.
-In the range $v_d \geq 2$~m/s we can see that increasing $v_d$ increases the overlap (for all the $k$ values studied).
-For a given $v_d$, the overlap increases as the $k$ value decreases.
-Reducing $k$ means reducing the normal body force which allows a greater invasion of the personal space of the individuals.\\
+A more detailed insight to the contact dynamics can be acquired from Fig.~\ref{overlap_vd}.
+The overlap between individuals is shown as a function of $v_d$.
+Recall from Section \ref{sfm} that the overlap is defined as $R_{ij}-r_{ij}$ where $R_{ij}$, is the sum of radius of particle $i$ and particle $j$ and $r_{ij}$  is the distance between both particles.
+Except for very low desired velocities (say, $v_d<2\,$m/s), we can see that the mean overlap is an increasing function of $v_d$ (for the studied $k$ values).\\
+
+% Agregar valor de kappa en todos los captions.
 
@@
 
-Increasing the stiffness has a significative impact on the evacuation dynamics.
-It reduces the overlap and reduces the mean degree between pedestrians.
-Both effects tend to reduce the friction in the crowd and the immediate consequence of this is a reduction of the evacuation time (pedestrians escape faster).
-The body force has a notorious impact in the number of pedestrians that each pedestrians touch (degree).
-This is clearly depicted in Fig.
-\ref{network_bottleneck} where four different configurations of the evacuation dynamics are shown.
-The configurations represent 225 pedestrians trying to escape through a 0.92 m door which center is located at $(x,y)=(20,10)$~m.
-The colors correspond to the degree of each node (pedestrian) and the lines between pedestrians represent the contacts among them.\\
+The regime for $v_d<2\,$m/s can be... \textcolor{red}{completar}.\\
 
-The four configurations corresponds to two different $v_d$ and two different $k$ values.
-Fig.
-\ref{network_vd2_kn0} represents $v_d=$2 and $k=0$, Fig.
-\ref{network_vd10_kn0} corresponds to $v_d=$10 and $k=0$ while \ref{network_vd2_kn1200000} and \ref{network_vd10_kn1200000} correspond to $v_d=$2 and $v_d=$10 respectively and both have the same body force coefficient $k=$1.2~E6.
-As expected, increasing the desired velocity compress the crowd towards the exit.
+Besides, for a given $v_d$, the overlap increases as the $k$ value decreases.
+\textcolor{red}{Reducing $k$ means reducing the normal body force which allows a greater invasion of the personal space of the individuals.} The increment in mean overlap, however, seems to be more significant than the mean degree.
 \\
 
-Comparing Fig.
-\ref{network_vd2_kn0} against Fig.
-\ref{network_vd2_kn1200000} and Fig \ref{network_vd10_kn0} against Fig.
-\ref{network_vd10_kn1200000} it is clear that increasing the stiffness reduces the degree.
-The most notorious case is exhibit in the pictures corresponding to $v_d=$10 in which, despite having the same $v_d$, the size of the bulk increases when the pedestrians are stiffer.
-Moreover, when pedestrians are stiffer they have fewer contacts in general (less degree).
-Notice that there are no pedestrians with degree 6 when $k=1.2$~E6 and there are a lot of pedestrians with degree 6 when $k$=0.
+An increase in the body stiffness is expected to impact on the evacuation dynamics.
+The simulations reduction of the overlap and the mean degree between pedestrians, tend to diminish the sliding friction within the crowd.
+Consequently, an enhancement in the evacuation time (pedestrians escape faster) should be observed, as pictured in Fig.~\ref{vd_vs_te}.
+Notice, however, that switching from a FIS regime (positive slope) to a  FIF regime (negative slope) in Fig.~\ref{vd_vs_te} appears as a more complex phenomenon.
+We will focus on this issue in an upcoming investigation.\\
+
+Despite the slidding friction, the body force has a notorious impact in the number of pedestrians touching each other (say, the degree).
+This is clearly depicted in Fig.~\ref{network_bottleneck} where four different configurations of the evacuation dynamics are shown.
+The configurations represent 225 pedestrians trying to escape through a door see caption for details.
+The colors correspond to the degree of each node (pedestrian) and the lines between pedestrians represent the contacts among them.\\
 
@@
 \end{figure}
+
+The four configurations corresponds to two different $v_d$ and two different $k$ values (say, the  minimum and maximum explored values).
+Fig.~\ref{network_vd2_kn0} and Fig.~\ref{network_vd10_kn0} shows a snapshot for $k=$0, at desired velocities of 2$\,$m/s and 10$\,$m/s respectively.
+Fig.~\ref{network_vd2_kn1200000} and Fig.~\ref{network_vd10_kn1200000} show similar situations, but for  $k=$1.2$\,$E6.
+As expected, increasing the desired velocity compresses the crowd towards the exit.
+\\
+
+The four snapshots in \ref{network_bottleneck} comfirm (visually) the fact that more rigid bodies releases the crowd environment, widening the occupied region.
+At $v_d=10\,$m/s (the maximum explored velocity), it can hardly be found pedestians with degree 6 when $k=1.2\,$E6, while a lot of them are present for $k$=0.
 

### 2020-01-03 paper.tex
agregue el recordatorio de escribir una conclusion al final de bottleneck

@@
 The four snapshots in \ref{network_bottleneck} comfirm (visually) the fact that more rigid bodies releases the crowd environment, widening the occupied region.
-At $v_d=10\,$m/s (the maximum explored velocity), it can hardly be found pedestians with degree 6 when $k=1.2\,$E6, while a lot of them are present for $k$=0.
+At $v_d=10\,$m/s (the maximum explored velocity), it can hardly be found pedestians with degree 6 when $k=1.2\,$E6, while a lot of them are present for $k$=0.\\
+
+\textcolor{red}{Agregar una conclusion}
 

### 2020-01-09 paper.tex
algunas mejoras en la parte de bottleneck

@@
 In order to investigate this issue, we computed the mean velocity of the whole crowd as a function of the stiffens $k$.
-\textcolor{red}{agregar figura velocidad (k)}.
+Fig.~\ref{kn_vs_vx_bottleneck} shows the mean velocity in the x-direction as a function of the stiffness $k$ for three different desired velocities.
+In all cases, the velocity increases with the stiffness.
+From $k_n=0$ to $k_n=$1.2~E4 the increment of velocity is not as significative as it is for higher $k_n$.
 \\
+
+\begin{figure}[!htbp]
+\centering
+    \subfloat[]{\includegraphics[width=0.7\columnwidth]{./kn_vs_vx_bottleneck.eps}\label{kn_vs_vx_bottleneck}}\\
+\caption[width=0.47\columnwidth]{}
+\end{figure}
 
@@
 
-The regime for $v_d<2\,$m/s can be... \textcolor{red}{completar}.\\
+The regime for $v_d<2\,$m/s is different from the rest since most of the pedestrians are not touching each other.
+The only pedestrians who touch each other are the ones who are being re-injected in the room.
+The overlap is higher than, for example, $v_d=3\,$m/s because of the pedestrians who are re-injected bump against the bulk.
+\\
 
 Besides, for a given $v_d$, the overlap increases as the $k$ value decreases.
-\textcolor{red}{Reducing $k$ means reducing the normal body force which allows a greater invasion of the personal space of the individuals.} The increment in mean overlap, however, seems to be more significant than the mean degree.
+Reducing $k$ means reducing the normal body force which allows a greater invasion of the personal space of the individuals ( this means more overlap between pedestrians).
+The increment in mean overlap, however, seems to be more significant than the mean degree.
 \\

### 2020-01-09 paper.tex
agregue mini conclusion en la parte de bottleneck

@@
  \hline
- $\tau$[s]   & $m$[kg]     & $v_d$[m/s]  &  $B$[m]  & $k$[kg/s$^2$] &  Refs. \\
+ $\tau$[s]   & $m$[kg]     & $v_d$[m/s]  &  $B$[m]  & $k_n$[kg/s$^2$] &  Refs. \\
  \hline
@@
 The reports from Refs.~\cite{seyfried_2007,weidmann_1992} do not include any 
-values for the compressibility $k$ since these experiments were carried out 
+values for the compressibility $k_n$ since these experiments were carried out 
 under low density conditions. Notice that the minimum (perceived) step distance 
@@
 desired speed and the body compresibility could be achieved. The reported 
-magnitude $k$ assesses either the clothes and the body compressibility. The 
+magnitude $k_n$ assesses either the clothes and the body compressibility. The 
 final value, though, is linearly related to the compression $x$. \\
@@
 The maximum (realistic) compressions may be computed from the relation 
-$F=k(x)\,x$ and the compressibility $k(x)$ reported in Table~\ref{table_data}. 
+$F=k(x)\,x$ and the compressibility $k_n(x)$ reported in Table~\ref{table_data}. 
 An ``uncomfortable'' body force of $30\,$N can address compressions in the 
@@
 compressions between $0.045$ and $0.065\,$m. Thus, according to 
-Table~\ref{table_data}, we may expect experimental values for $k(x)$ up to 
+Table~\ref{table_data}, we may expect experimental values for $k_n(x)$ up to 
 $1000\,$kg/s$^2$ (for $F=30\,$N), or, up to $1400\,$kg/s$^2$ (for $F=60\,$N). \\
@@
 linearly related to the difference between the (tangential) velocities. The 
-coefficients $\kappa$ (for the sliding friction) and $k$ (for the 
+coefficients $\kappa$ (for the sliding friction) and $k_n$ (for the 
 body force) are supposed to be related to the areas of contact and the clothes 
@@
 We stress that the expression (\ref{eqn_friction}) assumes fixed values for 
-$\kappa$ and $k$. This may not be completely true according to 
+$\kappa$ and $k_n$. This may not be completely true according to 
 Table~\ref{table_data}. The local density (and thus, the pedestrians' 
-compression) may affect the compressibility parameter $k$ by more than an order 
-of magnitude. We will vary $k$ (and $\kappa$) in order to explore this 
+compression) may affect the compressibility parameter $k_n$ by more than an order 
+of magnitude. We will vary $k_n$ (and $\kappa$) in order to explore this 
 phenomenon. \\
@@
 environment). The presence of the body force moves the dynamics to a more 
-complex context. We will investigate this context in Section~\ref{results}. \\
+complex context. We will investigate this context in section~\ref{results}. \\
 
@@
 
-We present in this Section the results corresponding to the bottleneck geometry.
-We show the consequences of modifying the body force coefficient $k$ in the evacuation dynamics.
+We present in this section the results corresponding to the bottleneck geometry.
+We show the consequences of modifying the body force coefficient $k_n$ in the evacuation dynamics.
 Recall that this coefficient is associated with the stiffness of the pedestrians.
@@
 
-Fig.
-\ref{vd_vs_te} shows the evacuation time as a function of the pedestrian's desired velocity.
+Fig.~\ref{vd_vs_te} shows the evacuation time as a function of the pedestrian's desired velocity.
 The evacuation time is defined as the time until 80\% of the pedestrians left the room.
-The different markers correspond to different $k$ values (\textit{i.e.} different body ``stiffness''; see caption for details).
-We will focus on the evacuation time for $v_d>2\,$m/s.\\
+The different markers correspond to different $k_n$ values (\textit{i.e.} different body ``stiffness''; see caption for details).
+In this section we will focus on the evacuation time for $v_d>2\,$m/s.\\
 
@@
 Each process was finished when 158 pedestrians left the room.
-The different symbols indicate the $k$ value corresponding to the body force (see the label).
-The crosses correspond to the Helbing original SFM parameter, the up-triangles correspond to the value measured in Ref ..., squares correspond to zero body force and circles correspond to an extreme value of stiffness (one order of magnitude higher than the original SFM).
-The down triangles correspond to an intermediate value between the empirical value presented in Ref...
-and the chosen by Helbing in Ref.~\cite{helbing_2000} }
+The different symbols indicate the $k_n$ value corresponding to the body force (see the label).
+The crosses correspond to the Helbing original SFM parameter, the up-triangles correspond to the value measured in Ref.~\cite{gordon1989anthropometric}, squares correspond to zero body force and circles correspond to an extreme value of stiffness (one order of magnitude higher than the original SFM).
+The down triangles correspond to an intermediate value between the empirical value presented in Ref.~\cite{gordon1989anthropometric} and the chosen by Helbing in Ref.~\cite{helbing_2000} }
 \end{figure}
@@
 Two behavioral patterns can be seen in Fig.~\ref{vd_vs_te}.
-Whenever the slope is positive it means that the harder the pedestrians try to get out (higher $v_d$), the higher it takes them to evacuate.
+Whenever the slope is positive, it means that the harder the pedestrians trying to get out (higher $v_d$), the higher it takes them to evacuate.
 This is the Faster-is-slower (FIS) regime.
@@
 Fig.~\ref{vd_vs_te} shows a change in the slope sign only for stiffness values below $k=1.2$~E5.
-This mean that ``soft'' individuals are required to attain this behavioral change.
-Notice that for  $k=1.2$~E6 (the stiffest explored pedestrians) no FIS can be seen at all.
-Besides, the evacuation pattern for $k = 0$ and $k = 1.2$~E4 are very similar since the body force is comparable to the social force for these stiffness values.
+This means that ``soft'' individuals are required to attain this behavioral change.
+Notice that for  $k_n=1.2$~E6 (the stiffest explored pedestrians), no FIS can be seen at all.
+Besides, the evacuation pattern for $k_n = 0$ and $k_n = 1.2$~E4 are very similar since the body force is comparable to the social force for these stiffness values.
 \\
 
-Despite the presence of the FIS or FIF phenomenon, the evacuation time at a fixed value of $v_d$ decreases for increasing values of $k$.
+Despite the presence of the FIS or FIF phenomenon, the evacuation time at a fixed value of $v_d$ decreases for increasing values of $k_n$.
 This means that stiffer pedestrians evacuate faster than soft pedestrians.
-In order to investigate this issue, we computed the mean velocity of the whole crowd as a function of the stiffens $k$.
-Fig.~\ref{kn_vs_vx_bottleneck} shows the mean velocity in the x-direction as a function of the stiffness $k$ for three different desired velocities.
+To investigate this issue, we computed the mean velocity of the whole crowd as a function of the stiffens $k_n$.
+Fig.~\ref{kn_vs_vx_bottleneck} shows the mean velocity in the x-direction as a function of the stiffness $k_n$ for three different desired velocities.
 In all cases, the velocity increases with the stiffness.
@@
 \centering
-    \subfloat[]{\includegraphics[width=0.7\columnwidth]{./kn_vs_vx_bottleneck.eps}\label{kn_vs_vx_bottleneck}}\\
-\caption[width=0.47\columnwidth]{}
+    \subfloat[]{\includegraphics[width=0.7\columnwidth]{./kn_vs_vx_bottleneck.eps}}\\
+\caption[width=0.47\columnwidth]{Mean velocity in the x-direction as a function of the stiffness level $k_n$ for different desired velocities (see label).
+The data corresponds to a bottleneck with periodic boundary conditions (re-injecting pedestrians).
+The average was taken every two seconds once the crowd reaches the stationary state ($t=$20~s) until the end of the simulation ($t=$110~s).
+}
+\label{kn_vs_vx_bottleneck}
 \end{figure}
 
-The presence of a FIF phenomenon for only (soft individuals) open many questions on the microscopic dynamics of pedestrians.
+The presence of a FIF phenomenon only for soft individuals opens many questions on the microscopic dynamics of pedestrians.
 We may presume that contacts between pedestrians are quite different for soft individuals than for stiff individuals.
-In order to study the contacts dynamics, regardless of the compression effects, we assimilate the pedestrians as nodes and the whole crowd as a network.
+To study the dynamics of the contact, regardless of the compression effects, we assimilate the pedestrians as nodes and the whole crowd as a network.
 We set a link between any two individuals if both are in physical contact (\textit{i.e.} $r_{ij} \leq R{ij}$).\\
@@
 Fig.~\ref{degree_vd} shows the mean degree of the contact network as a function of the desired velocity.
-The degree of a node is defined as the number of links that connecting this node to any other node.
+The degree of a node is defined as the number of links that connect this node to any other node.
 This means, the number of pedestrians that are in physical contact with a given pedestrian.
 The mean degree is the average of the degree over all the nodes (pedestrians) and over the whole sampled time.
-We report mean values after the system has reached the stationary state, that is, after a well formed bulk has been established.\\
+We report mean values after the system has reached the stationary state, that is after a well-formed bulk has been established.\\
 
@@
 This occurs because increasing $v_d$ produces higher densities that force individuals to touch each other.
-But surprisingly.
-for a given $v_d$ the mean degree reduces as the $k$ value increases.
-A noticeable decrease of the mean degree can be seen for the highest explored value of $k$.
+But surprisingly, for a given $v_d$, the mean degree reduces as the $k_n$ value increases.
+A noticeable decrease in the mean degree can be seen for the highest explored value of $k_n$.
 We may expect a significant change in the sliding friction due to this fact.\\
 
-A more detailed insight to the contact dynamics can be acquired from Fig.~\ref{overlap_vd}.
+A more detailed insight into the contact dynamics can be acquired from Fig.~\ref{overlap_vd}.
 The overlap between individuals is shown as a function of $v_d$.
-Recall from Section \ref{sfm} that the overlap is defined as $R_{ij}-r_{ij}$ where $R_{ij}$, is the sum of radius of particle $i$ and particle $j$ and $r_{ij}$  is the distance between both particles.
-Except for very low desired velocities (say, $v_d<2\,$m/s), we can see that the mean overlap is an increasing function of $v_d$ (for the studied $k$ values).\\
+Recall from section \ref{sfm} that the overlap is defined as $R_{ij}-r_{ij}$ where $R_{ij}$, is the sum of radius of particle $i$ and particle $j$ and $r_{ij}$  is the distance between both particles.
+Except for very low desired velocities (say, $v_d<2\,$m/s), we can see that the mean overlap is an increasing function of $v_d$ (for the studied $k_n$ values).\\
 
@@
 (b) Mean overlap as a function of the pedestrians desired velocity.
-Each symbol indicates the $k$ value corresponding to the body force (see the labels).
+Each symbol indicates the $k_n$ value corresponding to the body force (see the labels).
 The data corresponds to a bottleneck with periodic boundary conditions (re-injecting pedestrians).
@@
 
-Besides, for a given $v_d$, the overlap increases as the $k$ value decreases.
-Reducing $k$ means reducing the normal body force which allows a greater invasion of the personal space of the individuals ( this means more overlap between pedestrians).
+Besides, for a given $v_d$, the overlap increases as the $k_n$ value decreases.
+Reducing $k_n$ means reducing the normal body force, which allows a more significant invasion of the personal space of the individuals ( this means more overlap between pedestrians).
 The increment in mean overlap, however, seems to be more significant than the mean degree.
@@
 
-An increase in the body stiffness is expected to impact on the evacuation dynamics.
+Increasing body stiffness has a significant impact on evacuation dynamics.
 The simulations reduction of the overlap and the mean degree between pedestrians, tend to diminish the sliding friction within the crowd.
-Consequently, an enhancement in the evacuation time (pedestrians escape faster) should be observed, as pictured in Fig.~\ref{vd_vs_te}.
+Consequently, an enhancement in the evacuation time (pedestrians escape faster) is observed, as pictured in Fig.~\ref{vd_vs_te}.
 Notice, however, that switching from a FIS regime (positive slope) to a  FIF regime (negative slope) in Fig.~\ref{vd_vs_te} appears as a more complex phenomenon.
@@
 
-Despite the slidding friction, the body force has a notorious impact in the number of pedestrians touching each other (say, the degree).
+Despite the sliding friction, the body force has a notorious impact in the number of pedestrians touching each other (say, the degree).
 This is clearly depicted in Fig.~\ref{network_bottleneck} where four different configurations of the evacuation dynamics are shown.
-The configurations represent 225 pedestrians trying to escape through a door see caption for details.
-The colors correspond to the degree of each node (pedestrian) and the lines between pedestrians represent the contacts among them.\\
+The configurations represent 225 pedestrians trying to escape through a door see the caption for details.
+The colors correspond to the degree of each node (pedestrian), and the lines between pedestrians represent the contacts among them.\\
 
@@
 (a) and (b) correspond to a simulation without body force with $v_d=$2 and $v_d=$10 respectively.
-(c) and (d) correspond to simulations with $k$=1.2~E6 with $v_d=$2 and $v_d=$10 respectively.}
+(c) and (d) correspond to simulations with $k_n$=1.2~E6 with $v_d=$2 and $v_d=$10 respectively.}
 \label{network_bottleneck}
@@
 
-The four configurations corresponds to two different $v_d$ and two different $k$ values (say, the  minimum and maximum explored values).
-Fig.~\ref{network_vd2_kn0} and Fig.~\ref{network_vd10_kn0} shows a snapshot for $k=$0, at desired velocities of 2$\,$m/s and 10$\,$m/s respectively.
-Fig.~\ref{network_vd2_kn1200000} and Fig.~\ref{network_vd10_kn1200000} show similar situations, but for  $k=$1.2$\,$E6.
+The four configurations corresponds to two different $v_d$ and two different $k_n$ values (say, the  minimum and maximum explored values).
+Fig.~\ref{network_vd2_kn0} and Fig.~\ref{network_vd10_kn0} shows a snapshot for $k_n=$0, at desired velocities of 2$\,$m/s and 10$\,$m/s respectively.
+Fig.~\ref{network_vd2_kn1200000} and Fig.~\ref{network_vd10_kn1200000} show similar situations, but for  $k_n=$1.2$\,$E6.
 As expected, increasing the desired velocity compresses the crowd towards the exit.
@@
 
-The four snapshots in \ref{network_bottleneck} comfirm (visually) the fact that more rigid bodies releases the crowd environment, widening the occupied region.
-At $v_d=10\,$m/s (the maximum explored velocity), it can hardly be found pedestians with degree 6 when $k=1.2\,$E6, while a lot of them are present for $k$=0.\\
+The four snapshots in Fig.~\ref{network_bottleneck} confirm (visually) the fact that more rigid pedestrians release the crowded environment, widening the occupied region.
+At $v_d=10\,$m/s (the maximum explored velocity), it can hardly be found pedestrians with degree 6 when $k_n=1.2\,$E6, while a lot of them are present for $k_n$=0.\\
 
-\textcolor{red}{Agregar una conclusion}
+To conclude this section, we want to emphasize that increasing body stiffness has a significant impact on the evacuation dynamics.
+The stiffer pedestrians are, the less they touch to each other (less degree and less overlap).
+This yields a reduction of an increment of the speed, which reduces the evacuation time.
+\\
 
@@
 
-In this section, we present the results corresponding to the corridor geometry. We show the effects of modifying the body force coefficient $k$ in the dynamics.\\
+In this section, we present the results corresponding to the corridor geometry. We show the effects of modifying the body force coefficient $k_n$ in the dynamics.\\
 
@@
 It is worth mentioning that increasing the body force reduces the flow, for a given density and a given friction value (compare \ref{flow_density_no_body_force} with \ref{flow_density_body_force} ).
-In other words, pedestrians walk slower along the corridor if the $k$ value increases (\textit{i.e.} if they are stiffer).
+In other words, pedestrians walk slower along the corridor if the $k_n$ value increases (\textit{i.e.} if they are stiffer).
 This result is the opposite of what we get in bottleneck geometry since in bottleneck, the stiffer the pedestrians are, the faster they walk (and evacuate).\\
@@
 The desired velocity was $v_d=1$ in all the cases.
-(a) corresponds to simulations without body force and (b) corresponds to a body force with $k=$1.2~E5.}
+(a) corresponds to simulations without body force and (b) corresponds to a body force with $k_n=$1.2~E5.}
 \label{flow_density}
@@
 
-Fig.~\ref{degree_dens} shows the mean degree as a function of the global density for different $k$ values.
+Fig.~\ref{degree_dens} shows the mean degree as a function of the global density for different $k_n$ values.
 When the density is low,  the degree is zero because the pedestrians do not touch each other.
@@
 desired velocity obtained for bottleneck geometry.
-The higher the value of $k$ the higher the repulsion of the pedestrian-pedestrian interaction since the body force is acting in the normal direction $n_{ij}$.\\
+The higher the value of $k_n$ the higher the repulsion of the pedestrian-pedestrian interaction since the body force is acting in the normal direction $n_{ij}$.\\
 
@@
     \subfloat[]{\includegraphics[width=0.45\columnwidth]{./overlap_vs_dens_multi_kn.eps}\label{overlap_dens}}\\
-\caption[width=0.47\columnwidth]{(a) Mean degree as a function of the global density for different $k$ values.
+\caption[width=0.47\columnwidth]{(a) Mean degree as a function of the global density for different $k_n$ values.
 (b) mean overlap as a function of the global density.
@@
 
-As was mentioned above, increasing the $k$ value of the body force increases the stiffness of pedestrians.
+As was mentioned above, increasing the $k_n$ value of the body force increases the stiffness of pedestrians.
 Increasing the stiffness reduces the overlap (both in bottleneck and corridor).
@@
 In Fig.~\ref{network_corridor} it shown the contact network corresponding to the corridor at a particular timestep and a particular global density.
-Fig.~\ref{network_d6_kn0} corresponds to $k=0$ while Fig.
-\ref{network_d6_knE5} corresponds to $k=1.2$~E5.
+Fig.~\ref{network_d6_kn0} corresponds to $k_n=0$ while Fig.
+\ref{network_d6_knE5} corresponds to $k_n=1.2$~E5.
 This is an example to show that increasing the stiffness increases the number of contacts between pedestrians (the network connectivity).
-Notice that there are many more pedestrians with degree 6 in the case of $k=1.2$~E5 than the case of $k=0$.
+Notice that there are many more pedestrians with degree 6 in the case of $k_n=1.2$~E5 than the case of $k_n=0$.
 \\
@@
 The corridor was 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
-(a) corresponds to a simulation without body force and (b) corresponds to a simulation with $k=1.2$~E5.}
+(a) corresponds to a simulation without body force and (b) corresponds to a simulation with $k_n=1.2$~E5.}
 \label{network_corridor}
@@
 A triangle is defined as a structure composed of three nodes all in contact with each other.
-Fig.~\ref{triangles} shows the triangles per node as a function of the global density for different stiffness values $k$.
+Fig.~\ref{triangles} shows the triangles per node as a function of the global density for different stiffness values $k_n$.
 This descriptor allows to distinguish states with the same global density but different stiffness levels.
@@
 A triangle in a network is defined as three nodes all connected.
-Each marker corresponds to a different stiffness $k$ (see the label in the plot).
+Each marker corresponds to a different stiffness $k_n$ (see the label in the plot).
 The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
@@
 
-The SFM description in Section~\ref{sfm} introduces seven parameters ($m$, 
-$\tau$, $v_d$, $B$, $A$, $\kappa$ and $k$) attaining for the ``individual'' 
+The SFM description in section~\ref{sfm} introduces seven parameters ($m$, 
+$\tau$, $v_d$, $B$, $A$, $\kappa$ and $k_n$) attaining for the ``individual'' 
 behavior of each pedestrian. The collective dynamic, however, requires a 
@@
 explanation on the meaning  of the set 
-($\mathcal{A}$,$\mathcal{K}$,$\mathcal{K}_c$) see Section~\ref{parameters}. \\
+($\mathcal{A}$,$\mathcal{K}$,$\mathcal{K}_c$) see section~\ref{parameters}. \\
 

### 2020-01-09 plots/bottleneck/k_vs_vx/plot_k_vs_vx.py

@@ -1,0 +1,76 @@
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+import pandas as pd
+#import numarray
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+###  DATA  ###
+data_vd2 = pd.read_csv("k_vs_vx_vd2.txt",sep="\t")
+k_vd2 = data_vd2["k"].tolist()
+mean_vx_vd2 = data_vd2["mean vx"].tolist()
+std_vx_vd2 = data_vd2["std vx"].tolist()
+
+data_vd4 = pd.read_csv("k_vs_vx_vd4.txt",sep="\t")
+k_vd4 = data_vd4["k"].tolist()
+mean_vx_vd4 = data_vd4["mean vx"].tolist()
+std_vx_vd4 = data_vd4["std vx"].tolist()
+
+data_vd6 = pd.read_csv("k_vs_vx_vd6.txt",sep="\t")
+k_vd6 = data_vd6["k"].tolist()
+mean_vx_vd6 = data_vd6["mean vx"].tolist()
+std_vx_vd6 = data_vd6["std vx"].tolist()
+
+data_vd8 = pd.read_csv("k_vs_vx_vd8.txt",sep="\t")
[…]

### 2020-01-09 plots/bottleneck/network_config/plot_config_graph.py
reemplace k por kn en la parte de bottleneck

@@ -160,9 +160,9 @@ def main():
 
      ############# PARAMETERS #############
      #1200000
-     input_filename = 'config_bottleneck_vd2_k0'
-     output_filename = 'network_vd2_kn0'
-     title = "$v_d=$2 m~s$^{-1}$ \hspace{0.5cm} $k=$0"
+     input_filename = 'config_bottleneck_vd2_k1200000'
+     output_filename = 'network_vd2_kn1200000'
+     title = "$v_d=$2 m~s$^{-1}$ \hspace{0.5cm} $k_n=$1.2~E6"
      time = 100
      sum_rads = 0.46
      ######################################

### 2020-01-09 plots/bottleneck/overlap_vs_vd/plot_comp_vs_vd.py

@@ -70,19 +70,19 @@ std_comp_knE6 = data_knE6["list_std_overlap"].tolist()
 
 fig, ax1 = plt.subplots()
 
-plt.plot(vd_kn0,mean_comp_kn0,'-cs',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k=0$') 
+plt.plot(vd_kn0,mean_comp_kn0,'-cs',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=0$') 
 #plt.errorbar(density_kn_kt,flow_kn_kt, yerr=std_flow_kn_kt,color='y')
 
-plt.plot(vd_knE4,mean_comp_knE4,'-y^',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k=1.2$~E4') 
+plt.plot(vd_knE4,mean_comp_knE4,'-y^',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=1.2$~E4') 
 #plt.errorbar(density_kn_kt,flow_kn_kt, yerr=std_flow_kn_kt,color='y')
 
-plt.plot(vd_knx5,mean_comp_knx5,'-rv',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k=6$~E4') 
+plt.plot(vd_knx5,mean_comp_knx5,'-rv',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=6$~E4') 
 #plt.errorbar(density_kn_kt,flow_kn_kt, yerr=std_flow_kn_kt,color='y')
 
-plt.plot(vd_knE5,mean_comp_knE5,'-bx',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k=1.2$~E5') 
+plt.plot(vd_knE5,mean_comp_knE5,'-bx',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=1.2$~E5') 
 #plt.errorbar(density_kn_kt,flow_kn_kt, yerr=std_flow_kn_kt,color='y')
 
-plt.plot(vd_knE6,mean_comp_knE6,'-ko',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k=1.2$~E6') 
[…]

### 2020-01-09 plots/corridor/degree_vs_density/plot_degree_vs.py

@@ -65,7 +65,7 @@ plt.plot(vd_knE6,mean_degree_knE6,'-ko',mew=0.7,markeredgecolor='k',markersize=3
 
 pylab.grid(False)
 pylab.xlabel('density~(p m$^{-2})$')
-pylab.ylabel('Mean degree~(m)')
+pylab.ylabel('Mean degree')
 plt.ylim(0.0,6.1)
 lgd=plt.legend(numpoints=1,handlelength=0.8) 
 plt.legend(frameon=False,loc='best',labelspacing=0.2,borderpad=0.3,handletextpad=0.5,fontsize=7,numpoints=1) 

### 2020-01-09 plots/corridor/fundamental_diagram/kn0/flow_density_multi.py

@@ -108,13 +108,14 @@ plt.plot(density_kn0_ktx10,speed_kn0_ktx10,'g-^',mew=0.7,markerfacecolor='g',mar
 pylab.grid(False)
 pylab.xlabel('Density~(p~m$^{-2}$)')
 pylab.ylabel('Flow~(p~m$^{-1}$s$^{-1}$)')
+
 #pylab.ylabel('Speed~(m s$^{-1}$)')
 #pylab.legend()
 pylab.ylim(0.0,6)
 #pylab.xlim(1.0, 10)
 #pylab.yticks(np.arange(3,11,2))
 #pylab.xticks(np.arange(0,1100,200))
-#pylab.title("$k_n=$0")
+pylab.title("$k_n=$0")
 lgd=plt.legend(numpoints=1,handlelength=0.8) 
 plt.legend(frameon=False,loc='upper left',labelspacing=0.2,borderpad=0.3,handletextpad=0.5,fontsize=7,numpoints=1) 
 pylab.savefig('flow-density_multifric_nobodyforce.png', format='png', dpi=300, bbox_inches='tight')

### 2020-01-09 plots/corridor/fundamental_diagram/knE5/flow_density_multi.py

@@ -119,7 +119,7 @@ pylab.ylim(0.0,6)
 #pylab.xlim(1.0, 10)
 #pylab.yticks(np.arange(3,11,2))
 #pylab.xticks(np.arange(0,1100,200))
-#pylab.title("$k_n=$0")
+pylab.title("$k_n=$1.2~E5")
 lgd=plt.legend(numpoints=1,handlelength=0.8) 
 plt.legend(frameon=False,loc='upper left',labelspacing=0.2,borderpad=0.3,handletextpad=0.5,fontsize=7,numpoints=1) 
 pylab.savefig('flow-density_multifric_comp.png', format='png', dpi=300, bbox_inches='tight')

### 2020-01-09 plots/bottleneck/degree_vs_vd/plot_degree_vs.py
agrego archivos que faltaban subir

@@ -63,11 +63,11 @@ std_comp_knE6 = data_knE6["list_std_degree"].tolist()
 ###  PLOT  ###
 fig, ax1 = plt.subplots()
 
-plt.plot(vd_kn0,mean_comp_kn0,'-cs',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k=0$') 
-plt.plot(vd_knE4,mean_comp_knE4,'-y^',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$k=1.2$ E4') 
-plt.plot(vd_kn6E4,mean_comp_kn6E4,'-rv',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$k=6$ E4') 
-plt.plot(vd_kn,mean_comp_kn,'-bx',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$k=1.2$ E5') 
-plt.plot(vd_knE6,mean_comp_knE6,'-ko',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$k=1.2$ E6') 
+plt.plot(vd_kn0,mean_comp_kn0,'-cs',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=0$') 
+plt.plot(vd_knE4,mean_comp_knE4,'-y^',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$k_n=1.2$ E4') 
+plt.plot(vd_kn6E4,mean_comp_kn6E4,'-rv',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$k_n=6$ E4') 
+plt.plot(vd_kn,mean_comp_kn,'-bx',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$k_n=1.2$ E5') 
+plt.plot(vd_knE6,mean_comp_knE6,'-ko',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$k_n=1.2$ E6') 
 
 pylab.grid(False)
 pylab.xlabel('$v_d$~(m~s$^{-1})$')

### 2020-01-10 paper.tex
modificaciones en corridor + agregue grafico para corridor

@@
 \ref{flow_density} we show the flow as a function of the global density (fundamental diagram).
-\ref{flow_density_no_body_force} corresponds to zero body force (\textit{i.e.} $k_n=0$), \ref{flow_density_body_force} corresponds to a body force with $k_n$=1.2~E5.
-Each curve correspond to a different friction value.
-The circles correspond to the value of the original SFM ($\kappa = 2.4$~E5), the "+" symbol correspond to the original value increased by a factor of five and triangles correspond to the original value increased by a factor of ten.
-\\
+\ref{flow_density_no_body_force} corresponds to zero body force (\textit{i.e.} $k_n=0$), Fig.~\ref{flow_density_body_force} corresponds to a body force with $k_n$=1.2~E5.
+Each curve correspond to a different friction value (see the caption).\\
 
-According to most of the empirical measurements, the flow decreases for high enough values of density because pedestrians become jammed.
+According to most of the empirical measurements, the flow decreases for high enough values of density because the crowd becomes jammed.
 Notice that the original friction does not produce a reduction of the flow when there is zero body force but when the body force is included (with the original SFM value), the flow reduces from  5 p m$^{-2}$ to 7 p m$^{-2}$ and increases for higher values of density.
@@
 This result suggests that even including the body force, the original SFM requires an increment of the friction in order to reproduce the flow reduction reported in empirical measurements.\\
-
-It is worth mentioning that increasing the body force reduces the flow, for a given density and a given friction value (compare \ref{flow_density_no_body_force} with \ref{flow_density_body_force} ).
-In other words, pedestrians walk slower along the corridor if the $k_n$ value increases (\textit{i.e.} if they are stiffer).
-This result is the opposite of what we get in bottleneck geometry since in bottleneck, the stiffer the pedestrians are, the faster they walk (and evacuate).\\
 
@@
 
-To understand why in corridor geometry pedestrians walk slower as they become stiffer it is important to take into account that pedestrians walk slower if the friction increases.
-In corridors, the friction increases when pedestrians become stiffer because the crowd tends to be more connected.
-To be more connected means that more pedestrians are touching each other.
-\\
-
-One way to analyze the increment of connectivity is by creating a network out of the (x,y) positions of the pedestrians.
-In this network, each node represents a pedestrian and there is a link between a pair of nodes $i,j$ if the pair of pedestrians represented by the nodes are touching each other (\textit{i.e.} $r_{ij} \leq R_{ij}$).
-Once the network is created, it is possible to use the analytical tools that allow describing the network such as the mean degree, the distribution of clusters, the shortest path length, etc.\\
-
+In the same way as with the bottleneck geometry, we computed the contact network to study the topological differences that arise from increasing the $k_n$ value.
 Fig.~\ref{degree_dens} shows the mean degree as a function of the global density for different $k_n$ values.
@@
 As the density increases, the mean degree increases too until reaching an asymptotic behavior in degree six.
-When the degree is six, it corresponds to the densest packing possible for identical hard circles, the result is a hexagonal packing arrangement.\\
+Degree six, corresponds to the densest packing possible for identical hard circles, the result is a hexagonal packing arrangement.\\
 
@@
 \ref{degree_dens} for a given value of density, the stiffer the pedestrians, the higher the degree.
-A higher degree means more friction force which is the cause of the reduction of the flow.
-In the bottleneck geometry, the opposite thing happens, the stiffer the pedestrians the lower the mean degree.
-This is the reason why in a bottleneck, pedestrians evacuate faster as they become stiffer while in a corridor the pedestrian\textsc{\char13}s flow is lower as they become stiffer.\\
+In the bottleneck geometry, the opposite thing happens, the stiffer the pedestrians the lower the mean degree.\\
 
@@
 As was mentioned above, increasing the $k_n$ value of the body force increases the stiffness of pedestrians.
-Increasing the stiffness reduces the overlap (both in bottleneck and corridor).
+Increasing the stiffness reduces the overlap (both in the bottleneck and corridor).
 Regarding the network connectivity, increasing the stiffness reduces the mean degree in a bottleneck but increases the mean degree in a corridor.
-In Fig.~\ref{network_corridor} it shown the contact network corresponding to the corridor at a particular timestep and a particular global density.
-Fig.~\ref{network_d6_kn0} corresponds to $k_n=0$ while Fig.
-\ref{network_d6_knE5} corresponds to $k_n=1.2$~E5.
+Fig.~\ref{network_corridor} it shows the contact network corresponding to the corridor at a particular timestep and a particular global density.
+Fig.~\ref{network_d6_kn0} corresponds to $k_n=0$ while Fig.~\ref{network_d6_knE5} corresponds to $k_n=1.2$~E5.
 This is an example to show that increasing the stiffness increases the number of contacts between pedestrians (the network connectivity).
@@
 
-The increment of the connectedness is responsible for the reduction of the flow.
 In the corridor geometry, the crowd gets more connected if the pedestrians become stiffer.
@@
 \end{figure}
+
+The most important result is that increasing the $k_n$ value reduces the flow (hence reduces the walking speed of the overall crowd) in the corridor geometry.
+Fig.~\ref{kn_vs_vx_corridor} shows the velocity in the direction of displacement $v_x$ as a function of the stiffness for different global density levels.
+$v_x$ reduces as $k_n$ increases as opposed to what happens in the bottleneck geometry.
+There is little to no change in the speed from zero to $k_n=$1.2~E4, from this value on, the diminishing of velocity is more abrupt.\\
+
+The reason why the velocity reduces as the stiffness of the pedestrians increases is that it becomes harder for the pedestrians to walk forward since the repulsion force (body force) against the pedestrian that is ahead becoming higher.
+Thus, they have no other option than moving at (almost) the same speed than the pedestrians that they have at their sides.\\
+
+\begin{figure}[htbp!]
+\centering
+\includegraphics[width=0.7\columnwidth]{./kn_vs_vx_corridor.eps}
+\caption{\label{kn_vs_vx_corridor}   }
+\end{figure}
+
+The value of $k_n$ affects the velocity all along the corridor.
+Fig...
+shows the velocity profile ($v_x$ vs.
+the longitudinal coordinate $y$) for different $k_n$ values.
+For $k_n=0$, we can see a parabolic-like velocity profile that resembles the Poissele flow for a viscous liquid.
+As $k_n$ increases the velocity profile flattens until becoming a constant ($k_n=$ 1.2~E6) which $v_x$ value is much lower than on the case of soft pedestrians ($k_n=$0).\\
+
+If the stiffness is high enough, the crowd behaves like a solid; this means that the crowd can not be deformed. This is express by the strain rate, which is shown in Fig.~\ref{}. \\
+
+The strain rate is a quantity that characterizes the deformation of a physical object.
+It is defined as a tensor ....
+For this particular problem we define a discrete version of the strain rate that compares the velocity of the pedestrians close to the wall (boundary) and the pedestrians that are in the center of the corridor (center).
+\\
 

### 2020-01-10 plots/corridor/k_vs_vx/plot_k_vs_vx.py

@@ -1,0 +1,77 @@
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+import pandas as pd
+#import numarray
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+###  DATA  ###
+
+data_d5_5 = pd.read_csv("k_vs_vx_d5.5.txt",sep="\t")
+k_d5_5 = data_d5_5["k"].tolist()
+mean_vx_d5_5 = data_d5_5["mean vx"].tolist()
+std_vx_d5_5 = data_d5_5["std vx"].tolist()
+
+data_d6 = pd.read_csv("k_vs_vx_d6.txt",sep="\t")
+k_d6 = data_d6["k"].tolist()
+mean_vx_d6 = data_d6["mean vx"].tolist()
+std_vx_d6 = data_d6["std vx"].tolist()
+'''
+data_d7 = pd.read_csv("k_vs_vx_d7.txt",sep="\t")
+k_d7 = data_d7["k"].tolist()
+mean_vx_d7 = data_d7["mean vx"].tolist()
+std_vx_d7 = data_d7["std vx"].tolist()
+'''
+data_d8 = pd.read_csv("k_vs_vx_d8.txt",sep="\t")
+k_d8 = data_d8["k"].tolist()
[…]

### 2020-01-10 paper.tex
agregue mas texto y figuras a la parte de corridor de resultados

@@
 
-The reason why the velocity reduces as the stiffness of the pedestrians increases is that it becomes harder for the pedestrians to walk forward since the repulsion force (body force) against the pedestrian that is ahead becoming higher.
-Thus, they have no other option than moving at (almost) the same speed than the pedestrians that they have at their sides.\\
+The reason why the velocity reduces as the stiffness of the pedestrians' increases is that it becomes harder for pedestrians to walk forward.
+The difficulty arises because the pedestrian feels a much higher repulsion from the pedestrian ahead (due to the body force increment).
+Thus, they have no other option than moving at (almost) the same speed as the pedestrians that they have at their sides.
+This microscopic mechanism explains the macroscopic behavior of the crowd that turns the crowd from a fluid-like state into a solid-like state.
+When the stiffness is high enough (say $k_n=$1.2~E6), all the pedestrians walk at the same velocity.
+The pedestrians that walk in physical contact with the wall are the ones who determine the velocity of the whole crowd.\\
 
@@
 \includegraphics[width=0.7\columnwidth]{./kn_vs_vx_corridor.eps}
-\caption{\label{kn_vs_vx_corridor}   }
+\caption{\label{kn_vs_vx_corridor} Mean velocity in the longitudinal coordinate $(v_x)$ as a function of the stiffness $k_n$ for three different global densities (see label in the plot).
+The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
+}
 \end{figure}
@@
 The value of $k_n$ affects the velocity all along the corridor.
-Fig...
-shows the velocity profile ($v_x$ vs.
+Fig.~\ref{vx_profile} shows the velocity profile ($v_x$ vs.
 the longitudinal coordinate $y$) for different $k_n$ values.
-For $k_n=0$, we can see a parabolic-like velocity profile that resembles the Poissele flow for a viscous liquid.
+For $k_n=0$, we can see a parabolic-like velocity profile that resembles the Poiseuille flow (for Newtonian and incompressible fluids in laminar flow flowing through a pipe).
 As $k_n$ increases the velocity profile flattens until becoming a constant ($k_n=$ 1.2~E6) which $v_x$ value is much lower than on the case of soft pedestrians ($k_n=$0).\\
 
-If the stiffness is high enough, the crowd behaves like a solid; this means that the crowd can not be deformed. This is express by the strain rate, which is shown in Fig.~\ref{}. \\
+If the stiffness is high enough, the crowd behaves like a solid; this means that the crowd can not be easily deformed.
+In this context, to deform means to have parts of the crowd that move faster than other parts of the crowd.
+\\
 
-The strain rate is a quantity that characterizes the deformation of a physical object.
-It is defined as a tensor ....
-For this particular problem we define a discrete version of the strain rate that compares the velocity of the pedestrians close to the wall (boundary) and the pedestrians that are in the center of the corridor (center).
+The strain rate is a tensor for every point in the space.
+It expresses how the relative velocity of a medium changes when one moves away from a position in a specific direction.
+For this particular problem, we define the following version of the strain rate:
+
+\begin{equation}
+S = \frac{<v_x(center)> - <v_x(boundary)> }{\left | y(center) - y(boundary) \right |} 
+\end{equation}
+
+Where $<>$ means the average taken over time.
+By this definition we compare the velocity of the pedestrians close to the wall (boundary) with respect to the velocity of the pedestrians in the center of the corridor (center).
+As the stiffness level increases, the crowd becomes less deformable.
+This phenomenon is shown in Fig.~\ref{strain_rate_vs_kn} where we can see that the strain rate decreases with $k_n$.
+\\
+
+\begin{figure}[!htbp]
+\centering
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./vx_profile.eps}\label{vx_profile}}\ 
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./strain_rate_vs_kn.eps}\label{strain_rate_vs_kn}}\\
+\caption[width=0.47\columnwidth]{(a) Velocity in the $x$ coordinate as a function of the transversal coordinate $y$ for three different stiffness values $k$ (see the label).
+(b) Strain rate as a function of the stiffness level $k$.
+The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
+The global density was 7 p~m$^{-2}$.
+}
+\label{profile_strain}
+\end{figure}
+
+To conclude this section, we remark that increasing the stiffness produces the opposite results in corridors respect to bottlenecks.
+The walls in the corridors play a critical role that prevents pedestrians from detaching from each other.
+This effect has consequences such as increasing the connectivity of the contact network, flattening the velocity profile (thus reducing the strain rate).
+If the stiffness is high enough, the pedestrians can not push to the pedestrian ahead since the body force repulsion becomes very high.
+This leads to a"solidification" of the crowd that makes all the pedestrians walk at almost the same velocity.
+The pedestrians that are in contact with the wall are the ones who determine the velocity of the whole crowd.
 \\

### 2020-01-10 plots/corridor/strain_rate/plot_strain_rate.py

@@ -1,0 +1,90 @@
+'''
+Dados los archivos de velocity profile, calcula strain rate vs k
+El strain rate esta definido como la secante entre un borde y el centro.
+
+e = (v(centro)-v(borde))/(y(centro)-y(borde))
+'''
+
+import sys
+import os
+import pandas as pd
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+
+
+def main():
+
+
+     list_k = [0,12000,120000,1200000]
+     y_borde = 0.5
+     y_centro = 10.5
+     plot_name = 'strain_rate_vs_kn'
+     strain_rate = []
+     error_strain_rate = []
+
+     for k in list_k:
+          file_name = 'vx_profile_kn{}.txt'.format(k)
+          df = pd.read_csv('{}'.format(file_name),sep='\t')
+          vx_borde = float(df.loc[df['bin y'] == y_borde, 'mean vx'])
+          vx_centro = float(df.loc[df['bin y'] == y_centro, 'mean vx'])
+          strain_rate += [(vx_centro-vx_borde)/float(y_centro-y_borde)] 
[…]

### 2020-01-10 plots/corridor/velocity_profile/plot_velocity_profile.py

@@ -1,0 +1,88 @@
+import sys
+import os
+import pandas as pd
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+
+
+def main():
+
+     file_name = 'vx_profile_kn0.txt'
+     simbol ='-s'
+     color = 'c'
+     label = "$k_n=$~0"
+     plot_triangles(file_name,simbol,color,label)
+
+     file_name = 'vx_profile_kn1.2E5.txt' 
+     simbol ='-x'
+     color = 'b'
+     label = "$k_n=1.2$~E5"
+     plot_triangles(file_name,simbol,color,label)
+
+
+     file_name = 'vx_profile_kn1.2E6.txt'
+     simbol ='-o'
+     color = 'k'
+     label = "$k_n=1.2$~E6"
+     plot_triangles(file_name,simbol,color,label)
+
+
+
+def plot_triangles(file_name,simbol,color,label):
+     '''
+     Importa un archivo con las caracteristicas de la red 
+     y grafica triangulos vs densidad
+     '''
+     df = pd.read_csv('{}'.format(file_name),delimiter = '\t') 
+     y = df['bin y'].tolist()
+     vx = df['mean vx'].tolist()
+     std_vx = df['std vx'].tolist()
+
[…]

### 2020-01-14 paper.tex
agregue grafico de blocking clusters vs vd para distintos kn

@@
 
+The clusterization of the pedestrians has a significant impact on the blocking clusters (the group of pedestrians that clog the exit).
+Fig.~\ref{pbc_vs_vd_multi_kn} shows the blocking cluster existence probability as a function of the desired velocity for different $k$ values.
+The blocking clusters occur more often when the desired velocity increases because increasing $v_d$ increase the density in the area close to the exit.
+The most remarkable fact of Fig.~\ref{pbc_vs_vd_multi_kn} is that increasing the stiffness reduces the blocking cluster existence for a fixed value of $v_d$.
+Under these conditions, the blocking clusters strictly govern the evacuation dynamics~\cite{dorso_2005}.
+Thus, increasing the stiffness reduces the blocking cluster existence, which improves the evacuation time.\\
+
+\begin{figure}[htbp!]
+\centering
+\includegraphics[width=0.7\columnwidth]
+{./pbc_vs_vd_multi_kn.eps}
+\caption{\label{pbc_vs_vd_multi_kn} Blocking cluster existence probability as a function of $v_d$ for different stiffness levels (see label).
+The probability is calculated as the amount of time a blocking cluster is present divided by the overall simulation time.
+The result correspond to a bottleneck geometry with 225 pedestrians in periodic boundary conditions (re-injection of pedestrians once the exited the room).
+The simulation lasted $t_f =$ 1000~s.
+}
+\end{figure}
+
 To conclude this section, we want to emphasize that increasing body stiffness has a significant impact on the evacuation dynamics.
 The stiffer pedestrians are, the less they touch to each other (less degree and less overlap).
-This yields a reduction of an increment of the speed, which reduces the evacuation time.
+This phenomenon yields a reduction of the existence of the blocking clusters, which reduces the overall evacuation time.
+\\
 \\

### 2020-01-14 plots/bottleneck/pbc_vs_vd/plot_pbc_vs_vd.py

@@ -1,0 +1,87 @@
+'''
+Grafica compresion vs vd para muchos kn diferentes
+'''
+
+import pylab
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+import pandas as pd
+
+# a dos columnas: 3+3/8 (ancho, in)
+# a una columna : 6.5   (ancho  in)
+
+golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
+fig_width = 3+3/8 			    # width  in inches
+fig_height = fig_width*golden_mean          # height in inches
+fig_size =  [fig_width,fig_height]
+
+params = {'backend': 'ps',
+          'axes.titlesize': 8,
+          'axes.labelsize': 9,
+          'axes.linewidth': 0.5, 
+          'axes.grid': True,
+          'axes.labelweight': 'normal',  
+          'font.family': 'serif',
+          'font.size': 8.0,
+          'font.weight': 'normal',
+          'text.color': 'black',
+          'xtick.labelsize': 8,
+          'ytick.labelsize': 8,
+          'text.usetex': True,
+          'legend.fontsize': 8,
+          'figure.dpi': 300,
+          'figure.figsize': fig_size,
+          'savefig.dpi': 300,
+         }
+
+pylab.rcParams.update(params)
+
+### DATA ###
+
+data_kn0 = pd.read_csv("vd_pbc_kn0.txt",sep=" ")
+vd_kn0 = data_kn0.iloc[:,0]
+pbc_kn0 =  data_kn0.iloc[:,1]
+
+data_knE4 = pd.read_csv("vd_pbc_kn12000.txt",sep=" ")
+vd_knE4 = data_knE4.iloc[:,0]
+pbc_knE4 =  data_knE4.iloc[:,1]
+
+data_knE5 = pd.read_csv("vd_pbc_kn120000.txt",sep=" ")
+vd_knE5 = data_knE5.iloc[:,0]
+pbc_knE5 =  data_knE5.iloc[:,1]
+
+data_knE6 = pd.read_csv("vd_pbc_kn1200000.txt",sep=" ")
+vd_knE6 = data_knE6.iloc[:,0]
+pbc_knE6 =  data_knE6.iloc[:,1]
+
+
+###  PLOT  ###
+
+
+fig, ax1 = plt.subplots()
+
[…]

### 2020-01-15 plots/corridor/strain_rate/plot_strain_rate.py
agregue mas densidades al grafico de strain rate

@@ -48,31 +48,33 @@ def main():
 
 
      list_k = [0,12000,120000,1200000]
+     list_d = [6,7,8]
+     list_symbol = ['-o','-v','-^']
+     list_color = ['b','g','r']
      y_borde = 0.5
      y_centro = 10.5
      plot_name = 'strain_rate_vs_kn'
-     strain_rate = []
-     error_strain_rate = []
-
-     for k in list_k:
-          file_name = 'vx_profile_kn{}.txt'.format(k)
-          df = pd.read_csv('{}'.format(file_name),sep='\t')
-          vx_borde = float(df.loc[df['bin y'] == y_borde, 'mean vx'])
-          vx_centro = float(df.loc[df['bin y'] == y_centro, 'mean vx'])
-          strain_rate += [(vx_centro-vx_borde)/float(y_centro-y_borde)] 
-          error_strain_rate += [(float(df.loc[df['bin y'] == y_borde, 'std vx'])+float(df.loc[df['bin y'] == y_centro, 'std vx']))/float(y_centro-y_borde)]
-     print(error_strain_rate)
-
-     plot_strainrate_vs_k(plot_name,list_k,strain_rate,error_strain_rate)
-
-def plot_strainrate_vs_k(plot_name,list_k,strain_rate,error_strain_rate):
-     '''
-
-     '''
 
 
-     plt.errorbar(list_k,strain_rate,error_strain_rate, fmt='none')     
-     plt.plot(list_k,strain_rate,'b-o',mec='k',mew=0.8,linewidth = '1',markersize=4)     
+     i = 0
+     for d in list_d:
+          strain_rate = []
+          error_strain_rate = []
+          for k in list_k:
+               file_name = 'vx_profile_d{}_kn{}.txt'.format(d,k)
+               df = pd.read_csv('{}'.format(file_name),sep='\t')
+               vx_borde = float(df.loc[df['bin y'] == y_borde, 'mean vx'])
+               vx_centro = float(df.loc[df['bin y'] == y_centro, 'mean vx'])
+               strain_rate += [(vx_centro-vx_borde)/float(y_centro-y_borde)] 
+               error_strain_rate += [(float(df.loc[df['bin y'] == y_borde, 'std vx'])+float(df.loc[df['bin y'] == y_centro, 'std vx']))/float(y_centro-y_borde)]
+
[…]

### 2020-01-16 paper.tex
modifique el caption de strain rate
agregue las conclusiones

@@
 \caption[width=0.47\columnwidth]{(a) Velocity in the $x$ coordinate as a function of the transversal coordinate $y$ for three different stiffness values $k$ (see the label).
-(b) Strain rate as a function of the stiffness level $k$.
+(b) Strain rate as a function of the stiffness level $k_n$ for three different global density values (see label).
 The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
@@
 \section{\label{conclusions}Conclusions}
+
+In this research, we have explored the effects of the body force in the original SFM.
+We showed that the stiffness coefficient ($k_n$) has a significant impact on the evacuation dynamics (bottleneck) and also in the dynamics of pedestrians walking along a straight corridor.\\
+
+In the bottleneck geometry, the evacuation time diminishes (pedestrians move faster) as pedestrians become stiffer for all the ranges of the desired velocities explored.
+This phenomenon happens because increasing the stiffness level promotes the repulsion between pedestrians pair interactions.
+As pedestrians detach from each other, the friction force diminishes due to the reduction of overlap and contacts among them.
+The general decrease in frictional force reduces the probability of producing a cluster of pedestrians blocking the exist (blocking cluster), which finally leads to a more efficient evacuation dynamics.
+\\
+
+In the corridor geometry, the walking speed reduces as pedestrians become stiffer.
+This is the opposite behavior we obtained in bottleneck geometry.
+The difference is explained because although increasing stiffness further separates individuals, they can not detach from each other as much as possible due to the lateral walls (these walls are not relevant in the bottleneck geometry).
+Thus, when the stiffness increases, pedestrians reduce the overlap but increase the number of contacts (degree).
+In high density scenarios, the stiffness promotes the friction force.
+Granular materials can behave like fluid or solids, depending on several conditions.
+If the stiffness level is low, the entire crowd behaves like a viscous fluid (with a parabolic velocity profile).
+However, if the stiffness level is high enough, the whole crowd behaves like a solid (with a constant velocity profile which depends on the friction against the walls).\\
+
+Regarding the parameters of the model, we found out that it is possible to reduce the original SFM parameters to three dimensionless parameters.
+The original parameters interrelate to each other through the dimensionless ones.
+Many different settings can produce the same dimensionless parameters.
+Thus, no univocal relations can be established between the individualistic parameters and collective dynamics.\\
 

### 2020-01-17 plots/bottleneck/overlap_distribution/plot_histo.py
borre la carpeta overlap distribution

@@ -1,113 +1,0 @@
-# Sacado de https://scipy.github.io/old-wiki/pages/Cookbook/Matplotlib/LaTeX_Examples.html
-'''
-Grafica histogramas 
-'''
-
-import pylab
-import numpy as np
-import matplotlib.pyplot as plt
-import math
-#import numarray
-
-# a dos columnas: 3+3/8 (ancho, in)
-# a una columna : 6.5   (ancho  in)
-
-golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
-fig_width = 3+3/8 			    # width  in inches
-fig_height = fig_width*golden_mean          # height in inches
-fig_size =  [fig_width,fig_height]
-
-params = {'backend': 'ps',
-          'axes.titlesize': 8,
-          'axes.labelsize': 9,
-          'axes.linewidth': 0.5, 
-          'axes.grid': True,
-          'axes.labelweight': 'normal',  
-          'font.family': 'serif',
-          'font.size': 8.0,
-          'font.weight': 'normal',
-          'text.color': 'black',
-          'xtick.labelsize': 8,
-          'ytick.labelsize': 8,
-          'text.usetex': True,
-          'legend.fontsize': 8,
-          'figure.dpi': 300,
-          'figure.figsize': fig_size,
-          'savefig.dpi': 300,
-         }
-
-pylab.rcParams.update(params)
-
-########################  MAIN  ########################
-def main():
-
-     ##### PARAMETERS ##### 
-     vd = 10
-     kn = "0"
-     clase = "bottleneck_vd{}_k{}".format(vd,kn)
-     distribucion = np.genfromtxt("distrib_comp_{}".format(clase),delimiter = ' ')    
-     title_plot= "Bottleneck - $k_n$={} - $v_d$={}".format(kn,vd)
-     out_name = "histo_grado_{}".format(clase)
-     binwidth = 0.005
-     min_comp = 0.0
-     max_comp = 0.20
-     min_grado = 0
-     max_grado = 7
-     print("media= ",np.mean(distribucion))
-     #plot_histo_norm_discreta(distribucion,title_plot,out_name,min_grado,max_grado)
-     plot_histo_normalized(distribucion,title_plot,out_name,binwidth,min_comp,max_comp)
-
-
-
-
[…]

### 2020-01-17 plots/corridor/degree_distribution/plot_histo.py
borre carpetas que no sirven mas

@@ -1,114 +1,0 @@
-# Sacado de https://scipy.github.io/old-wiki/pages/Cookbook/Matplotlib/LaTeX_Examples.html
-'''
-Grafica histogramas 
-'''
-
-import pylab
-import numpy as np
-import matplotlib.pyplot as plt
-import math
-#import numarray
-
-# a dos columnas: 3+3/8 (ancho, in)
-# a una columna : 6.5   (ancho  in)
-
-golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
-fig_width = 3+3/8 			    # width  in inches
-fig_height = fig_width*golden_mean          # height in inches
-fig_size =  [fig_width,fig_height]
-
-params = {'backend': 'ps',
-          'axes.titlesize': 8,
-          'axes.labelsize': 9,
-          'axes.linewidth': 0.5, 
-          'axes.grid': True,
-          'axes.labelweight': 'normal',  
-          'font.family': 'serif',
-          'font.size': 8.0,
-          'font.weight': 'normal',
-          'text.color': 'black',
-          'xtick.labelsize': 8,
-          'ytick.labelsize': 8,
-          'text.usetex': True,
-          'legend.fontsize': 8,
-          'figure.dpi': 300,
-          'figure.figsize': fig_size,
-          'savefig.dpi': 300,
-         }
-
-pylab.rcParams.update(params)
-
-########################  MAIN  ########################
-def main():
-
-	##### PARAMETERS ##### 
-	density = 7
-	kn = "E5"
-	clase = "density{}_width22_kn{}".format(density,kn)
-	distribucion = np.genfromtxt("distrib_grado_{}".format(clase),delimiter = ' ')    
-	title_plot= "Corridor $w=$22~m - $k_n$={} - Density={}".format(kn,density)
-	out_name = "histo_grado_{}".format(clase)
-	binwidth = 0.007
-	min_comp = 0.0
-	max_comp = 0.17
-
-	min_grado = 0
-	max_grado = 7
-	plot_histo_norm_discreta(distribucion,title_plot,out_name,min_grado,max_grado)
-	#plot_histo_normalized(distribucion,title_plot,out_name,binwidth,min_comp,max_comp)
-
-
-
-
-def plot_histo_ocurrence(distribucion,titulo,out_name):
-     plt.figure()
[…]

### 2020-01-17 plots/corridor/g_r/plot_gr.py

@@ -1,61 +1,0 @@
-'''
-Calcula la funcion de correlacion radial g(r)
-'''
-import pylab
-import numpy as np
-import math
-import matplotlib.pyplot as plt
-import pandas as pd
-
-golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
-fig_width = 3+3/8                            # width  in inches
-fig_height = fig_width*golden_mean          # height in inches
-fig_size =  [fig_width,fig_height]
-
-params = {'backend': 'ps',
-          'axes.titlesize': 8,
-          'axes.labelsize': 9,
-          'axes.linewidth': 0.5, 
-          'axes.grid': True,
-          'axes.labelweight': 'normal',  
-          'font.family': 'serif',
-          'font.size': 8.0,
-          'font.weight': 'normal',
-          'text.color': 'black',
-          'xtick.labelsize': 8,
-          'ytick.labelsize': 8,
-          'text.usetex': True,
-          'legend.fontsize': 8,
-          'figure.dpi': 300,
-          'figure.figsize': fig_size,
-          'savefig.dpi': 600,
-         }
-
-pylab.rcParams.update(params)
-
-density = "7"
-output_name_histo = "g(r)_d{}_knE5".format(density)
-titulo = "Global density ={}".format(density)+" p.m$^{-2}$"
-
-data_kn0_d7 = pd.read_csv("r_g_density{}_width22_kn0_r28x22".format(density),sep="\t")
-r_kn0_d7 =  data_kn0_d7["bins"].tolist()
-g_kn0_d7 =  data_kn0_d7["g"].tolist()
-
-data_knE5_d7 = pd.read_csv("r_g_density{}_width22_knE5_r28x22".format(density),sep="\t")
-r_knE5_d7 =  data_knE5_d7["bins"].tolist()
-g_knE5_d7 =  data_knE5_d7["g"].tolist()
-
-
-#plt.plot(r_kn0_d7, g_kn0_d7, '-r',lw=1,label="$k_n=$0")
-plt.plot(r_knE5_d7, g_knE5_d7, '-b',lw=1,label="$k_n=$1.2 E5")
-
-pylab.grid(False)
-pylab.xlabel('$r$(m)',fontsize=10)
-pylab.ylabel('$g~(r)$',fontsize=10)
-pylab.title('{}'.format(titulo),fontsize=10)
-pylab.xlim(0.0, 2)
[…]

### 2020-01-17 plots/corridor/voronoi/plot_voronoi_tessellation_color.py

@@ -1,165 +1,0 @@
-import pylab
-import numpy as np
-import math
-import matplotlib.pyplot as plt
-import pandas as pd
-from   scipy.spatial import Voronoi, voronoi_plot_2d
-from   scipy.spatial import ConvexHull
-import matplotlib.patches as patches
-import matplotlib as mpl
-import matplotlib.cm as cm
-
-golden_mean = (math.sqrt(5)-1.0)/2.0        # Aesthetic ratio
-fig_width = 3+3/8                            # width  in inches
-fig_height = fig_width*golden_mean          # height in inches
-fig_size =  [fig_width,fig_height]
-
-params = {'backend': 'ps',
-          'axes.titlesize': 8,
-          'axes.labelsize': 9,
-          'axes.linewidth': 0.5, 
-          'axes.grid': True,
-          'axes.labelweight': 'normal',  
-          'font.family': 'serif',
-          'font.size': 8.0,
-          'font.weight': 'normal',
-          'text.color': 'black',
-          'xtick.labelsize': 8,
-          'ytick.labelsize': 8,
-          'text.usetex': True,
-          'legend.fontsize': 8,
-          'figure.dpi': 300,
-          'figure.figsize': fig_size,
-          'savefig.dpi': 600,
-         }
-
-pylab.rcParams.update(params)
-
-
-################## PRAMETERS ######################### 
-selected_time = 30
-global_density = 7
-output_name = "tesselation_d{}_time{}_color_relative_kn0".format(global_density,selected_time)
-data_config = "config_density{}_width22_kn0".format(global_density)
-xmin = 1.0
-xmax = 27.0
-ymin = 1
-ymax = 21.0
-
-
-######################## Functions ##################### 
-
-def extract_config(data,t):
-     '''
-     t is the selected time
-     this function extracts the configuration for the time t
-     only one timestep is extracted
-     '''
-     ESCALA_TIME = 10000
-
-     str_selected_timestep='{}\n'.format(int(t*ESCALA_TIME))
-     f=open(data, 'r')
-     lines=f.readlines()
-     x=[]
-     y=[]
-     i=0
-     flag=True
-     while i<len(lines) and flag:
-          line = lines[i].rstrip('\n')
-          if(line=='ITEM: TIMESTEP'):
-               iter_time=lines[i+1]
-               if(iter_time==str_selected_timestep):
-                    number_pedestrians=int(lines[i+3])
-                    first_line_table=i+9
[…]

### 2020-01-27 paper.tex
Add files via upload
Correcction from Claudio Dorso (only section 4.1)

@@
 %\usepackage[backend=biber,citestyle=authoryear]{biblatex}
+\usepackage{ulem}         %permite el tachado de texto.
 
@@
 We present in this section the results corresponding to the bottleneck geometry. 
-We show the consequences of modifying the body force coefficient $k_n$ in the evacuation dynamics.
-Recall that this coefficient is associated with the stiffness of the pedestrians.
-\\
+We show the consequences of modifying the body force coefficient $k_n$ in the 
+evacuation dynamics. Recall that this coefficient is associated 
+\textcolor{red}{to the compression of the human body}. \\
 
-Fig.~\ref{vd_vs_te} shows the evacuation time as a function of the pedestrian's desired velocity.
-The evacuation time is defined as the time until 80\% of the pedestrians left the room.
-The different markers correspond to different $k_n$ values (\textit{i.e.} different body ``stiffness''; see caption for details).
-In this section we will focus on the evacuation time for $v_d>2\,$m/s.\\
+Fig.~\ref{vd_vs_te} shows the evacuation time as a function of the pedestrian's 
+desired velocity \textcolor{red}{for different values of $k_n$}. The evacuation 
+time is defined as the time until 80\% of the pedestrians \textcolor{red}{have} 
+left the room. In this section we will focus on the evacuation time for 
+\textcolor{red}{$2\,$m/s$<v_d<10\,$m/s}.\\
 
@@
 {./vd_vs_te_N225.eps}
-\caption{\label{vd_vs_te}Mean evacuation time (s) vs.
-the pedestrian’s desired velocity (m/s) for a bottleneck.
-The room was 20 m x 20 m size.
-The door was 0.92 m width.
-Mean values were computed from 10 evacuation processes.
-225 pedestrians were initially placed in a square lattice with a random initial velocity.
-Each process was finished when 158 pedestrians left the room.
-The different symbols indicate the $k_n$ value corresponding to the body force (see the label).
-The crosses correspond to the Helbing original SFM parameter, the up-triangles correspond to the value measured in Ref.~\cite{gordon1989anthropometric}, squares correspond to zero body force and circles correspond to an extreme value of stiffness (one order of magnitude higher than the original SFM).
-The down triangles correspond to an intermediate value between the empirical value presented in Ref.~\cite{gordon1989anthropometric} and the chosen by Helbing in Ref.~\cite{helbing_2000} }
+\caption{\label{vd_vs_te}Mean evacuation time (s) vs. the pedestrian’s desired  
+velocity (m/s) for a bottleneck. The room was 20 m x 20 m size. The door was 
+0.92 m width. Mean values were computed from 10 evacuation processes. 225 
+pedestrians were initially placed in a square lattice with a random initial 
+velocity. Each process was finished when 158 pedestrians left the room. The 
+different symbols indicate the $k_n$ value corresponding to the body force (see 
+the label). The crosses correspond to the Helbing's original SFM parameter, the 
+up-triangles correspond to the value measured in 
+Ref.~\cite{anthropometric}, \textcolor{red}{empty} squares correspond 
+to zero body force and circles correspond to an extreme value of stiffness (one 
+order of magnitude higher than the original SFM). The \textcolor{red}{empty} 
+ down triangles correspond to an intermediate value between the empirical value 
+presented in Ref.~\cite{anthropometric} and the chosen by Helbing in 
+Ref.~\cite{helbing_2000} }
 \end{figure}
@@
 Two behavioral patterns can be seen in Fig.~\ref{vd_vs_te}. 
-Whenever the slope is positive, it means that the harder the pedestrians trying to get out (higher $v_d$), the higher it takes them to evacuate.
-This is the Faster-is-slower (FIS) regime.
-Conversely, the negative slope corresponds to a Faster-is-Faster (FIF) phenomenon (the harder they try, the quicker they leave).
-Fig.~\ref{vd_vs_te} shows a change in the slope sign only for stiffness values below $k=1.2$~E5.
-This means that ``soft'' individuals are required to attain this behavioral change.
-Notice that for  $k_n=1.2$~E6 (the stiffest explored pedestrians), no FIS can be seen at all.
-Besides, the evacuation pattern for $k_n = 0$ and $k_n = 1.2$~E4 are very similar since the body force is comparable to the social force for these stiffness values.
-\\
+\textcolor{red}{The region in which the slope is positive} means that the 
+harder the pedestrians try to get out (higher $v_d$), the 
+\textcolor{red}{longer} it takes them to evacuate. This is the Faster-is-slower 
+(FIS) regime. Conversely, \textcolor{red}{the region in which the slope is 
+negative}  corresponds to a Faster-is-Faster (FIF) \textcolor{red}{regime} (the 
+harder they try, the quicker they leave). Fig.~\ref{vd_vs_te} shows a change in 
+\textcolor{red}{in the behavior for desired velocities $v_d>1.2\,$m/s. The 
+evacuation time is of type FIS+FIF for compression coefficients below 
+$k=1.2\,$E5}. This means that ``soft'' individuals are required to attain this 
+behavioral change.  Notice that \textcolor{red}{higher values of $k_n$ allow 
+only FIS or FIF behaviors. For the highest explored value $k_n=1.2\,$E6}, no 
+FIS can be seen at all. Besides, the evacuation pattern for $k_n = 0$ and $k_n 
+= 1.2\,$E4 are very similar since the body force is comparable to the social 
+force for these stiffness values. \\
 
-Despite the presence of the FIS or FIF phenomenon, the evacuation time at a fixed value of $v_d$ decreases for increasing values of $k_n$.
-This means that stiffer pedestrians evacuate faster than soft pedestrians.
-To investigate this issue, we computed the mean velocity of the whole crowd as a function of the stiffens $k_n$.
-Fig.~\ref{kn_vs_vx_bottleneck} shows the mean velocity in the x-direction as a function of the stiffness $k_n$ for three different desired velocities.
-In all cases, the velocity increases with the stiffness.
-From $k_n=0$ to $k_n=$1.2~E4 the increment of velocity is not as significative as it is for higher $k_n$.
-\\
+Despite the presence of the FIS or FIF phenomenon, the evacuation time at a 
+fixed value of $v_d$ decreases for increasing values of $k_n$. This means that 
+stiffer pedestrians evacuate faster than soft pedestrians. To investigate this 
+issue, we computed the mean velocity of the whole crowd as a function of the 
+stiffens $k_n$. Fig.~\ref{kn_vs_vx_bottleneck} shows the mean velocity in the 
+x-direction as a function of the stiffness $k_n$ for three different desired 
+velocities. In all cases, the velocity increases with the stiffness. From 
+$k_n=0$ to $k_n=$1.2~E4 the increment of velocity is not as significative as it 
+is for higher $k_n$. \\
 
@@
     \subfloat[]{\includegraphics[width=0.7\columnwidth]{./kn_vs_vx_bottleneck.eps}}\\
-\caption[width=0.47\columnwidth]{Mean velocity in the x-direction as a function of the stiffness level $k_n$ for different desired velocities (see label).
-The data corresponds to a bottleneck with periodic boundary conditions (re-injecting pedestrians).
-The average was taken every two seconds once the crowd reaches the stationary state ($t=$20~s) until the end of the simulation ($t=$110~s).
-}
+\caption[width=0.47\columnwidth]{Mean velocity in the x-direction as a function 
+of the stiffness level $k_n$ for different desired velocities (see label). The 
+data corresponds to a bottleneck with periodic boundary conditions (re-injecting 
+pedestrians). The average was taken every two seconds once the crowd reaches the 
+stationary state ($t=$20~s) until the end of the simulation ($t=$110~s). }
 \label{kn_vs_vx_bottleneck}
@@
 
-The presence of a FIF phenomenon only for soft individuals opens many questions on the microscopic dynamics of pedestrians.
-We may presume that contacts between pedestrians are quite different for soft individuals than for stiff individuals.
-To study the dynamics of the contact, regardless of the compression effects, we assimilate the pedestrians as nodes and the whole crowd as a network.
-We set a link between any two individuals if both are in physical contact (\textit{i.e.} $r_{ij} \leq R{ij}$).\\
+The presence of a FIF phenomenon only for soft individuals opens many questions 
+on the microscopic dynamics of pedestrians. We may presume that contacts 
+between pedestrians are quite different for soft individuals than for stiff 
+individuals. To study the dynamics of the contact, regardless of the compression 
+effects, we assimilate the pedestrians as nodes and the whole crowd as a 
+network. We set a link between any two individuals if both are in physical 
+contact (\textit{i.e.} $r_{ij} \leq R{ij}$).\\
 
-Fig.~\ref{degree_vd} shows the mean degree of the contact network as a function of the desired velocity.
-The degree of a node is defined as the number of links that connect this node to any other node.
-This means, the number of pedestrians that are in physical contact with a given pedestrian.
-The mean degree is the average of the degree over all the nodes (pedestrians) and over the whole sampled time.
-We report mean values after the system has reached the stationary state, that is after a well-formed bulk has been established.\\
+Fig.~\ref{degree_vd} shows the mean degree of the contact network as a function  
+of the desired velocity. The degree of a node is defined as the number of links 
+that connect this node to any other node. This means, the number of pedestrians 
+that are in physical contact with a given pedestrian. The mean degree is the 
+average of the degree over all the nodes (pedestrians) and over the whole 
+sampled time. We report mean values after the system has reached the stationary 
+state, that is after a well-formed bulk has been established.\\
 
-Increasing $v_d$ increases the mean degree, as expected.
-This occurs because increasing $v_d$ produces higher densities that force individuals to touch each other.
-But surprisingly, for a given $v_d$, the mean degree reduces as the $k_n$ value increases.
-A noticeable decrease in the mean degree can be seen for the highest explored value of $k_n$.
-We may expect a significant change in the sliding friction due to this fact.\\
+Increasing $v_d$ increases the mean degree, as expected. This occurs because 
+increasing $v_d$ produces higher densities that force individuals to touch each 
+other. But surprisingly, for a given $v_d$, the mean degree reduces as the $k_n$ 
+value increases. A noticeable decrease in the mean degree can be seen for the 
+highest explored value of $k_n$. We may expect a significant change in the 
+sliding friction due to this fact.\\
 
-A more detailed insight into the contact dynamics can be acquired from Fig.~\ref{overlap_vd}.
-The overlap between individuals is shown as a function of $v_d$.
-Recall from section \ref{sfm} that the overlap is defined as $R_{ij}-r_{ij}$ where $R_{ij}$, is the sum of radius of particle $i$ and particle $j$ and $r_{ij}$  is the distance between both particles.
-Except for very low desired velocities (say, $v_d<2\,$m/s), we can see that the mean overlap is an increasing function of $v_d$ (for the studied $k_n$ values).\\
+A more detailed insight into the contact dynamics can be acquired from 
+Fig.~\ref{overlap_vd}. The overlap between individuals is shown as a function of 
+$v_d$. Recall from section \ref{sfm} that the overlap is defined as 
+$R_{ij}-r_{ij}$ where $R_{ij}$, is the sum of radius of particle $i$ and 
+particle $j$ and $r_{ij}$  is the distance between both particles. Except for 
+very low desired velocities (say, $v_d<2\,$m/s), we can see that the mean 
+overlap is an increasing function of $v_d$ (for the studied $k_n$ values).\\
 
@@
 
-The regime for $v_d<2\,$m/s is different from the rest since most of the pedestrians are not touching each other.
-The only pedestrians who touch each other are the ones who are being re-injected in the room.
-The overlap is higher than, for example, $v_d=3\,$m/s because of the pedestrians who are re-injected bump against the bulk.
-\\
+The regime for $v_d<2\,$m/s is different from the rest since most of the 
+pedestrians are not touching each other. The only pedestrians who touch each 
+other are the ones who are being re-injected in the room. The overlap is higher 
+than, for example, $v_d=3\,$m/s because of the pedestrians \textcolor{red}{that 
+are re-injected and collide with pedestrians in the bulk}. \\
 
 Besides, for a given $v_d$, the overlap increases as the $k_n$ value decreases. 
-Reducing $k_n$ means reducing the normal body force, which allows a more significant invasion of the personal space of the individuals ( this means more overlap between pedestrians).
-The increment in mean overlap, however, seems to be more significant than the mean degree.
-\\
+Reducing $k_n$ means reducing the normal body force, which allows a more 
+significant \textcolor{red}{intrusion} of the personal space of the individuals 
+(this means more overlap between pedestrians). \textcolor{red}{\sout{The 
+increment in mean overlap, however, seems to be more significant than the mean 
+degree.}} \\
 
-Increasing body stiffness has a significant impact on evacuation dynamics.
-The simulations reduction of the overlap and the mean degree between pedestrians, tend to diminish the sliding friction within the crowd.
-Consequently, an enhancement in the evacuation time (pedestrians escape faster) is observed, as pictured in Fig.~\ref{vd_vs_te}.
-Notice, however, that switching from a FIS regime (positive slope) to a  FIF regime (negative slope) in Fig.~\ref{vd_vs_te} appears as a more complex phenomenon.
-We will focus on this issue in an upcoming investigation.\\
+Increasing \textcolor{red}{the} body stiffness has a significant impact on 
+evacuation dynamics. The reduction of the overlap and the mean degree between 
+pedestrians \textcolor{red}{in the simulation}, tend to diminish the sliding 
+friction within the crowd. Consequently, an enhancement in the evacuation time 
+(pedestrians escape faster) is observed, as pictured in Fig.~\ref{vd_vs_te}. 
+Notice, however, that switching from a FIS regime (positive slope) to a  FIF 
+regime (negative slope) in Fig.~\ref{vd_vs_te} appears as a more complex 
+phenomenon. We will focus on this issue in an upcoming investigation.\\
 
-Despite the sliding friction, the body force has a notorious impact in the number of pedestrians touching each other (say, the degree).
-This is clearly depicted in Fig.~\ref{network_bottleneck} where four different configurations of the evacuation dynamics are shown.
-The configurations represent 225 pedestrians trying to escape through a door see the caption for details.
-The colors correspond to the degree of each node (pedestrian), and the lines between pedestrians represent the contacts among them.\\
+Despite \textcolor{red}{the effects on the} sliding friction, the body force 
+has a notorious impact in the number of pedestrians touching each other (say, 
+the degree). This is clearly depicted in Fig.~\ref{network_bottleneck} where 
+four different configurations of the evacuation dynamics are shown. The 
+configurations represent 225 pedestrians trying to escape through a door see the 
+caption for details. The colors correspond to the degree of each node 
+(pedestrian), and the lines between pedestrians represent the contacts among 
+them.\\
 

### 2020-01-28 paper.tex
Agregue las correcciones de Dorso

--- 2020-01-16 paper.tex
@@
 We present in this section the results corresponding to the bottleneck geometry. 
-We show the consequences of modifying the body force coefficient $k_n$ in the evacuation dynamics.
-Recall that this coefficient is associated with the stiffness of the pedestrians.
-\\
+We show the consequences of modifying the body force coefficient $k_n$ in the 
+evacuation dynamics. Recall that this coefficient is associated 
+to the compression of the human body. \\
 
-Fig.~\ref{vd_vs_te} shows the evacuation time as a function of the pedestrian's desired velocity.
-The evacuation time is defined as the time until 80\% of the pedestrians left the room.
-The different markers correspond to different $k_n$ values (\textit{i.e.} different body ``stiffness''; see caption for details).
-In this section we will focus on the evacuation time for $v_d>2\,$m/s.\\
+Fig.~\ref{vd_vs_te} shows the evacuation time as a function of the pedestrian's 
+desired velocity for different values of $k_n$. The evacuation 
+time is defined as the time until 80\% of the pedestrians have 
+left the room. In this section we will focus on the evacuation time for 
+$2\,$m/s$<v_d<10\,$m/s.\\
 
@@
 {./vd_vs_te_N225.eps}
-\caption{\label{vd_vs_te}Mean evacuation time (s) vs.
-the pedestrian’s desired velocity (m/s) for a bottleneck.
-The room was 20 m x 20 m size.
-The door was 0.92 m width.
-Mean values were computed from 10 evacuation processes.
-225 pedestrians were initially placed in a square lattice with a random initial velocity.
-Each process was finished when 158 pedestrians left the room.
-The different symbols indicate the $k_n$ value corresponding to the body force (see the label).
-The crosses correspond to the Helbing original SFM parameter, the up-triangles correspond to the value measured in Ref.~\cite{gordon1989anthropometric}, squares correspond to zero body force and circles correspond to an extreme value of stiffness (one order of magnitude higher than the original SFM).
-The down triangles correspond to an intermediate value between the empirical value presented in Ref.~\cite{gordon1989anthropometric} and the chosen by Helbing in Ref.~\cite{helbing_2000} }
+\caption{\label{vd_vs_te}Mean evacuation time (s) vs. the pedestrian’s desired  
+velocity (m/s) for a bottleneck. The room was 20 m x 20 m size. The door was 
+0.92 m width. Mean values were computed from 10 evacuation processes. 225 
+pedestrians were initially placed in a square lattice with a random initial 
+velocity. Each process was finished when 158 pedestrians left the room. The 
+different symbols indicate the $k_n$ value corresponding to the body force (see 
+the label). The crosses correspond to the Helbing's original SFM parameter, the 
+up-triangles correspond to the value measured in 
+Ref.~\cite{anthropometric}, squares correspond 
+to zero body force and circles correspond to an extreme value of stiffness (one 
+order of magnitude higher than the original SFM). The 
+ down triangles correspond to an intermediate value between the empirical value 
+presented in Ref.~\cite{anthropometric} and the chosen by Helbing in 
+Ref.~\cite{helbing_2000} }
 \end{figure}
@@
 Two behavioral patterns can be seen in Fig.~\ref{vd_vs_te}. 
-Whenever the slope is positive, it means that the harder the pedestrians trying to get out (higher $v_d$), the higher it takes them to evacuate.
-This is the Faster-is-slower (FIS) regime.
-Conversely, the negative slope corresponds to a Faster-is-Faster (FIF) phenomenon (the harder they try, the quicker they leave).
-Fig.~\ref{vd_vs_te} shows a change in the slope sign only for stiffness values below $k=1.2$~E5.
-This means that ``soft'' individuals are required to attain this behavioral change.
-Notice that for  $k_n=1.2$~E6 (the stiffest explored pedestrians), no FIS can be seen at all.
-Besides, the evacuation pattern for $k_n = 0$ and $k_n = 1.2$~E4 are very similar since the body force is comparable to the social force for these stiffness values.
-\\
+The region in which the slope is positive means that the 
+harder the pedestrians try to get out (higher $v_d$), the 
+longer it takes them to evacuate. This is the Faster-is-slower 
+(FIS) regime. Conversely, the region in which the slope is 
+negative  corresponds to a Faster-is-Faster (FIF) regime (the 
+harder they try, the quicker they leave). Fig.~\ref{vd_vs_te} shows a change in 
+in the behavior for desired velocities $v_d>1.2\,$m/s. The 
+evacuation time is of type FIS+FIF for compression coefficients below 
+$k=1.2\,$E5. This means that ``soft'' individuals are required to attain this 
+behavioral change.  Notice that higher values of $k_n$ allow 
+only FIS or FIF behaviors. For the highest explored value $k_n=1.2\,$E6, no 
+FIS can be seen at all. Besides, the evacuation pattern for $k_n = 0$ and $k_n 
+= 1.2\,$E4 are very similar since the body force is comparable to the social 
+force for these stiffness values. \\
 
-Despite the presence of the FIS or FIF phenomenon, the evacuation time at a fixed value of $v_d$ decreases for increasing values of $k_n$.
-This means that stiffer pedestrians evacuate faster than soft pedestrians.
-To investigate this issue, we computed the mean velocity of the whole crowd as a function of the stiffens $k_n$.
-Fig.~\ref{kn_vs_vx_bottleneck} shows the mean velocity in the x-direction as a function of the stiffness $k_n$ for three different desired velocities.
-In all cases, the velocity increases with the stiffness.
-From $k_n=0$ to $k_n=$1.2~E4 the increment of velocity is not as significative as it is for higher $k_n$.
-\\
+Despite the presence of the FIS or FIF phenomenon, the evacuation time at a 
+fixed value of $v_d$ decreases for increasing values of $k_n$. This means that 
+stiffer pedestrians evacuate faster than soft pedestrians. To investigate this 
+issue, we computed the mean velocity of the whole crowd as a function of the 
+stiffens $k_n$. Fig.~\ref{kn_vs_vx_bottleneck} shows the mean velocity in the 
+x-direction as a function of the stiffness $k_n$ for three different desired 
+velocities. In all cases, the velocity increases with the stiffness. From 
+$k_n=0$ to $k_n=$1.2~E4 the increment of velocity is not as significative as it 
+is for higher $k_n$. \\
 
@@
 
-The regime for $v_d<2\,$m/s is different from the rest since most of the pedestrians are not touching each other.
-The only pedestrians who touch each other are the ones who are being re-injected in the room.
-The overlap is higher than, for example, $v_d=3\,$m/s because of the pedestrians who are re-injected bump against the bulk.
-\\
+The regime for $v_d<2\,$m/s is different from the rest since most of the 
+pedestrians are not touching each other. The only pedestrians who touch each 
+other are the ones who are being re-injected in the room. The overlap is higher 
+than, for example, $v_d=3\,$m/s because of the pedestrians that 
+are re-injected and collide with pedestrians in the bulk. \\
 
 Besides, for a given $v_d$, the overlap increases as the $k_n$ value decreases. 
-Reducing $k_n$ means reducing the normal body force, which allows a more significant invasion of the personal space of the individuals ( this means more overlap between pedestrians).
-The increment in mean overlap, however, seems to be more significant than the mean degree.
-\\
+Reducing $k_n$ means reducing the normal body force, which allows a more 
+significant intrusion of the personal space of the individuals 
+(this means more overlap between pedestrians).\\
 
-Increasing body stiffness has a significant impact on evacuation dynamics.
-The simulations reduction of the overlap and the mean degree between pedestrians, tend to diminish the sliding friction within the crowd.
-Consequently, an enhancement in the evacuation time (pedestrians escape faster) is observed, as pictured in Fig.~\ref{vd_vs_te}.
-Notice, however, that switching from a FIS regime (positive slope) to a  FIF regime (negative slope) in Fig.~\ref{vd_vs_te} appears as a more complex phenomenon.
-We will focus on this issue in an upcoming investigation.\\
+Increasing the body stiffness has a significant impact on 
+evacuation dynamics. The reduction of the overlap and the mean degree between 
+pedestrians in the simulation, tend to diminish the sliding 
+friction within the crowd. Consequently, an enhancement in the evacuation time 
+(pedestrians escape faster) is observed, as pictured in Fig.~\ref{vd_vs_te}. 
+Notice, however, that switching from a FIS regime (positive slope) to a  FIF 
+regime (negative slope) in Fig.~\ref{vd_vs_te} appears as a more complex 
+phenomenon. We will focus on this issue in an upcoming investigation.\\
 
-Despite the sliding friction, the body force has a notorious impact in the number of pedestrians touching each other (say, the degree).
-This is clearly depicted in Fig.~\ref{network_bottleneck} where four different configurations of the evacuation dynamics are shown.
-The configurations represent 225 pedestrians trying to escape through a door see the caption for details.
-The colors correspond to the degree of each node (pedestrian), and the lines between pedestrians represent the contacts among them.\\
+Despite the effects on the sliding friction, the body force 
+has a notorious impact in the number of pedestrians touching each other (say, 
+the degree). This is clearly depicted in Fig.~\ref{network_bottleneck} where 
+four different configurations of the evacuation dynamics are shown. The 
+configurations represent 225 pedestrians trying to escape through a door see the 
+caption for details. The colors correspond to the degree of each node 
+(pedestrian), and the lines between pedestrians represent the contacts among 
+them.\\
 
@@
 
-In this research, we have explored the effects of the body force in the original SFM.
+In this research, we explore the effect on the pedestrians dynamics of the (sometimes neglected) body force in the framework of the SFM.
 We showed that the stiffness coefficient ($k_n$) has a significant impact on the evacuation dynamics (bottleneck) and also in the dynamics of pedestrians walking along a straight corridor.\\
@@
 In the bottleneck geometry, the evacuation time diminishes (pedestrians move faster) as pedestrians become stiffer for all the ranges of the desired velocities explored.
-This phenomenon happens because increasing the stiffness level promotes the repulsion between pedestrians pair interactions.
-As pedestrians detach from each other, the friction force diminishes due to the reduction of overlap and contacts among them.
-The general decrease in frictional force reduces the probability of producing a cluster of pedestrians blocking the exist (blocking cluster), which finally leads to a more efficient evacuation dynamics.
+This phenomenon occurs because increasing the stiffness level promotes the repulsion between pedestrians pair interactions.
+As pedestrians detach from each other, the friction force diminishes due to the reduction of overlap between pedestrians and the contacts among them.
+The general decrease in frictional force reduces the probability of producing a cluster of pedestrians blocking the exist (blocking cluster), which leads to a more efficient evacuation dynamics.
 \\
 
-In the corridor geometry, the walking speed reduces as pedestrians become stiffer.
-This is the opposite behavior we obtained in bottleneck geometry.
+In the corridor geometry, the actual walking speed reduces as pedestrians become stiffer.
+This is the opposite behavior with respect to the obtained in bottleneck geometry.
 The difference is explained because although increasing stiffness further separates individuals, they can not detach from each other as much as possible due to the lateral walls (these walls are not relevant in the bottleneck geometry).
-Thus, when the stiffness increases, pedestrians reduce the overlap but increase the number of contacts (degree).
-In high density scenarios, the stiffness promotes the friction force.
+Thus, when the stiffness increases, the overlap between pedestrians is reduced while the number of contacts (degree) increases.
 Granular materials can behave like fluid or solids, depending on several conditions.
 If the stiffness level is low, the entire crowd behaves like a viscous fluid (with a parabolic velocity profile).
-However, if the stiffness level is high enough, the whole crowd behaves like a solid (with a constant velocity profile which depends on the friction against the walls).\\
+However, if the stiffness level is high enough, the whole crowd behaves like a crystalline solid with a constant velocity profile which only depends on the friction interaction with the walls.\\
 

### 2020-01-29 paper.tex
correcciones en la intro

@@
 
-The Social Force Model (SFM) addresses two physical forces as 
-\textit{essential}: the ``body force'' and the ``sliding friction''. Both are 
+\textcolor{red}{The Social Force Model (SFM) is a pedestrian dynamics model that
+considers three kinds of forces: desired forces, social forces, and physical forces.
+In its original version, the SFM, addresses two physical forces as essential: 
+\sout{The Social Force Model (SFM) addresses two physical forces as 
+\textit{essential}:}} the ``body force'' and the ``sliding friction''. Both are 
 inspired by granular interactions and were claimed to be necessary  
@@
 The 
-point seems to be that the SFM focuses on the ``incoordination phenomenon'' due 
+point seems to be that the SFM focuses on the \textcolor{red}{``collective behavior''
+ \sout{``incoordination phenomenon''}} due 
 to clogging, missing the ``individualistic'' perspective  of single pedestrians 
@@
 
-A meaningful (individualistic) numerical setting appears not available yet (to 
-our knowledge). The reason is that different numerical settings can lead to 
+\textcolor{red}{A unique (and universal) setting appears not available yet. 
+\sout{A meaningful (individualistic) numerical setting appears not available yet (to 
+our knowledge).}} The reason is that different numerical settings can lead to 
 the same crowd dynamics. Actually, only a small set of dimensionless 
@@
 \cite{marchetti_2014}. We may hypothesize that while the dimensionless 
-``numbers'' provide some kind of control on the ``incoordination phenomenon'' 
-in 
+``numbers'' provide some kind of control on the \textcolor{red}{\sout{
+``incoordination phenomenon''} collective behavior} in 
 crowds, only a few numerical settings can attain an ``individualistic'' 
@@
 We now widen the investigation on the parameter settings to include the one 
-associated to the body force. We will focus on the complex interplay between 
+associated to the body force. We will \textcolor{red}{\sout{focus} explore} 
+on the complex interplay between 
 the body force and the sliding friction among pedestrians. Recall that the 

### 2020-01-29 paper.tex
correcciones en la parte de experimental background

@@
 
-The complex behavior of pedestrians feature either his (her) feelings and 
+The complex behavior of pedestrians \textcolor{red}{\sout{feature} features}
+ either his (her) feelings and 
 the environmental conditions. The former is expressed, for example, by his 
@@
 \item[(i)] The walking attitude of a pedestrian may appear somewhat 
-``assertive'' if he (she) reacts actively to unexpected behaviors 
+ \textcolor{red}{\sout{``assertive''} ``aggressive''} if he (she) reacts actively to unexpected behaviors 
 \cite{lakoba_2005,helbing_1995}. The smaller the reaction time, the more 
-assertive or aggresive observed posture. The associated parameter to this 
+\textcolor{red}{\sout{assertive or}}  aggressive observed posture. The associated parameter to this 
 behavior is the relaxation or characteristic time $\tau$ 
@@
 crowded environments because they perceive not enough space for taking a 
-step  \cite{johansson_2009}. This (perceived) step distance is therefore an 
-influential parameter on the pedestrians behavior. It is known as the 
-characteristic length $B$.
+step  \cite{johansson_2009}. \textcolor{red}{\sout{This (perceived) step distance 
+is therefore an influential parameter on the pedestrians behavior.} The perceived 
+step distance is associated with the personal space (private-sphere),
+ which therefore influences the pedestrian behavior. } 
+It is known as the characteristic length $B$.
 
@@
 $F=k(x)\,x$ and the compressibility $k_n(x)$ reported in Table~\ref{table_data}. 
-An ``uncomfortable'' body force of $30\,$N can address compressions in the 
+An ``uncomfortable'' body force \textcolor{red}{\sout{of $30\,$N}} can address compressions in the 
 range of $0.030-0.055\,$m. Also, a ``hitting'' force of $60\,$N can address 
@@
 Besides, no realiable values for the sliding friction $\kappa$ appears to be 
-available in the literature (to our knowledge). We may pressume, however, that 
+available in the literature (to our knowledge). We may presume, however, that 
 the sliding friction approaches a fraction of the body force. We will come back 
@@
 The numerical setting of the parameters may affect the dynamics of the 
-pedestrians. Some settings, however, yield similar collective dynamics. In 
-order to investigate these similarities, we introduce unit-less magnitudes 
+pedestrians. Some settings, however, yield similar collective dynamics.
+\textcolor{red}{\sout{In order to investigate these similarities, we} We}
+ introduce unit-less magnitudes 
 and proceed straightforward as indicated in \ref{appendix1}. We realize from 

### 2020-01-29 paper.tex
deshice un cambio de la explicacion del parametro B

@@
 crowded environments because they perceive not enough space for taking a 
-step  \cite{johansson_2009}. \textcolor{red}{\sout{This (perceived) step distance 
-is therefore an influential parameter on the pedestrians behavior.} The perceived 
-step distance is associated with the personal space (private-sphere),
- which therefore influences the pedestrian behavior. } 
+step  \cite{johansson_2009}. This (perceived) step distance 
+is therefore an influential parameter on the pedestrians behavior. 
 It is known as the characteristic length $B$.
@@
 values for the compressibility $k_n$ since these experiments were carried out 
-under low density conditions. Notice that the minimum (perceived) step distance 
-is $0.36\,$m \cite{seyfried_2007}, but the pedestrians seem to require larger 
+under low density conditions. \textcolor{red}{\sout{Notice that the} The} 
+minimum (perceived) step distance 
+is $0.36\,$m \textcolor{red}{according to Ref.}\cite{seyfried_2007}, but the
+ pedestrians seem to require larger 
 distances when they walk faster. The commonly accepted value $B\simeq 

### 2020-01-29 paper.tex
correcciones menores

@@
 
-In Fig.
-\ref{flow_density} we show the flow as a function of the global density (fundamental diagram).
-\ref{flow_density_no_body_force} corresponds to zero body force (\textit{i.e.} $k_n=0$), Fig.~\ref{flow_density_body_force} corresponds to a body force with $k_n$=1.2~E5.
-Each curve correspond to a different friction value (see the caption).\\
-
-According to most of the empirical measurements, the flow decreases for high enough values of density because the crowd becomes jammed.
-Notice that the original friction does not produce a reduction of the flow when there is zero body force but when the body force is included (with the original SFM value), the flow reduces from  5 p m$^{-2}$ to 7 p m$^{-2}$ and increases for higher values of density.
-When the friction is five times the original value, the flow reduces for densities higher than 5 p m$^{-2}$ in both cases (with body force and without body force).
-The main qualitative difference is that including the body force produces a subtle increment in the flow for densities higher than 7 p m$^{-2}$.
-When the friction is increased by a factor of ten, the flow reduces or remains constant when the density is higher than 5 p m$^{-2}$ for both cases (with body force and without body force).
-This result suggests that even including the body force, the original SFM requires an increment of the friction in order to reproduce the flow reduction reported in empirical measurements.\\
-
-\begin{figure}[!htbp]
-\centering
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_nobodyforce.eps}\label{flow_density_no_body_force}}\ 
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_bodyforce.eps}\label{flow_density_body_force}}\\
-\caption[width=0.47\columnwidth]{Flow vs.
-global density.
-The flow is calculated in a circular area of R=1~m at the center of the corridor.
-The circular markers correspond to the original friction of the SFM, the "+" symbol corresponds to the friction increased by a factor of five and the triangles correspond to the friction increased by a factor of ten.
-The desired velocity was $v_d=1$ in all the cases.
-(a) corresponds to simulations without body force and (b) corresponds to a body force with $k_n=$1.2~E5.}
-\label{flow_density}
-\end{figure}
-
 In the same way as with the bottleneck geometry, we computed the contact network to study the topological differences that arise from increasing the $k_n$ value.
@@
 
-To conclude this section, we remark that increasing the stiffness produces the opposite results in corridors respect to bottlenecks.
+\subsection{Dimensionless numbers and comparison with empirical data}
+
+Fig.
+\ref{flow_density} shows the flow as a function of the global density (fundamental diagram).
+\ref{flow_density_no_body_force} corresponds to zero body force (\textit{i.e.} $k_n=0$), Fig.~\ref{flow_density_body_force} corresponds to a body force with $k_n$=1.2~E5.
+Each curve correspond to a different friction value (see the caption).\\
+
+According to most of the empirical measurements, the flow decreases for high enough values of density because the crowd becomes jammed.
+Notice that the original friction does not produce a reduction of the flow when there is zero body force but when the body force is included (with the original SFM value), the flow reduces from  5 p m$^{-2}$ to 7 p m$^{-2}$ and increases for higher values of density.
+When the friction is five times the original value, the flow reduces for densities higher than 5 p m$^{-2}$ in both cases (with body force and without body force).
+The main qualitative difference is that including the body force produces a subtle increment in the flow for densities higher than 7 p m$^{-2}$.
+When the friction is increased by a factor of ten, the flow reduces or remains constant when the density is higher than 5 p m$^{-2}$ for both cases (with body force and without body force).
+This result suggests that even including the body force, the original SFM requires an increment of the friction in order to reproduce the flow reduction reported in empirical measurements.\\
+
+\begin{figure}[!htbp]
+\centering
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_nobodyforce.eps}\label{flow_density_no_body_force}}\ 
+    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_bodyforce.eps}\label{flow_density_body_force}}\\
+\caption[width=0.47\columnwidth]{Flow vs.
+global density.
+The flow is calculated in a circular area of R=1~m at the center of the corridor.
+The circular markers correspond to the original friction of the SFM, the "+" symbol corresponds to the friction increased by a factor of five and the triangles correspond to the friction increased by a factor of ten.
+The desired velocity was $v_d=1$ in all the cases.
+(a) corresponds to simulations without body force and (b) corresponds to a body force with $k_n=$1.2~E5.}
+\label{flow_density}
+\end{figure}
+
+To conclude section \ref{results}, we remark that increasing the stiffness produces the opposite results in corridors respect to bottlenecks.
 The walls in the corridors play a critical role that prevents pedestrians from detaching from each other.

### 2020-01-30 paper.tex
agregue texto a la ultima seccion de resultados

@@
 
+In this section, we inspect different values of the dimensionless numbers $\mathcal{K}_c$ and $\mathcal{K}$ and compare the results with the empirical measurements of Ref.~\cite{helbing_2007}.
+We varied the body force coefficient ($k_c$) and the friction coefficient ($k_t$) to inspect different values of $\mathcal{K}_c$ and $\mathcal{K}$ respectively.\\
+
+The empirical measurements correspond to the fundamental diagram at the entrance of the Jamaraat bridge (see the inset in Fig.~\ref{flow_density_no_body_force}).
+We aim to reproduce the qualitative behavior of these measurements roughly.\\
+
+Figs.
+\ref{flow_density} show the flow as a function of the global density (fundamental diagram).
+\ref{flow_density_no_body_force} corresponds to $\mathcal{K}_c=$ 0 (zero body force \textit{i.e.} $k_n=0$) while Fig.~\ref{flow_density_body_force} corresponds to $\mathcal{K}_c=$68 (which is the value of the original SFM with $k_n$=1.2~E5 ).
+Each curve correspond to a different friction value, hence different $K_t$ value (see the caption).\\
+
+According to most of the empirical measurements of the fundamental diagram, the flow decreases for high enough values of density because the crowd becomes jammed.
+Notice that the original friction ($\mathcal{K}=$137) does not produce a reduction of the flow when there is zero body force.
+Nevertheless, when the body force is included, and we remain the original friction (circles from Fig.~\ref{flow_density_body_force}), the flow reduces from  5 p m$^{-2}$ to 7 p m$^{-2}$ and increases for higher values of density.\\
+
+When the dimensionless number associated with the friction is $\mathcal{K} = $ 685 
+(the friction is five times the original SFM value), the flow reduces for densities higher than 5 p m$^{-2}$ in both cases (with body force and without body force).
+The main qualitative difference is that including the body force produces a subtle increment in the flow for densities higher than 7 p m$^{-2}$ (black curve of Fig.~\ref{flow_density_no_body_force}).
+\\
+
+When the dimensionless number associated to the friction is $\mathcal{K}=$1371  (the friction is ten times the original SFM value), in this case, the flow reduces or remains constant when the density is higher than 5 p m$^{-2}$ for both cases (with body force and without body force).\\
+
+These results suggest that although increasing $\mathcal{K}_c$ produces a reduction in flow, it is necessary to increase $\mathcal{K}$ (for instance, increasing friction $k_t$) to reproduce the reduction in the flow that characterizes the high-density regime.
+It is still a pending challenge to find the values of the dimensionless numbers that reproduce the qualitative behavior of the fundamental diagram, but this first approach narrows down the search.\\
+
+\begin{comment}
 Fig.
@@
 This result suggests that even including the body force, the original SFM requires an increment of the friction in order to reproduce the flow reduction reported in empirical measurements.\\
+\end{comment}
 
@@
 \\
-
-\section{\label{discussion}Discussion}
 

### 2020-01-30 plots/corridor/fundamental_diagram/kn0/flow_density_multi.py
agregue data empirica diagrama fundamental

@@ -115,8 +115,45 @@ pylab.ylim(0.0,6)
 #pylab.xlim(1.0, 10)
 #pylab.yticks(np.arange(3,11,2))
 #pylab.xticks(np.arange(0,1100,200))
-pylab.title("$k_n=$0")
-lgd=plt.legend(numpoints=1,handlelength=0.8) 
-plt.legend(frameon=False,loc='upper left',labelspacing=0.2,borderpad=0.3,handletextpad=0.5,fontsize=7,numpoints=1) 
+pylab.title("$\\mathcal{K}_c=$ 0")
+#lgd=plt.legend(numpoints=1,handlelength=0.8) 
+#plt.legend(frameon=False,loc='upper left',labelspacing=0.2,borderpad=0.3,handletextpad=0.5,fontsize=7,numpoints=1) 
+
+
+############ Insert plot ############
+
+
+
+data_johansson = np.genfromtxt('Flujo_vs_densidad_Helbing_2007.dat', delimiter = '')
+density_johansson = data_johansson[:,0] 
+flow_johansson = data_johansson[:,1] 
+
+############  PLOT  ############
+
+
+left, bottom, width, height = [0.15, 0.60, 0.28, 0.28]
+ax2 = fig.add_axes([left, bottom, width, height])
+
+ax2.plot(density_johansson,flow_johansson,'*',color='orange',markeredgecolor='orange',markersize=2) 
+fig.patch.set_facecolor('black')
+#pylab.yticks(np.arange(0,1.1,1),size='4.5')
+#pylab.xticks(np.arange(0,1.1,1),size='0.0')
+pylab.xlabel('Density ',size='4.5',labelpad=1)
+pylab.ylabel('Flow  ',size='3.5',labelpad=-6,zorder=1)
+#pylab.ylim(0.3, 1.1)
+#pylab.xlim(0, 1.02)
+#ax2.tick_params(axis='y', pad=-4)
+ax2.set_yticklabels([])
+plt.tick_params(axis='x',which='both',bottom=False,top=False,labelbottom=False) 
+plt.tick_params(axis='y',which='both',bottom=False,top=False,labelbottom=False) 
+
+ax2.xaxis.set_ticks_position('none') 
+ax2.yaxis.set_ticks_position('none') 
+ax2.grid(False)
+plt.text(1.05, -0.1, "0", size=4.5)
+#plt.text(9, -0.1, "10", size=4.5)
+plt.text(0.25, 1.7, "2", size=4.5)
+
+
[…]

### 2020-01-30 plots/corridor/fundamental_diagram/kn0/flow_density_multi.py
cambie los colores del diagrama fundamental

@@ -82,29 +82,16 @@ speed_ktx10_kn0 = np.divide(flow_ktx10_kn0,density_ktx10_kn0)
 
 fig, ax1 = plt.subplots()
 
-plt.plot(global_density_kn0_kt,flow_kn0_kt,'y-o',mew=0.7,markerfacecolor='y',markeredgecolor='k',markersize=4,zorder=3,label='$\\kappa = 1 \\times \\kappa_o$') 
-plt.errorbar(global_density_kn0_kt,flow_kn0_kt, yerr=std_flow_kn0_kt,color='y')
+plt.plot(global_density_kn0_kt,flow_kn0_kt,'-o',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$\\kappa = 1 \\times \\kappa_o$') 
+plt.errorbar(global_density_kn0_kt,flow_kn0_kt, yerr=std_flow_kn0_kt,color='b')
 
-plt.plot(global_density_ktx5_kn0,flow_ktx5_kn0,'k-+',mew=0.7,markerfacecolor='g',markeredgecolor='k',markersize=4,zorder=3,label='$\\kappa = 5 \\times \\kappa_o$') 
-plt.errorbar(global_density_ktx5_kn0,flow_ktx5_kn0, yerr=std_flow_ktx5_kn0,color='k')
+plt.plot(global_density_ktx5_kn0,flow_ktx5_kn0,'-+',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$\\kappa = 5 \\times \\kappa_o$') 
+plt.errorbar(global_density_ktx5_kn0,flow_ktx5_kn0, yerr=std_flow_ktx5_kn0,color='orange')
 
-plt.plot(global_density_ktx10_kn0,flow_ktx10_kn0,'g-^',mew=0.7,markerfacecolor='g',markeredgecolor='k',markersize=4,zorder=3,label='$\\kappa = 10 \\times \\kappa_o$') 
+plt.plot(global_density_ktx10_kn0,flow_ktx10_kn0,'-^',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$\\kappa = 10 \\times \\kappa_o$') 
 plt.errorbar(global_density_ktx10_kn0,flow_ktx10_kn0, yerr=std_flow_ktx10_kn0,color='g')
 
[…]

### 2020-01-30 paper.tex
correcciones de gramatica en resultados

--- 2020-01-29 paper.tex
@@
 
+In this section, we inspect different values of the dimensionless numbers $\mathcal{K}_c$ and $\mathcal{K}$ and compare the results with the empirical measurements of Ref.~\cite{helbing_2007}.
+We varied the body force coefficient ($k_c$) and the friction coefficient ($k_t$) to inspect different values of $\mathcal{K}_c$ and $\mathcal{K}$ respectively.\\
+
+The empirical measurements correspond to the fundamental diagram at the entrance of the Jamaraat bridge (see the inset in Fig.~\ref{flow_density_no_body_force}).
+We aim to reproduce the qualitative behavior of these measurements roughly.\\
+
+Figs.
+\ref{flow_density} show the flow as a function of the global density (fundamental diagram).
+Fig.~\ref{flow_density_no_body_force} corresponds to $\mathcal{K}_c=$ 0 (zero body force \textit{i.e.} $k_n=0$) while Fig.~\ref{flow_density_body_force} corresponds to $\mathcal{K}_c=$68 (which is the value of the original SFM with $k_n$=1.2~E5 ).
+Each curve correspond to a different friction value, hence different $k_t$ value (see the caption).\\
+
+According to most of the empirical measurements of the fundamental diagram, the flow decreases for high enough values of density because the crowd becomes jammed.
+Notice that the original friction (corresponding to $\mathcal{K}=$137) does not produce a reduction of the flow when there is zero body force ($\mathcal{K}_c$=0).
+Nevertheless, when the body force is included, and we remain the original friction (circles from Fig.~\ref{flow_density_body_force}), the flow reduces from  5 p m$^{-2}$ to 7 p m$^{-2}$ and then increases for higher values of density.\\
+
+When the dimensionless number associated with the friction is $\mathcal{K} = $ 685 (the friction is five times the original SFM value), the flow reduces for densities higher than 5 p m$^{-2}$ in both cases (with body force and without body force).
+The main qualitative difference is that including the body force produces a subtle increment in the flow for densities higher than 7 p m$^{-2}$ (orange curve of Fig.~\ref{flow_density_no_body_force}).
+\\
+
+When the dimensionless number associated to the friction is $\mathcal{K}=$1371  (the friction is ten times the original SFM value), in this case, the flow reduces or remains constant when the density is higher than 5 p m$^{-2}$ for both cases (with $\mathcal{K}_c=$ 0 and $\mathcal{K}_c = $ 68).\\
+
+These results suggest that although increasing $\mathcal{K}_c$ produces a reduction in the flow, it is necessary to increase $\mathcal{K}$ (for instance, increasing friction $k_t$) to reproduce the reduction in the flow that characterizes the high-density regime.
+It is still a pending challenge to find the values of the dimensionless numbers that reproduce the qualitative behavior of the fundamental diagram, but this first approach narrows down the search.\\
+
+\begin{comment}
 Fig.
@@
 The desired velocity was $v_d=1$ in all the cases.
-(a) corresponds to simulations without body force and (b) corresponds to a body force with $k_n=$1.2~E5.}
+(a) corresponds to simulations without body force ($\mathcal{K}_c =$0) and (b) corresponds to a body force with the original value of the body stiffness ($\mathcal{K}_c =$68).}
 \label{flow_density}

### 2020-01-30 paper.tex
correcciones de gramatica en la intro

@@
 the SFM context \cite{lakoba_2005}. As a matter of fact, the usual setting by 
-Helbing prevents the overlapping among pedestrians, but it is known to 
+Helbing prevents the \textcolor{red}{excessive} overlapping among pedestrians, but it is known to 
 accomplish artificially high force levels 
@@
 
-Table~\ref{table_data} shows a few empirical figures for the most common 
+Table~\ref{table_data} shows a few empirical \textcolor{red}{\sout{figures} values}
+ for the most common 
 parameters. More data is available throughout the literature (see, for example, 
@@
 acceleration (or deceleration) of the pedestrian due to his (her) own willings. 
-The social force $\mathbf{f}_s$, intead, describes the tendency of the 
+The social force $\mathbf{f}_s$, \textcolor{red}{\sout{intead} instead}, describes the tendency of the 
 pedestrians to stay away from each other. The granular force $\mathbf{f}_g$ 
@@
 
-The net distance $|R_{ij}-r_{ij}|$ scales to the parameter $B$ in the 
+The net distance \textcolor{red}{(overlap)} $|R_{ij}-r_{ij}|$ scales to the parameter $B$ in the 
 expression (\ref{eqn_social}). This parameter plays the role of a fall-off 
@@
 parameters are represented as elements within each set. The shared elements 
-between $\mathcal{A}$, $\mathcal{K}$ and $\mathcal{K}_c$ are placed inside de 
+between $\mathcal{A}$, $\mathcal{K}$ and $\mathcal{K}_c$ are placed inside the 
 intersecting regions. \\

### 2020-01-31 plots/corridor/velocity_profile/plot_velocity_profile.py
mejore el grafico del perfil de velocidades

@@ -70,8 +70,8 @@ def plot_triangles(file_name,simbol,color,label):
      vx = df['mean vx'].tolist()
      std_vx = df['std vx'].tolist()
 
-     plt.errorbar(y,vx,std_vx,color=color)     
      plt.plot(y,vx,simbol,color=color,mec='k',mew=0.8,linewidth = '1',markersize=4,label=label)     
+     plt.errorbar(y,vx,std_vx,color=color,zorder =1)     
      pylab.grid(False)
      pylab.xlabel('y~(m)')
      pylab.ylabel('$v_x$~(m/s)')

### 2020-01-31 paper.tex
agregue las working hypotheses en español

@@
 
-\textcolor{red}{The Social Force Model (SFM) is a pedestrian dynamics model that
-considers three kinds of forces: desired forces, social forces, and physical forces.
+The Social Force Model (SFM) models the crowd dynamics 
+considering three kinds of force: desired forces, social forces, and physical forces.
 In its original version, the SFM, addresses two physical forces as essential: 
-\sout{The Social Force Model (SFM) addresses two physical forces as 
-\textit{essential}:}} the ``body force'' and the ``sliding friction''. Both are 
+ the ``body force'' and the ``sliding friction''. Both are 
 inspired by granular interactions and were claimed to be necessary  
@@
 the SFM context \cite{lakoba_2005}. As a matter of fact, the usual setting by 
-Helbing prevents the \textcolor{red}{excessive} overlapping among pedestrians, but it is known to 
+Helbing prevents the excessive overlapping among pedestrians, but it is known to 
 accomplish artificially high force levels 
@@
 The 
-point seems to be that the SFM focuses on the \textcolor{red}{``collective behavior''
- \sout{``incoordination phenomenon''}} due 
+point seems to be that the SFM focuses on the ``collective behavior'' due 
 to clogging, missing the ``individualistic'' perspective  of single pedestrians 
@@
 
-\textcolor{red}{A unique (and universal) setting appears not available yet. 
-\sout{A meaningful (individualistic) numerical setting appears not available yet (to 
-our knowledge).}} The reason is that different numerical settings can lead to 
+A unique (and universal) setting appears not available yet to
+our knowledge. 
+ The reason is that different numerical settings can lead to 
 the same crowd dynamics. Actually, only a small set of dimensionless 
@@
 \cite{marchetti_2014}. We may hypothesize that while the dimensionless 
-``numbers'' provide some kind of control on the \textcolor{red}{\sout{
-``incoordination phenomenon''} collective behavior} in 
+``numbers'' provide some kind of control on the 
+collective behavior in 
 crowds, only a few numerical settings can attain an ``individualistic'' 
@@
 We now widen the investigation on the parameter settings to include the one 
-associated to the body force. We will \textcolor{red}{\sout{focus} explore} 
-on the complex interplay between 
+associated to the body force. We will  explore 
+ the complex interplay between 
 the body force and the sliding friction among pedestrians. Recall that the 
@@
 scenario in Sections \ref{bottleneck} and \ref{corridor}, respectively. 
-Section \ref{discussion} opens a detailed discussion raising from of the results 
-in Section \ref{results}. The last Section closes the investigation with our 
-main conclusions.
+Section \ref{conclusions} opens a detailed discussion from results in Section \ref{results}
+and resumes our main conclusions.
 
@@
 
-The complex behavior of pedestrians \textcolor{red}{\sout{feature} features}
+The complex behavior of pedestrians features
  either his (her) feelings and 
@@
 \item[(i)] The walking attitude of a pedestrian may appear somewhat 
- \textcolor{red}{\sout{``assertive''} ``aggressive''} if he (she) reacts actively to unexpected behaviors 
+  ``aggressive'' if he (she) reacts actively to unexpected behaviors 
 \cite{lakoba_2005,helbing_1995}. The smaller the reaction time, the more 
-\textcolor{red}{\sout{assertive or}}  aggressive observed posture. The associated parameter to this 
+ aggressive observed posture. The associated parameter to this 
 behavior is the relaxation or characteristic time $\tau$ 
@@
 \item[(ii)] Despite the reactive attitude $\tau$, the pedestrian addresses a 
-``free'' (undisturbed) walking speed $v_0$. This speed expresses his (her) 
+``free'' (undisturbed) walking speed $v_d$. This speed expresses his (her) 
 motivation or intention to reach a certain destination (as comfortable as 
@@
 
-Table~\ref{table_data} shows a few empirical \textcolor{red}{\sout{figures} values}
+Table~\ref{table_data} shows a few empirical values
  for the most common 
@@
 \caption{The experimental data for the pedestrian parameters, as explained in 
-Section~\ref{experimental}. The magnitude $v$ means de pedestrian velocity 
+Section~\ref{experimental}. The magnitude $v$ means the actual pedestrian velocity 
 (m/s). The magnitude $x$ means the compression length (m). The upper row for 
-Ref.~\cite{song_2019} corresponds data acquired in winter and the lower row to 
-datas acquiquired in summer. The asterisk ($^*$) corresponds to reasonable 
+Ref.~\cite{song_2019} corresponds to data acquired in winter and the lower row to 
+data acquired in summer. The asterisk ($^*$) corresponds to reasonable 
 estimates from the authors. }
@@
 A first examination of the figures in Table~\ref{table_data} shows that the 
-choise $\tau\simeq0.6\,$s seems to be a reasonable estimation for the 
+choice $\tau\simeq0.6\,$s seems to be a reasonable estimation for the 
 relaxation time, although this may vary with respect to gender or culture 
@@
 values for the compressibility $k_n$ since these experiments were carried out 
-under low density conditions. \textcolor{red}{\sout{Notice that the} The} 
-minimum (perceived) step distance 
-is $0.36\,$m \textcolor{red}{according to Ref.}\cite{seyfried_2007}, but the
+under low density conditions.  The minimum (perceived) step distance 
+is $0.36\,$m according to Ref.~\cite{seyfried_2007}, but the
  pedestrians seem to require larger 
@@
 providing information on the step distance $B$, but estimates for the 
-desired speed and the body compresibility could be achieved. The reported 
+desired speed and the body compressibility could be achieved. The reported 
 magnitude $k_n$ assesses either the clothes and the body compressibility. The 
@@
 
-We measured the maximum attainable forces at the subway in Buenos Aires, 
+We measured the maximum attainable forces during the spring of 2019 at the subway in Buenos Aires, 
 Argentina. Our preliminary results show that pedestrians feel ``uncomfortable'' 
@@
 
-The maximum (realistic) compressions may be computed from the relation 
-$F=k(x)\,x$ and the compressibility $k_n(x)$ reported in Table~\ref{table_data}. 
-An ``uncomfortable'' body force \textcolor{red}{\sout{of $30\,$N}} can address compressions in the 
+The maximum (realistic) compressions may be computed from the hook relation 
+$F(x)=k_n(x)\,x$ and the compressibility $k_n(x)$ reported in Table~\ref{table_data}. 
+An ``uncomfortable'' body force  $10\,$N $-$ $30\,$N can address compressions in the 
 range of $0.030-0.055\,$m. Also, a ``hitting'' force of $60\,$N can address 
@@
 
-Besides, no realiable values for the sliding friction $\kappa$ appears to be 
+Besides, no reliable values for the sliding friction $\kappa$ appears to be 
 available in the literature (to our knowledge). We may presume, however, that 
@@
 acceleration (or deceleration) of the pedestrian due to his (her) own willings. 
-The social force $\mathbf{f}_s$, \textcolor{red}{\sout{intead} instead}, describes the tendency of the 
+The social force $\mathbf{f}_s$, instead, describes the tendency of the 
 pedestrians to stay away from each other. The granular force $\mathbf{f}_g$ 
@@
 
-The net distance \textcolor{red}{(overlap)} $|R_{ij}-r_{ij}|$ scales to the parameter $B$ in the 
+The net distance (overlap) $|R_{ij}-r_{ij}|$ scales to the parameter $B$ in the 
 expression (\ref{eqn_social}). This parameter plays the role of a fall-off 
@@
 pedestrians. Some settings, however, yield similar collective dynamics.
-\textcolor{red}{\sout{In order to investigate these similarities, we} We}
- introduce unit-less magnitudes 
+We introduce unit-less magnitudes 
 and proceed straightforward as indicated in \ref{appendix1}. We realize from 
@@
 complex context. We will investigate this context in section~\ref{results}. \\
+
+\section{\label{hypotheses}Working hypotheses and procedure}
+
+\begin{itemize}
+
+\item 1)  Nos enfocamos en estudiar principalmente los efectos del parametro kn. Variamos kn en la mayoria de los resultados, salvo en el diagrama fundamental donde tambien variamos kt.
+
+\item 2)  No usamos anisotropia. Estamos interesados en las situaciones de alta densidad donde suponemos que la anisotropia no juega ningun papel relevante.
+
+\item 3) Las simulaciones numéricas las hacemos con LAMMPS usando módulos creados por nosotros para calcular las fuerzas del modelo de Helbing.
+
+\item 4) Exploramos situaciones de muy alta densidad (muy alta presion), sabemos que en estas situaciones pueden producirse caidas y desmayos pero en este paper ignoramos esos efectos.
+
+\end{itemize}
 

### 2020-01-31 paper.tex
agregue un parrafo en resultados y otro en conclusion

@@
 
+To conclude section \ref{corridor}, we remark that increasing the stiffness produces the opposite results in corridors respect to bottlenecks.
+The walls in the corridors play a critical role that prevents pedestrians from detaching from each other.
+This effect has consequences such as increasing the connectivity of the contact network and flattening the velocity profile (thus reducing the strain rate).
+If the stiffness is high enough, the pedestrians can not push to the pedestrian ahead since the body force repulsion becomes very high.
+This leads to a "solidification" of the crowd that makes all the pedestrians walk at almost the same velocity.
+The pedestrians that are in contact with the wall are the ones who determine the velocity of the whole crowd.
+\\
+
 \subsection{Dimensionless numbers and comparison with empirical data}
@@
 According to most of the empirical measurements of the fundamental diagram, the flow decreases for high enough values of density because the crowd becomes jammed.
-Notice that the original friction (corresponding to $\mathcal{K}=$137) does not produce a reduction of the flow when there is zero body force ($\mathcal{K}_c$=0).
+Notice that the original friction (corresponding to $\mathcal{K}=$137) does not produce a reduction of the flow when there is zero body force ($\mathcal{K}_c=$0).
 Nevertheless, when the body force is included, and we remain the original friction (circles from Fig.~\ref{flow_density_body_force}), the flow reduces from  5 p m$^{-2}$ to 7 p m$^{-2}$ and then increases for higher values of density.\\
 
-When the dimensionless number associated with the friction is $\mathcal{K} = $ 685 (the friction is five times the original SFM value), the flow reduces for densities higher than 5 p m$^{-2}$ in both cases (with body force and without body force).
-The main qualitative difference is that including the body force produces a subtle increment in the flow for densities higher than 7 p m$^{-2}$ (orange curve of Fig.~\ref{flow_density_no_body_force}).
+When the dimensionless number associated with the friction is $\mathcal{K} = $ 685, the friction is five times the original SFM value.
+In this scenario, the flow reduces for densities higher than 5 p m$^{-2}$ in both cases (with body force and without body force).
+The main qualitative difference is that including the body force produces a subtle increment in the flow for densities higher than 7 p m$^{-2}$ (orange curve from Fig.~\ref{flow_density_no_body_force}).
 \\
@@
 When the dimensionless number associated to the friction is $\mathcal{K}=$1371  (the friction is ten times the original SFM value), in this case, the flow reduces or remains constant when the density is higher than 5 p m$^{-2}$ for both cases (with $\mathcal{K}_c=$ 0 and $\mathcal{K}_c = $ 68).\\
+
+It worth mentioning that the SFM contemplates the possibility of overlapping between pedestrians (unlike the models stated in Refs.~\cite{kabalan_2017,jebrane_2019}).
+Despite this hard-to-interpret feature, the SFM can reproduce empirical behaviors of collective pedestrian dynamics.\\
 
@@
 
-To conclude section \ref{results}, we remark that increasing the stiffness produces the opposite results in corridors respect to bottlenecks.
-The walls in the corridors play a critical role that prevents pedestrians from detaching from each other.
-This effect has consequences such as increasing the connectivity of the contact network, flattening the velocity profile (thus reducing the strain rate).
-If the stiffness is high enough, the pedestrians can not push to the pedestrian ahead since the body force repulsion becomes very high.
-This leads to a"solidification" of the crowd that makes all the pedestrians walk at almost the same velocity.
-The pedestrians that are in contact with the wall are the ones who determine the velocity of the whole crowd.
-\\
-
 \section{\label{conclusions}Conclusions}
@@
 
-Regarding the parameters of the model, we found out that it is possible to reduce the original SFM parameters to three dimensionless parameters.
+Regarding the parameters of the model, we found that it is possible to reduce the original SFM parameters to three dimensionless parameters.
 The original parameters interrelate to each other through the dimensionless ones.
 Many different settings can produce the same dimensionless parameters.
-Thus, no univocal relations can be established between the individualistic parameters and collective dynamics.\\
+Thus, no univocal relations can be established between the individualistic parameters and collective dynamics.
+In order to explore the outcomes from different dimensionless numbers, we compared numerical results with empirical measurements.
+We found good candidates to reproduce the qualitative behavior of empirical measurements in the range and $0 < \mathcal{K}_c < 68$ with $\mathcal{K} = 685$.
+Nevertheless, this is a first sketch to arrive at a set of dimensionless parameters that may be suitable to reproduce empirical measurements.
+We encourage further research that seeks to find the values of the dimensionless numbers that can reproduce experimental data.\\
 

### 2020-01-31 plots/bottleneck/te/plot_fis.py
mejoras en los graficos

@@ -76,18 +76,18 @@ std_te = data.groupby(data['vd'])['te'].std().values.tolist()
 ###  PLOT  ###
 
 ### No compression ###
-plt.plot(vd,avg_te,'-cs',mew=0.7,mec='k',markersize=4,label='$k_n =$ 0 ') 
-plt.errorbar(vd,avg_te,std_te,linestyle='none',fmt='none',color='none',ecolor='c') 
+plt.plot(vd,avg_te,'-s',mew=0.7,mec='k',markersize=4,label='$k_n =$ 0 ') 
+plt.errorbar(vd,avg_te,std_te,linestyle='none',fmt='none',color='b',ecolor='#1f77b4') 
 
 ### With compression ###
-plt.plot(vd_kcomp_E4,avg_te_kcomp_E4,'-y^',mew=0.7,mec='k',markersize=4,label='$k_n =$ 1.2 E4 ') 
-plt.errorbar(vd_kcomp_E4,avg_te_kcomp_E4,std_te_kcomp_E4,linestyle='none',fmt='none',color='none',ecolor='y') 
+plt.plot(vd_kcomp_E4,avg_te_kcomp_E4,'-^',mew=0.7,mec='k',markersize=4,label='$k_n =$ 1.2 E4 ') 
+plt.errorbar(vd_kcomp_E4,avg_te_kcomp_E4,std_te_kcomp_E4,linestyle='none',fmt='none',color='orange',ecolor='#ff7f0e') 
 
-plt.plot(vd_6E4,avg_te_6E4,'-rv',mew=0.7,mec='k',markersize=4,label='$k_n =$ 6 E4') 
-plt.errorbar(vd_6E4,avg_te_6E4,std_te_6E4,linestyle='none',fmt='none',color='none',ecolor='r') 
+plt.plot(vd_6E4,avg_te_6E4,'-v',color='firebrick',mew=0.7,mec='k',markersize=4,label='$k_n =$ 6 E4') 
+plt.errorbar(vd_6E4,avg_te_6E4,std_te_6E4,linestyle='none',fmt='none',color='firebrick',ecolor='firebrick') 
 
-plt.plot(vd_kcomp_E5,avg_te_kcomp_E5,'-bx',mew=0.7,mec='k',markersize=4,label='$k_n =$ 1.2 E5') 
[…]

### 2020-01-31 plots/corridor/velocity_profile/plot_velocity_profile.py

@@ -41,13 +41,13 @@ def main():
 
      file_name = 'vx_profile_kn0.txt'
      simbol ='-s'
-     color = 'c'
+     color = 'b'
      label = "$k_n=$~0"
      plot_triangles(file_name,simbol,color,label)
 
      file_name = 'vx_profile_kn1.2E5.txt' 
      simbol ='-x'
-     color = 'b'
+     color = 'orange'
      label = "$k_n=1.2$~E5"
      plot_triangles(file_name,simbol,color,label)
 

### 2020-02-03 plots/bottleneck/te/plot_fis.py
mejore grafico de triangulos y agregue el kn2.6E4 al grafico de tiempo de evacuacion

@@ -42,7 +42,7 @@ pylab.rcParams.update(params)
 ### DATA ###
 
 
-data_kcomp_E4 = pd.read_csv("tevsvd_N225_k12000.txt", header=None,delimiter=' ') 
+data_kcomp_E4 = pd.read_csv("tevsvd_N225_k26200.txt", header=None,delimiter=' ') 
 data_kcomp_E4.columns=['vd','iter','te','N_quedaron','nan']
 vd_kcomp_E4 = list(data_kcomp_E4.vd.unique())
 avg_te_kcomp_E4 = data_kcomp_E4.groupby(data_kcomp_E4['vd'])['te'].mean().values.tolist()
@@ -80,7 +80,7 @@ plt.plot(vd,avg_te,'-s',mew=0.7,mec='k',markersize=4,label='$k_n =$ 0 ')
 plt.errorbar(vd,avg_te,std_te,linestyle='none',fmt='none',color='b',ecolor='#1f77b4') 
 
 ### With compression ###
-plt.plot(vd_kcomp_E4,avg_te_kcomp_E4,'-^',mew=0.7,mec='k',markersize=4,label='$k_n =$ 1.2 E4 ') 
+plt.plot(vd_kcomp_E4,avg_te_kcomp_E4,'-^',mew=0.7,mec='k',markersize=4,label='$k_n =$ 2.62 E4 ') 
 plt.errorbar(vd_kcomp_E4,avg_te_kcomp_E4,std_te_kcomp_E4,linestyle='none',fmt='none',color='orange',ecolor='#ff7f0e') 
 
 plt.plot(vd_6E4,avg_te_6E4,'-v',color='firebrick',mew=0.7,mec='k',markersize=4,label='$k_n =$ 6 E4') 

### 2020-02-03 paper.tex
corregi la cita que sita el parametro experimental que es 2.62E4

@@
 up-triangles correspond to the value measured in 
-Ref.~\cite{anthropometric}, squares correspond 
+Ref.~\cite{melvin1988aatd}, squares correspond 
 to zero body force and circles correspond to an extreme value of stiffness (one 
@@
  down triangles correspond to an intermediate value between the empirical value 
-presented in Ref.~\cite{anthropometric} and the chosen by Helbing in 
+presented in Ref.~\cite{melvin1988aatd} and the chosen by Helbing in 
 Ref.~\cite{helbing_2000} }

### 2020-02-03 plots/bottleneck/degree_vs_vd/plot_degree_vs.py
mejore todos los graficos

@@ -40,7 +40,7 @@ vd_kn0 = data_kn0["vd"].tolist()
 mean_comp_kn0 = data_kn0["list_mean_degree"].tolist()
 std_comp_kn0 = data_kn0["list_std_degree"].tolist()
 
-data_knE4 = pd.read_csv("degree_vs_vd_kn12000.txt",sep="\t")
+data_knE4 = pd.read_csv("degree_vs_vd_k26200.txt",sep="\t")
 vd_knE4 = data_knE4["vd"].tolist()
 mean_comp_knE4 = data_knE4["list_mean_degree"].tolist()
 std_comp_knE4 = data_knE4["list_std_degree"].tolist()
@@ -63,10 +63,10 @@ std_comp_knE6 = data_knE6["list_std_degree"].tolist()
 ###  PLOT  ###
 fig, ax1 = plt.subplots()
 
-plt.plot(vd_kn0,mean_comp_kn0,'-cs',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=0$') 
-plt.plot(vd_knE4,mean_comp_knE4,'-y^',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$k_n=1.2$ E4') 
-plt.plot(vd_kn6E4,mean_comp_kn6E4,'-rv',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$k_n=6$ E4') 
-plt.plot(vd_kn,mean_comp_kn,'-bx',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$k_n=1.2$ E5') 
+plt.plot(vd_kn0,mean_comp_kn0,'-s',color='#1f77b4',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=0$') 
+plt.plot(vd_knE4,mean_comp_knE4,'-^',color = '#ff7f0e',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$k_n=2.6$ E4') 
+plt.plot(vd_kn6E4,mean_comp_kn6E4,'-v',color='firebrick',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$k_n=6$ E4') 
+plt.plot(vd_kn,mean_comp_kn,'-x',color = 'g',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$k_n=1.2$ E5') 
[…]

### 2020-02-03 plots/bottleneck/k_vs_vx/plot_k_vs_vx.py

@@ -58,9 +58,9 @@ std_vx_vd8 = data_vd8["std vx"].tolist()
 ###  PLOT  ###
 fig, ax1 = plt.subplots()
 
-plt.plot(k_vd2,mean_vx_vd2,'-bx',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$v_d=2$~m s$^{-1}$') 
-plt.plot(k_vd4,mean_vx_vd4,'-y^',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$v_d=4$~m s$^{-1}$') 
-plt.plot(k_vd6,mean_vx_vd6,'-rv',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$v_d=6$~m s$^{-1}$') 
+plt.plot(k_vd2,mean_vx_vd2,'-s',color='#1f77b4',mew=0.7,markeredgecolor='k',markersize=5,zorder=1,label='$v_d=2$~m s$^{-1}$') 
+plt.plot(k_vd4,mean_vx_vd4,'-^',color = '#ff7f0e',mew=0.7,markeredgecolor='k',markersize=5,zorder=3,label='$v_d=4$~m s$^{-1}$') 
+plt.plot(k_vd6,mean_vx_vd6,'-x',color = 'g',mew=0.7,markeredgecolor='k',markersize=5,zorder=1,label='$v_d=6$~m s$^{-1}$') 
 #plt.plot(k_vd8,mean_vx_vd8,'-rv',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$v_d=8$~m s$^{-1}$') 
 #plt.plot(vd_knE6,mean_comp_knE6,'-ko',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$k=1.2$ E6') 
 

### 2020-02-03 plots/bottleneck/pbc_vs_vd/plot_pbc_vs_vd.py

@@ -43,7 +43,7 @@ data_kn0 = pd.read_csv("vd_pbc_kn0.txt",sep=" ")
 vd_kn0 = data_kn0.iloc[:,0]
 pbc_kn0 =  data_kn0.iloc[:,1]
 
-data_knE4 = pd.read_csv("vd_pbc_kn12000.txt",sep=" ")
+data_knE4 = pd.read_csv("vd_pbc_kn26200.txt",sep=" ")
 vd_knE4 = data_knE4.iloc[:,0]
 pbc_knE4 =  data_knE4.iloc[:,1]
 
@@ -61,12 +61,12 @@ pbc_knE6 =  data_knE6.iloc[:,1]
 
 fig, ax1 = plt.subplots()
 
-plt.plot(vd_kn0,pbc_kn0,'-cs',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=$0') 
+plt.plot(vd_kn0,pbc_kn0,'-s',color='#1f77b4',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=$0') 
 
 
-plt.plot(vd_knE4,pbc_knE4,'-y^',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k=1.2$~E4') 
+plt.plot(vd_knE4,pbc_knE4,'-^',color = '#ff7f0e',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=2.6$~E4') 
 
-plt.plot(vd_knE5,pbc_knE5,'-bx',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=1.2$~E5') 
+plt.plot(vd_knE5,pbc_knE5,'-x',color = 'g',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=1.2$~E5') 
 
 
 plt.plot(vd_knE6,pbc_knE6,'-ko',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=1.2$~E6') 

### 2020-02-03 plots/corridor/degree_vs_density/plot_degree_vs.py

@@ -58,10 +58,10 @@ std_degree_knE6 = data_knE6["list_std_degree"].tolist()
 ###  PLOT  ###
 fig, ax1 = plt.subplots()
 
-plt.plot(vd_kn0,mean_degree_kn0,'-cs',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k=0$') 
-plt.plot(vd_knE4,mean_degree_knE4,'-y^',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k=1.2$ E4') 
-plt.plot(vd_kn,mean_degree_kn,'-bx',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k=1.2$ E5') 
-plt.plot(vd_knE6,mean_degree_knE6,'-ko',mew=0.7,markeredgecolor='k',markersize=3,zorder=3,label='$k=1.2$ E6') 
+plt.plot(vd_kn0,mean_degree_kn0,'-s',color='#1f77b4',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=0$') 
+plt.plot(vd_knE4,mean_degree_knE4,'-^',color = '#ff7f0e',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=1.2$ E4') 
+plt.plot(vd_kn,mean_degree_kn,'-x',color = 'g',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=1.2$ E5') 
+plt.plot(vd_knE6,mean_degree_knE6,'-ko',mew=0.7,markeredgecolor='k',markersize=3,zorder=3,label='$k_n=1.2$ E6') 
 
 pylab.grid(False)
 pylab.xlabel('density~(p m$^{-2})$')

### 2020-02-03 plots/corridor/overlap_vs_density/plot_overlap_vs.py

@@ -58,10 +58,10 @@ std_overlap_knE6 = data_knE6["list_std_overlap"].tolist()
 ###  PLOT  ###
 fig, ax1 = plt.subplots()
 
-plt.plot(dens_kn0,mean_overlap_kn0,'-cs',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k=0$') 
-plt.plot(dens_knE4,mean_overlap_knE4,'-y^',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k=1.2$ E4') 
-plt.plot(dens_kn,mean_overlap_kn,'-bx',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k=1.2$ E5') 
-plt.plot(dens_knE6,mean_overlap_knE6,'-ko',mew=0.7,markeredgecolor='k',markersize=3,zorder=3,label='$k=1.2$ E6') 
+plt.plot(dens_kn0,mean_overlap_kn0,'-s',color='#1f77b4',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=0$') 
+plt.plot(dens_knE4,mean_overlap_knE4,'-^',color = '#ff7f0e',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=1.2$ E4') 
+plt.plot(dens_kn,mean_overlap_kn,'-x',color = 'g',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$k_n=1.2$ E5') 
+plt.plot(dens_knE6,mean_overlap_knE6,'-ko',mew=0.7,markeredgecolor='k',markersize=3,zorder=3,label='$k_n=1.2$ E6') 
 
 
 pylab.grid(False)

### 2020-02-03 plots/corridor/strain_rate/plot_strain_rate.py

@@ -50,7 +50,7 @@ def main():
      list_k = [0,12000,120000,1200000]
      list_d = [6,7,8]
      list_symbol = ['-o','-v','-^']
-     list_color = ['b','g','r']
+     list_color = ['#1f77b4','#ff7f0e','g']
      y_borde = 0.5
      y_centro = 10.5
      plot_name = 'strain_rate_vs_kn'
@@ -74,7 +74,7 @@ def main():
 def plot_strainrate_vs_k(plot_name,list_k,strain_rate,error_strain_rate,d,symbol,color):
 
      plt.errorbar(list_k,strain_rate,error_strain_rate,color=color, fmt='none')     
-     plt.plot(list_k,strain_rate,symbol,color=color,mec='k',mew=0.8,linewidth = '1',markersize=4,label='$\\rho=${}'.format(d))     
+     plt.plot(list_k,strain_rate,symbol,color=color,mec='k',mew=0.8,linewidth = '1',markersize=5,label='$\\rho=${}'.format(d))     
      pylab.grid(False)
      pylab.xlabel('$k_n$')
      pylab.ylabel('Strain rate~(1/s)')

### 2020-02-03 plots/corridor/velocity_profile/plot_velocity_profile.py

@@ -41,13 +41,13 @@ def main():
 
      file_name = 'vx_profile_kn0.txt'
      simbol ='-s'
-     color = 'b'
+     color = '#1f77b4'
      label = "$k_n=$~0"
      plot_triangles(file_name,simbol,color,label)
 
      file_name = 'vx_profile_kn1.2E5.txt' 
      simbol ='-x'
-     color = 'orange'
+     color = 'g'
      label = "$k_n=1.2$~E5"
      plot_triangles(file_name,simbol,color,label)
 

### 2020-02-03 paper.tex
commit para hacer pull

--- 2020-01-31 paper.tex
@@
 
-The Social Force Model (SFM) models the crowd dynamics 
-considering three kinds of force: desired forces, social forces, and physical forces.
+\textcolor{red}{The Social Force Model (SFM) is a pedestrian dynamics model that
+considers three kinds of forces: desired forces, social forces, and physical forces.
 In its original version, the SFM, addresses two physical forces as essential: 
- the ``body force'' and the ``sliding friction''. Both are 
+\sout{The Social Force Model (SFM) addresses two physical forces as 
+\textit{essential}:}} the ``body force'' and the ``sliding friction''. Both are 
 inspired by granular interactions and were claimed to be necessary  
@@
 the SFM context \cite{lakoba_2005}. As a matter of fact, the usual setting by 
-Helbing prevents the excessive overlapping among pedestrians, but it is known to 
+Helbing prevents the \textcolor{red}{excessive} overlapping among pedestrians, but it is known to 
 accomplish artificially high force levels 
@@
 The 
-point seems to be that the SFM focuses on the ``collective behavior'' due 
+point seems to be that the SFM focuses on the \textcolor{red}{``collective behavior''
+ \sout{``incoordination phenomenon''}} due 
 to clogging, missing the ``individualistic'' perspective  of single pedestrians 
@@
 
-A unique (and universal) setting appears not available yet to
-our knowledge. 
- The reason is that different numerical settings can lead to 
+\textcolor{red}{A unique (and universal) setting appears not available yet. 
+\sout{A meaningful (individualistic) numerical setting appears not available yet (to 
+our knowledge).}} The reason is that different numerical settings can lead to 
 the same crowd dynamics. Actually, only a small set of dimensionless 
@@
 \cite{marchetti_2014}. We may hypothesize that while the dimensionless 
-``numbers'' provide some kind of control on the 
-collective behavior in 
+``numbers'' provide some kind of control on the \textcolor{red}{\sout{
+``incoordination phenomenon''} collective behavior} in 
 crowds, only a few numerical settings can attain an ``individualistic'' 
@@
 We now widen the investigation on the parameter settings to include the one 
-associated to the body force. We will  explore 
- the complex interplay between 
+associated to the body force. We will \textcolor{red}{\sout{focus} explore} 
+on the complex interplay between 
 the body force and the sliding friction among pedestrians. Recall that the 
@@
 scenario in Sections \ref{bottleneck} and \ref{corridor}, respectively. 
-Section \ref{conclusions} opens a detailed discussion from results in Section \ref{results}
-and resumes our main conclusions.
+Section \ref{discussion} opens a detailed discussion raising from of the results 
+in Section \ref{results}. The last Section closes the investigation with our 
+main conclusions.
 
@@
 
-The complex behavior of pedestrians features
+The complex behavior of pedestrians \textcolor{red}{\sout{feature} features}
  either his (her) feelings and 
@@
 \item[(i)] The walking attitude of a pedestrian may appear somewhat 
-  ``aggressive'' if he (she) reacts actively to unexpected behaviors 
+ \textcolor{red}{\sout{``assertive''} ``aggressive''} if he (she) reacts actively to unexpected behaviors 
 \cite{lakoba_2005,helbing_1995}. The smaller the reaction time, the more 
- aggressive observed posture. The associated parameter to this 
+\textcolor{red}{\sout{assertive or}}  aggressive observed posture. The associated parameter to this 
 behavior is the relaxation or characteristic time $\tau$ 
@@
 \item[(ii)] Despite the reactive attitude $\tau$, the pedestrian addresses a 
-``free'' (undisturbed) walking speed $v_d$. This speed expresses his (her) 
+``free'' (undisturbed) walking speed $v_0$. This speed expresses his (her) 
 motivation or intention to reach a certain destination (as comfortable as 
@@
 
-Table~\ref{table_data} shows a few empirical values
+Table~\ref{table_data} shows a few empirical \textcolor{red}{\sout{figures} values}
  for the most common 
@@
 \caption{The experimental data for the pedestrian parameters, as explained in 
-Section~\ref{experimental}. The magnitude $v$ means the actual pedestrian velocity 
+Section~\ref{experimental}. The magnitude $v$ means de pedestrian velocity 
 (m/s). The magnitude $x$ means the compression length (m). The upper row for 
-Ref.~\cite{song_2019} corresponds to data acquired in winter and the lower row to 
-data acquired in summer. The asterisk ($^*$) corresponds to reasonable 
+Ref.~\cite{song_2019} corresponds data acquired in winter and the lower row to 
+datas acquiquired in summer. The asterisk ($^*$) corresponds to reasonable 
 estimates from the authors. }
@@
 A first examination of the figures in Table~\ref{table_data} shows that the 
-choice $\tau\simeq0.6\,$s seems to be a reasonable estimation for the 
+choise $\tau\simeq0.6\,$s seems to be a reasonable estimation for the 
 relaxation time, although this may vary with respect to gender or culture 
@@
 values for the compressibility $k_n$ since these experiments were carried out 
-under low density conditions.  The minimum (perceived) step distance 
-is $0.36\,$m according to Ref.~\cite{seyfried_2007}, but the
+under low density conditions. \textcolor{red}{\sout{Notice that the} The} 
+minimum (perceived) step distance 
+is $0.36\,$m \textcolor{red}{according to Ref.}\cite{seyfried_2007}, but the
  pedestrians seem to require larger 
@@
 providing information on the step distance $B$, but estimates for the 
-desired speed and the body compressibility could be achieved. The reported 
+desired speed and the body compresibility could be achieved. The reported 
 magnitude $k_n$ assesses either the clothes and the body compressibility. The 
@@
 
-We measured the maximum attainable forces during the spring of 2019 at the subway in Buenos Aires, 
+We measured the maximum attainable forces at the subway in Buenos Aires, 
 Argentina. Our preliminary results show that pedestrians feel ``uncomfortable'' 
@@
 
-The maximum (realistic) compressions may be computed from the hook relation 
-$F(x)=k_n(x)\,x$ and the compressibility $k_n(x)$ reported in Table~\ref{table_data}. 
-An ``uncomfortable'' body force  $10\,$N $-$ $30\,$N can address compressions in the 
+The maximum (realistic) compressions may be computed from the relation 
+$F=k(x)\,x$ and the compressibility $k_n(x)$ reported in Table~\ref{table_data}. 
+An ``uncomfortable'' body force \textcolor{red}{\sout{of $30\,$N}} can address compressions in the 
 range of $0.030-0.055\,$m. Also, a ``hitting'' force of $60\,$N can address 
 compressions between $0.045$ and $0.065\,$m. Thus, according to 
-Table~\ref{table_data}, we may expect experimental values for $k_n(x)$ up to 
-$1000\,$kg/s$^2$ (for $F=30\,$N), or, up to $1400\,$kg/s$^2$ (for $F=60\,$N). \\
+Table~\ref{table_data}, \textcolor{blue}{we may expect experimental values for $k_n(x)$ up to 
+$1000\,$kg/s$^2$ (for $F=30\,$N), or, up to $1400\,$kg/s$^2$ (for $F=60\,$N).} \\
 
-Besides, no reliable values for the sliding friction $\kappa$ appears to be 
+Besides, no realiable values for the sliding friction $\kappa$ appears to be 
 available in the literature (to our knowledge). We may presume, however, that 
@@
 acceleration (or deceleration) of the pedestrian due to his (her) own willings. 
-The social force $\mathbf{f}_s$, instead, describes the tendency of the 
+The social force $\mathbf{f}_s$, \textcolor{red}{\sout{intead} instead}, describes the tendency of the 
 pedestrians to stay away from each other. The granular force $\mathbf{f}_g$ 
@@
 
-The net distance (overlap) $|R_{ij}-r_{ij}|$ scales to the parameter $B$ in the 
+The net distance \textcolor{red}{(overlap)} $|R_{ij}-r_{ij}|$ scales to the parameter $B$ in the 
 expression (\ref{eqn_social}). This parameter plays the role of a fall-off 
@@
 pedestrians. Some settings, however, yield similar collective dynamics.
-We introduce unit-less magnitudes 
+\textcolor{red}{\sout{In order to investigate these similarities, we} We}
+ introduce unit-less magnitudes 
 and proceed straightforward as indicated in \ref{appendix1}. We realize from 
@@
 complex context. We will investigate this context in section~\ref{results}. \\
-
-\section{\label{hypotheses}Working hypotheses and procedure}
-
-\begin{itemize}
-
-\item 1)  Nos enfocamos en estudiar principalmente los efectos del parametro kn. Variamos kn en la mayoria de los resultados, salvo en el diagrama fundamental donde tambien variamos kt.
-
-\item 2)  No usamos anisotropia. Estamos interesados en las situaciones de alta densidad donde suponemos que la anisotropia no juega ningun papel relevante.
-
-\item 3) Las simulaciones numéricas las hacemos con LAMMPS usando módulos creados por nosotros para calcular las fuerzas del modelo de Helbing.
-
-\item 4) Exploramos situaciones de muy alta densidad (muy alta presion), sabemos que en estas situaciones pueden producirse caidas y desmayos pero en este paper ignoramos esos efectos.
-
-\end{itemize}
 

### 2020-02-04 paper.tex

--- 2020-02-03 paper.tex
@@
 compressions between $0.045$ and $0.065\,$m. Thus, according to 
-Table~\ref{table_data}, we may expect experimental values for $k_n(x)$ up to 
-$1000\,$kg/s$^2$ (for $F=30\,$N), or, up to $1400\,$kg/s$^2$ (for $F=60\,$N). \\
+Table~\ref{table_data}, \textcolor{blue}{we may expect experimental values for $k_n(x)$ up to 
+$1000\,$kg/s$^2$ (for $F=30\,$N), or, up to $1400\,$kg/s$^2$ (for $F=60\,$N).} \\
 

### 2020-02-04 paper.tex
agregue una hipotesis adicional
agregue el abstract y mejore el grafico de los triangulos

@@
 \begin{abstract}
+
+The Social Force Model (SFM) is a suitable model for describing crowds behaviors.
+In this research, we analyze the role of the body force in the original SFM. 
+We focus on the parameter associated with the body stiffness ($k_n$) and its impact on the pedestrian dynamics in two different geometries: bottleneck and corridor.
+Increasing $k_n$ produces opposite effects depending on the geometry analyzed.
+Pedestrians move faster in a bottleneck, but they move slower in corridors as $k_n$ increases.
+The improvement in the bottleneck geometry is because increasing the stiffness reduces the contacts among pedestrians.
+This effect reduces the number of blocking clusters close to the exit door (which is critical to improving the evacuation).
+The slow down in the corridor geometry occurs because when $k_n$ increases, the crowd behaves like a solid-granular-system in which the friction interaction with the wall determines the velocity of the whole crowd.
+We have also explored the dimensionless parameters that arise from the reduced-in-units equation of motion and tune them to reproduce the qualitative behavior of the empirical fundamental diagram.
 
@@
 \item 4) Exploramos situaciones de muy alta densidad (muy alta presion), sabemos que en estas situaciones pueden producirse caidas y desmayos pero en este paper ignoramos esos efectos.
+
+\item 5) No contemplamos los efectos de la turbulencia.
+Solo nos interesan los comportamientos macroscopicos.
+Por eso buscamos reproducir comportamientos macroscopicos con el modelo mas simple posible.
 

### 2020-02-04 plots/corridor/triangles/plot_density_triangles.py

@@ -45,10 +45,10 @@ def main():
      label = "$k_n=$~0"
      plot_triangles(file_name,simbol,color,label)
 
-     file_name= 'network_data_corridor_avgt_kn1.2E4.txt' 
+     file_name= 'network_data_corridor_avgt_kn2.6E4.txt' 
      simbol ='-^'
      color = '#ff7f0e'
-     label = "$k_n=1.2$~E4"
+     label = "$k_n=2.6$~E4"
      plot_triangles(file_name,simbol,color,label)
 
      file_name = 'network_data_corridor_avgt_kn1.2E5.txt' 

### 2020-02-04 paper.tex
arregle la figura de los triangulos y mejore una parte de resultados

@@
 When the density is around 4.5, a few pedestrians start to touch each other increasing the mean degree.
-As the density increases, the mean degree increases too until reaching an asymptotic behavior in degree six.
-Degree six, corresponds to the densest packing possible for identical hard circles, the result is a hexagonal packing arrangement.\\
+As the density increases, the mean degree increases until reaching an asymptotic behavior as approaching degree six.
+Degree six corresponds to the densest packing possible for identical hard circles; the result is a hexagonal packing arrangement.\\
 
 It is important to notice that in Fig.
-\ref{degree_dens} for a given value of density, the stiffer the pedestrians, the higher the degree.
-In the bottleneck geometry, the opposite thing happens, the stiffer the pedestrians the lower the mean degree.\\
+\ref{degree_dens}, for a given value of density, the stiffer the pedestrians, the higher the degree.
+In the bottleneck geometry, the opposite thing happens.
+The stiffer the pedestrians, the lower the mean degree.
+\\
 
 The mean overlap increases as the global density increases (see Fig.
-\ref{overlap_dens}) and the higher the stiffness the lower the overlap.
+\ref{overlap_dens}).
+For a given density, there is an inverse relation between stiffness and mean overlap.
 This result is similar to the overlap vs.
 desired velocity obtained for bottleneck geometry.
-The higher the value of $k_n$ the higher the repulsion of the pedestrian-pedestrian interaction since the body force is acting in the normal direction $n_{ij}$.\\
+The higher the value of $k_n$, the higher the repulsion of the pedestrian-pedestrian interaction since the body force is acting on the direction $n_{ij}$.\\
 
@@
 Regarding the network connectivity, increasing the stiffness reduces the mean degree in a bottleneck but increases the mean degree in a corridor.
-Fig.~\ref{network_corridor} it shows the contact network corresponding to the corridor at a particular timestep and a particular global density.
+Fig.~\ref{network_corridor} shows the contact network corresponding to the corridor at a particular timestep ($t=50$~s) and at a particular global density ($\rho=7$).
 Fig.~\ref{network_d6_kn0} corresponds to $k_n=0$ while Fig.~\ref{network_d6_knE5} corresponds to $k_n=1.2$~E5.
@@
 
-This result is exactly the opposite of what we get in the bottleneck.
-This happens because, in the corridor, the lateral walls act like containers that force the pedestrian to increase their contacts.
-Whereas in the bottleneck there are no lateral walls.
-Thus, when increasing the stiffness they have more space to detach from each other, reducing the connectedness (hence reducing the mean degree).
+This result is exactly the opposite of what we get in the bottleneck geometry.
+This phenomenon occurs because, in the corridor, the lateral walls act like a containment barrier that forces the pedestrian to increase their contacts.
+Whereas in the bottleneck there are no lateral walls, thus, when increasing the stiffness they have more space to detach from each other, reducing the connectedness (hence reducing the mean degree).
 \\
@@
 We found that a good descriptor to exhibit the connectivity is the number of triangles per node.
-A triangle is defined as a structure composed of three nodes all in contact with each other.
+A triangle is defined as a structure composed of three nodes, all in contact with each other.
 Fig.~\ref{triangles} shows the triangles per node as a function of the global density for different stiffness values $k_n$.
-This descriptor allows to distinguish states with the same global density but different stiffness levels.
+This descriptor allows distinguishing states with the same global density but different stiffness levels.
 In other words, it is a descriptor very sensitive to changes in stiffness that allow expressing the connectivity of the system even better than the mean degree.
@@
 
-This result is consistent with the results obtained in Ref.~\cite{pugnaloni_2013} where the authors explore several topological and geometric descriptors capable of properly describing granular systems with different stiffness.
-While our study system is self-propelled, there are analogies with the system studied in Ref.~\cite{pugnaloni_2013} Like the authors, we recommend using topological descriptors (in particular triangles per node) to describe systems with equal global density and different stiffness levels.\\
+This result is consistent with the results obtained in Ref.~\cite{pugnaloni_2013} where the authors explore several topological and geometrical descriptors capable of properly describing granular systems with different stiffness levels.
+While our study system is self-propelled, there are analogies with the system studied in Ref.~\cite{pugnaloni_2013}.
+Like the authors, we recommend using topological descriptors (in particular triangles per node) to describe systems with equal global density and different stiffness levels.\\
 
@@
 The most important result is that increasing the $k_n$ value reduces the flow (hence reduces the walking speed of the overall crowd) in the corridor geometry.
-Fig.~\ref{kn_vs_vx_corridor} shows the velocity in the direction of displacement $v_x$ as a function of the stiffness for different global density levels.
+Fig.~\ref{kn_vs_vx_corridor} shows the mean velocity in the direction of displacement $v_x$ as a function of the stiffness for different global density levels.
 $v_x$ reduces as $k_n$ increases as opposed to what happens in the bottleneck geometry.
@@
 The difficulty arises because the pedestrian feels a much higher repulsion from the pedestrian ahead (due to the body force increment).
-Thus, they have no other option than moving at (almost) the same speed as the pedestrians that they have at their sides.
-This microscopic mechanism explains the macroscopic behavior of the crowd that turns the crowd from a fluid-like state into a solid-like state.
+Thus, they have no choice but to move at (almost) the same speed as the individuals they have at their sides.
+This microscopic mechanism explains the macroscopic behavior that turns the crowd from a ``fluid-like state'' into a ``solid-like state''.
 When the stiffness is high enough (say $k_n=$1.2~E6), all the pedestrians walk at the same velocity.
@@
 For $k_n=0$, we can see a parabolic-like velocity profile that resembles the Poiseuille flow (for Newtonian and incompressible fluids in laminar flow flowing through a pipe).
+This behavior was observed in empirical measurements reported in Ref.~\cite{}.
 As $k_n$ increases the velocity profile flattens until becoming a constant ($k_n=$ 1.2~E6) which $v_x$ value is much lower than on the case of soft pedestrians ($k_n=$0).\\

### 2020-02-04 paper.tex
agregue una referencia de data empirica del perfil de velocidad
agregue la cita de plimpton

@@
 For $k_n=0$, we can see a parabolic-like velocity profile that resembles the Poiseuille flow (for Newtonian and incompressible fluids in laminar flow flowing through a pipe).
-This behavior was observed in empirical measurements reported in Ref.~\cite{}.
-As $k_n$ increases the velocity profile flattens until becoming a constant ($k_n=$ 1.2~E6) which $v_x$ value is much lower than on the case of soft pedestrians ($k_n=$0).\\
+This behavior was observed in empirical measurements reported in Ref.~\cite{zhang2013empirical}.
+As $k_n$ increases the velocity profile flattens until becoming a constant ($k_n=$ 1.2~E6).
+In this scenario, the value of mean $v_x$ is much lower than on the case of soft pedestrians ($k_n=$0).\\
 
-If the stiffness is high enough, the crowd behaves like a solid; this means that the crowd can not be easily deformed.
-In this context, to deform means to have parts of the crowd that move faster than other parts of the crowd.
+If the stiffness is high enough, the crowd behaves like a solid; this means that the crowd can not be easily ``deformed''.
+In this context, to deform means to have certain parts of the crowd that manage to move faster than other parts of the crowd.
 \\
@@
 If the stiffness is high enough, the pedestrians can not push to the pedestrian ahead since the body force repulsion becomes very high.
-This leads to a "solidification" of the crowd that makes all the pedestrians walk at almost the same velocity.
+This leads to a ``solidification'' of the crowd that makes all the pedestrians walk at almost the same velocity.
 The pedestrians that are in contact with the wall are the ones who determine the velocity of the whole crowd.

### 2020-02-04 paper.tex
mejore la redaccion de la parte final de resultados

@@
 
-The empirical measurements correspond to the fundamental diagram at the entrance of the Jamaraat bridge (see the inset in Fig.~\ref{flow_density_no_body_force}).
+The empirical measurements correspond to the fundamental diagram measured at the entrance of the Jamaraat bridge (see the inset in Fig.~\ref{flow_density_no_body_force}).
 We aim to reproduce the qualitative behavior of these measurements roughly.\\
@@
 Notice that the original friction (corresponding to $\mathcal{K}=$137) does not produce a reduction of the flow when there is zero body force ($\mathcal{K}_c=$0).
-Nevertheless, when the body force is included, and we remain the original friction (circles from Fig.~\ref{flow_density_body_force}), the flow reduces from  5 p m$^{-2}$ to 7 p m$^{-2}$ and then increases for higher values of density.\\
+Nevertheless, when the body force is included, and we remain the original friction (circles from Fig.~\ref{flow_density_body_force}), the flow reduces in the range of densities from  5 p m$^{-2}$ to 7 p m$^{-2}$; then increases for higher values of density.\\
 
@@
 
-These results suggest that although increasing $\mathcal{K}_c$ produces a reduction in the flow, it is necessary to increase $\mathcal{K}$ (for instance, increasing friction $k_t$) to reproduce the reduction in the flow that characterizes the high-density regime.
+These results suggest that although increasing $\mathcal{K}_c$ produces a reduction in the flow, it is necessary to increase $\mathcal{K}$ (for instance, increasing the friction coefficient $k_t$) to reproduce the reduction in the flow that characterizes the high-density regime.
 It is still a pending challenge to find the values of the dimensionless numbers that reproduce the qualitative behavior of the fundamental diagram, but this first approach narrows down the search.\\

### 2020-02-04 paper.tex
mejore las conclusiones

@@
 As pedestrians detach from each other, the friction force diminishes due to the reduction of overlap between pedestrians and the contacts among them.
-The general decrease in frictional force reduces the probability of producing a cluster of pedestrians blocking the exist (blocking cluster), which leads to a more efficient evacuation dynamics.
+The general decrease in frictional force reduces the probability of producing a cluster of pedestrians blocking the exit (blocking cluster), which leads to a more efficient evacuation dynamics.
 \\
@@
 In order to explore the outcomes from different dimensionless numbers, we compared numerical results with empirical measurements.
-We found good candidates to reproduce the qualitative behavior of empirical measurements in the range and $0 < \mathcal{K}_c < 68$ with $\mathcal{K} = 685$.
+We found good candidates to reproduce the qualitative behavior of empirical measurements in the range $0 < \mathcal{K}_c < 68$ with $\mathcal{K} = 685$.
 Nevertheless, this is a first sketch to arrive at a set of dimensionless parameters that may be suitable to reproduce empirical measurements.
-We encourage further research that seeks to find the values of the dimensionless numbers that can reproduce experimental data.\\
+We encourage further research that seeks to find values of the dimensionless numbers that best reproduce experimental data.\\
 

### 2020-02-04 paper.tex
Update paper.tex
Working hypoheses (from Guillermo Frank)

@@
 
-\section{\label{hypotheses}Working hypotheses and procedure}
+\section{\label{hypotheses}Working hypotheses and procedures}
+
+\subsection{Working hypotheses}
+
+Our working hypotheses are similar to those mentioned in 
+Ref.~\cite{dorso_2019}, 
+although the presence of the body force opens inquiries about the proper 
+exploration of the parameter space. To be precise
 
 \begin{itemize}
-
-\item 1)  Nos enfocamos en estudiar principalmente los efectos del parametro kn. Variamos kn en la mayoria de los resultados, salvo en el diagrama fundamental donde tambien variamos kt.
-
-\item 2)  No usamos anisotropia. Estamos interesados en las situaciones de alta densidad donde suponemos que la anisotropia no juega ningun papel relevante.
-
-\item 3) Las simulaciones numéricas las hacemos con LAMMPS usando módulos creados por nosotros para calcular las fuerzas del modelo de Helbing.
-
-\item 4) Exploramos situaciones de muy alta densidad (muy alta presion), sabemos que en estas situaciones pueden producirse caidas y desmayos pero en este paper ignoramos esos efectos.
-
-\item 5) No contemplamos los efectos de la turbulencia.
-Solo nos interesan los comportamientos macroscopicos.
-Por eso buscamos reproducir comportamientos macroscopicos con el modelo mas simple posible.
+ \item[(a)] The ``faster-is-slower'' (or the ``faster-is-faster'') phenomenon 
+occurs when varying the values of $v_d$ (see Section~\ref{bottleneck}). This is 
+equivalent to vary simultaneously $\mathcal{A}$ and $\mathcal{K}_c$ by the same 
+amount in the (unit-less) parameter space (see Section~\ref{parameters}). We 
+may visualize this sampling procedure as moving along a straight line in the 
+space $(\mathcal{A},\mathcal{K},\mathcal{K}_c)$. Further variations of 
+$k_n$ turns the sample points out of this line, but on the plane of constant
+$\mathcal{K}_c$. We will step up $k_n$ by several orders of magnitude in order 
+to get the big picture of this surface.
+
+\item[(b)] We will consider the parameter setting in Ref.~\cite{helbing_2000} 
+as a starting point for exploring the parameter space. The reason for this is 
+that a complete set of experimental parameters is still not available (to our 
+konwledge). We are aware, though, of the drawbacks for this choise, say, the 
+unrealistic meanings for the length $B$ and the compressibility $k_n$ (see 
+Section~\ref{experimental}). But these are irrelevant in the context of the 
+(unit-less) parameter space and the corresponding collective dynamics (see 
+Section~\ref{introduction}).
+
+\item[(c)] We will explore crowd densities allowing body compressions up to 
+$0.1\,$m. This corresponds to remarkably high densities, since our own 
+(real-life) estimates do not surpass $0.065\,$m (see 
+Section~\ref{experimental}). Therefore, the extremely high density 
+scenarios (say, above $0.065\,$m) will be considered for the purpose of a 
+tendency, but not as a common real-life situation. No casualties due to high 
+pressures will be further considered.
 
 \end{itemize}
+
+We stress the fact that our concern is placed on the collective dynamics of 
+crowded environments. We will work on the hypothesis that any ``reasonable'' 
+parameter set should reproduce the collective behavior (say, the slowing down 
+in the fundamental diagram; see Section~\ref{corridor}). We will not attempt to 
+optimize parameters from other objective functions. \\
+
+We will further sustain the hypothesis of soft matter in the context of crowded 
+environments. The body compression and the sliding friction parameters are 
+supposed to be connected in some way under this hypothesis. However, we will 
+not introduce any direct link between $\mathcal{K}$ and $\mathcal{K}_c$. We 
+will investigate the interplay between both in Section~\ref{corridor}. 
+\\
+
+In order to keep the model as simple as possible, we will only consider 
+isothropic pedestrians, since anisothropy does not play a relevant role at high 
+densities. \\
+
+\subsection{Procedures}
+
+The SFM was implemented on the LAMMPS simulation software \cite{plimpton}. 
+Additional modules for LAMMPS were also written in C++ in order to expand the 
+software capabilities. All these were able to run in a high performance 
+environment (HPC). \\
+
+The implemented SFM parameters were the same as those in 
+Ref.~\cite{helbing_2000} (at the begining of the exploratory procedure only). 
+But the pedestrian's mass and radius were set to the more realistic values of 
+$70\,$kg and $0.2\,$m, respectively. The force interaccions between 
+pedestrians were limited, however, to a cut-off distance of $0.88\,$m for 
+attaining a \textit{privacy sphere} from first neighbors only. The desired 
+velcity was always set to $1\,$m/s in the corridor situation. Besides, the 
+explored values of $v_d$ for the bottleneck scenario ranged from $1\,$m/s to the 
+extremely anxious situation of $10\,$m/s. \\
+
+The Eq.~(\ref{eqn_motion}) was numerically integrated by means of the velocity 
+Verlet algorithm, with a timestep of $10^{-4}$ seconds. The pedestrians 
+positions and velocities were recorded every $0.05\,$sec, but post-processing 
+computing was done over samples acquired every $5\,$sec., in order to avoid 
+data correlations. Those pedestrians leaving the simulations box were 
+re-introduced into the box, on the opposite side (periodic boundary 
+conditions). We only ommitted this mechamism when computing the evacuation time 
+for the bottleneck geometry. \\
+
+The post-processing computing was assisted by Python functions. The NetworkX 
+package was used among others.   \\
 

### 2020-02-04 paper.tex
cambios menores en conclu

--- 2020-02-04 paper.tex
@@
 \subfloat[\label{venn_2parameters}]
-{\includegraphics[width=0.45\columnwidth]{./venn_2parameters.png}}
+{\includegraphics[width=0.49\columnwidth]{./venn_2parameters.png}}
 \hfill    
 \subfloat[\label{venn_3parameters}]
-{\includegraphics[width=0.45\columnwidth]{./venn_3parameters.png}
+{\includegraphics[width=0.49\columnwidth]{./venn_3parameters.png}
 }\\
@@
 \centering
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./degree_vs_vd_multi_kn.eps}\label{degree_vd}}\ 
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./overlap_vs_vd_multi_kn.eps}\label{overlap_vd}}\\
+    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./degree_vs_vd_multi_kn.eps}\label{degree_vd}}\ 
+    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./overlap_vs_vd_multi_kn.eps}\label{overlap_vd}}\\
 \caption[width=0.47\columnwidth]{(a) Mean degree as a function of the pedestrian’s desired velocity (m/s).
@@
 \centering
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn0.eps}\label{network_vd2_kn0}}\ 
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn0.eps}\label{network_vd10_kn0}}\\
-        \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn1200000.eps}\label{network_vd2_kn1200000}}\ 
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn1200000.eps}\label{network_vd10_kn1200000}}\\
+    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_vd2_kn0.eps}\label{network_vd2_kn0}}\ 
+    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_vd10_kn0.eps}\label{network_vd10_kn0}}\\
+        \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_vd2_kn1200000.eps}\label{network_vd2_kn1200000}}\ 
+    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_vd10_kn1200000.eps}\label{network_vd10_kn1200000}}\\
 \caption[width=0.47\columnwidth]{Contact networks of a 225 pedestrian evacuation through a bottleneck.
@@
 \centering
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./degree_vs_dens_multi_kn.eps}\label{degree_dens}}\ 
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./overlap_vs_dens_multi_kn.eps}\label{overlap_dens}}\\
+    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./degree_vs_dens_multi_kn.eps}\label{degree_dens}}\ 
+    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./overlap_vs_dens_multi_kn.eps}\label{overlap_dens}}\\
 \caption[width=0.47\columnwidth]{(a) Mean degree as a function of the global density for different $k_n$ values.
@@
 \centering
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_d6_kn0.eps}\label{network_d6_kn0}}\ 
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_d6_knE5.eps}\label{network_d6_knE5}}\\
+    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_d6_kn0.eps}\label{network_d6_kn0}}\ 
+    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_d6_knE5.eps}\label{network_d6_knE5}}\\
 \caption[width=0.47\columnwidth]{Contact network of the pedestrians along the corridor.
@@
 \centering
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./vx_profile.eps}\label{vx_profile}}\ 
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./strain_rate_vs_kn.eps}\label{strain_rate_vs_kn}}\\
+    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./vx_profile.eps}\label{vx_profile}}\ 
+    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./strain_rate_vs_kn.eps}\label{strain_rate_vs_kn}}\\
 \caption[width=0.47\columnwidth]{(a) Velocity in the $x$ coordinate as a function of the transversal coordinate $y$ for three different stiffness values $k$ (see the label).
@@
 \centering
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_nobodyforce.eps}\label{flow_density_no_body_force}}\ 
-    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./flow-density_multifric_bodyforce.eps}\label{flow_density_body_force}}\\
+    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./flow-density_multifric_nobodyforce.eps}\label{flow_density_no_body_force}}\ 
+    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./flow-density_multifric_bodyforce.eps}\label{flow_density_body_force}}\\
 \caption[width=0.47\columnwidth]{Flow vs.

### 2020-02-04 paper.tex
Update paper.tex
Agregue Working hypotheses (Guillermo Frank)
agruegue los txt de datos y cambie el titulo
modifique el valor del radio a 0.23

@@
 
-\title{Effects of the body force on the evacuation dynamics}
+\title{Effects of the body force on the pedestrian and evacuation dynamics}
 
@@
 But the pedestrian's mass and radius were set to the more realistic values of 
-$70\,$kg and $0.2\,$m, respectively. The force interaccions between 
+$70\,$kg and $0.23\,$m, respectively. The force interaccions between 
 pedestrians were limited, however, to a cut-off distance of $0.88\,$m for 

### 2020-02-05 paper.tex
muchas correcciones de guille en la parte de bottleneck

@@
 positions and velocities were recorded every $0.05\,$sec, but post-processing 
-computing was done over samples acquired every $5\,$sec., in order to avoid 
+computing was done over samples acquired at least every $2\,$sec., in order to avoid 
 data correlations. Those pedestrians leaving the simulations box were 
@@
 We present in this section the results corresponding to the bottleneck geometry. 
-We show the consequences of modifying the body force coefficient $k_n$ in the 
+We show the consequences of modifying the body force coefficient $k_n$ on the 
 evacuation dynamics. Recall that this coefficient is associated 
@@
 velocity (m/s) for a bottleneck. The room was 20 m x 20 m size. The door was 
-0.92 m width. Mean values were computed from 10 evacuation processes. 225 
+0.92 m width (two pedestrians' width). Mean values were computed from 10 evacuation processes. 225 
 pedestrians were initially placed in a square lattice with a random initial 
@@
  down triangles correspond to an intermediate value between the empirical value 
-presented in Ref.~\cite{melvin1988aatd} and the chosen by Helbing in 
+presented in Ref.~\cite{melvin1988aatd} and the one provided by Helbing in 
 Ref.~\cite{helbing_2000} }
@@
 
-Two behavioral patterns can be seen in Fig.~\ref{vd_vs_te}. 
-The region in which the slope is positive means that the 
+Three behavioral patterns can be distinguished in Fig.~\ref{vd_vs_te}. 
+Each pattern can accomplish a positive slope, a negative slope
+or both. The interval in which the slope is positive means that the 
 harder the pedestrians try to get out (higher $v_d$), the 
 longer it takes them to evacuate. This is the Faster-is-slower 
-(FIS) regime. Conversely, the region in which the slope is 
+(FIS) regime. Conversely, the interval in which the slope is 
 negative  corresponds to a Faster-is-Faster (FIF) regime (the 
-harder they try, the quicker they leave). Fig.~\ref{vd_vs_te} shows a change in 
-in the behavior for desired velocities $v_d>1.2\,$m/s. The 
-evacuation time is of type FIS+FIF for compression coefficients below 
-$k=1.2\,$E5. This means that ``soft'' individuals are required to attain this 
-behavioral change.  Notice that higher values of $k_n$ allow 
-only FIS or FIF behaviors. For the highest explored value $k_n=1.2\,$E6, no 
+harder they try, the quicker they leave).\\
+
+Fig.~\ref{vd_vs_te}  shows either FIS or FIF, and a FIS+FIF pattern
+for desired velocities $v_d>1.2\,$m/s. The 
+evacuation time attains a FIS+FIF pattern for compression coefficients below 
+$k=1.2\,$E5. This means that ``soft'' individuals can attain this 
+behavioral pattern.  Notice that higher values of $k_n$ allow 
+only FIS or FIF patterns. For the highest explored value $k_n=1.2\,$E6, no 
 FIS can be seen at all. Besides, the evacuation pattern for $k_n = 0$ and $k_n 
-= 1.2\,$E4 are very similar since the body force is comparable to the social 
+= 1.2\,$E4 are very similar since the body force intensity is of the same order
+or less than the social 
 force for these stiffness values. \\
 
-Despite the presence of the FIS or FIF phenomenon, the evacuation time at a 
-fixed value of $v_d$ decreases for increasing values of $k_n$. This means that 
-stiffer pedestrians evacuate faster than soft pedestrians. To investigate this 
-issue, we computed the mean velocity of the whole crowd as a function of the 
-stiffens $k_n$. Fig.~\ref{kn_vs_vx_bottleneck} shows the mean velocity in the 
-x-direction as a function of the stiffness $k_n$ for three different desired 
+Despite the presence of the FIS or FIF pattern, the evacuation time at a 
+fixed value of $v_d$ decreases for increasing values of $k_n$ (whiting the examined interval). 
+This means that stiffer pedestrians evacuate faster than soft pedestrians. 
+To further investigate this 
+phenomenon, we computed the mean velocity of the whole crowd as a function of the 
+stiffness $k_n$. Fig.~\ref{kn_vs_vx_bottleneck} shows the actual mean velocity in the 
+$x-$direction as a function of the stiffness $k_n$ for three different desired 
 velocities. In all cases, the velocity increases with the stiffness. From 
-$k_n=0$ to $k_n=$1.2~E4 the increment of velocity is not as significative as it 
+$k_n=0$ to $k_n=1.2\,$E4 the increment of velocity is not as significative as it 
 is for higher $k_n$. \\
@@
     \subfloat[]{\includegraphics[width=0.7\columnwidth]{./kn_vs_vx_bottleneck.eps}}\\
-\caption[width=0.47\columnwidth]{Mean velocity in the x-direction as a function 
+\caption[width=0.47\columnwidth]{Mean velocity in the $x-$direction as a function 
 of the stiffness level $k_n$ for different desired velocities (see label). The 
 data corresponds to a bottleneck with periodic boundary conditions (re-injecting 
-pedestrians). The average was taken every two seconds once the crowd reaches the 
+pedestrians). The average was taken every five seconds once the crowd reaches the 
 stationary state ($t=$20~s) until the end of the simulation ($t=$110~s). }
@@
 
-The presence of a FIF phenomenon only for soft individuals opens many questions 
+The presence of the FIF phenomenon for only ``soft'' individuals opens many questions 
 on the microscopic dynamics of pedestrians. We may presume that contacts 
 between pedestrians are quite different for soft individuals than for stiff 
-individuals. To study the dynamics of the contact, regardless of the compression 
-effects, we assimilate the pedestrians as nodes and the whole crowd as a 
-network. We set a link between any two individuals if both are in physical 
-contact (\textit{i.e.} $r_{ij} \leq R{ij}$).\\
+individuals. Thus, we proceed to study the dynamics of contacting pedestrians, regardless of the compression 
+effects. We will assimilate the pedestrians as nodes and the whole crowd as a 
+network. We will link any two individuals whenever they get in physical 
+contact (\textit{i.e.} $r_{ij} \leq R_{ij}$).\\
 
@@
 average of the degree over all the nodes (pedestrians) and over the whole 
-sampled time. We report mean values after the system has reached the stationary 
-state, that is after a well-formed bulk has been established.\\
-
-Increasing $v_d$ increases the mean degree, as expected. This occurs because 
-increasing $v_d$ produces higher densities that force individuals to touch each 
+sampled interval. We computed mean values only after the system reached the stationary 
+state, that is, after a well-formed bulk has been established.\\
+
+Notice that the mean degree increases as $v_d$ increases, as expected. This expresses the fact that
+higher $v_d$ values accomplish higher densities, enforcing individuals to touch each 
 other. But surprisingly, for a given $v_d$, the mean degree reduces as the $k_n$ 
 value increases. A noticeable decrease in the mean degree can be seen for the 
-highest explored value of $k_n$. We may expect a significant change in the 
-sliding friction due to this fact.\\
+highest explored value of $k_n$. This was not expected and opens the question on how would
+this affect the sliding friction among pedestrians.\\
 
@@
 Fig.~\ref{overlap_vd}. The overlap between individuals is shown as a function of 
-$v_d$. Recall from section \ref{sfm} that the overlap is defined as 
+$v_d$. Recall from Section \ref{sfm} that the overlap is defined as 
 $R_{ij}-r_{ij}$ where $R_{ij}$, is the sum of radius of particle $i$ and 
@@
 very low desired velocities (say, $v_d<2\,$m/s), we can see that the mean 
-overlap is an increasing function of $v_d$ (for the studied $k_n$ values).\\
+overlap is an increasing function of $v_d$ (withing the studied
+range of $v_d$ and $k_n$).\\
 
@@
 The data corresponds to a bottleneck with periodic boundary conditions (re-injecting pedestrians).
-The average was taken every two seconds once the crowd reaches the stationary state ($t=$20~s) until the end of the simulation ($t=$110~s).}
+The average was taken every five seconds once the crowd reached the stationary state (say, $t=$20~s) until the end of the simulation ($t=$110~s).}
 \label{degree_overlap_vd}
@@
 
-The regime for $v_d<2\,$m/s is different from the rest since most of the 
+The regime for $v_d<2\,$m/s is qualitatively different from the clogged regime since most of the 
 pedestrians are not touching each other. The only pedestrians who touch each 
-other are the ones who are being re-injected in the room. The overlap is higher 
-than, for example, $v_d=3\,$m/s because of the pedestrians that 
-are re-injected and collide with pedestrians in the bulk. \\
-
-Besides, for a given $v_d$, the overlap increases as the $k_n$ value decreases. 
-Reducing $k_n$ means reducing the normal body force, which allows a more 
-significant intrusion of the personal space of the individuals 
-(this means more overlap between pedestrians).\\
-
-Increasing the body stiffness has a significant impact on 
-evacuation dynamics. The reduction of the overlap and the mean degree between 
-pedestrians in the simulation, tend to diminish the sliding 
-friction within the crowd. Consequently, an enhancement in the evacuation time 
-(pedestrians escape faster) is observed, as pictured in Fig.~\ref{vd_vs_te}. 
+other are the ones who are being re-injected on the opposite side of the room.
+This collides against the bulk, providing some kind of overlap during very short time. We will
+not analize this regime.\\
+
+Besides, for a given $v_d>2\,$m/s, the overlap increases as the $k_n$ value decreases. 
+This can be explained by considering the bulk at a (quasi) equilibrium situation. 
+The social and compression forces counterbalance the desired force. Thus, for any fixed $v_d$,
+the product $k_n \times (R_{ij}-r_{ij})$ remains (almost) fixed. Any decrease in $k_n$
+allows a more significant intrusion. This (partially) supports the argument that
+the sliding friction should weaken for stiffer pedestrians (say increasing
+$k_n$ values). \\
+
+The sliding friction reduction appears as the fist feature for enhancing
+the overall evacuation performance. Either reducing the mean overlap and the mean degree
+tend to diminish the mean sliding 
+friction within the crowd. 
 Notice, however, that switching from a FIS regime (positive slope) to a  FIF 
@@
 
-Despite the effects on the sliding friction, the body force 
+The body force 
 has a notorious impact in the number of pedestrians touching each other (say, 
@@
 four different configurations of the evacuation dynamics are shown. The 
-configurations represent 225 pedestrians trying to escape through a door see the 
-caption for details. The colors correspond to the degree of each node 
+configurations represent 225 pedestrians trying to escape through a door (see 
+caption for details). The colors correspond to the degree of each node 
 (pedestrian), and the lines between pedestrians represent the contacts among 
@@
     \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_vd10_kn1200000.eps}\label{network_vd10_kn1200000}}\\
-\caption[width=0.47\columnwidth]{Contact networks of a 225 pedestrian evacuation through a bottleneck.
+\caption[width=0.47\columnwidth]{Snapshots of the contact networks of a 225 pedestrian evacuation through a bottleneck.
 The door is placed at $(x,y)=(20,10)$~m, the width of the door is 0.92~m (equivalent to 2 pedestrian\textsc{\char13}s diameter).
@@
 (a) and (b) correspond to a simulation without body force with $v_d=$2 and $v_d=$10 respectively.
-(c) and (d) correspond to simulations with $k_n$=1.2~E6 with $v_d=$2 and $v_d=$10 respectively.}
+(c) and (d) correspond to simulations with $k_n$=1.2\,E6 with $v_d=$2 and $v_d=$10 respectively.}
 \label{network_bottleneck}
@@
 The four configurations corresponds to two different $v_d$ and two different $k_n$ values (say, the  minimum and maximum explored values).
-Fig.~\ref{network_vd2_kn0} and Fig.~\ref{network_vd10_kn0} shows a snapshot for $k_n=$0, at desired velocities of 2$\,$m/s and 10$\,$m/s respectively.
+Fig.~\ref{network_vd2_kn0} and Fig.~\ref{network_vd10_kn0} show snapshots for $k_n=0$, at the desired velocities of 2$\,$m/s and 10$\,$m/s, respectively.
 Fig.~\ref{network_vd2_kn1200000} and Fig.~\ref{network_vd10_kn1200000} show similar situations, but for  $k_n=$1.2$\,$E6.
@@
 The clusterization of the pedestrians has a significant impact on the blocking clusters (the group of pedestrians that clog the exit).
-Fig.~\ref{pbc_vs_vd_multi_kn} shows the blocking cluster existence probability as a function of the desired velocity for different $k$ values.
-The blocking clusters occur more often when the desired velocity increases because increasing $v_d$ increase the density in the area close to the exit.
-The most remarkable fact of Fig.~\ref{pbc_vs_vd_multi_kn} is that increasing the stiffness reduces the blocking cluster existence for a fixed value of $v_d$.
-Under these conditions, the blocking clusters strictly govern the evacuation dynamics~\cite{dorso_2005}.
-Thus, increasing the stiffness reduces the blocking cluster existence, which improves the evacuation time.\\
+Fig.~\ref{pbc_vs_vd_multi_kn} shows the blocking cluster probability as a function of the desired velocity for different $k_n$ values (see caption for details).
+The blocking clusters become more probable for high desired velocity, since the clogged area gets more compact as $v_d$ increases (for any fixed value of $k_n$).
+But, the most remarkable fact in Fig.~\ref{pbc_vs_vd_multi_kn} is that increasing the body stiffness reduces the blocking cluster probability for any fixed value of $v_d$.
+Recall from Ref.~\cite{dorso_2005} that the evacuation time is controlled by the blocking.
+Thus, increasing the body stiffness affects the presence of the blocking clusters, and consequently improves the evacuation time.
+This raises as a second feature for enhancing the overall evacuation performance.
+\\
 
@@
 {./pbc_vs_vd_multi_kn.eps}
-\caption{\label{pbc_vs_vd_multi_kn} Blocking cluster existence probability as a function of $v_d$ for different stiffness levels (see label).
+\caption{\label{pbc_vs_vd_multi_kn} Blocking cluster probability as a function of $v_d$ for different stiffness levels (see label).
 The probability is calculated as the amount of time a blocking cluster is present divided by the overall simulation time.
-The result correspond to a bottleneck geometry with 225 pedestrians in periodic boundary conditions (re-injection of pedestrians once the exited the room).
-The simulation lasted $t_f =$ 1000~s.
+The situation corresponds to a bottleneck with 225 pedestrians under periodic boundary conditions (re-injection of pedestrians once they left the room).
+The sampled interval was set to $t_f =$ 1000~s.
 }
@@
 
-To conclude this section, we want to emphasize that increasing body stiffness has a significant impact on the evacuation dynamics.
-The stiffer pedestrians are, the less they touch to each other (less degree and less overlap).
-This phenomenon yields a reduction of the existence of the blocking clusters, which reduces the overall evacuation time.
-\\
-\\
+We may summarize this Section as follows.
+We explored the parameter space along $v_d$ and $k_n$ for the bottleneck situation.
+Varying $v_d$ (at a fixed $k_n$) explores the collective behavior for different $(\mathcal{A},\mathcal{K}_c)$ pairs.
+We realized that increasing $\mathcal{K}_c$ only improves the evacuation performance through the bottleneck.
 

### 2020-02-05 paper.tex
cambie los <> de los grficos

@@
 of the collective dynamics. Conversely, either $v_d$ and $B$ may counterbalance 
-$\mathcal{K}_c$ in order to keep the colletive dynamic (qualitatively) 
+$\mathcal{K}_c$ in order to keep the collective dynamic (qualitatively) 
 unchanged.  \\
@@
 complex context. We will investigate this context in section~\ref{results}. \\
+
+\subsection{\label{blocking_clusters} Blocking clusters}
+
+A characteristic feature of pedestrian dynamics is the formation of clusters. Clusters of pedestrians can 
+be defined as the set of individuals that for any member of the group (say, $i$) there exists at least another member belonging to the same group ($j$) in contact with the former.
+Thus, we define a ``granular cluster'' ($C_g$) following the mathematical formula given in Ref.~\cite{dorso_2005}
+
+\begin{equation}
+C_g:P_i~\epsilon~ C_g \Leftrightarrow \exists~ j~\epsilon~C_g / r_{ij} < (R_i+R_j) \label{ec-cluster}
+\end{equation}
+
+where ($P_i$) indicate the \textit{ith} pedestrian and $R_i$ is his (her) radius (shoulder width). That means, $C_g$ is a
+set of pedestrians that interact not only with the social force, but also with physical forces (\textit{i.e.} friction force and body force).
+A ``blocking cluster'' is defined as the subset of clusterized particles (granular cluster) closest to the door whose first 
+and last component particles are in contact with the walls at both sides of the door. This clogging structure is responsible for 
+worsening the evacuation performance.
 
@@
 pedestrians). The average was taken every five seconds once the crowd reaches the 
-stationary state ($t=$20~s) until the end of the simulation ($t=$110~s). }
+stationary state ($t=$20~s) until the end of the simulation ($t=$110~s). 
+Color online only. }
 \label{kn_vs_vx_bottleneck}
@@
 The data corresponds to a bottleneck with periodic boundary conditions (re-injecting pedestrians).
-The average was taken every five seconds once the crowd reached the stationary state (say, $t=$20~s) until the end of the simulation ($t=$110~s).}
+The average was taken every five seconds once the crowd reached the stationary state (say, $t=$20~s) until the end of the simulation ($t=$110~s).
+Color online only.}
 \label{degree_overlap_vd}
@@
 The regime for $v_d<2\,$m/s is qualitatively different from the clogged regime since most of the 
-pedestrians are not touching each other. The only pedestrians who touch each 
+pedestrians are not touching each other (as was already observed in Ref~\cite{dorso_2005,dorso_2011}). The only pedestrians who touch each 
 other are the ones who are being re-injected on the opposite side of the room.
@@
 (a) and (b) correspond to a simulation without body force with $v_d=$2 and $v_d=$10 respectively.
-(c) and (d) correspond to simulations with $k_n$=1.2\,E6 with $v_d=$2 and $v_d=$10 respectively.}
+(c) and (d) correspond to simulations with $k_n$=1.2\,E6 with $v_d=$2 and $v_d=$10 respectively.
+Color online only.}
 \label{network_bottleneck}
@@
 The sampled interval was set to $t_f =$ 1000~s.
+Color online only.
 }
@@
 The mean values are averages over all the pedestrians and over time once the system reaches the stationary state.
-Both measurements correspond to corridor geometry with desired velocity $v_d=1$.}
+Both measurements correspond to corridor geometry with desired velocity $v_d=1$.
+Color online only.}
 \label{network_corridor}
@@
 The corridor was 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
-(a) corresponds to a simulation without body force and (b) corresponds to a simulation with $k_n=1.2$~E5.}
+(a) corresponds to a simulation without body force and (b) corresponds to a simulation with $k_n=1.2$~E5.
+Color online only.}
 \label{network_corridor}
@@
 The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
+Color online only.
 }
@@
 The global density was 7 p~m$^{-2}$.
+Color online only.
 }
@@
 The desired velocity was $v_d=1$ in all the cases.
-(a) corresponds to simulations without body force ($\mathcal{K}_c =$0) and (b) corresponds to a body force with the original value of the body stiffness ($\mathcal{K}_c =$68).}
+(a) corresponds to simulations without body force ($\mathcal{K}_c =$0) and (b) corresponds to a body force with the original value of the body stiffness ($\mathcal{K}_c =$68).
+Color online only.}
 \label{flow_density}

### 2020-02-05 plots/bottleneck/k_vs_vx/plot_k_vs_vx.py

@@ -66,7 +66,7 @@ plt.plot(k_vd6,mean_vx_vd6,'-x',color = 'g',mew=0.7,markeredgecolor='k',markersi
 
 pylab.grid(False)
 pylab.xlabel('$k_n$')
-pylab.ylabel('$<v_x> $')
+pylab.ylabel('$\\langle v_x \\rangle $')
 plt.xscale('symlog')
 plt.title("Bottleneck")
 lgd=plt.legend(numpoints=1,handlelength=0.8) 

### 2020-02-05 plots/bottleneck/pbc_vs_vd/plot_pbc_vs_vd.py

@@ -74,7 +74,7 @@ plt.plot(vd_knE6,pbc_knE6,'-ko',mew=0.7,markeredgecolor='k',markersize=4,zorder=
 
 pylab.grid(False)
 pylab.xlabel('$v_d$~(m~s$^{-1})$')
-pylab.ylabel('Blocking cluster existence probability',fontsize='6')
+pylab.ylabel('Blocking cluster probability',fontsize='6')
 #pylab.legend()
 #plt.ylim(-0.001,0.1)
 #pylab.xlim(1.0, 10)

### 2020-02-05 plots/corridor/k_vs_vx/plot_k_vs_vx.py

@@ -67,7 +67,7 @@ plt.plot(k_d8,mean_vx_d8,'-x',color = 'g',mew=0.7,markeredgecolor='k',markersize
 
 pylab.grid(False)
 pylab.xlabel('$k_n$')
-pylab.ylabel('$<v_x> $')
+pylab.ylabel('$\\langle v_x \\rangle $')
 plt.xscale('symlog')
 plt.title("Corridor")
 lgd=plt.legend(numpoints=1,handlelength=0.8) 

### 2020-02-05 paper.tex
correcciones en la primer parte de corridor

@@
 We explored the parameter space along $v_d$ and $k_n$ for the bottleneck situation.
-Varying $v_d$ (at a fixed $k_n$) explores the collective behavior for different $(\mathcal{A},\mathcal{K}_c)$ pairs.
-We realized that increasing $\mathcal{K}_c$ only improves the evacuation performance through the bottleneck.
+This is similar to explore the unitless space $(\mathcal{A},\mathcal{K}_c)$.
+Soft pedestrians attain a FIS or FIS+FIF evacuation pattern but, stiff pedestrians (for any fixed $\mathcal{A}$ value within the explored range) exhibit a single FIF pattern.
+Stiffness affects either the presence of the blocking clusters and the pedestrians overlap.
+The less they compress, the less intense becomes the sliding friction among them.
+Additionally, the fewer the blocking clusters the easier they get out.
+\\
 
@@
 
-In this section, we present the results corresponding to the corridor geometry. We show the effects of modifying the body force coefficient $k_n$ in the dynamics.\\
-
-In the same way as with the bottleneck geometry, we computed the contact network to study the topological differences that arise from increasing the $k_n$ value.
-Fig.~\ref{degree_dens} shows the mean degree as a function of the global density for different $k_n$ values.
-When the density is low,  the degree is zero because the pedestrians do not touch each other.
-When the density is around 4.5, a few pedestrians start to touch each other increasing the mean degree.
-As the density increases, the mean degree increases until reaching an asymptotic behavior as approaching degree six.
-Degree six corresponds to the densest packing possible for identical hard circles; the result is a hexagonal packing arrangement.\\
-
-It is important to notice that in Fig.
-\ref{degree_dens}, for a given value of density, the stiffer the pedestrians, the higher the degree.
-In the bottleneck geometry, the opposite thing happens.
-The stiffer the pedestrians, the lower the mean degree.
-\\
-
-The mean overlap increases as the global density increases (see Fig.
-\ref{overlap_dens}).
-For a given density, there is an inverse relation between stiffness and mean overlap.
-This result is similar to the overlap vs.
-desired velocity obtained for bottleneck geometry.
-The higher the value of $k_n$, the higher the repulsion of the pedestrian-pedestrian interaction since the body force is acting on the direction $n_{ij}$.\\
+We present in this section the results corresponding to the corridor geometry. We show the effects of modifying the body force coefficient $k_n$ on the collective dynamics.\\
+
+We computed the contact network in the same way in the bottleneck geometry.
+Fig.~\ref{degree_dens} shows the mean degree as a function of the global density for different $k_n$ values (see caption for details).
+The degree is zero because the pedestrians do not touch each other.
+When the density reaches 4.5, a few pedestrians start to touch each other increasing the mean degree.
+As the density continuous increasing, the mean degree increases towards the asymptotic degree six.
+Degree six corresponds to the maximum packing density for identical hard circles.\\
+
+Fig.
+\ref{degree_dens} exhibits a somewhat opposite behavior with respect to the bottleneck geometry, for a given value of density.
+Here, the stiffer the pedestrians the higher the degree.
+In the bottleneck geometry, however, the stiffer the pedestrians, the lower the mean degree.
+Besides, Fig.
+\ref{overlap_dens} shows that the mean overlap increases as the global density increases.
+This behavior appears similar to the bottleneck situation, in the sense that the higher the value of $k_n$ the less they overlap.
+The same reasoning in Section \ref{bottleneck} apply to this situation.
+\\
 
@@
 (b) mean overlap as a function of the global density.
-The mean values are averages over all the pedestrians and over time once the system reaches the stationary state.
+The global density is the total number of pedestrians per unit area.
+The mean values are averages over all the pedestrians and over time once the system reached the stationary state.
 Both measurements correspond to corridor geometry with desired velocity $v_d=1$.
@@
 
-As was mentioned above, increasing the $k_n$ value of the body force increases the stiffness of pedestrians.
-Increasing the stiffness reduces the overlap (both in the bottleneck and corridor).
-Regarding the network connectivity, increasing the stiffness reduces the mean degree in a bottleneck but increases the mean degree in a corridor.
-Fig.~\ref{network_corridor} shows the contact network corresponding to the corridor at a particular timestep ($t=50$~s) and at a particular global density ($\rho=7$).
-Fig.~\ref{network_d6_kn0} corresponds to $k_n=0$ while Fig.~\ref{network_d6_knE5} corresponds to $k_n=1.2$~E5.
-This is an example to show that increasing the stiffness increases the number of contacts between pedestrians (the network connectivity).
-Notice that there are many more pedestrians with degree 6 in the case of $k_n=1.2$~E5 than the case of $k_n=0$.
+In order to get a better insight on how the pedestrians contact to each other, we present in Fig.~\ref{network_corridor} two snapshots of the corridor at the stationary situation.
+Fig.~\ref{network_d6_knE5} corresponds to $k_n=1.2$~E5.
+It can be seen that increasing ther stiffness increases the number of contacts between pedestrians (say, the network connectivity).
+The number of nodes attaining degree 6 is far larger in the case of $k_n=1.2\,$E5 than the case of $k_n=0$.
 \\
@@
     \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_d6_knE5.eps}\label{network_d6_knE5}}\\
-\caption[width=0.47\columnwidth]{Contact network of the pedestrians along the corridor.
+\caption[width=0.47\columnwidth]{Contact network of the pedestrians along the corridor at time $t=50\,$s.
+The global density was $\rho=6$.
 The lines that connect the nodes (pedestrians) represent the contact between them.
@@
 (a) corresponds to a simulation without body force and (b) corresponds to a simulation with $k_n=1.2$~E5.
+The friction coefficient and the other SFM parameters are the same as in Section \ref{bottleneck}.
 Color online only.}

### 2020-02-05 paper.tex
agregamos a jose y aye a los agradecimientos

@@
 Research Council (spanish: Consejo Nacional de Investigaciones Cient\'\i ficas 
-y T\'ecnicas - CONICET, Argentina) grant Programaci\'on Cient\'\i fica 2018 (UBACYT) Number 20020170100628BA.
+y T\'ecnicas - CONICET, Argentina) grant Programaci\'on Cient\'\i fica 2018 (UBACYT) Number 20020170100628BA.\\
+
+The authors want to thanks the degree students Josefina Catoni and Ayelen Santos for providing data acquired at 
+the subway in Buenos Aires, Argentina.
 

### 2020-02-06 paper.tex
algunas correcciones de signos
correcciones menores de gramatica en la parte de bottleneck

@@
 
-The sliding friction reduction appears as the fist feature for enhancing
+The sliding friction reduction appears as the first feature for enhancing
 the overall evacuation performance. Either reducing the mean overlap and the mean degree
@@
 Stiffness affects either the presence of the blocking clusters and the pedestrians overlap.
-The less they compress, the less intense becomes the sliding friction among them.
+The less they overlap, the less intense becomes the sliding friction among them.
 Additionally, the fewer the blocking clusters the easier they get out.
@@
 \begin{equation}
-S = \frac{<v_x(center)> - <v_x(boundary)> }{\left | y(center) - y(boundary) \right |} 
+S = \frac{\langle v_x(center)\rangle - \langle v_x(boundary)\rangle }{\left | y(center) - y(boundary) \right |} 
 \end{equation}
 
-Where $<>$ means the average taken over time.
+Where $\langle \rangle$ means the average taken over time.
 By this definition we compare the velocity of the pedestrians close to the wall (boundary) with respect to the velocity of the pedestrians in the center of the corridor (center).

### 2020-02-06 paper.tex
correccion de gramatica chica
reemplace los 1.2E4 por 2.6E4

@@
 FIS can be seen at all. Besides, the evacuation pattern for $k_n = 0$ and $k_n 
-= 1.2\,$E4 are very similar since the body force intensity is of the same order
+= 2.6\,$E4 are very similar since the body force intensity is of the same order
 or less than the social 
@@
 velocities. In all cases, the velocity increases with the stiffness. From 
-$k_n=0$ to $k_n=1.2\,$E4 the increment of velocity is not as significative as it 
+$k_n=0$ to $k_n=2.6\,$E4 the increment of velocity is not as significative as it 
 is for higher $k_n$. \\
@@
 
-We computed the contact network in the same way in the bottleneck geometry.
+We computed the contact network in the same way as in the bottleneck geometry.
 Fig.~\ref{degree_dens} shows the mean degree as a function of the global density for different $k_n$ values (see caption for details).
-The degree is zero because the pedestrians do not touch each other.
+The degree is zero when the pedestrians do not touch each other.
 When the density reaches 4.5, a few pedestrians start to touch each other increasing the mean degree.
@@
 $v_x$ reduces as $k_n$ increases as opposed to what happens in the bottleneck geometry.
-There is little to no change in the speed from zero to $k_n=$1.2~E4, from this value on, the diminishing of velocity is more abrupt.\\
+There is little to no change in the speed from zero to $k_n=$2.6~E4, from this value on, the diminishing of velocity is more abrupt.\\
 

### 2020-02-06 paper.tex
correcciones de ortografia en todo el paper

@@
 $x-$direction as a function of the stiffness $k_n$ for three different desired 
-velocities. In all cases, the velocity increases with the stiffness. From 
-$k_n=0$ to $k_n=2.6\,$E4 the increment of velocity is not as significative as it 
-is for higher $k_n$. \\
+velocities. In all cases, the velocity increases with the stiffness. The most significative 
+increment of velocity is in the interval $k_n>$E4. \\
 
@@
 pedestrians). The average was taken every five seconds once the crowd reaches the 
-stationary state ($t=$20~s) until the end of the simulation ($t=$110~s). 
+stationary state ($t=$20~s) until the end of the simulation ($t=$1000~s). 
 Color online only. }
@@
 
-% Agregar valor de kappa en todos los captions.
-
 \begin{figure}[!htbp]
@@
 The data corresponds to a bottleneck with periodic boundary conditions (re-injecting pedestrians).
-The average was taken every five seconds once the crowd reached the stationary state (say, $t=$20~s) until the end of the simulation ($t=$110~s).
+The average was taken every five seconds once the crowd reached the stationary state (say, $t=$20~s) until the end of the simulation ($t=$1000~s).
 Color online only.}
@@
 Fig.~\ref{network_d6_knE5} corresponds to $k_n=1.2$~E5.
-It can be seen that increasing ther stiffness increases the number of contacts between pedestrians (say, the network connectivity).
+It can be seen that increasing the stiffness increases the number of contacts between pedestrians (say, the network connectivity).
 The number of nodes attaining degree 6 is far larger in the case of $k_n=1.2\,$E5 than the case of $k_n=0$.

### 2020-02-06 paper.tex
reemplace ~ por \,

@@
 environment). The presence of the body force moves the dynamics to a more 
-complex context. We will investigate this context in section~\ref{results}. \\
+complex context. We will investigate this context in Section~\ref{results}. \\
 
@@
 velocities. In all cases, the velocity increases with the stiffness. The most significative 
-increment of velocity is in the interval $k_n>$E4. \\
+increment of velocity is in the interval $k_n>\,$E4. \\
 
@@
 pedestrians). The average was taken every five seconds once the crowd reaches the 
-stationary state ($t=$20~s) until the end of the simulation ($t=$1000~s). 
+stationary state ($t=20\,$s) until the end of the simulation ($t=1000\,$s). 
 Color online only. }
@@
 (a) and (b) correspond to a simulation without body force with $v_d=$2 and $v_d=$10 respectively.
-(c) and (d) correspond to simulations with $k_n$=1.2\,E6 with $v_d=$2 and $v_d=$10 respectively.
+(c) and (d) correspond to simulations with $k_n=1.2\,$E6 with $v_d=$2 and $v_d=$10 respectively.
 Color online only.}
@@
 Fig.~\ref{network_vd2_kn0} and Fig.~\ref{network_vd10_kn0} show snapshots for $k_n=0$, at the desired velocities of 2$\,$m/s and 10$\,$m/s, respectively.
-Fig.~\ref{network_vd2_kn1200000} and Fig.~\ref{network_vd10_kn1200000} show similar situations, but for  $k_n=$1.2$\,$E6.
+Fig.~\ref{network_vd2_kn1200000} and Fig.~\ref{network_vd10_kn1200000} show similar situations, but for  $k_n=1.2\,$E6.
 As expected, increasing the desired velocity compresses the crowd towards the exit.
@@
 In order to get a better insight on how the pedestrians contact to each other, we present in Fig.~\ref{network_corridor} two snapshots of the corridor at the stationary situation.
-Fig.~\ref{network_d6_knE5} corresponds to $k_n=1.2$~E5.
+Fig.~\ref{network_d6_knE5} corresponds to $k_n=1.2\,$E5.
 It can be seen that increasing the stiffness increases the number of contacts between pedestrians (say, the network connectivity).
@@
 The corridor was 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
-(a) corresponds to a simulation without body force and (b) corresponds to a simulation with $k_n=1.2$~E5.
+(a) corresponds to a simulation without body force and (b) corresponds to a simulation with $k_n=1.2\,$E5.
 The friction coefficient and the other SFM parameters are the same as in Section \ref{bottleneck}.
@@
 $v_x$ reduces as $k_n$ increases as opposed to what happens in the bottleneck geometry.
-There is little to no change in the speed from zero to $k_n=$2.6~E4, from this value on, the diminishing of velocity is more abrupt.\\
+There is little to no change in the speed from zero to $k_n=2.6\,$E4, from this value on, the diminishing of velocity is more abrupt.\\
 
@@
 This microscopic mechanism explains the macroscopic behavior that turns the crowd from a ``fluid-like state'' into a ``solid-like state''.
-When the stiffness is high enough (say $k_n=$1.2~E6), all the pedestrians walk at the same velocity.
+When the stiffness is high enough (say $k_n=1.2\,$E6), all the pedestrians walk at the same velocity.
 The pedestrians that walk in physical contact with the wall are the ones who determine the velocity of the whole crowd.\\
@@
 This behavior was observed in empirical measurements reported in Ref.~\cite{zhang2013empirical}.
-As $k_n$ increases the velocity profile flattens until becoming a constant ($k_n=$ 1.2~E6).
+As $k_n$ increases the velocity profile flattens until becoming a constant ($k_n=1.2\,$E6).
 In this scenario, the value of mean $v_x$ is much lower than on the case of soft pedestrians ($k_n=$0).\\
@@
 \ref{flow_density} show the flow as a function of the global density (fundamental diagram).
-Fig.~\ref{flow_density_no_body_force} corresponds to $\mathcal{K}_c=$ 0 (zero body force \textit{i.e.} $k_n=0$) while Fig.~\ref{flow_density_body_force} corresponds to $\mathcal{K}_c=$68 (which is the value of the original SFM with $k_n$=1.2~E5 ).
+Fig.~\ref{flow_density_no_body_force} corresponds to $\mathcal{K}_c=$ 0 (zero body force \textit{i.e.} $k_n=0$) while Fig.~\ref{flow_density_body_force} corresponds to $\mathcal{K}_c=$68 (which is the value of the original SFM with $k_n=1.2\,$E5 ).
 Each curve correspond to a different friction value, hence different $k_t$ value (see the caption).\\
@@
 \ref{flow_density} shows the flow as a function of the global density (fundamental diagram).
-\ref{flow_density_no_body_force} corresponds to zero body force (\textit{i.e.} $k_n=0$), Fig.~\ref{flow_density_body_force} corresponds to a body force with $k_n$=1.2~E5.
+\ref{flow_density_no_body_force} corresponds to zero body force (\textit{i.e.} $k_n=0$), Fig.~\ref{flow_density_body_force} corresponds to a body force with $k_n=1.2\,$E5.
 Each curve correspond to a different friction value (see the caption).\\

### 2020-02-06 paper.tex
mas correcciones de estilo y reemplazo de d por delta

@@
 The data corresponds to a bottleneck with periodic boundary conditions (re-injecting pedestrians).
-The average was taken every five seconds once the crowd reached the stationary state (say, $t=$20~s) until the end of the simulation ($t=$1000~s).
+The average was taken every five seconds once the crowd reached the stationary state (say, $t=20\,$s) until the end of the simulation ($t=1000\,$s).
 Color online only.}
@@
 \caption[width=0.47\columnwidth]{Snapshots of the contact networks of a 225 pedestrian evacuation through a bottleneck.
-The door is placed at $(x,y)=(20,10)$~m, the width of the door is 0.92~m (equivalent to 2 pedestrian\textsc{\char13}s diameter).
+The door is placed at $(x,y)=(20,10)\,$m, the width of the door is 0.92$\,$m (equivalent to 2 pedestrian\textsc{\char13}s diameter).
 The lines that connect the nodes (pedestrians) represent the contact between them.
@@
 The situation corresponds to a bottleneck with 225 pedestrians under periodic boundary conditions (re-injection of pedestrians once they left the room).
-The sampled interval was set to $t_f =$ 1000~s.
+The sampled interval was set to $t_f =$ 1000$\,$s.
 Color online only.
@@
 The colors stand for the degree of the node (the number of pedestrians that are in contact with him/her).
-The corridor was 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
+The corridor was 28$\,$m $\times$ 22$\,$m with periodic boundary conditions and $v_d=1$.
 (a) corresponds to a simulation without body force and (b) corresponds to a simulation with $k_n=1.2\,$E5.
@@
 Each marker corresponds to a different stiffness $k_n$ (see the label in the plot).
-The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
+The measurements correspond to a corridor of 28$\,$m $\times$ 22$\,$m with periodic boundary conditions and $v_d=1$.
 Color online only.
@@
 \caption{\label{kn_vs_vx_corridor} Mean velocity in the longitudinal coordinate $(v_x)$ as a function of the stiffness $k_n$ for three different global densities (see label in the plot).
-The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
+The measurements correspond to a corridor of 28$\,$m $\times$ 22$\,$m with periodic boundary conditions and $v_d=1$.
 Color online only.
@@
 (b) Strain rate as a function of the stiffness level $k_n$ for three different global density values (see label).
-The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
-The global density was 7 p~m$^{-2}$.
+The measurements correspond to a corridor of 28$\,$m $\times$ 22$\,$m with periodic boundary conditions and $v_d=1$.
+The global density was 7 p$\,$m$^{-2}$.
 Color online only.
@@
 \ref{flow_density} show the flow as a function of the global density (fundamental diagram).
-Fig.~\ref{flow_density_no_body_force} corresponds to $\mathcal{K}_c=$ 0 (zero body force \textit{i.e.} $k_n=0$) while Fig.~\ref{flow_density_body_force} corresponds to $\mathcal{K}_c=$68 (which is the value of the original SFM with $k_n=1.2\,$E5 ).
+Fig.~\ref{flow_density_no_body_force} corresponds to $\mathcal{K}_c=$ 0 (zero body force \textit{i.e.} $k_n=0$) while Fig.~\ref{flow_density_body_force} corresponds to $\mathcal{K}_c=$68 (which is the E6value of the original SFM with $k_n=1.2\,$E5 ).
 Each curve correspond to a different friction value, hence different $k_t$ value (see the caption).\\
@@
 global density.
-The flow is calculated in a circular area of R=1~m at the center of the corridor.
+The flow is calculated in a circular area of $R=1\,$m at the center of the corridor.
 The circular markers correspond to the original friction of the SFM, the "+" symbol corresponds to the friction increased by a factor of five and the triangles correspond to the friction increased by a factor of ten.

### 2020-02-06 plots/corridor/k_vs_vx/plot_k_vs_vx.py
agrego el archivo de python que grafica vx vs kn en corridor

@@ -59,10 +59,10 @@ std_vx_d8 = data_d8["std vx"].tolist()
 ###  PLOT  ###
 fig, ax1 = plt.subplots()
 
-plt.plot(k_d5_5,mean_vx_d5_5,'-s',color='#1f77b4',mew=0.7,markeredgecolor='k',markersize=5,zorder=1,label='$d=5.5$')
-plt.plot(k_d6,mean_vx_d6,'-^',color = '#ff7f0e',mew=0.7,markeredgecolor='k',markersize=5,zorder=1,label='$d=6$') 
+plt.plot(k_d5_5,mean_vx_d5_5,'-s',color='#1f77b4',mew=0.7,markeredgecolor='k',markersize=5,zorder=1,label='$\\rho=5.5$')
+plt.plot(k_d6,mean_vx_d6,'-^',color = '#ff7f0e',mew=0.7,markeredgecolor='k',markersize=5,zorder=1,label='$\\rho=6$') 
 #plt.plot(k_d7,mean_vx_d7,'-cs',mew=0.7,markeredgecolor='k',markersize=4,zorder=3,label='$d=7$') 
-plt.plot(k_d8,mean_vx_d8,'-x',color = 'g',mew=0.7,markeredgecolor='k',markersize=5,zorder=1,label='$d=8$') 
+plt.plot(k_d8,mean_vx_d8,'-x',color = 'g',mew=0.7,markeredgecolor='k',markersize=5,zorder=1,label='$\\rho=8$') 
 #plt.plot(vd_knE6,mean_comp_knE6,'-ko',mew=0.7,markeredgecolor='k',markersize=4,zorder=1,label='$k=1.2$ E6') 
 
 pylab.grid(False)

### 2020-02-07 paper.tex
reemplazo de compression por overlap
agregue las correcciones de guille del 6/2

@@
 between pedestrians are quite different for soft individuals than for stiff 
-individuals. Thus, we proceed to study the dynamics of contacting pedestrians, regardless of the compression 
+individuals. Thus, we proceed to study the dynamics of contacting pedestrians, regardless of the overlap 
 effects. We will assimilate the pedestrians as nodes and the whole crowd as a 
@@
 We explored the parameter space along $v_d$ and $k_n$ for the bottleneck situation.
-This is similar to explore the unitless space $(\mathcal{A},\mathcal{K}_c)$.
+This is similar to explore the unitless plane $(\mathcal{A},\mathcal{K}_c)$.
 Soft pedestrians attain a FIS or FIS+FIF evacuation pattern but, stiff pedestrians (for any fixed $\mathcal{A}$ value within the explored range) exhibit a single FIF pattern.
@@
 
-We present in this section the results corresponding to the corridor geometry. We show the effects of modifying the body force coefficient $k_n$ on the collective dynamics.\\
-
-We computed the contact network in the same way as in the bottleneck geometry.
-Fig.~\ref{degree_dens} shows the mean degree as a function of the global density for different $k_n$ values (see caption for details).
-The degree is zero when the pedestrians do not touch each other.
-When the density reaches 4.5, a few pedestrians start to touch each other increasing the mean degree.
-As the density continuous increasing, the mean degree increases towards the asymptotic degree six.
-Degree six corresponds to the maximum packing density for identical hard circles.\\
-
-Fig.
-\ref{degree_dens} exhibits a somewhat opposite behavior with respect to the bottleneck geometry, for a given value of density.
-Here, the stiffer the pedestrians the higher the degree.
-In the bottleneck geometry, however, the stiffer the pedestrians, the lower the mean degree.
-Besides, Fig.
-\ref{overlap_dens} shows that the mean overlap increases as the global density increases.
-This behavior appears similar to the bottleneck situation, in the sense that the higher the value of $k_n$ the less they overlap.
-The same reasoning in Section \ref{bottleneck} apply to this situation.
-\\
+We present in this section the results corresponding to the corridor geometry. 
+We show the effects of modifying the body force coefficient $k_n$ on the 
+collective dynamics. We will keep $v_d$ (or $\mathcal{A}$) 
+fixed along this Section. \\
+
+We first computed the contact network in the same way 
+as in the bottleneck geometry. Fig.~\ref{degree_dens} shows the 
+mean degree as a function of the global density for different $k_n$ values (see 
+caption for details). The mean degree vanishes at very low 
+densities because the pedestrians do not touch each other. When the density 
+surpasses 4.5, a few pedestrians start to touch each other, 
+raising the mean degree. As the density continuous increasing, 
+the mean degree approaches the asymptotic value 
+of six. Degree six corresponds to the maximum packing density for identical 
+hard circles.\\
 
@@
 \centering
-    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./degree_vs_dens_multi_kn.eps}\label{degree_dens}}\ 
-    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./overlap_vs_dens_multi_kn.eps}\label{overlap_dens}}\\
-\caption[width=0.47\columnwidth]{(a) Mean degree as a function of the global density for different $k_n$ values.
-(b) mean overlap as a function of the global density.
-The global density is the total number of pedestrians per unit area.
-The mean values are averages over all the pedestrians and over time once the system reached the stationary state.
-Both measurements correspond to corridor geometry with desired velocity $v_d=1$.
-Color online only.}
+
+\subfloat[]{\includegraphics[width=0.49\columnwidth]
+{./degree_vs_dens_multi_kn.eps}\label{degree_dens}}\ 
+\subfloat[]{\includegraphics[width=0.49\columnwidth]
+{./triangles.eps}\label{triangles}}\\
+% \subfloat[]{\includegraphics[width=0.49\columnwidth]
+%{./overlap_vs_dens_multi_kn.eps}\label{overlap_dens}}\\
+\caption[width=0.47\columnwidth]{(a) Mean degree as a function 
+of the global density for different $k_n$ values. (b)  Triangles per node as a 
+function of the global density. The global density is the total number of 
+pedestrians per unit area. The mean values are averages over all the pedestrians 
+and over time once the system reached the stationary state. The measurements 
+correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions 
+and $v_d=1$. Color online only.}
 \label{network_corridor}
@@
 
-In order to get a better insight on how the pedestrians contact to each other, we present in Fig.~\ref{network_corridor} two snapshots of the corridor at the stationary situation.
-Fig.~\ref{network_d6_knE5} corresponds to $k_n=1.2\,$E5.
-It can be seen that increasing the stiffness increases the number of contacts between pedestrians (say, the network connectivity).
-The number of nodes attaining degree 6 is far larger in the case of $k_n=1.2\,$E5 than the case of $k_n=0$.
-\\
-
-This result is exactly the opposite of what we get in the bottleneck geometry.
-This phenomenon occurs because, in the corridor, the lateral walls act like a containment barrier that forces the pedestrian to increase their contacts.
-Whereas in the bottleneck there are no lateral walls, thus, when increasing the stiffness they have more space to detach from each other, reducing the connectedness (hence reducing the mean degree).
-\\
+\textcolor{red}{It is worth noting} from Fig.~\ref{degree_dens} that ``stiff''
+pedestrians exhibit a sharper transition to the maximum packing density than 
+the ``soft'' pedestrians. We further checked this phenomenon by counting the 
+number of loops of three nodes (say, the triangles) present in the network. 
+This magnitude was reported to be a sensitive magnitude for characterizing the 
+jamming transition in a compressed granular packing (see 
+Ref.~\cite{pugnaloni_2013} for details).  As can be seen in 
+Fig.~\ref{triangles}, the ``stiff'' pedestrians share more triangles 
+than the ``soft'' ones.\textcolor{red}{ The maximum number of allowed triangles is 6, 
+corresponding to a hexagonal arrangement.}    \\
+
+In order to get a better insight on how the pedestrians contact to each other, 
+we present in Fig.~\ref{network_corridor} two snapshots of the corridor at the 
+stationary situation. Fig.~\ref{network_d6_kn0} corresponds to 
+$k_n=0$, while Fig.~\ref{network_d6_knE5} corresponds to $k_n=1.2$~E5. The 
+former shows a somewhat disordered network, while the latter exhibits an almost 
+completely ordered lattice. The missing triangles in Fig.~\ref{network_d6_kn0} 
+are replaced by other polygons of more than three edges.    \\
 
@@
 The colors stand for the degree of the node (the number of pedestrians that are in contact with him/her).
-The corridor was 28$\,$m $\times$ 22$\,$m with periodic boundary conditions and $v_d=1$.
-(a) corresponds to a simulation without body force and (b) corresponds to a simulation with $k_n=1.2\,$E5.
+The corridor was 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
+(a) corresponds to a simulation without body force and (b) corresponds to a simulation with $k_n=1.2$~E5.
 The friction coefficient and the other SFM parameters are the same as in Section \ref{bottleneck}.
@@
 
-In the corridor geometry, the crowd gets more connected if the pedestrians become stiffer.
-We studied the network properties of the contact graph arising from the positions $(x,y)$ of every pedestrian.
-We found that a good descriptor to exhibit the connectivity is the number of triangles per node.
-A triangle is defined as a structure composed of three nodes, all in contact with each other.
-Fig.~\ref{triangles} shows the triangles per node as a function of the global density for different stiffness values $k_n$.
-This descriptor allows distinguishing states with the same global density but different stiffness levels.
-In other words, it is a descriptor very sensitive to changes in stiffness that allow expressing the connectivity of the system even better than the mean degree.
-\\
-
-This result is consistent with the results obtained in Ref.~\cite{pugnaloni_2013} where the authors explore several topological and geometrical descriptors capable of properly describing granular systems with different stiffness levels.
-While our study system is self-propelled, there are analogies with the system studied in Ref.~\cite{pugnaloni_2013}.
-Like the authors, we recommend using topological descriptors (in particular triangles per node) to describe systems with equal global density and different stiffness levels.\\
+We find these topological magnitudes useful for comparing the 
+corridor geometry with respect to the bottleneck geometry. A re-examination of 
+Fig.~\ref{degree_dens} (corridor) and Fig.~\ref{degree_vd} (bottleneck) reveal 
+that the pedestrian stiffness $k_n$ affects differently the way they contact 
+each other. The mean degree increases for ``stiff'' pedestrians moving along 
+the corridor (at densities above $5\,$p/m$^2$). Conversely, the mean degree 
+increases for ``soft'' pedestrians in the bottleneck situation.\\
+
+Fig.~\ref{network_bottleneck} and 
+Fig.~\ref{network_corridor} illustrate the connectivity differences between 
+the bottleneck and the corridor situation. The bulk in 
+Fig.~\ref{network_bottleneck} appears more heavily connected among ``soft'' 
+pedestrians than among ``stiff'' pedestrians (see both snapshots at $v_d=10$). 
+The opposite occurs in Fig.~\ref{network_corridor}. This discrepancy seems to 
+be related to the boundary conditions, since the same SFM parameters were 
+applied on both situations. We may speculate that this phenomenon occurs 
+because, in the corridor, the lateral walls act like a containment barrier that 
+forces the ``stiff'' pedestrian to increase his (her) contacts. On the contrary, 
+no real containment walls exist in the bottleneck situation (regardless the side 
+walls). \\
+
+We can test our hypothesis by computing the mean overlap. 
+Fig.~\ref{overlap_dens} shows this magnitude for the corridor situation. Notice 
+that ``soft'' pedestrians attain a more intruding overlap than the ``stiff'' 
+ones, as expected. This is in agreement with Fig.~\ref{overlap_vd} for the 
+bottleneck situation (at a fixed value of $v_d$). The curves in 
+Fig.~\ref{overlap_vd}, however, do not meet each other as in  
+Fig.~\ref{overlap_dens}. The curve meeting attains for space limitations in 
+the corridor, since overlapping occurs (almost) independently of the value of
+$k_n$. This is clearly not the case in the bottleneck situation. \\
 
@@
 \includegraphics[width=0.7\columnwidth]
-{./triangles.eps}
-\caption{\label{triangles} Triangles per node as a function of the global density.
-A triangle in a network is defined as three nodes all connected.
-Each marker corresponds to a different stiffness $k_n$ (see the label in the plot).
-The measurements correspond to a corridor of 28$\,$m $\times$ 22$\,$m with periodic boundary conditions and $v_d=1$.
-Color online only.
-}
+{./overlap_vs_dens_multi_kn.eps}
+\caption{\label{overlap_dens} Mean overlap as a function of the 
+global density. The global density is the total number of pedestrians per unit 
+area. The mean values are averages over all the pedestrians and over time once 
+the system reached the stationary state. Both measurements correspond to 
+the corridor geometry with desired velocity $v_d=1$. Color 
+online only. }
 \end{figure}
 
-The most important result is that increasing the $k_n$ value reduces the flow (hence reduces the walking speed of the overall crowd) in the corridor geometry.
-Fig.~\ref{kn_vs_vx_corridor} shows the mean velocity in the direction of displacement $v_x$ as a function of the stiffness for different global density levels.
-$v_x$ reduces as $k_n$ increases as opposed to what happens in the bottleneck geometry.
-There is little to no change in the speed from zero to $k_n=2.6\,$E4, from this value on, the diminishing of velocity is more abrupt.\\
-
-The reason why the velocity reduces as the stiffness of the pedestrians' increases is that it becomes harder for pedestrians to walk forward.
-The difficulty arises because the pedestrian feels a much higher repulsion from the pedestrian ahead (due to the body force increment).
-Thus, they have no choice but to move at (almost) the same speed as the individuals they have at their sides.
-This microscopic mechanism explains the macroscopic behavior that turns the crowd from a ``fluid-like state'' into a ``solid-like state''.
-When the stiffness is high enough (say $k_n=1.2\,$E6), all the pedestrians walk at the same velocity.
-The pedestrians that walk in physical contact with the wall are the ones who determine the velocity of the whole crowd.\\
+The above results correspond to a milestone in the 
+investigation. The connectivity differences between the bottleneck geometry 
+and the corridor geometry were not expected and opens two major questions: how 
+does the body stiffness interact with the walls, and consequently, how does 
+this affect the flux across the corridor.\\
+
+We start by computing the mean velocity across the corridor.  
+Fig.~\ref{kn_vs_vx_corridor} shows the mean velocity 
+$\langle v_x\rangle$ (parallel to the corridor) as a function 
+of the stiffness for different global density levels. This 
+plot shows a flat pattern for $k_n<10^4$ and a slowing down above this 
+threshold. Notice from Fig.~\ref{kn_vs_vx_bottleneck} that this is opposed
+to what happens in the bottleneck geometry. \\
 
@@
 \caption{\label{kn_vs_vx_corridor} Mean velocity in the longitudinal coordinate $(v_x)$ as a function of the stiffness $k_n$ for three different global densities (see label in the plot).
-The measurements correspond to a corridor of 28$\,$m $\times$ 22$\,$m with periodic boundary conditions and $v_d=1$.
+The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
 Color online only.
@@
 \end{figure}
+
+The $\langle v_x\rangle$ values in Fig.~\ref{kn_vs_vx_corridor} 
+were computed at densities $\rho\geq 5.5$. According to 
+Fig.~\ref{overlap_dens}, these densities attain relevant overlaps. Furthermore, 
+stiffness values $k_n\geq 10^4$ move the system to a more heavily connected 
+stage, and thus, pedestrians have no choice but to walk at 
+(almost) the same speed as his (her) neighbors. This 
+behavior may be envisaged as the passage from a released 
+walking movement to a tigh movement as the stiffness increases. A more 
+physical picture would assimilate te former as a ``fluid-like 
+state'' and the latter as a ``solid-like state''. When the stiffness is 
+very high (say $k_n=$1.2~E6), all the pedestrians 
+are expected to walk at a common velocity. The 
+pedestrians that walk in physical contact with the wall are the ones who 
+determine the velocity of the whole crowd, as discussed 
+below.\\
 

### 2020-02-07 paper.tex
puse kn y kt donde correspondia

@@
 
-Besides, no reliable values for the sliding friction $\kappa$ appears to be 
+Besides, no reliable values for the sliding friction $k_t$ appears to be 
 available in the literature (to our knowledge). We may presume, however, that 
@@
 \begin{equation}
- \mathbf{f}_g^{(ij)}=\kappa\,g(R_{ij}-r_{ij})\,
+ \mathbf{f}_g^{(ij)}=k_t\,g(R_{ij}-r_{ij})\,
 (\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij})\,\hat{\mathbf{t}}_{ij}+
-k\,g(R_{ij}-r_{ij})\,
+k_n\,g(R_{ij}-r_{ij})\,
 \,\hat{\mathbf{n}}_{ij}\label{eqn_friction}
@@
 linearly related to the difference between the (tangential) velocities. The 
-coefficients $\kappa$ (for the sliding friction) and $k_n$ (for the 
+coefficients $k_t$ (for the sliding friction) and $k_n$ (for the 
 body force) are supposed to be related to the areas of contact and the clothes 
@@
 We stress that the expression (\ref{eqn_friction}) assumes fixed values for 
-$\kappa$ and $k_n$. This may not be completely true according to 
+$k_t$ and $k_n$. This may not be completely true according to 
 Table~\ref{table_data}. The local density (and thus, the pedestrians' 
 compression) may affect the compressibility parameter $k_n$ by more than an order 
-of magnitude. We will vary $k_n$ (and $\kappa$) in order to explore this 
+of magnitude. We will vary $k_n$ (and $k_t$) in order to explore this 
 phenomenon. \\
@@
 Appendix~\ref{appendix1} for details). The sets correspond to 
-$\mathcal{A}=\{\tau/m,1/v_d,A\}$, $\mathcal{K}=\{\tau/m,B,\kappa\}$ and 
-$\mathcal{K}_c=\{\tau/m,1/v_d,B,k\}$. (a) The Venn diagram representation if no 
+$\mathcal{A}=\{\tau/m,1/v_d,A\}$, $\mathcal{K}=\{\tau/m,B,k_t\}$ and 
+$\mathcal{K}_c=\{\tau/m,1/v_d,B,k_n\}$. (a) The Venn diagram representation if no 
 body force is introduced in the SFM (only sets $\mathcal{A}$ and $\mathcal{K}$, 
@@
 Fig.~\ref{venn_2parameters} represents the situation when $\mathcal{K}_c$ is 
-absent. Notice that $A/v_d$ or $\kappa B$ may control the collective 
+absent. Notice that $A/v_d$ or $k_t B$ may control the collective 
 dynamic, in spite of the ``assertive'' attitude. The individual character of 
@@
 ``loosely'' that any numerical setting of these parameters may be 
-counterbalanced by the right setting of $A$ or $\kappa$, keeping the 
+counterbalanced by the right setting of $A$ or $k_t$, keeping the 
 colletive dynamic (qualitatively) unchanged.  \\
@@
 
-\textcolor{red}{It is worth noting} from Fig.~\ref{degree_dens} that ``stiff''
+It is worth noting from Fig.~\ref{degree_dens} that ``stiff''
 pedestrians exhibit a sharper transition to the maximum packing density than 
@@
 The SFM description in section~\ref{sfm} introduces seven parameters ($m$, 
-$\tau$, $v_d$, $B$, $A$, $\kappa$ and $k_n$) attaining for the ``individual'' 
+$\tau$, $v_d$, $B$, $A$, $k_t$ and $k_n$) attaining for the ``individual'' 
 behavior of each pedestrian. The collective dynamic, however, requires a 
@@
  \mathcal{A}=\displaystyle\frac{A\,\tau}{m\,v_d}\ \ \ \ , \ \ \ \ 
- \mathcal{K}=\displaystyle\frac{\kappa\,B\,\tau}{m}\ \ \ \ , \ \ \ \
+ \mathcal{K}=\displaystyle\frac{k_t\,B\,\tau}{m}\ \ \ \ , \ \ \ \
  \mathcal{K}_c=\displaystyle\frac{k\,B\,\tau}{m\,v_d}

### 2020-02-07 paper.tex
modificaciones leves de formato

@@
 The data corresponds to a bottleneck with periodic boundary conditions (re-injecting pedestrians).
-The average was taken every five seconds once the crowd reached the stationary state (say, $t=20\,$s) until the end of the simulation ($t=1000\,$s).
+The average was taken over time and the pedestrians in the bottleneck.
+The sampling was done every five seconds once the crowd reached the stationary state (say, $t=20\,$s) until the end of the simulation ($t=1000\,$s).
 Color online only.}
@@
 \includegraphics[width=0.7\columnwidth]{./kn_vs_vx_corridor.eps}
-\caption{\label{kn_vs_vx_corridor} Mean velocity in the longitudinal coordinate $(v_x)$ as a function of the stiffness $k_n$ for three different global densities (see label in the plot).
+\caption{\label{kn_vs_vx_corridor} Mean velocity in the longitudinal coordinate $(v_x)$
+ as a function of the stiffness $k_n$ for three different global densities (see label in the plot). 
  The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
-Color online only.
-}
+ The average was taken along the corridor and along the simulated time. Color online only.      }
 \end{figure}
@@
 \begin{equation}
-S = \frac{\langle v_x(center)\rangle - \langle v_x(boundary)\rangle }{\left | y(center) - y(boundary) \right |} 
+S = \frac{\langle v_x(\mathrm{center})\rangle - \langle v_x(\mathrm{boundary})\rangle }{\left | y(\mathrm{center}) - y(\mathrm{boundary}) \right |} 
 \end{equation}
@@
     \subfloat[]{\includegraphics[width=0.49\columnwidth]{./strain_rate_vs_kn.eps}\label{strain_rate_vs_kn}}\\
-\caption[width=0.47\columnwidth]{(a) Velocity in the $x$ coordinate as a function of the transversal coordinate $y$ for three different stiffness values $k$ (see the label).
+\caption[width=0.47\columnwidth]{(a) Velocity in the $x$ coordinate as a function of the transversal coordinate $y$ for three different stiffness values $k_n$ (see the label).
 (b) Strain rate as a function of the stiffness level $k_n$ for three different global density values (see label).
@@
 In this section, we inspect different values of the dimensionless numbers $\mathcal{K}_c$ and $\mathcal{K}$ and compare the results with the empirical measurements of Ref.~\cite{helbing_2007}.
-We varied the body force coefficient ($k_c$) and the friction coefficient ($k_t$) to inspect different values of $\mathcal{K}_c$ and $\mathcal{K}$ respectively.\\
+We varied the body force coefficient ($k_n$) and the friction coefficient ($k_t$) to inspect different values of $\mathcal{K}_c$ and $\mathcal{K}$ respectively.\\
 
@@
  \mathcal{K}=\displaystyle\frac{k_t\,B\,\tau}{m}\ \ \ \ , \ \ \ \
- \mathcal{K}_c=\displaystyle\frac{k\,B\,\tau}{m\,v_d}
+ \mathcal{K}_c=\displaystyle\frac{k_n\,B\,\tau}{m\,v_d}
 \end{equation}

### 2020-02-07 plots/reduced-in-units/venn.py
agrego graficador de venn

@@ -29,12 +29,12 @@ params = {'backend': 'ps',
 
 pylab.rcParams.update(params)
 
-'''
+
 ##### 3 parametros reducidos #####
-v = venn3(subsets=(1,1,1,1,1,1,1),set_labels = ('$\mathcal{A} =\\frac{A \\tau}{v_d m}$', '$\mathcal{K} = \\frac{\\kappa B \\tau}{m}$', '$\mathcal{K}_c = \\frac{k B \\tau}{v_d m}$'))
+v = venn3(subsets=(1,1,1,1,1,1,1),set_labels = ('$\mathcal{A} =\\frac{A \\tau}{v_d m}$', '$\mathcal{K} = \\frac{k_t B \\tau}{m}$', '$\mathcal{K}_c = \\frac{k_n B \\tau}{v_d m}$'))
 v.get_label_by_id('100').set_text('$A$')
-v.get_label_by_id('010').set_text('$\\kappa$')
-v.get_label_by_id('001').set_text('$k$')
+v.get_label_by_id('010').set_text('$k_t$')
+v.get_label_by_id('001').set_text('$k_n$')
 v.get_label_by_id('111').set_text('$\\frac{\\tau}{m}$')
 v.get_label_by_id('101').set_text('$\\frac{1}{v_d}$')
 v.get_label_by_id('110').set_text('')
@@ -42,10 +42,10 @@ v.get_label_by_id('011').set_text('$B$')
 '''
 
 ##### 2 parametros reducidos #####
-v = venn2(subsets=(1,1,1),set_labels = ('$\mathcal{A} = \\frac{A \\tau}{v_d m}$', '$\mathcal{K} = \\frac{\\kappa B \\tau}{m}$'))
+v = venn2(subsets=(1,1,1),set_labels = ('$\mathcal{A} = \\frac{A \\tau}{v_d m}$', '$\mathcal{K} = \\frac{k_t B \\tau}{m}$'))
 v.get_label_by_id('10').set_text(' $\\frac{A}{v_d}$')
-v.get_label_by_id('01').set_text('$\\kappa B$')
+v.get_label_by_id('01').set_text('$ k_t B$')
 v.get_label_by_id('11').set_text('$\\frac{\\tau}{m}$')
-
-pylab.savefig('venn_2parameters.png', format='png', dpi=300, bbox_inches='tight')
-pylab.savefig('venn_2parameters.eps', format='eps', dpi=300, bbox_inches='tight')
+'''
[…]

### 2020-02-07 paper.tex
correcciones en conclusion

@@
 
-\title{Effects of the body force on the pedestrian and evacuation dynamics}
+\title{Effects of the body force on the pedestrian and the evacuation dynamics}
 
@@
 range of $0.030-0.055\,$m. Also, a ``hitting'' force of $60\,$N can address 
-compressions between $0.045$ and $0.065\,$m. Thus, according to 
-Table~\ref{table_data}, \textcolor{blue}{we may expect experimental values for $k_n(x)$ up to 
-$1000\,$kg/s$^2$ (for $F=30\,$N), or, up to $1400\,$kg/s$^2$ (for $F=60\,$N).} \\
+compressions between $0.045$ and $0.065\,$m. \\
+%Thus, according to Table~\ref{table_data}, \textcolor{blue}{we may expect experimental values for $k_n(x)$ up to 
+%$1000\,$kg/s$^2$ (for $F=30\,$N), or, up to $1400\,$kg/s$^2$ (for $F=60\,$N).} \\
 
@@
 
-The value of $k_n$ affects the velocity all along the corridor.
-Fig.~\ref{vx_profile} shows the velocity profile ($v_x$ vs.
-the longitudinal coordinate $y$) for different $k_n$ values.
-For $k_n=0$, we can see a parabolic-like velocity profile that resembles the Poiseuille flow (for Newtonian and incompressible fluids in laminar flow flowing through a pipe).
-This behavior was observed in empirical measurements reported in Ref.~\cite{zhang2013empirical}.
-As $k_n$ increases the velocity profile flattens until becoming a constant ($k_n=1.2\,$E6).
-In this scenario, the value of mean $v_x$ is much lower than on the case of soft pedestrians ($k_n=$0).\\
-
-If the stiffness is high enough, the crowd behaves like a solid; this means that the crowd can not be easily ``deformed''.
-In this context, to deform means to have certain parts of the crowd that manage to move faster than other parts of the crowd.
+Fig.~\ref{vx_profile} shows the velocity profile ($\langle v_x \rangle$ vs.
+the transversal coordinate $y$) for different $k_n$ values.
+For $k_n=0$, we can see a parabolic-like velocity profile that resembles the Poiseuille flow (similar to Newtonian and incompressible fluids in a laminar regime).
+This behavior was also observed in empirical measurements of crowd dynamics reported in Ref.~\cite{zhang2013empirical}.
+But as $k_n$ increases the velocity profile flattens until becoming (almost) uniform (see Fig.~\ref{vx_profile} for $k_n=1.2\,$E6).
+In this scenario, $v_x$ attains a much lower level than in the case of soft pedestrians ($k_n=$0).\\
+
+The crowd behaves like a solid for very stiff pedestrians.
+This means that the crowd can not be easily ``deformed''.
+In this context, deformation means that parts of the crowd may be released to move faster than other parts of the crowd.
 \\
 
-The strain rate is a tensor for every point in the space.
-It expresses how the relative velocity of a medium changes when one moves away from a position in a specific direction.
-For this particular problem, we define the following version of the strain rate:
+The strain rate is the tensor that expresses how the relative velocity of a medium changes when one moves away from one position to another.
+We consider the following discrete definition of the strain rate:
 
@@
 \end{equation}
-
-Where $\langle \rangle$ means the average taken over time.
-By this definition we compare the velocity of the pedestrians close to the wall (boundary) with respect to the velocity of the pedestrians in the center of the corridor (center).
-As the stiffness level increases, the crowd becomes less deformable.
-This phenomenon is shown in Fig.~\ref{strain_rate_vs_kn} where we can see that the strain rate decreases with $k_n$.
-\\
 
@@
     \subfloat[]{\includegraphics[width=0.49\columnwidth]{./strain_rate_vs_kn.eps}\label{strain_rate_vs_kn}}\\
-\caption[width=0.47\columnwidth]{(a) Velocity in the $x$ coordinate as a function of the transversal coordinate $y$ for three different stiffness values $k_n$ (see the label).
+\caption[width=0.47\columnwidth]{(a) Mean velocity in the $x$ coordinate as a function of the transversal coordinate $y$ for three different stiffness values $k_n$ (see the label).
 (b) Strain rate as a function of the stiffness level $k_n$ for three different global density values (see label).
-The measurements correspond to a corridor of 28$\,$m $\times$ 22$\,$m with periodic boundary conditions and $v_d=1$.
-The global density was 7 p$\,$m$^{-2}$.
+Data correspond to a corridor of 28$\,$m $\times$ 22$\,$m with periodic boundary conditions and $v_d=1$.
+The global density was $\rho=7 p\,$m$^{-2}$.
 Color online only.
@@
 
-To conclude section \ref{corridor}, we remark that increasing the stiffness produces the opposite results in corridors respect to bottlenecks.
+Where $\langle \cdot \rangle$ means the average taken over time.
+This definition compares the velocity of the pedestrians close to the wall (boundary) with respect to the velocity of the pedestrians at the center of the corridor (center).
+Thus, $S$ vanishes (no deformation) as the stiffness level increases.
+This phenomenon is shown in Fig.~\ref{strain_rate_vs_kn} where we can see that the strain rate drops for high values of $k_n$.
+\\
+
+We conclude this Section by stressing that stiffer pedestrians attain opposite results in corridors with respect to bottlenecks.
 The walls in the corridors play a critical role that prevents pedestrians from detaching from each other.
-This effect has consequences such as increasing the connectivity of the contact network and flattening the velocity profile (thus reducing the strain rate).
-If the stiffness is high enough, the pedestrians can not push to the pedestrian ahead since the body force repulsion becomes very high.
-This leads to a ``solidification'' of the crowd that makes all the pedestrians walk at almost the same velocity.
-The pedestrians that are in contact with the wall are the ones who determine the velocity of the whole crowd.
+This effect has can be observed as an increment in the connectivity of the contact network and the flattening of the velocity profile (thus reducing the strain rate).
+Very high enough stiffness values stuck the pedestrians leading to a ``solidification'' of the crowd.
+All the pedestrians walk at almost the same velocity at this stage.
+The pedestrians that are in contact with the walls are the ones that determine the velocity of the whole crowd.
+We already analyzed this situation in Ref~\cite{dorso_2019}.
 \\
@@
 
-In this section, we inspect different values of the dimensionless numbers $\mathcal{K}_c$ and $\mathcal{K}$ and compare the results with the empirical measurements of Ref.~\cite{helbing_2007}.
-We varied the body force coefficient ($k_n$) and the friction coefficient ($k_t$) to inspect different values of $\mathcal{K}_c$ and $\mathcal{K}$ respectively.\\
-
-The empirical measurements correspond to the fundamental diagram measured at the entrance of the Jamaraat bridge (see the inset in Fig.~\ref{flow_density_no_body_force}).
-We aim to reproduce the qualitative behavior of these measurements roughly.\\
+IThe final stage of our investigation deals with the plausible values of the dimensionless numbers $\mathcal{K}_c$ and $\mathcal{K}$, in comparison to the empirical measurements.
+We vary the body force coefficient ($k_n$) and the friction coefficient ($k_t$) to explore different values of $\mathcal{K}_c$ and $\mathcal{K}$, respectively.\\
+
+We consider the empirical measurements from Ref.~\cite{helbing_2007} corresponding to the fundamental diagram obtained at the entrance of the Jamaraat bridge (see the inset in Fig.~\ref{flow_density_no_body_force}).
+Our aim is to reproduce the qualitative behavior of these measurements.\\
 
 Figs.
-\ref{flow_density} show the flow as a function of the global density (fundamental diagram).
-Fig.~\ref{flow_density_no_body_force} corresponds to $\mathcal{K}_c=$ 0 (zero body force \textit{i.e.} $k_n=0$) while Fig.~\ref{flow_density_body_force} corresponds to $\mathcal{K}_c=$68 (which is the E6value of the original SFM with $k_n=1.2\,$E5 ).
-Each curve correspond to a different friction value, hence different $k_t$ value (see the caption).\\
-
-According to most of the empirical measurements of the fundamental diagram, the flow decreases for high enough values of density because the crowd becomes jammed.
-Notice that the original friction (corresponding to $\mathcal{K}=$137) does not produce a reduction of the flow when there is zero body force ($\mathcal{K}_c=$0).
-Nevertheless, when the body force is included, and we remain the original friction (circles from Fig.~\ref{flow_density_body_force}), the flow reduces in the range of densities from  5 p m$^{-2}$ to 7 p m$^{-2}$; then increases for higher values of density.\\
-
-When the dimensionless number associated with the friction is $\mathcal{K} = $ 685, the friction is five times the original SFM value.
-In this scenario, the flow reduces for densities higher than 5 p m$^{-2}$ in both cases (with body force and without body force).
-The main qualitative difference is that including the body force produces a subtle increment in the flow for densities higher than 7 p m$^{-2}$ (orange curve from Fig.~\ref{flow_density_no_body_force}).
+\ref{flow_density} show the pedestrian flow as a function of the global density (fundamental diagram).
+Fig.~\ref{flow_density_no_body_force} corresponds to $\mathcal{K}_c=$ 0 (this is \textit{i.e.} $k_n=0$) while Fig.~\ref{flow_density_body_force} corresponds to $\mathcal{K}_c=$68 corresponding to the original SFM with $k_n=1.2\,$E5.
+Each curve represents different friction values (see the caption for details).\\
+
+According to the empirical measurements at Jamaraat, the flow slows down for high enough densities due to jamming.
+Notice that the original SFM (corresponding to $\mathcal{K}=$137) does not produce the expected slowing down for null body force ($\mathcal{K}_c=$0).
+However, when the body force is present (the original SFM) an ``U'' shape behavior occcurs for densities above 5 p$^{-2}$.\\
+
+The increase in $\mathcal{K}$ to $\mathcal{K} = $ 685 (five times the original SFM value) slows down  the flux for densities above 5 p m$^{-2}$, regardless of the presence of the body force.
+Including the body force, however, produces a subtle increment in the flow for densities higher than 7 p m$^{-2}$ (see orange curve from Fig.~\ref{flow_density_no_body_force}).
 \\
 
-When the dimensionless number associated to the friction is $\mathcal{K}=$1371  (the friction is ten times the original SFM value), in this case, the flow reduces or remains constant when the density is higher than 5 p m$^{-2}$ for both cases (with $\mathcal{K}_c=$ 0 and $\mathcal{K}_c = $ 68).\\
-
-It worth mentioning that the SFM contemplates the possibility of overlapping between pedestrians (unlike the models stated in Refs.~\cite{kabalan_2017,jebrane_2019}).
+A further increment of $\mathcal{K}$ to $\mathcal{K}=$137 (ten times the original SFM value) attains a plateau ($\rho>5$ p m$^{-2}$) before vanishing at very high densities.
+This occurs on either $\mathcal{K}_c=$ 0 and $\mathcal{K}_c = $ 68.\\
+
+%It is worth mentioning that the SFM contemplates the possibility of overlapping between pedestrians (unlike the models stated in Refs.~\cite{kabalan_2017,jebrane_2019}).
 Despite this hard-to-interpret feature, the SFM can reproduce empirical behaviors of collective pedestrian dynamics.\\
 
-These results suggest that although increasing $\mathcal{K}_c$ produces a reduction in the flow, it is necessary to increase $\mathcal{K}$ (for instance, increasing the friction coefficient $k_t$) to reproduce the reduction in the flow that characterizes the high-density regime.
-It is still a pending challenge to find the values of the dimensionless numbers that reproduce the qualitative behavior of the fundamental diagram, but this first approach narrows down the search.\\
+These results suggest that although increasing $\mathcal{K}_c$ slows down the flux, it is still necessary to increase $\mathcal{K}$ (by increasing the friction coefficient $k_t$) to avoid an ``U'' shape behavior for extremely high densities.
+It is still a challenge to find the optimal dimensionless numbers  $(\mathcal{A},\mathcal{K},\mathcal{K}_c)$ for the fundamental diagram.
+Our inspection into the parameter set is a first approach to narrow down the search.\\
 
@@
 
-In this research, we explore the effect on the pedestrians dynamics of the (sometimes neglected) body force in the framework of the SFM.
+We explored the effect on the pedestrians dynamics of the (sometimes neglected) body force in the framework of the SFM.
 We showed that the stiffness coefficient ($k_n$) has a significant impact on the evacuation dynamics (bottleneck) and also in the dynamics of pedestrians walking along a straight corridor.\\
 
-In the bottleneck geometry, the evacuation time diminishes (pedestrians move faster) as pedestrians become stiffer for all the ranges of the desired velocities explored.
-This phenomenon occurs because increasing the stiffness level promotes the repulsion between pedestrians pair interactions.
-As pedestrians detach from each other, the friction force diminishes due to the reduction of overlap between pedestrians and the contacts among them.
-The general decrease in frictional force reduces the probability of producing a cluster of pedestrians blocking the exit (blocking cluster), which leads to a more efficient evacuation dynamics.
+In the bottleneck geometry, the evacuation time diminishes (pedestrians move faster) as pedestrians become stiffer along the explored desired velocities.
+This phenomenon occurs because stiffer pedestrians reduce the overlapping and hence the sliding friction intensity.
+This scenario releases more easily the pedestrians and reduces the probability of producing a cluster of pedestrians blocking the exit (blocking cluster).
+This leads to a more efficient evacuation dynamics.
 \\
 
-In the corridor geometry, the actual walking speed reduces as pedestrians become stiffer.
-This is the opposite behavior with respect to the obtained in bottleneck geometry.
-The difference is explained because although increasing stiffness further separates individuals, they can not detach from each other as much as possible due to the lateral walls (these walls are not relevant in the bottleneck geometry).
-Thus, when the stiffness increases, the overlap between pedestrians is reduced while the number of contacts (degree) increases.
-Granular materials can behave like fluid or solids, depending on several conditions.
-If the stiffness level is low, the entire crowd behaves like a viscous fluid (with a parabolic velocity profile).
-However, if the stiffness level is high enough, the whole crowd behaves like a crystalline solid with a constant velocity profile which only depends on the friction interaction with the walls.\\
-
-Regarding the parameters of the model, we found that it is possible to reduce the original SFM parameters to three dimensionless parameters.
-The original parameters interrelate to each other through the dimensionless ones.
-Many different settings can produce the same dimensionless parameters.
-Thus, no univocal relations can be established between the individualistic parameters and collective dynamics.
-In order to explore the outcomes from different dimensionless numbers, we compared numerical results with empirical measurements.
-We found good candidates to reproduce the qualitative behavior of empirical measurements in the range $0 < \mathcal{K}_c < 68$ with $\mathcal{K} = 685$.
-Nevertheless, this is a first sketch to arrive at a set of dimensionless parameters that may be suitable to reproduce empirical measurements.
-We encourage further research that seeks to find values of the dimensionless numbers that best reproduce experimental data.\\
+The opposite behavior is obtained in the corridor geometry with respect to the bottleneck geometry.
+The major difference is that pedestrians are limited to the available space between walls in the corridor geometry.
+Walls are not relevant in the bottleneck geometry.
+Thus, the overlap between pedestrians is controlled by the available space.
+But, stiffer pedestrians are more likely to get stuck.
+The whole crowd can be compared to a granular material.
+Granular materials can be disordered (amorphous) or ordered depending on how particles link to each other.
+In the present context, at low stiffness levels, the crowd appears disordered attaining a parabolic velocity profile.
+If the stiffness level is high, the whole crowd appears ordered into a lattice (like a crystalline solid) with a uniform velocity profile that depends on the friction interaction with the walls.\\
+
+Our efforts to ``tune'' the original SFM to empirical data (say, the fundamental diagram) moved us to explore the dimensionless parameter space.
+We found that the qualitative behavior of empirical  data can be accomplished if the parameters are close to $\mathcal{K}_c < 68$, $\mathcal{K} = 685$ and $\mathcal{A}=14$.
+Nevertheless, this is a first attempt to arrive at suitable parameters, although we do not claim these to be optimal.
+We encourage further research to find dimensionless numbers that may better fit experimental data.\\
 

### 2020-02-07 plots/corridor/network_config/plot_config_graph.py
modifique el py que grafica network config

@@ -163,9 +163,9 @@ def plot_network(G,output_filename,title):
 def main():
 
      ############# PARAMETERS #############
-     input_filename = 'config_d6_knE5_t30s.txt'
-     output_filename = 'network_d6_knE5'
-     title = "Global density $=$ 6 \hspace{0.5cm} $k=1.2$~E5   "
+     input_filename = 'config_d6_kn0_t30s.txt'
+     output_filename = 'network_d6_kn0'
+     title = "Global density $=$ 6 \hspace{0.5cm} $k_n = 0$"
      time = 30
      sum_rads = 0.46
      ######################################

### 2020-02-07 paper.tex
mejoramos el resumen

@@
 
-The Social Force Model (SFM) is a suitable model for describing crowds behaviors.
-In this research, we analyze the role of the body force in the original SFM. 
-We focus on the parameter associated with the body stiffness ($k_n$) and its impact on the pedestrian dynamics in two different geometries: bottleneck and corridor.
-Increasing $k_n$ produces opposite effects depending on the geometry analyzed.
-Pedestrians move faster in a bottleneck, but they move slower in corridors as $k_n$ increases.
-The improvement in the bottleneck geometry is because increasing the stiffness reduces the contacts among pedestrians.
-This effect reduces the number of blocking clusters close to the exit door (which is critical to improving the evacuation).
-The slow down in the corridor geometry occurs because when $k_n$ increases, the crowd behaves like a solid-granular-system in which the friction interaction with the wall determines the velocity of the whole crowd.
-We have also explored the dimensionless parameters that arise from the reduced-in-units equation of motion and tune them to reproduce the qualitative behavior of the empirical fundamental diagram.
+The Social Force Model (SFM) is a suitable model for describing crowd behaviors.
+This research analyzes the role of the body force in the original SFM. 
+We focused on the parameter associated to the body stiffness ($k_n$) and its impact on
+the pedestrian dynamics for two different geometries: bottlenecks and corridors.
+Increasing $k_n$ produces opposite effects on either geometry: an increase of the 
+crowd velocity for bottlenecks, and a decrease for corridors. 
+The former reflects the fact that stiffness reduces the overlaps and the sliding friction
+among pedestrians. This reduces the number of blocking cluster close
+to the exit door.  The corridor, instead, tights the pedestrians into a lattice-like configuration
+due to space limitations. The friction interaction with the walls determine the velocity
+of the whole crowd along the corridor. 
+Additionally, the corridor geometry experiences a flux slowing down for very crowded environments,
+as observed in many real-life situations.
+We also explored the dimensionless parameters that arise from the reduced-in-units equation 
+of motion and tuned them to reproduce the qualitative behavior of the empirical fundamental diagram.
 
@@
 
-The presence of the FIF phenomenon for only ``soft'' individuals opens many questions 
+The existence of the FIF phenomenon for only ``stiff'' individuals opens many questions 
 on the microscopic dynamics of pedestrians. We may presume that contacts 

### 2020-02-07 paper.tex
pequeñas correcciones en resumen

@@
 This research analyzes the role of the body force in the original SFM.
-We focused on the parameter associated to the body stiffness ($k_n$) and its impact on
-the pedestrian dynamics for two different geometries: bottlenecks and corridors.
-Increasing $k_n$ produces opposite effects on either geometry: an increase of the 
-crowd velocity for bottlenecks, and a decrease for corridors. 
-The former reflects the fact that stiffness reduces the overlaps and the sliding friction
-among pedestrians. This reduces the number of blocking cluster close
-to the exit door.  The corridor, instead, tights the pedestrians into a lattice-like configuration
-due to space limitations. The friction interaction with the walls determine the velocity
-of the whole crowd along the corridor. 
-Additionally, the corridor geometry experiences a flux slowing down for very crowded environments,
-as observed in many real-life situations.
-We also explored the dimensionless parameters that arise from the reduced-in-units equation 
-of motion and tuned them to reproduce the qualitative behavior of the empirical fundamental diagram.
+We focused on the parameter associated with the body stiffness ($k_n$) and its impact on the pedestrian
+dynamics for two different geometries: bottlenecks and corridors.
+Increasing $k_n$ produces opposite effects on either geometry: an increase of the crowd velocity 
+for bottlenecks, and a decrease for corridors. 
+The former reflects the fact that the stiffness reduces
+the overlaps and the sliding friction among pedestrians. 
+This phenomenon reduces the number of blocking clusters close to the exit door. 
+The corridor, instead, tights the pedestrians into a lattice-like configuration due to space limitations.
+The friction interaction with the walls determines the velocity of the whole crowd along the corridor.
+Additionally, the corridor geometry experiences a flux slowing down for very
+crowded environments, as observed in many real-life situations.
+We also explored the dimensionless parameters that arose from the reduced-in-units
+equation of motion and tuned them to reproduce the qualitative behavior of the empirical fundamental diagram.
 

### 2020-02-07 paper.tex
saque la oracion de 6 triangulos por nodo

@@
 Fig.~\ref{triangles}, the ``stiff'' pedestrians share more triangles 
-than the ``soft'' ones.\textcolor{red}{ The maximum number of allowed triangles is 6, 
-corresponding to a hexagonal arrangement.}    \\
+than the ``soft'' ones.   \\
 

### 2020-02-12 paper.tex
correcciones de dorso en abstract

@@
 
-The Social Force Model (SFM) is a suitable model for describing crowd behaviors.
+The Social Force Model (SFM) is a suitable model for describing crowd behaviors
+\textcolor{blue}{under emotional stress}.
 This research analyzes the role of the body force in the original SFM.
@@
 dynamics for two different geometries: bottlenecks and corridors.
-Increasing $k_n$ produces opposite effects on either geometry: an increase of the crowd velocity 
+Increasing $k_n$ produces opposite effects on \textcolor{blue}{crowd dynamics for each geometry}: an increase of the crowd velocity 
 for bottlenecks, and a decrease for corridors. 
-The former reflects the fact that the stiffness reduces
-the overlaps and the sliding friction among pedestrians. 
+The former reflects the fact that \textcolor{blue}{an increase in the stiffness reduces
+the overlap between pedestrians and, as a consequence, the sliding friction is reduced.} 
 This phenomenon reduces the number of blocking clusters close to the exit door. 
-The corridor, instead, tights the pedestrians into a lattice-like configuration due to space limitations.
+\textcolor{blue}{In the case of the corridor, instead, due to the confining walls,
+the pedestrians get tight }
+ into a lattice-like configuration due to space limitations.
 The friction interaction with the walls determines the velocity of the whole crowd along the corridor.
-Additionally, the corridor geometry experiences a flux slowing down for very
+Additionally, the corridor geometry \textcolor{blue}{generates} a flux slowing down for very
 crowded environments, as observed in many real-life situations.

### 2020-02-12 paper.tex
correcciones de dorso en la parte de intro (las primeras)

@@
 Researchers, however, question the numerical setting for this force in 
-the SFM context \cite{lakoba_2005}. As a matter of fact, the usual setting by 
+the SFM context \cite{lakoba_2005}. As a matter of fact, the usual 
+\textcolor{blue}{\sout{setting by} set of parameters provided by }
 Helbing prevents the excessive overlapping among pedestrians, but it is known to 
@@
 life data (say, an order of magnitude). The crowd motion simulations, however, 
-present quite realistic results \cite{lakoba_2005,langston_2006,dorso_2017}. 
+present \textcolor{blue}{\sout{quite}} realistic results \cite{lakoba_2005,langston_2006,dorso_2017}. 
 The 
@@
 
-Many researchers realized that modifying the SFM may (partially) surpass the 
-misleading parameter setting. It was proposed that the pedestrians' 
+Many researchers realized that modifying the SFM may (partially)
+\textcolor{blue}{\sout{ surpass the misleading parameter setting}
+fix the misleading results}. It was proposed that the pedestrians' 
 psychological force (say, the ``social force'') should be suppressed in the 
@@
 
-A unique (and universal) setting appears not available yet to
-our knowledge. 
- The reason is that different numerical settings can lead to 
+A unique (and universal) \textcolor{blue}{set of parameters} appears not
+available yet to our knowledge. 
+ The reason is that different numerical \textcolor{blue}{set of parameters} can lead to 
 the same crowd dynamics. Actually, only a small set of dimensionless 
@@
 \cite{marchetti_2014}. We may hypothesize that while the dimensionless 
-``numbers'' provide some kind of control on the 
+\textcolor{blue}{parameters} provide some kind of control on the 
 collective behavior in 
@@
 
-The numerical setting for the ``faster is slower'' effect presented by 
+The numerical \textcolor{blue}{parameters} for the ``faster is slower'' effect presented by 
 Helbing and co-workers is somewhat cumbersome 
@@
 explain the phenomenon, the researcher looses sight of the dimensionless 
-``numbers'' that truly control the crowd dynamics. The setting in 
+``numbers'' that truly control the crowd dynamics. The \textcolor{blue}{set of parameters} in 
 Ref.~\cite{helbing_2000} also misses the ``faster is faster'' effect reported 
 to occur at very high pedestrian densities \cite{dorso_2017,haghani_2019}. 
-Alternatively, the empirical fundamental diagram raises as a point of reference 
+\textcolor{blue}{Moreover}, the empirical fundamental diagram raises as a point of reference 
 for the SFM control parameters \cite{helbing_2007,dorso_2017}. \\
 
-The fundamental diagram exhibits the flux behavior for either low dense crowds 
-(with seldom contacts between pedestrians) and highly dense crowds (dominated 
-by 
-body forces and sliding friction). The latter usually experiences a flux 
+The fundamental diagram exhibits the flux behavior for either low \textcolor{blue}{density} crowds 
+(with \textcolor{blue}{rare} contacts between pedestrians) and highly dense crowds (dominated 
+by body forces and sliding friction). The latter usually experiences a flux 
 slowing 

### 2020-02-12 paper.tex
agregue las correcciones de Dorso hasta la pag 17 (las gramaticales)

@@
 (with \textcolor{blue}{rare} contacts between pedestrians) and highly dense crowds (dominated 
-by body forces and sliding friction). The latter usually experiences a flux 
-slowing 
-down, but other behaviors are also possible \cite{helbing_2007,lohner_2018}. In 
+by \textcolor{blue}{two body interactions}). \textcolor{blue}{In the second case, crowds} experience a flux 
+slowing down, but other behaviors are also possible \cite{helbing_2007,lohner_2018}. In 
 light of our previous hypothesis, we may suspect that the  modeling of the 
 ``flux slowing down'' within the context of the SFM will require the proper 
-setting of the (dimensionless) controlling parameters. We examined this working 
-hypothesis in Ref.~\cite{dorso_2019}, but limiting the parameter exploration to 
-the sliding friction, disregarding the body force. \\
-
+setting of the (dimensionless) controlling parameters. We \textcolor{blue}{have already}
+examined this working hypothesis in Ref.~\cite{dorso_2019}, but limiting the parameter exploration to 
+the sliding friction, disregarding the body force. 
 We now widen the investigation on the parameter settings to include the one 
@@
 
-The investigation is organized as follows. We first recall the available 
+The \textcolor{blue}{paper} is organized as follows. We first recall the available 
 experimental values on the body force and the sliding friction (see Section 
@@
 observed separation between pedestrians. Also, the ``contacts'' between 
-individuals address some kind of ``unwanted'' slowing down. All these 
+individuals \textcolor{blue}{produce} some kind of ``unwanted'' slowing down. All these 
 observed patterns are commonly quantified in the literature into a set of 
@@
 
-\item[(ii)] Despite the reactive attitude $\tau$, the pedestrian addresses a 
+\item[(ii)] Despite the reactive attitude $\tau$, the pedestrian \textcolor{blue}{adopts} a 
 ``free'' (undisturbed) walking speed $v_d$. This speed expresses his (her) 
@@
 
-We measured the maximum attainable forces during the spring of 2019 at the subway in Buenos Aires, 
+We measured \textcolor{blue}{\sout{the maximum attainable forces}
+contact forces} during the spring of 2019 at the subway in Buenos Aires, 
 Argentina. Our preliminary results show that pedestrians feel ``uncomfortable'' 
@@
 
-The maximum (realistic) compressions may be computed from the hook relation 
+The maximum (realistic) compressions may be computed from the \textcolor{blue}{hook's} relation 
 $F(x)=k_n(x)\,x$ and the compressibility $k_n(x)$ reported in Table~\ref{table_data}. 
@@
 
-The Social Force Model (SFM) provides the necessary framework for simulating 
+The Social Force Model (SFM) provides \textcolor{blue}{a} necessary framework for simulating 
 the collective dynamics of self-driven particles (\textit{i.e.} pedestrians). 
@@
 are different in nature. The desire force $\mathbf{f}_d$ represents the 
-acceleration (or deceleration) of the pedestrian due to his (her) own willings. 
+acceleration (or deceleration) of the pedestrian due to his (her) own \textcolor{blue}{will}. 
 The social force $\mathbf{f}_s$, instead, describes the tendency of the 
@@
 
-The pedestrians' own willing is modeled by the desire force $\mathbf{f}_d$. 
-This force stands for the acceleration (deceleration) required to reach a 
-certain position at the desired walking speed $v_d$. This involves, however, a 
+The pedestrians' own \textcolor{blue}{will} is modeled by the desire force $\mathbf{f}_d$. 
+This force stands for the acceleration (deceleration) required to \textcolor{blue}{move}
+ at the desired walking speed $v_d$. This involves, however, a 
 personal attitude that makes him (her) appear more or less ``assertive''. As 
-mentioned in Section~\ref{experimental}, the reaction time $\tau$  attains for 
+mentioned in Section~\ref{experimental}, the reaction time $\tau$  \textcolor{blue}{reflects} for 
 this attitude. Thus, the desire force is modeled as follows
@@
 prevent the pedestrians from getting too close to each other (or to the walls) 
-in a crowded environment. If he (she) perceives that there is not enough space 
-to move, he (she) will decelerate or even move back. The model for this kind of 
+in a \textcolor{blue}{\sout{crowded} any} environment. \textcolor{blue}{\sout{If he (she) perceives that there is not enough space 
+to move, he (she) will decelerate or even move back.}} The model for this kind of 
 ``socio-psychological'' behavior is as follows
@@
 
-The granular force (say, the sliding friction plus the body force) attain to 
+The granular force (say, the sliding friction plus the body force) \textcolor{blue}{reflects} 
 the moving difficulties encountered in very crowded environments. The 
-expression for the granular force is has been borrowed from other granular 
-matter fields, as follows
+expression for the granular force has been borrowed from the granular 
+matter field, the mathematical expression reads as follows
 
@@
 vanished otherwise. $\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij}$ 
-represents the difference between the tangential velocities of the sliding 
+represents the \textcolor{blue}{relative} tangential velocities of the sliding 
 bodies (or between the individual and the walls).    \\
@@
 We stress that the expression (\ref{eqn_friction}) assumes fixed values for 
-$k_t$ and $k_n$. This may not be completely true according to 
+$k_t$ \textcolor{blue}{(and $k_n$)}. This may not be completely true according to 
 Table~\ref{table_data}. The local density (and thus, the pedestrians' 
@@
 pedestrians. Some settings, however, yield similar collective dynamics.
-We introduce unit-less magnitudes 
+We introduce \textcolor{blue}{dimensionless} magnitudes 
 and proceed straightforward as indicated in \ref{appendix1}. We realize from 
-\ref{appendix1} that only three (unit-less) parameters  are the true 
+\ref{appendix1} that only three (\textcolor{blue}{dimensionless}) parameters  are the true 
 ``control'' parameters for the collective dynamics. These are $\mathcal{A}$, 
@@
 
-The logical relations between the unit-less parameters and the ``individual'' 
+The logical relations between the \textcolor{blue}{dimensionless} parameters and the ``individual'' 
 parameters can be studied by means of the Venn diagrams exhibited in 
@@
 }\\
-\caption[width=0.47\columnwidth]{Venn diagrams for the unit-less parameters
+\caption[width=0.47\columnwidth]{Venn diagrams for the \textcolor{blue}{dimensionless} parameters
 appearing in the equation of motion (\ref{eqn_motion}) (see 
@@
 A characteristic feature of pedestrian dynamics is the formation of clusters. Clusters of pedestrians can 
-be defined as the set of individuals that for any member of the group (say, $i$) there exists at least another member belonging to the same group ($j$) in contact with the former.
-Thus, we define a ``granular cluster'' ($C_g$) following the mathematical formula given in Ref.~\cite{dorso_2005}
+be defined as the set of individuals that for any member of the group (say, $i$) there exists at least
+another member belonging to the same group ($j$) in contact with the former. 
+Thus, we define a ``granular cluster'' ($C_g$) following the mathematical formula given in Ref.~\cite{strachan1997fragment}
 
@@
 A ``blocking cluster'' is defined as the subset of clusterized particles (granular cluster) closest to the door whose first 
-and last component particles are in contact with the walls at both sides of the door. This clogging structure is responsible for 
-worsening the evacuation performance.
+and last component particles are in contact with the walls at both sides of the door ~\cite{dorso_2005}.
+This clogging structure is responsible for worsening the evacuation performance.
 
@@
 equivalent to vary simultaneously $\mathcal{A}$ and $\mathcal{K}_c$ by the same 
-amount in the (unit-less) parameter space (see Section~\ref{parameters}). We 
+amount in the (\textcolor{blue}{dimensionless}) parameter space (see Section~\ref{parameters}). We 
 may visualize this sampling procedure as moving along a straight line in the 
@@
 
-\item[(b)] We will consider the parameter setting in Ref.~\cite{helbing_2000} 
+\item[(b)] We will consider the parameter \textcolor{blue}{set of} Ref.~\cite{helbing_2000} 
 as a starting point for exploring the parameter space. The reason for this is 
 that a complete set of experimental parameters is still not available (to our 
-konwledge). We are aware, though, of the drawbacks for this choise, say, the 
+konwledge). We are aware, though, of the drawbacks \textcolor{blue}{of} this choise, say, the 
 unrealistic meanings for the length $B$ and the compressibility $k_n$ (see 
 Section~\ref{experimental}). But these are irrelevant in the context of the 
-(unit-less) parameter space and the corresponding collective dynamics (see 
+(\textcolor{blue}{dimensionless}) parameter space and the corresponding collective dynamics (see 
 Section~\ref{introduction}).
@@
 In order to keep the model as simple as possible, we will only consider 
-isothropic pedestrians, since anisothropy does not play a relevant role at high 
-densities. \\
+\textcolor{blue}{isotropic pedestrian interactions}, since \textcolor{blue}{anisotropic
+interactions} does not play a relevant role at high densities. \\
 
@@
 The implemented SFM parameters were the same as those in 
-Ref.~\cite{helbing_2000} (at the begining of the exploratory procedure only). 
+Ref.~\cite{helbing_2000} (at the beginning of the exploratory procedure only). 
 But the pedestrian's mass and radius were set to the more realistic values of 
-$70\,$kg and $0.23\,$m, respectively. The force interaccions between 
+$70\,$kg and $0.23\,$m, respectively. The force interactions between 
 pedestrians were limited, however, to a cut-off distance of $0.88\,$m for 
-attaining a \textit{privacy sphere} from first neighbors only. The desired 
+attaining a \textit{privacy sphere} \textcolor{blue}{only of the first neighbors}. The desired 
 velcity was always set to $1\,$m/s in the corridor situation. Besides, the 
@@
 re-introduced into the box, on the opposite side (periodic boundary 
-conditions). We only ommitted this mechamism when computing the evacuation time 
+conditions). We only omitted this mechanism when computing the evacuation time 
 for the bottleneck geometry. \\
@@
 desired velocity for different values of $k_n$. The evacuation 
-time is defined as the time until 80\% of the pedestrians have 
+time is defined as the time \textcolor{blue}{lapsed} until 80\% of the pedestrians have 
 left the room. In this section we will focus on the evacuation time for 
@@
 Three behavioral patterns can be distinguished in Fig.~\ref{vd_vs_te}. 
-Each pattern can accomplish a positive slope, a negative slope
+Each pattern can \textcolor{blue}{display} a positive slope, a negative slope
 or both. The interval in which the slope is positive means that the 
@@
 Despite the presence of the FIS or FIF pattern, the evacuation time at a 
-fixed value of $v_d$ decreases for increasing values of $k_n$ (whiting the examined interval). 
+fixed value of $v_d$ decreases for increasing values of $k_n$ (\textcolor{blue}{within} the examined interval). 
 This means that stiffer pedestrians evacuate faster than soft pedestrians. 
@@
 velocities. In all cases, the velocity increases with the stiffness. The most significative 
-increment of velocity is in the interval $k_n>\,$E4. \\
+increment of velocity is in the interval \textcolor{blue}{$k_n>\,10^{4}$}. \\
 
@@
 of the desired velocity. The degree of a node is defined as the number of links 
-that connect this node to any other node. This means, the number of pedestrians 
+that \textcolor{blue}{connects} this node to any other node. This means, the number of pedestrians 
 that are in physical contact with a given pedestrian. The mean degree is the 
@@
 Notice that the mean degree increases as $v_d$ increases, as expected. This expresses the fact that
-higher $v_d$ values accomplish higher densities, enforcing individuals to touch each 
-other. But surprisingly, for a given $v_d$, the mean degree reduces as the $k_n$ 
+higher $v_d$ values accomplish higher densities, \textcolor{blue}{forcing} individuals to touch each 
+other. For a given $v_d$, the mean degree reduces as the $k_n$ 
 value increases. A noticeable decrease in the mean degree can be seen for the 
-highest explored value of $k_n$. This was not expected and opens the question on how would
+highest explored value of $k_n$. This \textcolor{blue}{was not expected and} opens the question on how would
 this affect the sliding friction among pedestrians.\\
@@
 other are the ones who are being re-injected on the opposite side of the room.
-This collides against the bulk, providing some kind of overlap during very short time. We will
+\textcolor{blue}{These collide with the bulk}, providing some kind of overlap during very short time. We will
 not analize this regime.\\
@@
 
-The four snapshots in Fig.~\ref{network_bottleneck} confirm (visually) the fact that more rigid pedestrians release the crowded environment, widening the occupied region.
+The four snapshots in Fig.~\ref{network_bottleneck} confirm (visually) the fact that more rigid pedestrians \textcolor{blue}{ease} the crowded environment, widening the occupied region.
 At $v_d=10\,$m/s (the maximum explored velocity), it can hardly be found pedestrians with degree 6 when $k_n=1.2\,$E6, while a lot of them are present for $k_n$=0.\\
@@
 We explored the parameter space along $v_d$ and $k_n$ for the bottleneck situation.
-This is similar to explore the unitless plane $(\mathcal{A},\mathcal{K}_c)$.
+This is similar to explore the \textcolor{blue}{dimensionless} plane $(\mathcal{A},\mathcal{K}_c)$.
 Soft pedestrians attain a FIS or FIS+FIF evacuation pattern but, stiff pedestrians (for any fixed $\mathcal{A}$ value within the explored range) exhibit a single FIF pattern.
@@
 smaller set of parameters. In order to identify this smaller set, we introduce 
-the following unit-less magnitudes\\
+the following \textcolor{blue}{dimensionless} magnitudes\\
 
@@
 The equation of motion (\ref{eqn_motion}) can be written in terms of these 
-(unit-less) magnitudes, while only three (reduced) parameters are needed.\\
+(\textcolor{blue}{dimensionless}) magnitudes, while only three (reduced) parameters are needed.\\
 

### 2020-02-12 paper.tex
agregue unas correcciones de Dorso mas complicadas (se pueden modificar)

@@
 observed patterns are commonly quantified in the literature into a set of 
-characteristic  parameters. The experimental meaning of these parameters is as 
-follows.
+characteristic  parameters. \textcolor{blue}{It is worth mentioning that the empirical
+data reported in this Section corresponds to non-panicking situations in which pedestrians 
+do not experience anxiety. }
+The experimental meaning of these parameters is as follows.
 
@@
 \cite{helbing_1995,helbing_2000,li_2015}. 
+\textcolor{blue}{Nevertheless, when pedestrians are in a panic situation,
+ the actual speed tends to be lower than the desired velocity $v_d$. }
 
@@
 
-The maximum (realistic) compressions may be computed from the \textcolor{blue}{hook's} relation 
+The maximum (realistic) compressions may be computed from the \textcolor{blue}{Hook's} relation 
 $F(x)=k_n(x)\,x$ and the compressibility $k_n(x)$ reported in Table~\ref{table_data}. 
@@
 
-The equation of motion (\ref{eqn_motion}) can be written in terms of these 
+The equation of motion (\ref{eqn_motion}) can be \textcolor{blue}{rewritten} in terms of these 
 (\textcolor{blue}{dimensionless}) magnitudes, while only three (reduced) parameters are needed.\\

### 2020-02-12 paper.tex
agregue mas texto para las corrcciones de Dorso

@@
 a step distance of $1.3\,$m for the pedestrians to feel that there is enough 
-space to move along.     \\
+space to move along.\\
 
@@
 range of $0.030-0.055\,$m. Also, a ``hitting'' force of $60\,$N can address 
-compressions between $0.045$ and $0.065\,$m. \\
+compressions between $0.045$ and $0.065\,$m. \textcolor{blue}{
+Besides, no reliable values for the sliding friction $k_t$ appears to be 
+available in the literature (to our knowledge).}\\
 %Thus, according to Table~\ref{table_data}, \textcolor{blue}{we may expect experimental values for $k_n(x)$ up to 
@@
 
-Besides, no reliable values for the sliding friction $k_t$ appears to be 
+\textcolor{blue}{\sout{Besides, no reliable values for the sliding friction $k_t$ appears to be 
 available in the literature (to our knowledge). We may presume, however, that 
 the sliding friction approaches a fraction of the body force. We will come back 
-to this issue in Section~\ref{background}. \\
+to this issue in Section~\ref{background}.}} \\
 

### 2020-02-13 paper.tex
puse en rojo las correcciones que no estoy muy seguro

@@
 The numerical \textcolor{blue}{parameters} for the ``faster is slower'' effect presented by 
-Helbing and co-workers is somewhat cumbersome 
+Helbing and co-workers \textcolor{red}{\sout{is somewhat cumbersome} has some drawbacks} 
 Ref.~\cite{helbing_2000,dorso_2017,dorso_2019}. Although a single 
 parameter (say, the desired velocity $v_d$) is numerically varied to 
-explain the phenomenon, the researcher looses sight of the dimensionless 
+explain the phenomenon, the researcher \textcolor{red}{\sout{looses sight} may loose sight} of the dimensionless 
 ``numbers'' that truly control the crowd dynamics. The \textcolor{blue}{set of parameters} in 
@@
 by \textcolor{blue}{two body interactions}). \textcolor{blue}{In the second case, crowds} experience a flux 
-slowing down, but other behaviors are also possible \cite{helbing_2007,lohner_2018}. In 
-light of our previous hypothesis, we may suspect that the  modeling of the 
+slowing down, but other behaviors are also possible \cite{helbing_2007,lohner_2018}. \textcolor{red}{
+\sout{In light of our previous hypothesis, we } We} may suspect that the  modeling of the 
 ``flux slowing down'' within the context of the SFM will require the proper 
@@
 the environmental conditions. The former is expressed, for example, by his 
-(her) moving ``attitude'' (say, self-assuredness). The latter brings out the 
+(her) moving ``attitude'' (say,\textcolor{red}{\sout{self-assuredness} relaxed, normal, aggressive, etc}).
+The latter brings out the 
 observed separation between pedestrians. Also, the ``contacts'' between 
@@
 observed patterns are commonly quantified in the literature into a set of 
-characteristic  parameters. \textcolor{blue}{It is worth mentioning that the empirical
+characteristic  parameters. \textcolor{red}{It is worth mentioning that the empirical
 data reported in this Section corresponds to non-panicking situations in which pedestrians 
@@
 \cite{helbing_1995,helbing_2000,li_2015}. 
-\textcolor{blue}{Nevertheless, when pedestrians are in a panic situation,
+\textcolor{red}{Nevertheless, when pedestrians are in a panic situation,
  the actual speed tends to be lower than the desired velocity $v_d$. }
@@
 
-We measured \textcolor{blue}{\sout{the maximum attainable forces}
+We measured \textcolor{red}{\sout{the maximum attainable forces}
 contact forces} during the spring of 2019 at the subway in Buenos Aires, 
@@
 range of $0.030-0.055\,$m. Also, a ``hitting'' force of $60\,$N can address 
-compressions between $0.045$ and $0.065\,$m. \textcolor{blue}{
+compressions between $0.045$ and $0.065\,$m. \textcolor{red}{
 Besides, no reliable values for the sliding friction $k_t$ appears to be 
@@
 
-\textcolor{blue}{\sout{Besides, no reliable values for the sliding friction $k_t$ appears to be 
+\textcolor{red}{\sout{Besides, no reliable values for the sliding friction $k_t$ appears to be 
 available in the literature (to our knowledge). We may presume, however, that 

### 2020-02-13 paper.tex
saque la palabra setting de la mayor cantidad de lugares posible

@@
 collective behavior in 
-crowds, only a few numerical settings can attain an ``individualistic'' 
+crowds, only a few numerical \textcolor{blue}{\sout{settings} set of parameters} can attain an ``individualistic'' 
 meaning. 
@@
 the sliding friction, disregarding the body force. 
-We now widen the investigation on the parameter settings to include the one 
+We now widen the investigation on the \textcolor{blue}{\sout{parameter settings} set of parameters} to include the one 
 associated to the body force. We will  explore 
@@
 the body force and the sliding friction among pedestrians. Recall that the 
-interplay dynamics is not directly controlled by the numerical setting, but 
+interplay dynamics is not directly controlled by the \textcolor{blue}{\sout{numerical setting} set of parameters}, but 
 through dimensionless ``numbers'', where the model parameters appear mixed 
 between each other. Thus, this step up offers a challenge to the 
-``individualistic'' meaning of the parameter's setting. \\
+``individualistic'' meaning of the parameter's \textcolor{blue}{\sout{setting} set}. \\
 
@@
 
-\subsection{\label{parameters}The parameters setting}
-
-The numerical setting of the parameters may affect the dynamics of the 
-pedestrians. Some settings, however, yield similar collective dynamics.
+\subsection{\label{parameters} \textcolor{blue}{\sout{The parameters setting} The set of parameters}}
+
+The numerical \textcolor{blue}{\sout{setting} set} of the parameters may affect the dynamics of the 
+pedestrians. Some \textcolor{blue}{\sout{settings} sets}, however, yield similar collective dynamics.
 We introduce \textcolor{blue}{dimensionless} magnitudes 
@@
 $v_d$ or $B$ appears somehow ``loosely'' in the crowd dynamic. We mean by 
-``loosely'' that any numerical setting of these parameters may be 
-counterbalanced by the right setting of $A$ or $k_t$, keeping the 
+``loosely'' that any numerical \textcolor{blue}{\sout{setting} set} of these parameters may be 
+counterbalanced by the right \textcolor{blue}{\sout{setting} choise } of $A$ or $k_t$, keeping the 
 colletive dynamic (qualitatively) unchanged.  \\

### 2020-02-14 paper.tex
tache texto que no va
correcciones de guille sobre las correcciones de dorso

@@
 dynamics for two different geometries: bottlenecks and corridors.
-Increasing $k_n$ produces opposite effects on \textcolor{blue}{crowd dynamics for each geometry}: an increase of the crowd velocity 
+Increasing $k_n$ produces opposite effects on \textcolor{blue}{the crowd dynamics for each geometry}: an increase of the crowd velocity 
 for bottlenecks, and a decrease for corridors. 
@@
 The numerical \textcolor{blue}{parameters} for the ``faster is slower'' effect presented by 
-Helbing and co-workers \textcolor{red}{\sout{is somewhat cumbersome} has some drawbacks} 
+Helbing and co-workers \textcolor{red}{\sout{is somewhat cumbersome} appears to have some drawbacks} 
 Ref.~\cite{helbing_2000,dorso_2017,dorso_2019}. Although a single 
@@
 data reported in this Section corresponds to non-panicking situations in which pedestrians 
-do not experience anxiety. }
+do not experience high anxiety levels (see below). }
 The experimental meaning of these parameters is as follows.
@@
 \begin{itemize}
-\item[(i)] The walking attitude of a pedestrian may appear somewhat 
+\item[(i)] \textcolor{red}{\textbf{The walking attitude of a pedestrian may appear somewhat 
   ``aggressive'' if he (she) reacts actively to unexpected behaviors 
@@
 behavior is the relaxation or characteristic time $\tau$ 
-\cite{johansson_2009,helbing_2000}.
+\cite{johansson_2009,helbing_2000}}}.
 
@@
 \textcolor{red}{Nevertheless, when pedestrians are in a panic situation,
- the actual speed tends to be lower than the desired velocity $v_d$. }
+ they may not reach the ``free'' walking speed, but, $v_d$ may still be 
+ associated to his (her) motivation to get to a target position.  }
 
@@
 values for the compressibility $k_n$ since these experiments were carried out 
-under low density conditions.  The minimum (perceived) step distance 
+under low density \textcolor{red}{and non-panicking} conditions.  The minimum (perceived) step distance 
 is $0.36\,$m according to Ref.~\cite{seyfried_2007}, but the
@@
 distances when they walk faster. The commonly accepted value $B\simeq 
-0.5\,$m is somewhat valid for walking speeds under $0.5\,$m/s 
+0.5\,$m is somewhat valid for walking speeds under $0.5\,$m/s  \textcolor{red}{and non-panicking conditions}
 \cite{seyfried_2007}. Higher walking speeds (say, $1\,$m/s) will require 
@@
 
-The maximum (realistic) compressions may be computed from the \textcolor{blue}{Hook's} relation 
+The maximum (realistic) compressions may be computed from the \textcolor{blue}{Hooke's} relation 
 $F(x)=k_n(x)\,x$ and the compressibility $k_n(x)$ reported in Table~\ref{table_data}. 
@@
 pedestrians to stay away from each other. The granular force $\mathbf{f}_g$ 
-stands for either the sliding friction and the compression between 
+stands for \textcolor{red}{both} the sliding friction and the compression between 
 pedestrians. \\
@@
 is expected to be also present in the SFM. These will appear in connection to 
-the forces, although their meaning may be somewhat different. \\
+the forces \textcolor{red}{\sout{, although their meaning may be somewhat different}}. \\
 
@@
 length within the model, and thus, it may be somewhat connected to the 
-(perceived) step distance mentioned in Section~\ref{experimental}. The 
-parameter $A$, however, does not provide any direct link to other parameters 
-mentioned there. \\
+(perceived) step distance mentioned in Section~\ref{experimental}. 
+\textcolor{red}{Besides, the parameter $A$ reflects the intensity of the social repulsion.} \\
 
@@
 The numerical \textcolor{blue}{\sout{setting} set} of the parameters may affect the dynamics of the 
-pedestrians. Some \textcolor{blue}{\sout{settings} sets}, however, yield similar collective dynamics.
+pedestrians. Some \textcolor{blue}{\sout{settings} values}, however, yield similar collective dynamics.
 We introduce \textcolor{blue}{dimensionless} magnitudes 
@@
 $v_d$ or $B$ appears somehow ``loosely'' in the crowd dynamic. We mean by 
-``loosely'' that any numerical \textcolor{blue}{\sout{setting} set} of these parameters may be 
+``loosely'' that any numerical \textcolor{blue}{\sout{setting} set for} these parameters may be 
 counterbalanced by the right \textcolor{blue}{\sout{setting} choise } of $A$ or $k_t$, keeping the 
@@
 
-\item[(b)] We will consider the parameter \textcolor{blue}{set of} Ref.~\cite{helbing_2000} 
+\item[(b)] We will consider the parameter \textcolor{blue}{set from} Ref.~\cite{helbing_2000} 
 as a starting point for exploring the parameter space. The reason for this is 
 that a complete set of experimental parameters is still not available (to our 
-konwledge). We are aware, though, of the drawbacks \textcolor{blue}{of} this choise, say, the 
+konwledge). We are aware, though, of the drawbacks \textcolor{blue}{for} this choise, say, the 
 unrealistic meanings for the length $B$ and the compressibility $k_n$ (see 
@@
 \textcolor{blue}{isotropic pedestrian interactions}, since \textcolor{blue}{anisotropic
-interactions} does not play a relevant role at high densities. \\
+interactions do} not play a relevant role at high densities. \\
 
@@
 pedestrians were limited, however, to a cut-off distance of $0.88\,$m for 
-attaining a \textit{privacy sphere} \textcolor{blue}{only of the first neighbors}. The desired 
+attaining a \textit{privacy sphere} \textcolor{blue}{for the first neighbors only}. The desired 
 velcity was always set to $1\,$m/s in the corridor situation. Besides, the 
@@
 value increases. A noticeable decrease in the mean degree can be seen for the 
-highest explored value of $k_n$. This \textcolor{blue}{was not expected and} opens the question on how would
+highest explored value of $k_n$. This \textcolor{blue}{\sout{was not expected and}} opens the question on how would
 this affect the sliding friction among pedestrians.\\

### 2020-02-14 paper.tex
puse en azul cosas que antes estaban en rojo

@@
 The numerical \textcolor{blue}{parameters} for the ``faster is slower'' effect presented by 
-Helbing and co-workers \textcolor{red}{\sout{is somewhat cumbersome} appears to have some drawbacks} 
+Helbing and co-workers \textcolor{blue}{\sout{is somewhat cumbersome} appears to have some drawbacks} 
 Ref.~\cite{helbing_2000,dorso_2017,dorso_2019}. Although a single 
 parameter (say, the desired velocity $v_d$) is numerically varied to 
-explain the phenomenon, the researcher \textcolor{red}{\sout{looses sight} may loose sight} of the dimensionless 
+explain the phenomenon, the researcher \textcolor{blue}{\sout{looses sight} may loose sight} of the dimensionless 
 ``numbers'' that truly control the crowd dynamics. The \textcolor{blue}{set of parameters} in 
@@
 by \textcolor{blue}{two body interactions}). \textcolor{blue}{In the second case, crowds} experience a flux 
-slowing down, but other behaviors are also possible \cite{helbing_2007,lohner_2018}. \textcolor{red}{
+slowing down, but other behaviors are also possible \cite{helbing_2007,lohner_2018}. \textcolor{blue}{
 \sout{In light of our previous hypothesis, we } We} may suspect that the  modeling of the 
@@
 the environmental conditions. The former is expressed, for example, by his 
-(her) moving ``attitude'' (say,\textcolor{red}{\sout{self-assuredness} relaxed, normal, aggressive, etc}).
+(her) moving ``attitude'' (say,\textcolor{blue}{\sout{self-assuredness} relaxed, normal, aggressive, etc}).
 The latter brings out the 
@@
 \begin{itemize}
-\item[(i)] \textcolor{red}{\textbf{The walking attitude of a pedestrian may appear somewhat 
+\item[(i)] The walking attitude of a pedestrian may appear somewhat 
   ``aggressive'' if he (she) reacts actively to unexpected behaviors 
@@
 behavior is the relaxation or characteristic time $\tau$ 
-\cite{johansson_2009,helbing_2000}}}.
+\cite{johansson_2009,helbing_2000}.
 
@@
 pedestrians to stay away from each other. The granular force $\mathbf{f}_g$ 
-stands for \textcolor{red}{both} the sliding friction and the compression between 
+stands for \textcolor{blue}{both} the sliding friction and the compression between 
 pedestrians. \\

### 2020-02-23 paper.tex
primeras correcciones de Dorso de la segunda mitad

@@
 We present in this section the results corresponding to the corridor geometry. 
-We show the effects of modifying the body force coefficient $k_n$ on the 
+We show the effects of \textcolor{blue}{\sout{modifying} varying} the body force coefficient $k_n$ on the 
 collective dynamics. We will keep $v_d$ (or $\mathcal{A}$) 
@@
 We find these topological magnitudes useful for comparing the 
+\textcolor{blue}{pedestrian behavior in the} 
 corridor geometry with respect to the bottleneck geometry. A re-examination of 
@@
 applied on both situations. We may speculate that this phenomenon occurs 
-because, in the corridor, the lateral walls act like a containment barrier that 
+because, in the corridor, the lateral walls act like a \textcolor{blue}{\sout{containment}
+confining} barrier that 
 forces the ``stiff'' pedestrian to increase his (her) contacts. On the contrary, 
@@
 Fig.~\ref{overlap_dens} shows this magnitude for the corridor situation. Notice 
-that ``soft'' pedestrians attain a more intruding overlap than the ``stiff'' 
+that ``soft'' pedestrians attain \textcolor{blue}{\sout{a more intruding} more } overlap than the ``stiff'' 
 ones, as expected. This is in agreement with Fig.~\ref{overlap_vd} for the 

### 2020-02-23 paper.tex
agregue mas correcciones de Dorso de la 2a parte

@@
 
-The above results correspond to a milestone in the 
-investigation. The connectivity differences between the bottleneck geometry 
-and the corridor geometry were not expected and opens two major questions: how 
-does the body stiffness interact with the walls, and consequently, how does 
+The above results correspond to \textcolor{blue}{\sout{a milestone} an important step} in the 
+investigation. The \textcolor{blue}{inter-pedestrian} connectivity differences between the bottleneck geometry 
+and the corridor geometry were not expected and opens two major questions:
+\textcolor{blue}{\sout{ how 
+does the body stiffness interact with the walls} do the pedestrians interact with the walls as
+a function of the body stiffness}, and consequently, how does 
 this affect the flux across the corridor.\\
@@
 were computed at densities $\rho\geq 5.5$. According to 
-Fig.~\ref{overlap_dens}, these densities attain relevant overlaps. Furthermore, 
+Fig.~\ref{overlap_dens},\textcolor{blue}{\sout{ these densities attain relevant overlaps}
+at these densities, the overlaps among pedestrians attain significant values}. Furthermore, 
 stiffness values $k_n\geq 10^4$ move the system to a more heavily connected 
@@
 the transversal coordinate $y$) for different $k_n$ values.
-For $k_n=0$, we can see a parabolic-like velocity profile that resembles the Poiseuille flow (similar to Newtonian and incompressible fluids in a laminar regime).
+For $k_n=0$, we can see a parabolic-like velocity profile \textcolor{red}{which means that the friction with the walls reduces the speed of pedestrians.} \textcolor{blue}{\sout{that} The velocity profile} resembles the Poiseuille flow (similar to Newtonian and incompressible fluids in a laminar regime).
 This behavior was also observed in empirical measurements of crowd dynamics reported in Ref.~\cite{zhang2013empirical}.
 But as $k_n$ increases the velocity profile flattens until becoming (almost) uniform (see Fig.~\ref{vx_profile} for $k_n=1.2\,$E6).
-In this scenario, $v_x$ attains a much lower level than in the case of soft pedestrians ($k_n=$0).\\
+In this scenario, $v_x$ attains a much lower \textcolor{blue}{\sout{level} value}  than in the case of soft pedestrians ($k_n=$0).\\
 
@@
 This means that the crowd can not be easily ``deformed''.
-In this context, deformation means that parts of the crowd may be released to move faster than other parts of the crowd.
+In this context, deformation means that parts of the crowd may be \textcolor{blue}{\sout{released} allowed} to move faster than other parts of the crowd.
 \\
 
-The strain rate is the tensor that expresses how the relative velocity of a medium changes when one moves away from one position to another.
-We consider the following discrete definition of the strain rate:
+\textcolor{blue}{\sout{The strain rate is the tensor that expresses how the relative velocity of a medium changes when one moves away from one position to another.} The strain rate tensor displays the rate of change of the deformation of a body in the vincinity of a given point.} We consider the following discrete definition of the strain rate:
 
 \begin{equation}
-S = \frac{\langle v_x(\mathrm{center})\rangle - \langle v_x(\mathrm{boundary})\rangle }{\left | y(\mathrm{center}) - y(\mathrm{boundary}) \right |} 
+\dot{\gamma} = \frac{\langle v_x(\mathrm{center})\rangle - \langle v_x(\mathrm{boundary})\rangle }{\left | y(\mathrm{center}) - y(\mathrm{boundary}) \right |} 
 \end{equation}
@@
 This definition compares the velocity of the pedestrians close to the wall (boundary) with respect to the velocity of the pedestrians at the center of the corridor (center).
-Thus, $S$ vanishes (no deformation) as the stiffness level increases.
+Thus, $\dot{\gamma}$ vanishes (no deformation) as the stiffness level increases.
 This phenomenon is shown in Fig.~\ref{strain_rate_vs_kn} where we can see that the strain rate drops for high values of $k_n$.
@@
 
-We conclude this Section by stressing that stiffer pedestrians attain opposite results in corridors with respect to bottlenecks.
+We conclude this Section by stressing\textcolor{blue}{, once again,} that stiffer pedestrians attain opposite results in corridors with respect to bottlenecks.
 The walls in the corridors play a critical role that prevents pedestrians from detaching from each other.
@@
 
-We explored the effect on the pedestrians dynamics of the (sometimes neglected) body force in the framework of the SFM.
+\textcolor{blue}{Having adopted as fundamental philosophy of work that the parameters of the SFM should be properly determined by requiring that the model properly reproduces well established experimental data, we} explored the effect on the pedestrians dynamics of the (sometimes neglected) body force in the framework of the SFM.
 We showed that the stiffness coefficient ($k_n$) has a significant impact on the evacuation dynamics (bottleneck) and also in the dynamics of pedestrians walking along a straight corridor.\\
@@
 The whole crowd can be compared to a granular material.
-Granular materials can be disordered (amorphous) or ordered depending on how particles link to each other.
+Granular materials can be disordered (amorphous) or ordered depending on how particles \textcolor{blue}{\sout{link} interact}  to each other.
 In the present context, at low stiffness levels, the crowd appears disordered attaining a parabolic velocity profile.
@@
 
-Our efforts to ``tune'' the original SFM to empirical data (say, the fundamental diagram) moved us to explore the dimensionless parameter space.
-We found that the qualitative behavior of empirical  data can be accomplished if the parameters are close to $\mathcal{K}_c < 68$, $\mathcal{K} = 685$ and $\mathcal{A}=14$.
+Our efforts to ``tune'' the original SFM to \textcolor{blue}{reproduce} empirical data (say, the fundamental diagram) moved us to explore the dimensionless parameter space.
+We found that \textcolor{blue}{\sout{the qualitative behavior of empirical  data can be accomplished} we can qualitatively reproduce the empirical data} if the parameters are close to $\mathcal{K}_c < 68$, $\mathcal{K} = 685$ and $\mathcal{A}=14$.
 Nevertheless, this is a first attempt to arrive at suitable parameters, although we do not claim these to be optimal.

### 2020-02-23 plots/corridor/strain_rate/plot_strain_rate.py
modifique el eje y del grafico de strain rate

@@ -77,7 +77,7 @@ def plot_strainrate_vs_k(plot_name,list_k,strain_rate,error_strain_rate,d,symbol
      plt.plot(list_k,strain_rate,symbol,color=color,mec='k',mew=0.8,linewidth = '1',markersize=5,label='$\\rho=${}'.format(d))     
      pylab.grid(False)
      pylab.xlabel('$k_n$')
-     pylab.ylabel('Strain rate~(1/s)')
+     pylab.ylabel('$\\dot{\\gamma}$~(1/s)')
      plt.xscale('symlog')
      #plt.title("Global density = 7")
      #plt.ylim(-0.25,6.2)

### 2020-02-23 paper.tex
mas correcciones de Dorso

@@
 each other. The mean degree increases for ``stiff'' pedestrians moving along 
-the corridor (at densities above $5\,$p/m$^2$). Conversely, the mean degree 
+the corridor \textcolor{blue}{\sout{(at densities above} 
+as the density increased with a sharp increase at} $5\,$p/m$^2$\textcolor{blue}{\sout{)}}. Conversely, the mean degree 
 increases for ``soft'' pedestrians in the bottleneck situation.\\
@@
 \textcolor{blue}{\sout{ how 
-does the body stiffness interact with the walls} do the pedestrians interact with the walls as
+does the body stiffness interact with the walls} how do the pedestrians interact with the walls as
 a function of the body stiffness}, and consequently, how does 
@@
 
-The crowd behaves like a solid for very stiff pedestrians.
+\textcolor{blue}{From the results displayed above, we realize that \sout{The} the} crowd behaves like a solid for very stiff pedestrians.
 This means that the crowd can not be easily ``deformed''.
@@
 Our efforts to ``tune'' the original SFM to \textcolor{blue}{reproduce} empirical data (say, the fundamental diagram) moved us to explore the dimensionless parameter space.
-We found that \textcolor{blue}{\sout{the qualitative behavior of empirical  data can be accomplished} we can qualitatively reproduce the empirical data} if the parameters are close to $\mathcal{K}_c < 68$, $\mathcal{K} = 685$ and $\mathcal{A}=14$.
+We found that \textcolor{blue}{\sout{the qualitative behavior of empirical  data can be accomplished} we can qualitatively reproduce the empirical data} if the parameters are close to $\mathcal{•}hcal{K}_c < 68$, $\mathcal{K} = 685$ and $\mathcal{A}=14$.
 Nevertheless, this is a first attempt to arrive at suitable parameters, although we do not claim these to be optimal.

### 2020-02-27 paper.tex
ultimas correcciones de Dorso de la segunda parte + correccion de the + correccion de mathcal

@@
 Fig.~\ref{overlap_vd}, however, do not meet each other as in  
-Fig.~\ref{overlap_dens}. The curve meeting attains for space limitations in 
+Fig.~\ref{overlap_dens}. \textcolor{red}{\sout{The curve meeting attains for space limitations in 
 the corridor, since overlapping occurs (almost) independently of the value of
-$k_n$. This is clearly not the case in the bottleneck situation. \\
+$k_n$. This is clearly not the case in the bottleneck situation.} 
+All the curves meet each other at high-density values. This phenomenon occurs
+due to space limitations in the corridor that produces overlapping (almost) independently of the
+value of k n}. \\
 
@@
 (almost) the same speed as his (her) neighbors. This 
-behavior may be envisaged as the passage from a released 
-walking movement to a tigh movement as the stiffness increases. A more 
+behavior may be envisaged as the passage from a \textcolor{red}{\sout{released} ``free''} 
+walking movement to a \textcolor{red}{\sout{tigh} constrained} movement as the stiffness increases. A more 
 physical picture would assimilate te former as a ``fluid-like 
@@
 
-IThe final stage of our investigation deals with the plausible values of the dimensionless numbers $\mathcal{K}_c$ and $\mathcal{K}$, in comparison to the empirical measurements.
+The final stage of our investigation deals with the plausible values of the dimensionless numbers $\mathcal{K}_c$ and $\mathcal{K}$, in comparison to the empirical measurements.
 We vary the body force coefficient ($k_n$) and the friction coefficient ($k_t$) to explore different values of $\mathcal{K}_c$ and $\mathcal{K}$, respectively.\\
@@
 Our efforts to ``tune'' the original SFM to \textcolor{blue}{reproduce} empirical data (say, the fundamental diagram) moved us to explore the dimensionless parameter space.
-We found that \textcolor{blue}{\sout{the qualitative behavior of empirical  data can be accomplished} we can qualitatively reproduce the empirical data} if the parameters are close to $\mathcal{•}hcal{K}_c < 68$, $\mathcal{K} = 685$ and $\mathcal{A}=14$.
+We found that \textcolor{blue}{\sout{the qualitative behavior of empirical  data can be accomplished} we can qualitatively reproduce the empirical data} if the parameters are close to $\mathcal{K}_c < 68$, $\mathcal{K} = 685$ and $\mathcal{A}=14$.
 Nevertheless, this is a first attempt to arrive at suitable parameters, although we do not claim these to be optimal.

### 2020-02-27 paper.tex
correcciones menores de ortografia

@@
 ``loosely'' that any numerical \textcolor{blue}{\sout{setting} set for} these parameters may be 
-counterbalanced by the right \textcolor{blue}{\sout{setting} choise } of $A$ or $k_t$, keeping the 
+counterbalanced by the right \textcolor{blue}{\sout{setting} choice } of $A$ or $k_t$, keeping the 
 colletive dynamic (qualitatively) unchanged.  \\
@@
 that a complete set of experimental parameters is still not available (to our 
-konwledge). We are aware, though, of the drawbacks \textcolor{blue}{for} this choise, say, the 
+konwledge). We are aware, though, of the drawbacks \textcolor{blue}{of} this choice, say, the 
 unrealistic meanings for the length $B$ and the compressibility $k_n$ (see 
@@
 pedestrians were limited, however, to a cut-off distance of $0.88\,$m for 
-attaining a \textit{privacy sphere} \textcolor{blue}{for the first neighbors only}. The desired 
+attaining a \textit{privacy sphere} \textcolor{blue}{that excludes second neighbors}. The desired 
 velcity was always set to $1\,$m/s in the corridor situation. Besides, the 
@@
 due to space limitations in the corridor that produces overlapping (almost) independently of the
-value of k n}. \\
+value of $k_n$}. \\
 
@@
 
-The above results correspond to \textcolor{blue}{\sout{a milestone} an important step} in the 
+The above results \textcolor{blue}{\sout{correspond to a milestone} represent an important step} in the 
 investigation. The \textcolor{blue}{inter-pedestrian} connectivity differences between the bottleneck geometry 

### 2020-03-03 paper.tex
agregue el agradecimiento a la UTN
quite texto en azul y rojo de la intro

@@
 The Social Force Model (SFM) is a suitable model for describing crowd behaviors
-\textcolor{blue}{under emotional stress}.
+under emotional stress.
 This research analyzes the role of the body force in the original SFM.
@@
 dynamics for two different geometries: bottlenecks and corridors.
-Increasing $k_n$ produces opposite effects on \textcolor{blue}{the crowd dynamics for each geometry}: an increase of the crowd velocity 
+Increasing $k_n$ produces opposite effects on the crowd dynamics for each geometry: an increase of the crowd velocity 
 for bottlenecks, and a decrease for corridors. 
-The former reflects the fact that \textcolor{blue}{an increase in the stiffness reduces
-the overlap between pedestrians and, as a consequence, the sliding friction is reduced.} 
+The former reflects the fact that an increase in the stiffness reduces
+the overlap between pedestrians and, as a consequence, the sliding friction is reduced. 
 This phenomenon reduces the number of blocking clusters close to the exit door. 
-\textcolor{blue}{In the case of the corridor, instead, due to the confining walls,
-the pedestrians get tight }
+In the case of the corridor, instead, due to the confining walls,
+the pedestrians get tight
  into a lattice-like configuration due to space limitations.
 The friction interaction with the walls determines the velocity of the whole crowd along the corridor.
-Additionally, the corridor geometry \textcolor{blue}{generates} a flux slowing down for very
+Additionally, the corridor geometry generates a flux slowing down for very
 crowded environments, as observed in many real-life situations.
@@
 the SFM context \cite{lakoba_2005}. As a matter of fact, the usual 
-\textcolor{blue}{\sout{setting by} set of parameters provided by }
+ set of parameters provided by 
 Helbing prevents the excessive overlapping among pedestrians, but it is known to 
@@
 life data (say, an order of magnitude). The crowd motion simulations, however, 
-present \textcolor{blue}{\sout{quite}} realistic results \cite{lakoba_2005,langston_2006,dorso_2017}. 
+present realistic results \cite{lakoba_2005,langston_2006,dorso_2017}. 
 The 
@@
 Many researchers realized that modifying the SFM may (partially)
-\textcolor{blue}{\sout{ surpass the misleading parameter setting}
-fix the misleading results}. It was proposed that the pedestrians' 
+fix the misleading results. It was proposed that the pedestrians' 
 psychological force (say, the ``social force'') should be suppressed in the 
@@
 
-A unique (and universal) \textcolor{blue}{set of parameters} appears not
+A unique (and universal) set of parameters appears not
 available yet to our knowledge. 
- The reason is that different numerical \textcolor{blue}{set of parameters} can lead to 
+ The reason is that different numerical sets of parameters can lead to 
 the same crowd dynamics. Actually, only a small set of dimensionless 
@@
 \cite{marchetti_2014}. We may hypothesize that while the dimensionless 
-\textcolor{blue}{parameters} provide some kind of control on the 
+parameters provide some kind of control on the 
 collective behavior in 
-crowds, only a few numerical \textcolor{blue}{\sout{settings} set of parameters} can attain an ``individualistic'' 
+crowds, only a few numerical set of parameters can attain an ``individualistic'' 
 meaning. 
@@
 
-The numerical \textcolor{blue}{parameters} for the ``faster is slower'' effect presented by 
-Helbing and co-workers \textcolor{blue}{\sout{is somewhat cumbersome} appears to have some drawbacks} 
+The numerical parameters for the ``faster is slower'' effect presented by 
+Helbing and co-workers appears to have some drawbacks 
 Ref.~\cite{helbing_2000,dorso_2017,dorso_2019}. Although a single 
 parameter (say, the desired velocity $v_d$) is numerically varied to 
-explain the phenomenon, the researcher \textcolor{blue}{\sout{looses sight} may loose sight} of the dimensionless 
-``numbers'' that truly control the crowd dynamics. The \textcolor{blue}{set of parameters} in 
+explain the phenomenon, the researcher may loose sight of the dimensionless 
+``numbers'' that truly control the crowd dynamics. The set of parameters in 
 Ref.~\cite{helbing_2000} also misses the ``faster is faster'' effect reported 
 to occur at very high pedestrian densities \cite{dorso_2017,haghani_2019}. 
-\textcolor{blue}{Moreover}, the empirical fundamental diagram raises as a point of reference 
+Moreover, the empirical fundamental diagram raises as a point of reference 
 for the SFM control parameters \cite{helbing_2007,dorso_2017}. \\
 
-The fundamental diagram exhibits the flux behavior for either low \textcolor{blue}{density} crowds 
-(with \textcolor{blue}{rare} contacts between pedestrians) and highly dense crowds (dominated 
-by \textcolor{blue}{two body interactions}). \textcolor{blue}{In the second case, crowds} experience a flux 
-slowing down, but other behaviors are also possible \cite{helbing_2007,lohner_2018}. \textcolor{blue}{
-\sout{In light of our previous hypothesis, we } We} may suspect that the  modeling of the 
+The fundamental diagram exhibits the flux behavior for either low density crowds 
+(with rare contacts between pedestrians) and highly dense crowds (dominated 
+by two body interactions). In the second case, crowds experience a flux 
+slowing down, but other behaviors are also possible \cite{helbing_2007,lohner_2018}. 
+ We may suspect that the  modeling of the 
 ``flux slowing down'' within the context of the SFM will require the proper 
-setting of the (dimensionless) controlling parameters. We \textcolor{blue}{have already}
+setting of the (dimensionless) controlling parameters. We have already
 examined this working hypothesis in Ref.~\cite{dorso_2019}, but limiting the parameter exploration to 
 the sliding friction, disregarding the body force. 
-We now widen the investigation on the \textcolor{blue}{\sout{parameter settings} set of parameters} to include the one 
+We now widen the investigation on the set of parameters to include the one 
 associated to the body force. We will  explore 
@@
 the body force and the sliding friction among pedestrians. Recall that the 
-interplay dynamics is not directly controlled by the \textcolor{blue}{\sout{numerical setting} set of parameters}, but 
+interplay dynamics is not directly controlled by the set of parameters, but 
 through dimensionless ``numbers'', where the model parameters appear mixed 
 between each other. Thus, this step up offers a challenge to the 
-``individualistic'' meaning of the parameter's \textcolor{blue}{\sout{setting} set}. \\
-
-The \textcolor{blue}{paper} is organized as follows. We first recall the available 
+``individualistic'' meaning of the parameter's set. \\
+
+The paper is organized as follows. We first recall the available 
 experimental values on the body force and the sliding friction (see Section 
@@
 the environmental conditions. The former is expressed, for example, by his 
-(her) moving ``attitude'' (say,\textcolor{blue}{\sout{self-assuredness} relaxed, normal, aggressive, etc}).
+(her) moving ``attitude'' (say, relaxed, normal, aggressive, etc).
 The latter brings out the 
 observed separation between pedestrians. Also, the ``contacts'' between 
-individuals \textcolor{blue}{produce} some kind of ``unwanted'' slowing down. All these 
+individuals produce some kind of ``unwanted'' slowing down. All these 
 observed patterns are commonly quantified in the literature into a set of 
-characteristic  parameters. \textcolor{red}{It is worth mentioning that the empirical
+characteristic  parameters. It is worth mentioning that the empirical
 data reported in this Section corresponds to non-panicking situations in which pedestrians 
-do not experience high anxiety levels (see below). }
+do not experience high anxiety levels (see below). 
 The experimental meaning of these parameters is as follows.
@@
 
-\item[(ii)] Despite the reactive attitude $\tau$, the pedestrian \textcolor{blue}{adopts} a 
+\item[(ii)] Despite the reactive attitude $\tau$, the pedestrian adopts a 
 ``free'' (undisturbed) walking speed $v_d$. This speed expresses his (her) 
@@
 \cite{helbing_1995,helbing_2000,li_2015}. 
-\textcolor{red}{Nevertheless, when pedestrians are in a panic situation,
+Nevertheless, when pedestrians are in a panic situation,
  they may not reach the ``free'' walking speed, but, $v_d$ may still be 
- associated to his (her) motivation to get to a target position.  }
+ associated to his (her) motivation to get to a target position.
 
@@
 values for the compressibility $k_n$ since these experiments were carried out 
-under low density \textcolor{red}{and non-panicking} conditions.  The minimum (perceived) step distance 
+under low density and non-panicking conditions.  The minimum (perceived) step distance 
 is $0.36\,$m according to Ref.~\cite{seyfried_2007}, but the
@@
 distances when they walk faster. The commonly accepted value $B\simeq 
-0.5\,$m is somewhat valid for walking speeds under $0.5\,$m/s  \textcolor{red}{and non-panicking conditions}
+0.5\,$m is somewhat valid for walking speeds under $0.5\,$m/s  and non-panicking conditions
 \cite{seyfried_2007}. Higher walking speeds (say, $1\,$m/s) will require 
@@
 
-We measured \textcolor{red}{\sout{the maximum attainable forces}
-contact forces} during the spring of 2019 at the subway in Buenos Aires, 
+We measured 
+contact forces during the spring of 2019 at the subway in Buenos Aires, 
 Argentina. Our preliminary results show that pedestrians feel ``uncomfortable'' 
@@
 
-The maximum (realistic) compressions may be computed from the \textcolor{blue}{Hooke's} relation 
+The maximum (realistic) compressions may be computed from the Hooke's relation 
 $F(x)=k_n(x)\,x$ and the compressibility $k_n(x)$ reported in Table~\ref{table_data}. 
@@
 range of $0.030-0.055\,$m. Also, a ``hitting'' force of $60\,$N can address 
-compressions between $0.045$ and $0.065\,$m. \textcolor{red}{
+compressions between $0.045$ and $0.065\,$m. 
 Besides, no reliable values for the sliding friction $k_t$ appears to be 
-available in the literature (to our knowledge).}\\
+available in the literature (to our knowledge).\\
 %Thus, according to Table~\ref{table_data}, \textcolor{blue}{we may expect experimental values for $k_n(x)$ up to 
@@
 
-\textcolor{red}{\sout{Besides, no reliable values for the sliding friction $k_t$ appears to be 
-available in the literature (to our knowledge). We may presume, however, that 
-the sliding friction approaches a fraction of the body force. We will come back 
-to this issue in Section~\ref{background}.}} \\
-
 \section{\label{background}Theoretical background}
@@
 
-The Social Force Model (SFM) provides \textcolor{blue}{a} necessary framework for simulating 
+The Social Force Model (SFM) provides a necessary framework for simulating 
 the collective dynamics of self-driven particles (\textit{i.e.} pedestrians). 
@@
 
-\noindent where the subscript $j$ corrresponds to any neighboring pedestrian or 
+\noindent where the subscript $j$ corresponds to any neighboring pedestrian or 
 the walls. The three forces $\mathbf{f}_d$, $\mathbf{f}_s$ and $\mathbf{f}_g$ 
 are different in nature. The desire force $\mathbf{f}_d$ represents the 
-acceleration (or deceleration) of the pedestrian due to his (her) own \textcolor{blue}{will}. 
+acceleration (or deceleration) of the pedestrian due to his (her) own will. 
 The social force $\mathbf{f}_s$, instead, describes the tendency of the 
 pedestrians to stay away from each other. The granular force $\mathbf{f}_g$ 
-stands for \textcolor{blue}{both} the sliding friction and the compression between 
+stands for both the sliding friction and the compression between 
 pedestrians. \\
@@
 is expected to be also present in the SFM. These will appear in connection to 
-the forces \textcolor{red}{\sout{, although their meaning may be somewhat different}}. \\
-
-The pedestrians' own \textcolor{blue}{will} is modeled by the desire force $\mathbf{f}_d$. 
-This force stands for the acceleration (deceleration) required to \textcolor{blue}{move}
+the forces. \\
+
+The pedestrians' own will is modeled by the desire force $\mathbf{f}_d$. 
+This force stands for the acceleration (deceleration) required to move
  at the desired walking speed $v_d$. This involves, however, a 
 personal attitude that makes him (her) appear more or less ``assertive''. As 
-mentioned in Section~\ref{experimental}, the reaction time $\tau$  \textcolor{blue}{reflects} for 
+mentioned in Section~\ref{experimental}, the reaction time $\tau$ reflects for 
 this attitude. Thus, the desire force is modeled as follows
@@
 prevent the pedestrians from getting too close to each other (or to the walls) 
-in a \textcolor{blue}{\sout{crowded} any} environment. \textcolor{blue}{\sout{If he (she) perceives that there is not enough space 
-to move, he (she) will decelerate or even move back.}} The model for this kind of 
+in a any environment. The model for this kind of 
 ``socio-psychological'' behavior is as follows
@@
 (perceived) step distance mentioned in Section~\ref{experimental}. 
-\textcolor{red}{Besides, the parameter $A$ reflects the intensity of the social repulsion.} \\
-
-The granular force (say, the sliding friction plus the body force) \textcolor{blue}{reflects} 
+Besides, the parameter $A$ reflects the intensity of the social repulsion. \\
+
+The granular force (say, the sliding friction plus the body force) reflects 
 the moving difficulties encountered in very crowded environments. The 
@@
 vanished otherwise. $\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij}$ 
-represents the \textcolor{blue}{relative} tangential velocities of the sliding 
+represents the relative tangential velocities of the sliding 
 bodies (or between the individual and the walls).    \\
@@
 We stress that the expression (\ref{eqn_friction}) assumes fixed values for 
-$k_t$ \textcolor{blue}{(and $k_n$)}. This may not be completely true according to 
+$k_t$ (and $k_n$). This may not be completely true according to 
 Table~\ref{table_data}. The local density (and thus, the pedestrians' 
@@
 
-\subsection{\label{parameters} \textcolor{blue}{\sout{The parameters setting} The set of parameters}}
+\subsection{The set of parameters}
 
@@
 The authors want to thanks the degree students Josefina Catoni and Ayelen Santos for providing data acquired at 
-the subway in Buenos Aires, Argentina.
+the subway in Buenos Aires, Argentina. \\
+
+G. Frank thanks Universidad Tecnol\'olica Nacional (UTN) for partial
+support through Grant PID Number SIUTNBA0006595.
 

### 2020-03-04 paper.tex
quite el texto azul hasta corridor

@@
 
-The numerical \textcolor{blue}{\sout{setting} set} of the parameters may affect the dynamics of the 
-pedestrians. Some \textcolor{blue}{\sout{settings} values}, however, yield similar collective dynamics.
-We introduce \textcolor{blue}{dimensionless} magnitudes 
+The numerical of the parameters may affect the dynamics of the 
+pedestrians. Some values, however, yield similar collective dynamics.
+We introduce dimensionless magnitudes 
 and proceed straightforward as indicated in \ref{appendix1}. We realize from 
-\ref{appendix1} that only three (\textcolor{blue}{dimensionless}) parameters  are the true 
+\ref{appendix1} that only three (dimensionless) parameters  are the true 
 ``control'' parameters for the collective dynamics. These are $\mathcal{A}$, 
@@
 
-The logical relations between the \textcolor{blue}{dimensionless} parameters and the ``individual'' 
+The logical relations between the dimensionless parameters and the ``individual'' 
 parameters can be studied by means of the Venn diagrams exhibited in 
@@
 }\\
-\caption[width=0.47\columnwidth]{Venn diagrams for the \textcolor{blue}{dimensionless} parameters
+\caption[width=0.47\columnwidth]{Venn diagrams for the dimensionless parameters
 appearing in the equation of motion (\ref{eqn_motion}) (see 
@@
 $v_d$ or $B$ appears somehow ``loosely'' in the crowd dynamic. We mean by 
-``loosely'' that any numerical \textcolor{blue}{\sout{setting} set for} these parameters may be 
-counterbalanced by the right \textcolor{blue}{\sout{setting} choice } of $A$ or $k_t$, keeping the 
-colletive dynamic (qualitatively) unchanged.  \\
+``loosely'' that any numerical set for these parameters may be 
+counterbalanced by the right choice of $A$ or $k_t$, keeping the 
+collective dynamic (qualitatively) unchanged.  \\
 
@@
 equivalent to vary simultaneously $\mathcal{A}$ and $\mathcal{K}_c$ by the same 
-amount in the (\textcolor{blue}{dimensionless}) parameter space (see Section~\ref{parameters}). We 
+amount in the (dimensionless) parameter space (see Section~\ref{parameters}). We 
 may visualize this sampling procedure as moving along a straight line in the 
@@
 
-\item[(b)] We will consider the parameter \textcolor{blue}{set from} Ref.~\cite{helbing_2000} 
+\item[(b)] We will consider the parameter set from Ref.~\cite{helbing_2000} 
 as a starting point for exploring the parameter space. The reason for this is 
 that a complete set of experimental parameters is still not available (to our 
-konwledge). We are aware, though, of the drawbacks \textcolor{blue}{of} this choice, say, the 
+konwledge). We are aware, though, of the drawbacks of this choice, say, the 
 unrealistic meanings for the length $B$ and the compressibility $k_n$ (see 
 Section~\ref{experimental}). But these are irrelevant in the context of the 
-(\textcolor{blue}{dimensionless}) parameter space and the corresponding collective dynamics (see 
+(dimensionless) parameter space and the corresponding collective dynamics (see 
 Section~\ref{introduction}).
@@
 In order to keep the model as simple as possible, we will only consider 
-\textcolor{blue}{isotropic pedestrian interactions}, since \textcolor{blue}{anisotropic
-interactions do} not play a relevant role at high densities. \\
+isotropic pedestrian interactions, since anisotropic
+interactions do not play a relevant role at high densities. \\
 
@@
 pedestrians were limited, however, to a cut-off distance of $0.88\,$m for 
-attaining a \textit{privacy sphere} \textcolor{blue}{that excludes second neighbors}. The desired 
+attaining a \textit{privacy sphere} that excludes second neighbors. The desired 
 velcity was always set to $1\,$m/s in the corridor situation. Besides, the 
@@
 desired velocity for different values of $k_n$. The evacuation 
-time is defined as the time \textcolor{blue}{lapsed} until 80\% of the pedestrians have 
+time is defined as the time lapsed until 80\% of the pedestrians have 
 left the room. In this section we will focus on the evacuation time for 
@@
 Three behavioral patterns can be distinguished in Fig.~\ref{vd_vs_te}. 
-Each pattern can \textcolor{blue}{display} a positive slope, a negative slope
+Each pattern can display a positive slope, a negative slope
 or both. The interval in which the slope is positive means that the 
@@
 Despite the presence of the FIS or FIF pattern, the evacuation time at a 
-fixed value of $v_d$ decreases for increasing values of $k_n$ (\textcolor{blue}{within} the examined interval). 
+fixed value of $v_d$ decreases for increasing values of $k_n$ (within the examined interval). 
 This means that stiffer pedestrians evacuate faster than soft pedestrians. 
@@
 velocities. In all cases, the velocity increases with the stiffness. The most significative 
-increment of velocity is in the interval \textcolor{blue}{$k_n>\,10^{4}$}. \\
+increment of velocity is in the interval $k_n>\,10^{4}$. \\
 
@@
 of the desired velocity. The degree of a node is defined as the number of links 
-that \textcolor{blue}{connects} this node to any other node. This means, the number of pedestrians 
+that connects this node to any other node. This means, the number of pedestrians 
 that are in physical contact with a given pedestrian. The mean degree is the 
@@
 Notice that the mean degree increases as $v_d$ increases, as expected. This expresses the fact that
-higher $v_d$ values accomplish higher densities, \textcolor{blue}{forcing} individuals to touch each 
+higher $v_d$ values accomplish higher densities, forcing individuals to touch each 
 other. For a given $v_d$, the mean degree reduces as the $k_n$ 
 value increases. A noticeable decrease in the mean degree can be seen for the 
-highest explored value of $k_n$. This \textcolor{blue}{\sout{was not expected and}} opens the question on how would
+highest explored value of $k_n$. This opens the question on how would
 this affect the sliding friction among pedestrians.\\
@@
 other are the ones who are being re-injected on the opposite side of the room.
-\textcolor{blue}{These collide with the bulk}, providing some kind of overlap during very short time. We will
+These collide with the bulk, providing some kind of overlap during very short time. We will
 not analize this regime.\\
@@
 
-The four snapshots in Fig.~\ref{network_bottleneck} confirm (visually) the fact that more rigid pedestrians \textcolor{blue}{ease} the crowded environment, widening the occupied region.
+The four snapshots in Fig.~\ref{network_bottleneck} confirm (visually) the fact that more rigid pedestrians ease the crowded environment, widening the occupied region.
 At $v_d=10\,$m/s (the maximum explored velocity), it can hardly be found pedestrians with degree 6 when $k_n=1.2\,$E6, while a lot of them are present for $k_n$=0.\\
@@
 We explored the parameter space along $v_d$ and $k_n$ for the bottleneck situation.
-This is similar to explore the \textcolor{blue}{dimensionless} plane $(\mathcal{A},\mathcal{K}_c)$.
+This is similar to explore the dimensionless plane $(\mathcal{A},\mathcal{K}_c)$.
 Soft pedestrians attain a FIS or FIS+FIF evacuation pattern but, stiff pedestrians (for any fixed $\mathcal{A}$ value within the explored range) exhibit a single FIF pattern.

### 2020-03-04 paper.tex
quite el texto rojo y azul en todo el paper

@@
 available in the literature (to our knowledge).\\
-%Thus, according to Table~\ref{table_data}, \textcolor{blue}{we may expect experimental values for $k_n(x)$ up to 
-%$1000\,$kg/s$^2$ (for $F=30\,$N), or, up to $1400\,$kg/s$^2$ (for $F=60\,$N).} \\
 
@@
 We present in this section the results corresponding to the corridor geometry. 
-We show the effects of \textcolor{blue}{\sout{modifying} varying} the body force coefficient $k_n$ on the 
+We show the effects of varying the body force coefficient $k_n$ on the 
 collective dynamics. We will keep $v_d$ (or $\mathcal{A}$) 
@@
 We find these topological magnitudes useful for comparing the 
-\textcolor{blue}{pedestrian behavior in the} 
+pedestrian behavior in the 
 corridor geometry with respect to the bottleneck geometry. A re-examination of 
@@
 each other. The mean degree increases for ``stiff'' pedestrians moving along 
-the corridor \textcolor{blue}{\sout{(at densities above} 
-as the density increased with a sharp increase at} $5\,$p/m$^2$\textcolor{blue}{\sout{)}}. Conversely, the mean degree 
+the corridor as the density increased with a sharp increase at
+ $5\,$p/m$^2$. Conversely, the mean degree 
 increases for ``soft'' pedestrians in the bottleneck situation.\\
@@
 applied on both situations. We may speculate that this phenomenon occurs 
-because, in the corridor, the lateral walls act like a \textcolor{blue}{\sout{containment}
-confining} barrier that 
+because, in the corridor, the lateral walls act like a 
+confining barrier that 
 forces the ``stiff'' pedestrian to increase his (her) contacts. On the contrary, 
@@
 Fig.~\ref{overlap_dens} shows this magnitude for the corridor situation. Notice 
-that ``soft'' pedestrians attain \textcolor{blue}{\sout{a more intruding} more } overlap than the ``stiff'' 
+that ``soft'' pedestrians attain more overlap than the ``stiff'' 
 ones, as expected. This is in agreement with Fig.~\ref{overlap_vd} for the 
@@
 Fig.~\ref{overlap_vd}, however, do not meet each other as in  
-Fig.~\ref{overlap_dens}. \textcolor{red}{\sout{The curve meeting attains for space limitations in 
-the corridor, since overlapping occurs (almost) independently of the value of
-$k_n$. This is clearly not the case in the bottleneck situation.} 
-All the curves meet each other at high-density values. This phenomenon occurs
-due to space limitations in the corridor that produces overlapping (almost) independently of the
-value of $k_n$}. \\
+Fig.~\ref{overlap_dens}. All the curves meet each other at
+high-density values. This phenomenon occurs due to space limitations
+in the corridor that produces overlapping (almost) independently of 
+the value of $k_n$. \\
 
@@
 
-The above results \textcolor{blue}{\sout{correspond to a milestone} represent an important step} in the 
-investigation. The \textcolor{blue}{inter-pedestrian} connectivity differences between the bottleneck geometry 
+The above results represent an important step in the 
+investigation. The inter-pedestrian connectivity differences between the bottleneck geometry 
 and the corridor geometry were not expected and opens two major questions:
-\textcolor{blue}{\sout{ how 
-does the body stiffness interact with the walls} how do the pedestrians interact with the walls as
-a function of the body stiffness}, and consequently, how does 
+ how do the pedestrians interact with the walls as
+a function of the body stiffness, and consequently, how does 
 this affect the flux across the corridor.\\
@@
 were computed at densities $\rho\geq 5.5$. According to 
-Fig.~\ref{overlap_dens},\textcolor{blue}{\sout{ these densities attain relevant overlaps}
-at these densities, the overlaps among pedestrians attain significant values}. Furthermore, 
+Fig.~\ref{overlap_dens},
+at these densities, the overlaps among pedestrians attain significant values. Furthermore, 
 stiffness values $k_n\geq 10^4$ move the system to a more heavily connected 
@@
 (almost) the same speed as his (her) neighbors. This 
-behavior may be envisaged as the passage from a \textcolor{red}{\sout{released} ``free''} 
-walking movement to a \textcolor{red}{\sout{tigh} constrained} movement as the stiffness increases. A more 
-physical picture would assimilate te former as a ``fluid-like 
+behavior may be envisaged as the passage from a ``free'' 
+walking movement to a  constrained movement as the stiffness increases. A more 
+physical picture would assimilate the former as a ``fluid-like 
 state'' and the latter as a ``solid-like state''. When the stiffness is 
@@
 the transversal coordinate $y$) for different $k_n$ values.
-For $k_n=0$, we can see a parabolic-like velocity profile \textcolor{red}{which means that the friction with the walls reduces the speed of pedestrians.} \textcolor{blue}{\sout{that} The velocity profile} resembles the Poiseuille flow (similar to Newtonian and incompressible fluids in a laminar regime).
+For $k_n=0$, we can see a parabolic-like velocity profile which means that the friction with the walls reduces the speed of pedestrians.
+The velocity profile resembles the Poiseuille flow (similar to Newtonian and incompressible fluids in a laminar regime).
 This behavior was also observed in empirical measurements of crowd dynamics reported in Ref.~\cite{zhang2013empirical}.
 But as $k_n$ increases the velocity profile flattens until becoming (almost) uniform (see Fig.~\ref{vx_profile} for $k_n=1.2\,$E6).
-In this scenario, $v_x$ attains a much lower \textcolor{blue}{\sout{level} value}  than in the case of soft pedestrians ($k_n=$0).\\
-
-\textcolor{blue}{From the results displayed above, we realize that \sout{The} the} crowd behaves like a solid for very stiff pedestrians.
+In this scenario, $v_x$ attains a much lower  value  than in the case of soft pedestrians ($k_n=$0).\\
+
+From the results displayed above, we realize that the crowd behaves like a solid for very stiff pedestrians.
 This means that the crowd can not be easily ``deformed''.
-In this context, deformation means that parts of the crowd may be \textcolor{blue}{\sout{released} allowed} to move faster than other parts of the crowd.
+In this context, deformation means that parts of the crowd may be allowed to move faster than other parts of the crowd.
 \\
 
-\textcolor{blue}{\sout{The strain rate is the tensor that expresses how the relative velocity of a medium changes when one moves away from one position to another.} The strain rate tensor displays the rate of change of the deformation of a body in the vincinity of a given point.} We consider the following discrete definition of the strain rate:
+The strain rate tensor displays the rate of change of the deformation of a body in the vicinity of a given point.
+ We consider the following discrete definition of the strain rate:
 
@@
 
-We conclude this Section by stressing\textcolor{blue}{, once again,} that stiffer pedestrians attain opposite results in corridors with respect to bottlenecks.
+We conclude this Section by stressing, once again, that stiffer pedestrians attain opposite results in corridors with respect to bottlenecks.
 The walls in the corridors play a critical role that prevents pedestrians from detaching from each other.
@@
 
-\textcolor{blue}{Having adopted as fundamental philosophy of work that the parameters of the SFM should be properly determined by requiring that the model properly reproduces well established experimental data, we} explored the effect on the pedestrians dynamics of the (sometimes neglected) body force in the framework of the SFM.
+Having adopted as fundamental philosophy of work that the parameters of the SFM should be properly determined by requiring that the model properly reproduces well established experimental data, we explored the effect on the pedestrians dynamics of the (sometimes neglected) body force in the framework of the SFM.
 We showed that the stiffness coefficient ($k_n$) has a significant impact on the evacuation dynamics (bottleneck) and also in the dynamics of pedestrians walking along a straight corridor.\\
@@
 The whole crowd can be compared to a granular material.
-Granular materials can be disordered (amorphous) or ordered depending on how particles \textcolor{blue}{\sout{link} interact}  to each other.
+Granular materials can be disordered (amorphous) or ordered depending on how particles interact with each other.
 In the present context, at low stiffness levels, the crowd appears disordered attaining a parabolic velocity profile.
@@
 
-Our efforts to ``tune'' the original SFM to \textcolor{blue}{reproduce} empirical data (say, the fundamental diagram) moved us to explore the dimensionless parameter space.
-We found that \textcolor{blue}{\sout{the qualitative behavior of empirical  data can be accomplished} we can qualitatively reproduce the empirical data} if the parameters are close to $\mathcal{K}_c < 68$, $\mathcal{K} = 685$ and $\mathcal{A}=14$.
+Our efforts to ``tune'' the original SFM to reproduce empirical data (say, the fundamental diagram) moved us to explore the dimensionless parameter space.
+We found that  we can qualitatively reproduce the empirical data if the parameters are close to $\mathcal{K}_c < 68$, $\mathcal{K} = 685$ and $\mathcal{A}=14$.
 Nevertheless, this is a first attempt to arrive at suitable parameters, although we do not claim these to be optimal.
@@
 smaller set of parameters. In order to identify this smaller set, we introduce 
-the following \textcolor{blue}{dimensionless} magnitudes\\
+the following dimensionless magnitudes\\
 
@@
 
-The equation of motion (\ref{eqn_motion}) can be \textcolor{blue}{rewritten} in terms of these 
-(\textcolor{blue}{dimensionless}) magnitudes, while only three (reduced) parameters are needed.\\
+The equation of motion (\ref{eqn_motion}) can be rewritten in terms of these 
+(dimensionless) magnitudes, while only three (reduced) parameters are needed.\\
 

### 2020-03-04 paper.tex
hice word wrap 80 lineas en los archivos de texto

@@
 
-The Social Force Model (SFM) is a suitable model for describing crowd behaviors
-under emotional stress.
-This research analyzes the role of the body force in the original SFM.
-We focused on the parameter associated with the body stiffness ($k_n$) and its impact on the pedestrian
-dynamics for two different geometries: bottlenecks and corridors.
-Increasing $k_n$ produces opposite effects on the crowd dynamics for each geometry: an increase of the crowd velocity 
-for bottlenecks, and a decrease for corridors. 
-The former reflects the fact that an increase in the stiffness reduces
-the overlap between pedestrians and, as a consequence, the sliding friction is reduced. 
-This phenomenon reduces the number of blocking clusters close to the exit door. 
-In the case of the corridor, instead, due to the confining walls,
-the pedestrians get tight
- into a lattice-like configuration due to space limitations.
-The friction interaction with the walls determines the velocity of the whole crowd along the corridor.
-Additionally, the corridor geometry generates a flux slowing down for very
-crowded environments, as observed in many real-life situations.
-We also explored the dimensionless parameters that arose from the reduced-in-units
-equation of motion and tuned them to reproduce the qualitative behavior of the empirical fundamental diagram.
+The Social Force Model (SFM) is a suitable model for describing crowd
+behaviors under emotional stress. This research analyzes the role of the body
+force in the original SFM. We focused on the parameter associated with the
+body stiffness ($k_n$) and its impact on the pedestrian dynamics for two
+different geometries: bottlenecks and corridors. Increasing $k_n$ produces
+opposite effects on the crowd dynamics for each geometry: an increase of the
+crowd velocity  for bottlenecks, and a decrease for corridors.  The former
+reflects the fact that an increase in the stiffness reduces the overlap
+between pedestrians and, as a consequence, the sliding friction is reduced.
+This phenomenon reduces the number of blocking clusters close to the exit
+door.  In the case of the corridor, instead, due to the confining walls, the
+pedestrians get tight  into a lattice-like configuration due to space
+limitations. The friction interaction with the walls determines the velocity
+of the whole crowd along the corridor. Additionally, the corridor geometry
+generates a flux slowing down for very crowded environments, as observed in
+many real-life situations. We also explored the dimensionless parameters that
+arose from the reduced-in-units equation of motion and tuned them to reproduce
+the qualitative behavior of the empirical fundamental diagram.
 
@@
 
-The Social Force Model (SFM) models the crowd dynamics 
-considering three kinds of force: desired forces, social forces, and physical forces.
-In its original version, the SFM, addresses two physical forces as essential: 
- the ``body force'' and the ``sliding friction''. Both are 
-inspired by granular interactions and were claimed to be necessary  
-for attaining the particular effects in panicking crowds \cite{helbing_2000}. 
-The ``sliding friction'' actually proved to be an essential feature of the 
-``faster-is-slower'' effect, although the role of the ``body force'' appears, 
-at a first instance, not so clear \cite{dorso_2005,dorso_2007,dorso_2011}. \\
+The Social Force Model (SFM) models the crowd dynamics  considering three kinds
+of force: desired forces, social forces, and physical forces. In its original
+version, the SFM, addresses two physical forces as essential:   the ``body
+force'' and the ``sliding friction''. Both are  inspired by granular
+interactions and were claimed to be necessary   for attaining the particular
+effects in panicking crowds \cite{helbing_2000}.  The ``sliding friction''
+actually proved to be an essential feature of the  ``faster-is-slower'' effect,
+although the role of the ``body force'' appears,  at a first instance, not so
+clear \cite{dorso_2005,dorso_2007,dorso_2011}. \\
 
@@
 to 10$\,$people/m$^2$) is a commonsense matter \cite{henein_2007,fruin_1993}.
-Researchers, however, question the numerical setting for this force in 
-the SFM context \cite{lakoba_2005}. As a matter of fact, the usual 
- set of parameters provided by 
-Helbing prevents the excessive overlapping among pedestrians, but it is known to 
-accomplish artificially high force levels 
-\cite{helbing_2000,lakoba_2005,langston_2006,lin_2017}. The force estimates 
-from the SFM appear to be remarkably higher with respect to the reported real 
-life data (say, an order of magnitude). The crowd motion simulations, however, 
-present realistic results \cite{lakoba_2005,langston_2006,dorso_2017}. 
-The 
-point seems to be that the SFM focuses on the ``collective behavior'' due 
-to clogging, missing the ``individualistic'' perspective  of single pedestrians 
-or very small groups \cite{helbing_2000,henein_2007,narain_2009}.  \\
-
-Many researchers realized that modifying the SFM may (partially)
-fix the misleading results. It was proposed that the pedestrians' 
-psychological force (say, the ``social force'') should be suppressed in the 
-context of highly dense crowds 
-\cite{pelechano_2007,moussaid_2011,alonso_2014,bottinelli_2017}, or smoothly 
-quenched according to the crowd density \cite{song_2019}. The authors in 
-Refs.~\cite{kabalan_2017,jebrane_2019} further proposed a rigid body model in 
-order to completely avoid the overlapping phenomenon. This perspective 
-dismisses 
-any connection to a ``sliding friction''. Conversely, other authors tried to 
-limit the pedestrians acceleration by introducing ``static friction'' between 
-the pedestrians and the floor \cite{wang_2019}. This kind of friction, however, 
-reduces the effective willings of the pedestrians.  \\
-
-A unique (and universal) set of parameters appears not
-available yet to our knowledge. 
- The reason is that different numerical sets of parameters can lead to 
-the same crowd dynamics. Actually, only a small set of dimensionless 
+Researchers, however, question the numerical setting for this force in  the SFM
+context \cite{lakoba_2005}. As a matter of fact, the usual   set of parameters
+provided by  Helbing prevents the excessive overlapping among pedestrians, but
+it is known to  accomplish artificially high force levels
+\cite{helbing_2000,lakoba_2005,langston_2006,lin_2017}. The force estimates from
+the SFM appear to be remarkably higher with respect to the reported real life
+data (say, an order of magnitude). The crowd motion simulations, however,
+present realistic results \cite{lakoba_2005,langston_2006,dorso_2017}.  The
+point seems to be that the SFM focuses on the ``collective behavior'' due  to
+clogging, missing the ``individualistic'' perspective  of single pedestrians  or
+very small groups \cite{helbing_2000,henein_2007,narain_2009}.  \\
+
+Many researchers realized that modifying the SFM may (partially) fix the
+misleading results. It was proposed that the pedestrians'  psychological force
+(say, the ``social force'') should be suppressed in the  context of highly dense
+crowds  \cite{pelechano_2007,moussaid_2011,alonso_2014,bottinelli_2017}, or
+smoothly  quenched according to the crowd density \cite{song_2019}. The authors
+in  Refs.~\cite{kabalan_2017,jebrane_2019} further proposed a rigid body model
+in  order to completely avoid the overlapping phenomenon. This perspective
+dismisses  any connection to a ``sliding friction''. Conversely, other authors
+tried to  limit the pedestrians acceleration by introducing ``static friction''
+between  the pedestrians and the floor \cite{wang_2019}. This kind of friction,
+however,  reduces the effective willings of the pedestrians.  \\
+
+A unique (and universal) set of parameters appears not available yet to our
+knowledge.   The reason is that different numerical sets of parameters can lead
+to  the same crowd dynamics. Actually, only a small set of dimensionless
 ``numbers'' control the crowd dynamics \cite{dorso_2019}. These are similar to
@@
 \cite{marchetti_2014}. We may hypothesize that while the dimensionless
-parameters provide some kind of control on the 
-collective behavior in 
-crowds, only a few numerical set of parameters can attain an ``individualistic'' 
-meaning. 
- \\
+parameters provide some kind of control on the  collective behavior in  crowds,
+only a few numerical set of parameters can attain an ``individualistic''
+meaning.   \\
 
@@
 Helbing and co-workers appears to have some drawbacks
-Ref.~\cite{helbing_2000,dorso_2017,dorso_2019}. Although a single 
-parameter (say, the desired velocity $v_d$) is numerically varied to 
-explain the phenomenon, the researcher may loose sight of the dimensionless 
-``numbers'' that truly control the crowd dynamics. The set of parameters in 
+Ref.~\cite{helbing_2000,dorso_2017,dorso_2019}. Although a single  parameter
+(say, the desired velocity $v_d$) is numerically varied to  explain the
+phenomenon, the researcher may loose sight of the dimensionless  ``numbers''
+that truly control the crowd dynamics. The set of parameters in
 Ref.~\cite{helbing_2000} also misses the ``faster is faster'' effect reported
 to occur at very high pedestrian densities \cite{dorso_2017,haghani_2019}.
-Moreover, the empirical fundamental diagram raises as a point of reference 
-for the SFM control parameters \cite{helbing_2007,dorso_2017}. \\
+Moreover, the empirical fundamental diagram raises as a point of reference  for
+the SFM control parameters \cite{helbing_2007,dorso_2017}. \\
 
 The fundamental diagram exhibits the flux behavior for either low density crowds
-(with rare contacts between pedestrians) and highly dense crowds (dominated 
-by two body interactions). In the second case, crowds experience a flux 
-slowing down, but other behaviors are also possible \cite{helbing_2007,lohner_2018}. 
- We may suspect that the  modeling of the 
-``flux slowing down'' within the context of the SFM will require the proper 
-setting of the (dimensionless) controlling parameters. We have already
-examined this working hypothesis in Ref.~\cite{dorso_2019}, but limiting the parameter exploration to 
-the sliding friction, disregarding the body force. 
-We now widen the investigation on the set of parameters to include the one 
-associated to the body force. We will  explore 
- the complex interplay between 
-the body force and the sliding friction among pedestrians. Recall that the 
-interplay dynamics is not directly controlled by the set of parameters, but 
-through dimensionless ``numbers'', where the model parameters appear mixed 
-between each other. Thus, this step up offers a challenge to the 
-``individualistic'' meaning of the parameter's set. \\
-
-The paper is organized as follows. We first recall the available 
-experimental values on the body force and the sliding friction (see Section 
+(with rare contacts between pedestrians) and highly dense crowds (dominated  by
+two body interactions). In the second case, crowds experience a flux  slowing
+down, but other behaviors are also possible \cite{helbing_2007,lohner_2018}.
+We may suspect that the  modeling of the  ``flux slowing down'' within the
+context of the SFM will require the proper  setting of the (dimensionless)
+controlling parameters. We have already examined this working hypothesis in
+Ref.~\cite{dorso_2019}, but limiting the parameter exploration to  the sliding
+friction, disregarding the body force.  We now widen the investigation on the
+set of parameters to include the one  associated to the body force. We will
+explore   the complex interplay between  the body force and the sliding friction
+among pedestrians. Recall that the  interplay dynamics is not directly
+controlled by the set of parameters, but  through dimensionless ``numbers'',
+where the model parameters appear mixed  between each other. Thus, this step up
+offers a challenge to the  ``individualistic'' meaning of the parameter's set.
+\\
+
+The paper is organized as follows. We first recall the available  experimental
+values on the body force and the sliding friction (see Section
 \ref{experimental}). Secondly, we introduce the reduced-in-units SFM and the
@@
 \ref{background}). We present our numerical simulations in Section
-\ref{results}. For the sake of clarity, this Section is 
-separated into two major parts: the bottleneck scenario and the corridor 
-scenario in Sections \ref{bottleneck} and \ref{corridor}, respectively. 
-Section \ref{conclusions} opens a detailed discussion from results in Section \ref{results}
-and resumes our main conclusions.
+\ref{results}. For the sake of clarity, this Section is  separated into two
+major parts: the bottleneck scenario and the corridor  scenario in Sections
+\ref{bottleneck} and \ref{corridor}, respectively.  Section \ref{conclusions}
+opens a detailed discussion from results in Section \ref{results} and resumes
+our main conclusions.
 
@@
 
-The complex behavior of pedestrians features
- either his (her) feelings and 
-the environmental conditions. The former is expressed, for example, by his 
-(her) moving ``attitude'' (say, relaxed, normal, aggressive, etc).
-The latter brings out the 
-observed separation between pedestrians. Also, the ``contacts'' between 
-individuals produce some kind of ``unwanted'' slowing down. All these 
-observed patterns are commonly quantified in the literature into a set of 
-characteristic  parameters. It is worth mentioning that the empirical
-data reported in this Section corresponds to non-panicking situations in which pedestrians 
-do not experience high anxiety levels (see below). 
-The experimental meaning of these parameters is as follows.
-
-\begin{itemize}
-\item[(i)] The walking attitude of a pedestrian may appear somewhat 
-  ``aggressive'' if he (she) reacts actively to unexpected behaviors 
+The complex behavior of pedestrians features  either his (her) feelings and  the
+environmental conditions. The former is expressed, for example, by his  (her)
+moving ``attitude'' (say, relaxed, normal, aggressive, etc). The latter brings
+out the  observed separation between pedestrians. Also, the ``contacts'' between
+individuals produce some kind of ``unwanted'' slowing down. All these  observed
+patterns are commonly quantified in the literature into a set of  characteristic
+parameters. It is worth mentioning that the empirical data reported in this
+Section corresponds to non-panicking situations in which pedestrians  do not
+experience high anxiety levels (see below).  The experimental meaning of these
+parameters is as follows.
+
+\begin{itemize} \item[(i)] The walking attitude of a pedestrian may appear
+somewhat    ``aggressive'' if he (she) reacts actively to unexpected behaviors
 \cite{lakoba_2005,helbing_1995}. The smaller the reaction time, the more
- aggressive observed posture. The associated parameter to this 
-behavior is the relaxation or characteristic time $\tau$ 
-\cite{johansson_2009,helbing_2000}.
+aggressive observed posture. The associated parameter to this  behavior is the
+relaxation or characteristic time $\tau$  \cite{johansson_2009,helbing_2000}.
 
@@
 to relaxed, normal or nervous walking speeds, respectively
-\cite{helbing_1995,helbing_2000,li_2015}. 
-Nevertheless, when pedestrians are in a panic situation,
- they may not reach the ``free'' walking speed, but, $v_d$ may still be 
- associated to his (her) motivation to get to a target position.
-
-\item[(iii)] The walking speed of pedestrians appears to be lower in a 
-crowded walkway with respect to their usually expected ``free'' walking speeds 
+\cite{helbing_1995,helbing_2000,li_2015}.  Nevertheless, when pedestrians are in
+a panic situation,  they may not reach the ``free'' walking speed, but, $v_d$
+may still be   associated to his (her) motivation to get to a target position.
+
+\item[(iii)] The walking speed of pedestrians appears to be lower in a  crowded
+walkway with respect to their usually expected ``free'' walking speeds
 \cite{weidmann_1992,lakoba_2005}. Pedestrians tend to reduce their speed within
-crowded environments because they perceive not enough space for taking a 
-step  \cite{johansson_2009}. This (perceived) step distance 
-is therefore an influential parameter on the pedestrians behavior. 
-It is known as the characteristic length $B$.
+crowded environments because they perceive not enough space for taking a  step
+\cite{johansson_2009}. This (perceived) step distance  is therefore an
+influential parameter on the pedestrians behavior.  It is known as the
+characteristic length $B$.
 
@@
 ``body force''  and ``sliding friction'' can be introduced straight forward.
-This will be done in Section \ref{background}. But it is worth noting that 
-both are associated to the moving difficulties (say, slowing down and 
-obstructions) observed in contacting pedestrians.
+This will be done in Section \ref{background}. But it is worth noting that  both
+are associated to the moving difficulties (say, slowing down and  obstructions)
+observed in contacting pedestrians.
 
@@
 
-Table~\ref{table_data} shows a few empirical values
- for the most common 
+Table~\ref{table_data} shows a few empirical values  for the most common
 parameters. More data is available throughout the literature (see, for example,
@@
  \hline
- $\tau$[s]   & $m$[kg]     & $v_d$[m/s]  &  $B$[m]  & $k_n$[kg/s$^2$] &  Refs. \\
+ $\tau$[s]   & $m$[kg]     & $v_d$[m/s]  &  $B$[m]  & $k_n$[kg/s$^2$] &  Refs.\\
  \hline
@@
 
-\hline
-\end{tabular}
-\caption{The experimental data for the pedestrian parameters, as explained in 
-Section~\ref{experimental}. The magnitude $v$ means the actual pedestrian velocity 
-(m/s). The magnitude $x$ means the compression length (m). The upper row for 
-Ref.~\cite{song_2019} corresponds to data acquired in winter and the lower row to 
-data acquired in summer. The asterisk ($^*$) corresponds to reasonable 
-estimates from the authors. }
+\hline \end{tabular} \caption{The experimental data for the pedestrian
+parameters, as explained in  Section~\ref{experimental}. The magnitude $v$ means
+the actual pedestrian velocity  (m/s). The magnitude $x$ means the compression
+length (m). The upper row for  Ref.~\cite{song_2019} corresponds to data
+acquired in winter and the lower row to  data acquired in summer. The asterisk
+($^*$) corresponds to reasonable  estimates from the authors. }
 \label{table_data}
@@
 values for the compressibility $k_n$ since these experiments were carried out
-under low density and non-panicking conditions.  The minimum (perceived) step distance 
-is $0.36\,$m according to Ref.~\cite{seyfried_2007}, but the
- pedestrians seem to require larger 
-distances when they walk faster. The commonly accepted value $B\simeq 
-0.5\,$m is somewhat valid for walking speeds under $0.5\,$m/s  and non-panicking conditions
-\cite{seyfried_2007}. Higher walking speeds (say, $1\,$m/s) will require 
-a step distance of $1.3\,$m for the pedestrians to feel that there is enough 
-space to move along.\\
+under low density and non-panicking conditions.  The minimum (perceived) step
+distance  is $0.36\,$m according to Ref.~\cite{seyfried_2007}, but the
+pedestrians seem to require larger  distances when they walk faster. The
+commonly accepted value $B\simeq  0.5\,$m is somewhat valid for walking speeds
+under $0.5\,$m/s  and non-panicking conditions \cite{seyfried_2007}. Higher
+walking speeds (say, $1\,$m/s) will require  a step distance of $1.3\,$m for the
+pedestrians to feel that there is enough  space to move along.\\
 
@@
 environment of the Beijing subway. This environment was not suitable for
-providing information on the step distance $B$, but estimates for the 
-desired speed and the body compressibility could be achieved. The reported 
-magnitude $k_n$ assesses either the clothes and the body compressibility. The 
-final value, though, is linearly related to the compression $x$. \\
-
-We measured 
-contact forces during the spring of 2019 at the subway in Buenos Aires, 
-Argentina. Our preliminary results show that pedestrians feel ``uncomfortable'' 
-whenever a body force ranging from $5$ to $20\,$N is applied for at least ten 
-minutes. Short lasting forces (say, less than 4 minutes) may also be perceived 
-as ``uncomfortable'' for values ranging from $10$ to $30\,$N. We also recorded body 
-forces up to $60\,$N during very short ``hits''. The comparison with the 
-fittings provided by Ref.~\cite{song_2019} shows that these magnitudes 
-accomplish densities around 5 people/m$^2$.     \\
+providing information on the step distance $B$, but estimates for the  desired
+speed and the body compressibility could be achieved. The reported  magnitude
+$k_n$ assesses either the clothes and the body compressibility. The  final
+value, though, is linearly related to the compression $x$. \\
+
+We measured  contact forces during the spring of 2019 at the subway in Buenos
+Aires,  Argentina. Our preliminary results show that pedestrians feel
+``uncomfortable''  whenever a body force ranging from $5$ to $20\,$N is applied
+for at least ten  minutes. Short lasting forces (say, less than 4 minutes) may
+also be perceived  as ``uncomfortable'' for values ranging from $10$ to $30\,$N.
+We also recorded body  forces up to $60\,$N during very short ``hits''. The
+comparison with the  fittings provided by Ref.~\cite{song_2019} shows that these
+magnitudes  accomplish densities around 5 people/m$^2$.     \\
 
 The maximum (realistic) compressions may be computed from the Hooke's relation
-$F(x)=k_n(x)\,x$ and the compressibility $k_n(x)$ reported in Table~\ref{table_data}. 
-An ``uncomfortable'' body force  $10\,$N $-$ $30\,$N can address compressions in the 
-range of $0.030-0.055\,$m. Also, a ``hitting'' force of $60\,$N can address 
-compressions between $0.045$ and $0.065\,$m. 
+$F(x)=k_n(x)\,x$ and the compressibility $k_n(x)$ reported in
+Table~\ref{table_data}.  An ``uncomfortable'' body force  $10\,$N $-$ $30\,$N
+can address compressions in the  range of $0.030-0.055\,$m. Also, a ``hitting''
+force of $60\,$N can address  compressions between $0.045$ and $0.065\,$m.
 Besides, no reliable values for the sliding friction $k_t$ appears to be
@@
 
-The Social Force Model (SFM) provides a necessary framework for simulating 
-the collective dynamics of self-driven particles (\textit{i.e.} pedestrians). 
-The pedestrians are considered to follow an equation of motion involving 
-either ``socio-psychological'' forces and physical forces (say, granular 
-forces). The equation of motion for any pedestrian $i$ (of mass $m_i$) reads
+The Social Force Model (SFM) provides a necessary framework for simulating  the
+collective dynamics of self-driven particles (\textit{i.e.} pedestrians).  The
+pedestrians are considered to follow an equation of motion involving  either
+``socio-psychological'' forces and physical forces (say, granular  forces). The
+equation of motion for any pedestrian $i$ (of mass $m_i$) reads
 
@@
 are different in nature. The desire force $\mathbf{f}_d$ represents the
-acceleration (or deceleration) of the pedestrian due to his (her) own will. 
-The social force $\mathbf{f}_s$, instead, describes the tendency of the 
-pedestrians to stay away from each other. The granular force $\mathbf{f}_g$ 
-stands for both the sliding friction and the compression between 
-pedestrians. \\
+acceleration (or deceleration) of the pedestrian due to his (her) own will.  The
+social force $\mathbf{f}_s$, instead, describes the tendency of the  pedestrians
+to stay away from each other. The granular force $\mathbf{f}_g$  stands for both
+the sliding friction and the compression between  pedestrians. \\
 
@@
 
-The pedestrians' own will is modeled by the desire force $\mathbf{f}_d$. 
-This force stands for the acceleration (deceleration) required to move
- at the desired walking speed $v_d$. This involves, however, a 
-personal attitude that makes him (her) appear more or less ``assertive''. As 
-mentioned in Section~\ref{experimental}, the reaction time $\tau$ reflects for 
-this attitude. Thus, the desire force is modeled as follows
+The pedestrians' own will is modeled by the desire force $\mathbf{f}_d$.  This
+force stands for the acceleration (deceleration) required to move  at the
+desired walking speed $v_d$. This involves, however, a  personal attitude that
+makes him (her) appear more or less ``assertive''. As  mentioned in
+Section~\ref{experimental}, the reaction time $\tau$ reflects for  this
+attitude. Thus, the desire force is modeled as follows
 
@@
 
-\noindent where $\hat{\mathbf{e}}(t)$ represents the unit vector pointing to 
-the target position. $\mathbf{v}(t)$ stands for the pedestrian velocity at time 
-$t$. \\
+\noindent where $\hat{\mathbf{e}}(t)$ represents the unit vector pointing to the
+target position. $\mathbf{v}(t)$ stands for the pedestrian velocity at time $t$.
+\\
 
@@
 prevent the pedestrians from getting too close to each other (or to the walls)
-in a any environment. The model for this kind of 
-``socio-psychological'' behavior is as follows
+in a any environment. The model for this kind of  ``socio-psychological''
+behavior is as follows
 
@@
 length within the model, and thus, it may be somewhat connected to the
-(perceived) step distance mentioned in Section~\ref{experimental}. 
-Besides, the parameter $A$ reflects the intensity of the social repulsion. \\
-
-The granular force (say, the sliding friction plus the body force) reflects 
-the moving difficulties encountered in very crowded environments. The 
-expression for the granular force has been borrowed from the granular 
-matter field, the mathematical expression reads as follows
+(perceived) step distance mentioned in Section~\ref{experimental}.  Besides, the
+parameter $A$ reflects the intensity of the social repulsion. \\
+
+The granular force (say, the sliding friction plus the body force) reflects  the
+moving difficulties encountered in very crowded environments. The  expression
+for the granular force has been borrowed from the granular  matter field, the
+mathematical expression reads as follows
 
@@
 vanished otherwise. $\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij}$
-represents the relative tangential velocities of the sliding 
-bodies (or between the individual and the walls).    \\
+represents the relative tangential velocities of the sliding  bodies (or between
+the individual and the walls).    \\
 
@@
 linearly related to the difference between the (tangential) velocities. The
-coefficients $k_t$ (for the sliding friction) and $k_n$ (for the 
-body force) are supposed to be related to the areas of contact and the clothes 
-material, among others. \\
+coefficients $k_t$ (for the sliding friction) and $k_n$ (for the  body force)
+are supposed to be related to the areas of contact and the clothes  material,
+among others. \\
 
@@
 Table~\ref{table_data}. The local density (and thus, the pedestrians'
-compression) may affect the compressibility parameter $k_n$ by more than an order 
-of magnitude. We will vary $k_n$ (and $k_t$) in order to explore this 
+compression) may affect the compressibility parameter $k_n$ by more than an
+order  of magnitude. We will vary $k_n$ (and $k_t$) in order to explore this
 phenomenon. \\
 
-\subsection{The set of parameters}
-
-The numerical of the parameters may affect the dynamics of the 
-pedestrians. Some values, however, yield similar collective dynamics.
-We introduce dimensionless magnitudes 
-and proceed straightforward as indicated in \ref{appendix1}. We realize from 
-\ref{appendix1} that only three (dimensionless) parameters  are the true 
-``control'' parameters for the collective dynamics. These are $\mathcal{A}$, 
-$\mathcal{K}$, $\mathcal{K}_c$ as defined in \ref{appendix1}. Recall that 
-$\mathcal{A}$ and $\mathcal{K}$ are precisely the same as in 
-Ref.~\cite{dorso_2019}, but a novel $\mathcal{K}_c$ parameter has been 
-introduced due to the body force.   \\
-
-The logical relations between the dimensionless parameters and the ``individual'' 
-parameters can be studied by means of the Venn diagrams exhibited in 
-Fig.~\ref{venn_diagram}. The parameters $\mathcal{A}$, $\mathcal{K}$ and 
-$\mathcal{K}_c$ are represented as intersecting sets, and the ``individual'' 
-parameters are represented as elements within each set. The shared elements 
-between $\mathcal{A}$, $\mathcal{K}$ and $\mathcal{K}_c$ are placed inside the 
-intersecting regions. \\
+\subsection{\label{parameters}The set of parameters}
+
+The numerical of the parameters may affect the dynamics of the  pedestrians.
+Some values, however, yield similar collective dynamics. We introduce
+dimensionless magnitudes  and proceed straightforward as indicated in
+\ref{appendix1}. We realize from  \ref{appendix1} that only three
+(dimensionless) parameters  are the true  ``control'' parameters for the
+collective dynamics. These are $\mathcal{A}$,  $\mathcal{K}$, $\mathcal{K}_c$ as
+defined in \ref{appendix1}. Recall that  $\mathcal{A}$ and $\mathcal{K}$ are
+precisely the same as in  Ref.~\cite{dorso_2019}, but a novel $\mathcal{K}_c$
+parameter has been  introduced due to the body force.   \\
+
+The logical relations between the dimensionless parameters and the
+``individual''  parameters can be studied by means of the Venn diagrams
+exhibited in  Fig.~\ref{venn_diagram}. The parameters $\mathcal{A}$,
+$\mathcal{K}$ and  $\mathcal{K}_c$ are represented as intersecting sets, and the
+``individual''  parameters are represented as elements within each set. The
+shared elements  between $\mathcal{A}$, $\mathcal{K}$ and $\mathcal{K}_c$ are
+placed inside the  intersecting regions. \\
 
@@
 \subfloat[\label{venn_2parameters}]
-{\includegraphics[width=0.49\columnwidth]{./venn_2parameters.png}}
-\hfill    
+{\includegraphics[width=0.49\columnwidth]{./venn_2parameters.png}} \hfill
 \subfloat[\label{venn_3parameters}]
-{\includegraphics[width=0.49\columnwidth]{./venn_3parameters.png}
-}\\
+{\includegraphics[width=0.49\columnwidth]{./venn_3parameters.png} }\\
 \caption[width=0.47\columnwidth]{Venn diagrams for the dimensionless parameters
@@
 $\mathcal{A}=\{\tau/m,1/v_d,A\}$, $\mathcal{K}=\{\tau/m,B,k_t\}$ and
-$\mathcal{K}_c=\{\tau/m,1/v_d,B,k_n\}$. (a) The Venn diagram representation if no 
-body force is introduced in the SFM (only sets $\mathcal{A}$ and $\mathcal{K}$, 
-as in Ref.~\cite{dorso_2019}). (b) The Venn diagram representation for the sets 
-$\mathcal{A}$, $\mathcal{K}$ and $\mathcal{K}_c$. }
+$\mathcal{K}_c=\{\tau/m,1/v_d,B,k_n\}$. (a) The Venn diagram representation if
+no  body force is introduced in the SFM (only sets $\mathcal{A}$ and
+$\mathcal{K}$,  as in Ref.~\cite{dorso_2019}). (b) The Venn diagram
+representation for the sets  $\mathcal{A}$, $\mathcal{K}$ and $\mathcal{K}_c$.}
 \label{venn_diagram} 
@@
 Fig.~\ref{venn_2parameters} represents the situation when $\mathcal{K}_c$ is
-absent. Notice that $A/v_d$ or $k_t B$ may control the collective 
-dynamic, in spite of the ``assertive'' attitude. The individual character of 
-$v_d$ or $B$ appears somehow ``loosely'' in the crowd dynamic. We mean by 
-``loosely'' that any numerical set for these parameters may be 
-counterbalanced by the right choice of $A$ or $k_t$, keeping the 
-collective dynamic (qualitatively) unchanged.  \\
+absent. Notice that $A/v_d$ or $k_t B$ may control the collective  dynamic, in
+spite of the ``assertive'' attitude. The individual character of  $v_d$ or $B$
+appears somehow ``loosely'' in the crowd dynamic. We mean by  ``loosely'' that
+any numerical set for these parameters may be  counterbalanced by the right
+choice of $A$ or $k_t$, keeping the  collective dynamic (qualitatively)
+unchanged.  \\
 
@@
 
-A characteristic feature of pedestrian dynamics is the formation of clusters. Clusters of pedestrians can 
-be defined as the set of individuals that for any member of the group (say, $i$) there exists at least
-another member belonging to the same group ($j$) in contact with the former. 
-Thus, we define a ``granular cluster'' ($C_g$) following the mathematical formula given in Ref.~\cite{strachan1997fragment}
+A characteristic feature of pedestrian dynamics is the formation of clusters.
+Clusters of pedestrians can  be defined as the set of individuals that for any
+member of the group (say, $i$) there exists at least another member belonging to
+the same group ($j$) in contact with the former.  Thus, we define a ``granular
+cluster'' ($C_g$) following the mathematical formula given in
+Ref.~\cite{strachan1997fragment}
 
 \begin{equation}
-C_g:P_i~\epsilon~ C_g \Leftrightarrow \exists~ j~\epsilon~C_g / r_{ij} < (R_i+R_j) \label{ec-cluster}
+C_g:P_i~\epsilon~ C_g \Leftrightarrow \exists~ j~\epsilon~C_g / r_{ij} 
+< (R_i+R_j) \label{ec-cluster}
 \end{equation}
 
-where ($P_i$) indicate the \textit{ith} pedestrian and $R_i$ is his (her) radius (shoulder width). That means, $C_g$ is a
-set of pedestrians that interact not only with the social force, but also with physical forces (\textit{i.e.} friction force and body force).
-A ``blocking cluster'' is defined as the subset of clusterized particles (granular cluster) closest to the door whose first 
-and last component particles are in contact with the walls at both sides of the door ~\cite{dorso_2005}.
-This clogging structure is responsible for worsening the evacuation performance.
+where ($P_i$) indicate the \textit{ith} pedestrian and $R_i$ is his (her) radius
+(shoulder width). That means, $C_g$ is a set of pedestrians that interact not
+only with the social force, but also with physical forces (\textit{i.e.}
+friction force and body force). A ``blocking cluster'' is defined as the subset
+of clusterized particles (granular cluster) closest to the door whose first  and
+last component particles are in contact with the walls at both sides of the door
+~\cite{dorso_2005}. This clogging structure is responsible for worsening the
+evacuation performance.
 
@@
 Our working hypotheses are similar to those mentioned in
-Ref.~\cite{dorso_2019}, 
-although the presence of the body force opens inquiries about the proper 
-exploration of the parameter space. To be precise
-
-\begin{itemize}
- \item[(a)] The ``faster-is-slower'' (or the ``faster-is-faster'') phenomenon 
-occurs when varying the values of $v_d$ (see Section~\ref{bottleneck}). This is 
-equivalent to vary simultaneously $\mathcal{A}$ and $\mathcal{K}_c$ by the same 
-amount in the (dimensionless) parameter space (see Section~\ref{parameters}). We 
-may visualize this sampling procedure as moving along a straight line in the 
-space $(\mathcal{A},\mathcal{K},\mathcal{K}_c)$. Further variations of 
-$k_n$ turns the sample points out of this line, but on the plane of constant
+Ref.~\cite{dorso_2019},  although the presence of the body force opens inquiries
+about the proper  exploration of the parameter space. To be precise
+
+\begin{itemize}  \item[(a)] The ``faster-is-slower'' (or the ``faster-is-
+faster'') phenomenon  occurs when varying the values of $v_d$ (see
+Section~\ref{bottleneck}). This is  equivalent to vary simultaneously
+$\mathcal{A}$ and $\mathcal{K}_c$ by the same  amount in the (dimensionless)
+parameter space (see Section~\ref{parameters}). We  may visualize this sampling
+procedure as moving along a straight line in the  space
+$(\mathcal{A},\mathcal{K},\mathcal{K}_c)$. Further variations of  $k_n$ turns
+the sample points out of this line, but on the plane of constant
 $\mathcal{K}_c$. We will step up $k_n$ by several orders of magnitude in order
@@
 
-\item[(b)] We will consider the parameter set from Ref.~\cite{helbing_2000} 
-as a starting point for exploring the parameter space. The reason for this is 
-that a complete set of experimental parameters is still not available (to our 
+\item[(b)] We will consider the parameter set from Ref.~\cite{helbing_2000}  as
+a starting point for exploring the parameter space. The reason for this is  that
+a complete set of experimental parameters is still not available (to our
 konwledge). We are aware, though, of the drawbacks of this choice, say, the
@@
 \item[(c)] We will explore crowd densities allowing body compressions up to
-$0.1\,$m. This corresponds to remarkably high densities, since our own 
-(real-life) estimates do not surpass $0.065\,$m (see 
-Section~\ref{experimental}). Therefore, the extremely high density 
-scenarios (say, above $0.065\,$m) will be considered for the purpose of a 
-tendency, but not as a common real-life situation. No casualties due to high 
-pressures will be further considered.
+$0.1\,$m. This corresponds to remarkably high densities, since our own  (real-
+life) estimates do not surpass $0.065\,$m (see  Section~\ref{experimental}).
+Therefore, the extremely high density  scenarios (say, above $0.065\,$m) will be
+considered for the purpose of a  tendency, but not as a common real-life
+situation. No casualties due to high  pressures will be further considered.
 
@@
 not introduce any direct link between $\mathcal{K}$ and $\mathcal{K}_c$. We
-will investigate the interplay between both in Section~\ref{corridor}. 
-\\
+will investigate the interplay between both in Section~\ref{corridor}.  \\
 
 In order to keep the model as simple as possible, we will only consider
-isotropic pedestrian interactions, since anisotropic
-interactions do not play a relevant role at high densities. \\
+isotropic pedestrian interactions, since anisotropic interactions do not play a
+relevant role at high densities. \\
 
@@
 positions and velocities were recorded every $0.05\,$sec, but post-processing
-computing was done over samples acquired at least every $2\,$sec., in order to avoid 
-data correlations. Those pedestrians leaving the simulations box were 
+computing was done over samples acquired at least every $2\,$sec., in order to
+avoid  data correlations. Those pedestrians leaving the simulations box were
 re-introduced into the box, on the opposite side (periodic boundary
@@
 We show the consequences of modifying the body force coefficient $k_n$ on the
-evacuation dynamics. Recall that this coefficient is associated 
-to the compression of the human body. \\
+evacuation dynamics. Recall that this coefficient is associated  to the
+compression of the human body. \\
 
 Fig.~\ref{vd_vs_te} shows the evacuation time as a function of the pedestrian's
-desired velocity for different values of $k_n$. The evacuation 
-time is defined as the time lapsed until 80\% of the pedestrians have 
-left the room. In this section we will focus on the evacuation time for 
-$2\,$m/s$<v_d<10\,$m/s.\\
+desired velocity for different values of $k_n$. The evacuation  time is defined
+as the time lapsed until 80\% of the pedestrians have  left the room. In this
+section we will focus on the evacuation time for  $2\,$m/s$<v_d<10\,$m/s.\\
 
@@
 \centering
-\includegraphics[width=0.7\columnwidth]
-{./vd_vs_te_N225.eps}
+\includegraphics[width=0.7\columnwidth]{./vd_vs_te_N225.eps}
+
 \caption{\label{vd_vs_te}Mean evacuation time (s) vs. the pedestrian’s desired
 velocity (m/s) for a bottleneck. The room was 20 m x 20 m size. The door was
-0.92 m width (two pedestrians' width). Mean values were computed from 10 evacuation processes. 225 
-pedestrians were initially placed in a square lattice with a random initial 
-velocity. Each process was finished when 158 pedestrians left the room. The 
-different symbols indicate the $k_n$ value corresponding to the body force (see 
-the label). The crosses correspond to the Helbing's original SFM parameter, the 
-up-triangles correspond to the value measured in 
-Ref.~\cite{melvin1988aatd}, squares correspond 
-to zero body force and circles correspond to an extreme value of stiffness (one 
-order of magnitude higher than the original SFM). The 
- down triangles correspond to an intermediate value between the empirical value 
-presented in Ref.~\cite{melvin1988aatd} and the one provided by Helbing in 
-Ref.~\cite{helbing_2000} }
+0.92 m width (two pedestrians' width). Mean values were computed from 10
+evacuation processes. 225  pedestrians were initially placed in a square lattice
+with a random initial  velocity. Each process was finished when 158 pedestrians
+left the room. The  different symbols indicate the $k_n$ value corresponding to
+the body force (see  the label). The crosses correspond to the Helbing's
+original SFM parameter, the  up-triangles correspond to the value measured in
+Ref.~\cite{melvin1988aatd}, squares correspond  to zero body force and circles
+correspond to an extreme value of stiffness (one  order of magnitude higher than
+the original SFM). The   down triangles correspond to an intermediate value
+between the empirical value  presented in Ref.~\cite{melvin1988aatd} and the one
+provided by Helbing in  Ref.~\cite{helbing_2000} }
+
 \end{figure}
 
-Three behavioral patterns can be distinguished in Fig.~\ref{vd_vs_te}. 
-Each pattern can display a positive slope, a negative slope
-or both. The interval in which the slope is positive means that the 
-harder the pedestrians try to get out (higher $v_d$), the 
-longer it takes them to evacuate. This is the Faster-is-slower 
-(FIS) regime. Conversely, the interval in which the slope is 
-negative  corresponds to a Faster-is-Faster (FIF) regime (the 
-harder they try, the quicker they leave).\\
-
-Fig.~\ref{vd_vs_te}  shows either FIS or FIF, and a FIS+FIF pattern
-for desired velocities $v_d>1.2\,$m/s. The 
-evacuation time attains a FIS+FIF pattern for compression coefficients below 
-$k=1.2\,$E5. This means that ``soft'' individuals can attain this 
-behavioral pattern.  Notice that higher values of $k_n$ allow 
-only FIS or FIF patterns. For the highest explored value $k_n=1.2\,$E6, no 
-FIS can be seen at all. Besides, the evacuation pattern for $k_n = 0$ and $k_n 
-= 2.6\,$E4 are very similar since the body force intensity is of the same order
-or less than the social 
-force for these stiffness values. \\
-
-Despite the presence of the FIS or FIF pattern, the evacuation time at a 
-fixed value of $v_d$ decreases for increasing values of $k_n$ (within the examined interval). 
-This means that stiffer pedestrians evacuate faster than soft pedestrians. 
-To further investigate this 
-phenomenon, we computed the mean velocity of the whole crowd as a function of the 
-stiffness $k_n$. Fig.~\ref{kn_vs_vx_bottleneck} shows the actual mean velocity in the 
+Three behavioral patterns can be distinguished in Fig.~\ref{vd_vs_te}.  Each
+pattern can display a positive slope, a negative slope or both. The interval in
+which the slope is positive means that the  harder the pedestrians try to get
+out (higher $v_d$), the  longer it takes them to evacuate. This is the Faster-
+is-slower  (FIS) regime. Conversely, the interval in which the slope is
+negative  corresponds to a Faster-is-Faster (FIF) regime (the  harder they try,
+the quicker they leave).\\
+
+Fig.~\ref{vd_vs_te}  shows either FIS or FIF, and a FIS+FIF pattern for desired
+velocities $v_d>1.2\,$m/s. The  evacuation time attains a FIS+FIF pattern for
+compression coefficients below  $k=1.2\,$E5. This means that ``soft''
+individuals can attain this  behavioral pattern.  Notice that higher values of
+$k_n$ allow  only FIS or FIF patterns. For the highest explored value
+$k_n=1.2\,$E6, no  FIS can be seen at all. Besides, the evacuation pattern for
+$k_n = 0$ and $k_n  = 2.6\,$E4 are very similar since the body force intensity
+is of the same order or less than the social  force for these stiffness values.
+\\
+
+Despite the presence of the FIS or FIF pattern, the evacuation time at a  fixed
+value of $v_d$ decreases for increasing values of $k_n$ (within the examined
+interval).  This means that stiffer pedestrians evacuate faster than soft
+pedestrians.  To further investigate this  phenomenon, we computed the mean
+velocity of the whole crowd as a function of the  stiffness $k_n$.
+Fig.~\ref{kn_vs_vx_bottleneck} shows the actual mean velocity in the
 $x-$direction as a function of the stiffness $k_n$ for three different desired
-velocities. In all cases, the velocity increases with the stiffness. The most significative 
-increment of velocity is in the interval $k_n>\,10^{4}$. \\
+velocities. In all cases, the velocity increases with the stiffness. The most
+significative  increment of velocity is in the interval $k_n>\,10^{4}$. \\
 
@@
 \subfloat[]{\includegraphics[width=0.7\columnwidth]{./kn_vs_vx_bottleneck.eps}}\\
-\caption[width=0.47\columnwidth]{Mean velocity in the $x-$direction as a function 
-of the stiffness level $k_n$ for different desired velocities (see label). The 
-data corresponds to a bottleneck with periodic boundary conditions (re-injecting 
-pedestrians). The average was taken every five seconds once the crowd reaches the 
-stationary state ($t=20\,$s) until the end of the simulation ($t=1000\,$s). 
-Color online only. }
+\caption[width=0.47\columnwidth]{Mean velocity in the $x-$direction as a
+function  of the stiffness level $k_n$ for different desired velocities (see
+label). The  data corresponds to a bottleneck with periodic boundary conditions
+(re-injecting  pedestrians). The average was taken every five seconds once the
+crowd reaches the  stationary state ($t=20\,$s) until the end of the simulation
+($t=1000\,$s).  Color online only. }
 \label{kn_vs_vx_bottleneck}
@@
 
-The existence of the FIF phenomenon for only ``stiff'' individuals opens many questions 
-on the microscopic dynamics of pedestrians. We may presume that contacts 
-between pedestrians are quite different for soft individuals than for stiff 
-individuals. Thus, we proceed to study the dynamics of contacting pedestrians, regardless of the overlap 
-effects. We will assimilate the pedestrians as nodes and the whole crowd as a 
-network. We will link any two individuals whenever they get in physical 
-contact (\textit{i.e.} $r_{ij} \leq R_{ij}$).\\
+The existence of the FIF phenomenon for only ``stiff'' individuals opens many
+questions  on the microscopic dynamics of pedestrians. We may presume that
+contacts  between pedestrians are quite different for soft individuals than for
+stiff  individuals. Thus, we proceed to study the dynamics of contacting
+pedestrians, regardless of the overlap  effects. We will assimilate the
+pedestrians as nodes and the whole crowd as a  network. We will link any two
+individuals whenever they get in physical  contact (\textit{i.e.} $r_{ij} \leq
+R_{ij}$).\\
 
@@
 average of the degree over all the nodes (pedestrians) and over the whole
-sampled interval. We computed mean values only after the system reached the stationary 
-state, that is, after a well-formed bulk has been established.\\
-
-Notice that the mean degree increases as $v_d$ increases, as expected. This expresses the fact that
-higher $v_d$ values accomplish higher densities, forcing individuals to touch each 
-other. For a given $v_d$, the mean degree reduces as the $k_n$ 
-value increases. A noticeable decrease in the mean degree can be seen for the 
-highest explored value of $k_n$. This opens the question on how would
+sampled interval. We computed mean values only after the system reached the
+stationary  state, that is, after a well-formed bulk has been established.\\
+
+Notice that the mean degree increases as $v_d$ increases, as expected. This
+expresses the fact that higher $v_d$ values accomplish higher densities, forcing
+individuals to touch each  other. For a given $v_d$, the mean degree reduces as
+the $k_n$  value increases. A noticeable decrease in the mean degree can be seen
+for the  highest explored value of $k_n$. This opens the question on how would
 this affect the sliding friction among pedestrians.\\
@@
 very low desired velocities (say, $v_d<2\,$m/s), we can see that the mean
-overlap is an increasing function of $v_d$ (withing the studied
-range of $v_d$ and $k_n$).\\
+overlap is an increasing function of $v_d$ (withing the studied range of $v_d$
+and $k_n$).\\
 
@@
 \centering
-    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./degree_vs_vd_multi_kn.eps}\label{degree_vd}}\ 
-    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./overlap_vs_vd_multi_kn.eps}\label{overlap_vd}}\\
-\caption[width=0.47\columnwidth]{(a) Mean degree as a function of the pedestrian’s desired velocity (m/s).
-(b) Mean overlap as a function of the pedestrians desired velocity.
-Each symbol indicates the $k_n$ value corresponding to the body force (see the labels).
-The data corresponds to a bottleneck with periodic boundary conditions (re-injecting pedestrians).
-The average was taken over time and the pedestrians in the bottleneck.
-The sampling was done every five seconds once the crowd reached the stationary state (say, $t=20\,$s) until the end of the simulation ($t=1000\,$s).
-Color online only.}
+\subfloat[]{\includegraphics[width=0.49\columnwidth]
+{./degree_vs_vd_multi_kn.eps}\label{degree_vd}}\ 
+\subfloat[]{\includegraphics[width=0.49\columnwidth]
+{./overlap_vs_vd_multi_kn.eps}\label{overlap_vd}}\\
+\caption[width=0.47\columnwidth]{(a) Mean degree as a function of the
+pedestrian’s desired velocity (m/s). (b) Mean overlap as a function of the
+pedestrians desired velocity. Each symbol indicates the $k_n$ value
+corresponding to the body force (see the labels). The data corresponds to a
+bottleneck with periodic boundary conditions (re-injecting pedestrians). The
+average was taken over time and the pedestrians in the bottleneck. The sampling
+was done every five seconds once the crowd reached the stationary state (say,
+$t=20\,$s) until the end of the simulation ($t=1000\,$s). Color online only.}
 \label{degree_overlap_vd}
@@
 
-The regime for $v_d<2\,$m/s is qualitatively different from the clogged regime since most of the 
-pedestrians are not touching each other (as was already observed in Ref~\cite{dorso_2005,dorso_2011}). The only pedestrians who touch each 
-other are the ones who are being re-injected on the opposite side of the room.
-These collide with the bulk, providing some kind of overlap during very short time. We will
-not analize this regime.\\
-
-Besides, for a given $v_d>2\,$m/s, the overlap increases as the $k_n$ value decreases. 
-This can be explained by considering the bulk at a (quasi) equilibrium situation. 
-The social and compression forces counterbalance the desired force. Thus, for any fixed $v_d$,
-the product $k_n \times (R_{ij}-r_{ij})$ remains (almost) fixed. Any decrease in $k_n$
-allows a more significant intrusion. This (partially) supports the argument that
-the sliding friction should weaken for stiffer pedestrians (say increasing
-$k_n$ values). \\
-
-The sliding friction reduction appears as the first feature for enhancing
-the overall evacuation performance. Either reducing the mean overlap and the mean degree
-tend to diminish the mean sliding 
-friction within the crowd. 
-Notice, however, that switching from a FIS regime (positive slope) to a  FIF 
-regime (negative slope) in Fig.~\ref{vd_vs_te} appears as a more complex 
-phenomenon. We will focus on this issue in an upcoming investigation.\\
-
-The body force 
-has a notorious impact in the number of pedestrians touching each other (say, 
-the degree). This is clearly depicted in Fig.~\ref{network_bottleneck} where 
-four different configurations of the evacuation dynamics are shown. The 
-configurations represent 225 pedestrians trying to escape through a door (see 
-caption for details). The colors correspond to the degree of each node 
-(pedestrian), and the lines between pedestrians represent the contacts among 
-them.\\
+The regime for $v_d<2\,$m/s is qualitatively different from the clogged regime
+since most of the  pedestrians are not touching each other (as was already
+observed in Ref~\cite{dorso_2005,dorso_2011}). The only pedestrians who touch
+each  other are the ones who are being re-injected on the opposite side of the
+room. These collide with the bulk, providing some kind of overlap during very
+short time. We will not analize this regime.\\
+
+Besides, for a given $v_d>2\,$m/s, the overlap increases as the $k_n$ value
+decreases.  This can be explained by considering the bulk at a (quasi)
+equilibrium situation.  The social and compression forces counterbalance the
+desired force. Thus, for any fixed $v_d$, the product $k_n \times
+(R_{ij}-r_{ij})$ remains (almost) fixed. Any decrease in $k_n$ allows a more
+significant intrusion. This (partially) supports the argument that the sliding
+friction should weaken for stiffer pedestrians (say increasing $k_n$ values). \\
+
+The sliding friction reduction appears as the first feature for enhancing the
+overall evacuation performance. Either reducing the mean overlap and the mean
+degree tend to diminish the mean sliding  friction within the crowd.  Notice,
+however, that switching from a FIS regime (positive slope) to a  FIF  regime
+(negative slope) in Fig.~\ref{vd_vs_te} appears as a more complex  phenomenon.
+We will focus on this issue in an upcoming investigation.\\
+
+The body force  has a notorious impact in the number of pedestrians touching
+each other (say,  the degree). This is clearly depicted in
+Fig.~\ref{network_bottleneck} where  four different configurations of the
+evacuation dynamics are shown. The  configurations represent 225 pedestrians
+trying to escape through a door (see  caption for details). The colors
+correspond to the degree of each node  (pedestrian), and the lines between
+pedestrians represent the contacts among  them.\\
 
@@
 \centering
-    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_vd2_kn0.eps}\label{network_vd2_kn0}}\ 
-    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_vd10_kn0.eps}\label{network_vd10_kn0}}\\
-        \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_vd2_kn1200000.eps}\label{network_vd2_kn1200000}}\ 
-    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_vd10_kn1200000.eps}\label{network_vd10_kn1200000}}\\
-\caption[width=0.47\columnwidth]{Snapshots of the contact networks of a 225 pedestrian evacuation through a bottleneck.
-The door is placed at $(x,y)=(20,10)\,$m, the width of the door is 0.92$\,$m (equivalent to 2 pedestrian\textsc{\char13}s diameter).
-The lines that connect the nodes (pedestrians) represent the contact between them.
-The color represents the degree (the number of pedestrians with which it is connected).
-(a) and (b) correspond to a simulation without body force with $v_d=$2 and $v_d=$10 respectively.
-(c) and (d) correspond to simulations with $k_n=1.2\,$E6 with $v_d=$2 and $v_d=$10 respectively.
-Color online only.}
+\subfloat[]{\includegraphics[width=0.49\columnwidth]
+{./network_vd2_kn0.eps}\label{network_vd2_kn0}}\ 
+\subfloat[]{\includegraphics[width=0.49\columnwidth]
+{./network_vd10_kn0.eps}\label{network_vd10_kn0}}\\
+\subfloat[]{\includegraphics[width=0.49\columnwidth]
+{./network_vd2_kn1200000.eps}\label{network_vd2_kn1200000}}\ 
+\subfloat[]{\includegraphics[width=0.49\columnwidth]
+{./network_vd10_kn1200000.eps}\label{network_vd10_kn1200000}}\\
+
+\caption[width=0.47\columnwidth]{Snapshots of the contact networks of a 225
+pedestrian evacuation through a bottleneck. The door is placed at
+$(x,y)=(20,10)\,$m, the width of the door is 0.92$\,$m (equivalent to 2
+pedestrian\textsc{\char13}s diameter). The lines that connect the nodes
+(pedestrians) represent the contact between them. The color represents the
+degree (the number of pedestrians with which it is connected). (a) and (b)
+correspond to a simulation without body force with $v_d=$2 and $v_d=$10
+respectively. (c) and (d) correspond to simulations with $k_n=1.2\,$E6 with
+$v_d=$2 and $v_d=$10 respectively. Color online only.}
 \label{network_bottleneck}
@@
 
-The four configurations corresponds to two different $v_d$ and two different $k_n$ values (say, the  minimum and maximum explored values).
-Fig.~\ref{network_vd2_kn0} and Fig.~\ref{network_vd10_kn0} show snapshots for $k_n=0$, at the desired velocities of 2$\,$m/s and 10$\,$m/s, respectively.
-Fig.~\ref{network_vd2_kn1200000} and Fig.~\ref{network_vd10_kn1200000} show similar situations, but for  $k_n=1.2\,$E6.
-As expected, increasing the desired velocity compresses the crowd towards the exit.
-\\
-
-The four snapshots in Fig.~\ref{network_bottleneck} confirm (visually) the fact that more rigid pedestrians ease the crowded environment, widening the occupied region.
-At $v_d=10\,$m/s (the maximum explored velocity), it can hardly be found pedestrians with degree 6 when $k_n=1.2\,$E6, while a lot of them are present for $k_n$=0.\\
-
-The clusterization of the pedestrians has a significant impact on the blocking clusters (the group of pedestrians that clog the exit).
-Fig.~\ref{pbc_vs_vd_multi_kn} shows the blocking cluster probability as a function of the desired velocity for different $k_n$ values (see caption for details).
-The blocking clusters become more probable for high desired velocity, since the clogged area gets more compact as $v_d$ increases (for any fixed value of $k_n$).
-But, the most remarkable fact in Fig.~\ref{pbc_vs_vd_multi_kn} is that increasing the body stiffness reduces the blocking cluster probability for any fixed value of $v_d$.
-Recall from Ref.~\cite{dorso_2005} that the evacuation time is controlled by the blocking.
-Thus, increasing the body stiffness affects the presence of the blocking clusters, and consequently improves the evacuation time.
-This raises as a second feature for enhancing the overall evacuation performance.
-\\
+The four configurations corresponds to two different $v_d$ and two different
+$k_n$ values (say, the  minimum and maximum explored values).
+Fig.~\ref{network_vd2_kn0} and Fig.~\ref{network_vd10_kn0} show snapshots for
+$k_n=0$, at the desired velocities of 2$\,$m/s and 10$\,$m/s, respectively.
+Fig.~\ref{network_vd2_kn1200000} and Fig.~\ref{network_vd10_kn1200000} show
+similar situations, but for  $k_n=1.2\,$E6. As expected, increasing the desired
+velocity compresses the crowd towards the exit. \\
+
+The four snapshots in Fig.~\ref{network_bottleneck} confirm (visually) the fact
+that more rigid pedestrians ease the crowded environment, widening the occupied
+region. At $v_d=10\,$m/s (the maximum explored velocity), it can hardly be found
+pedestrians with degree 6 when $k_n=1.2\,$E6, while a lot of them are present
+for $k_n$=0.\\
+
+The clusterization of the pedestrians has a significant impact on the blocking
+clusters (the group of pedestrians that clog the exit).
+Fig.~\ref{pbc_vs_vd_multi_kn} shows the blocking cluster probability as a
+function of the desired velocity for different $k_n$ values (see caption for
+details). The blocking clusters become more probable for high desired velocity,
+since the clogged area gets more compact as $v_d$ increases (for any fixed value
+of $k_n$). But, the most remarkable fact in Fig.~\ref{pbc_vs_vd_multi_kn} is
+that increasing the body stiffness reduces the blocking cluster probability for
+any fixed value of $v_d$. Recall from Ref.~\cite{dorso_2005} that the evacuation
+time is controlled by the blocking. Thus, increasing the body stiffness affects
+the presence of the blocking clusters, and consequently improves the evacuation
+time. This raises as a second feature for enhancing the overall evacuation
+performance. \\
 
@@
 {./pbc_vs_vd_multi_kn.eps}
-\caption{\label{pbc_vs_vd_multi_kn} Blocking cluster probability as a function of $v_d$ for different stiffness levels (see label).
-The probability is calculated as the amount of time a blocking cluster is present divided by the overall simulation time.
-The situation corresponds to a bottleneck with 225 pedestrians under periodic boundary conditions (re-injection of pedestrians once they left the room).
-The sampled interval was set to $t_f =$ 1000$\,$s.
-Color online only.
-}
+\caption{\label{pbc_vs_vd_multi_kn} Blocking cluster probability as a function 
+of $v_d$ for different stiffness levels (see label). The probability is 
+calculated as the amount of time a blocking cluster is present divided by the 
+overall simulation time. The situation corresponds to a bottleneck with 225 
+pedestrians under periodic boundary conditions (re-injection of pedestrians once
+ they left the room). The sampled interval was set to $t_f =$ 1000$\,$s. 
+ Color online only. }
 \end{figure}
 
-We may summarize this Section as follows.
-We explored the parameter space along $v_d$ and $k_n$ for the bottleneck situation.
-This is similar to explore the dimensionless plane $(\mathcal{A},\mathcal{K}_c)$.
-Soft pedestrians attain a FIS or FIS+FIF evacuation pattern but, stiff pedestrians (for any fixed $\mathcal{A}$ value within the explored range) exhibit a single FIF pattern.
-Stiffness affects either the presence of the blocking clusters and the pedestrians overlap.
-The less they overlap, the less intense becomes the sliding friction among them.
-Additionally, the fewer the blocking clusters the easier they get out.
-\\
+We may summarize this Section as follows. We explored the parameter space along
+$v_d$ and $k_n$ for the bottleneck situation. This is similar to explore the
+dimensionless plane $(\mathcal{A},\mathcal{K}_c)$. Soft pedestrians attain a FIS
+or FIS+FIF evacuation pattern but, stiff pedestrians (for any fixed
+$\mathcal{A}$ value within the explored range) exhibit a single FIF pattern.
+Stiffness affects either the presence of the blocking clusters and the
+pedestrians overlap. The less they overlap, the less intense becomes the sliding
+friction among them. Additionally, the fewer the blocking clusters the easier
+they get out. \\
 
@@
 We show the effects of varying the body force coefficient $k_n$ on the
-collective dynamics. We will keep $v_d$ (or $\mathcal{A}$) 
-fixed along this Section. \\
-
-We first computed the contact network in the same way 
-as in the bottleneck geometry. Fig.~\ref{degree_dens} shows the 
-mean degree as a function of the global density for different $k_n$ values (see 
-caption for details). The mean degree vanishes at very low 
-densities because the pedestrians do not touch each other. When the density 
-surpasses 4.5, a few pedestrians start to touch each other, 
-raising the mean degree. As the density continuous increasing, 
-the mean degree approaches the asymptotic value 
-of six. Degree six corresponds to the maximum packing density for identical 
-hard circles.\\
+collective dynamics. We will keep $v_d$ (or $\mathcal{A}$)  fixed along this
+Section. \\
+
+We first computed the contact network in the same way  as in the bottleneck
+geometry. Fig.~\ref{degree_dens} shows the  mean degree as a function of the
+global density for different $k_n$ values (see  caption for details). The mean
+degree vanishes at very low  densities because the pedestrians do not touch each
+other. When the density  surpasses 4.5, a few pedestrians start to touch each
+other,  raising the mean degree. As the density continuous increasing,  the mean
+degree approaches the asymptotic value  of six. Degree six corresponds to the
+maximum packing density for identical  hard circles.\\
 
@@
 
-It is worth noting from Fig.~\ref{degree_dens} that ``stiff''
-pedestrians exhibit a sharper transition to the maximum packing density than 
-the ``soft'' pedestrians. We further checked this phenomenon by counting the 
-number of loops of three nodes (say, the triangles) present in the network. 
-This magnitude was reported to be a sensitive magnitude for characterizing the 
-jamming transition in a compressed granular packing (see 
-Ref.~\cite{pugnaloni_2013} for details).  As can be seen in 
-Fig.~\ref{triangles}, the ``stiff'' pedestrians share more triangles 
-than the ``soft'' ones.   \\
+It is worth noting from Fig.~\ref{degree_dens} that ``stiff'' pedestrians
+exhibit a sharper transition to the maximum packing density than  the ``soft''
+pedestrians. We further checked this phenomenon by counting the  number of loops
+of three nodes (say, the triangles) present in the network.  This magnitude was
+reported to be a sensitive magnitude for characterizing the  jamming transition
+in a compressed granular packing (see  Ref.~\cite{pugnaloni_2013} for details).
+As can be seen in  Fig.~\ref{triangles}, the ``stiff'' pedestrians share more
+triangles  than the ``soft'' ones.\\
 
@@
 we present in Fig.~\ref{network_corridor} two snapshots of the corridor at the
-stationary situation. Fig.~\ref{network_d6_kn0} corresponds to 
-$k_n=0$, while Fig.~\ref{network_d6_knE5} corresponds to $k_n=1.2$~E5. The 
-former shows a somewhat disordered network, while the latter exhibits an almost 
-completely ordered lattice. The missing triangles in Fig.~\ref{network_d6_kn0} 
-are replaced by other polygons of more than three edges.    \\
+stationary situation. Fig.~\ref{network_d6_kn0} corresponds to  $k_n=0$, while
+Fig.~\ref{network_d6_knE5} corresponds to $k_n=1.2$~E5. The  former shows a
+somewhat disordered network, while the latter exhibits an almost  completely
+ordered lattice. The missing triangles in Fig.~\ref{network_d6_kn0}  are
+replaced by other polygons of more than three edges. \\
 
@@
 \centering
-    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_d6_kn0.eps}\label{network_d6_kn0}}\ 
-    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./network_d6_knE5.eps}\label{network_d6_knE5}}\\
-\caption[width=0.47\columnwidth]{Contact network of the pedestrians along the corridor at time $t=50\,$s.
-The global density was $\rho=6$.
-The lines that connect the nodes (pedestrians) represent the contact between them.
-The colors stand for the degree of the node (the number of pedestrians that are in contact with him/her).
-The corridor was 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
-(a) corresponds to a simulation without body force and (b) corresponds to a simulation with $k_n=1.2$~E5.
-The friction coefficient and the other SFM parameters are the same as in Section \ref{bottleneck}.
-Color online only.}
+\subfloat[]{\includegraphics[width=0.49\columnwidth]
+{./network_d6_kn0.eps}\label{network_d6_kn0}}\ 
+\subfloat[]{\includegraphics[width=0.49\columnwidth]
+{./network_d6_knE5.eps}\label{network_d6_knE5}}\\
+\caption[width=0.47\columnwidth]{Contact network of the pedestrians along the 
+corridor at time $t=50\,$s. The global density was $\rho=6$.  The lines that 
+connect the nodes (pedestrians) represent the contact between them. The colors 
+stand for the degree of the node (the number of pedestrians that are in contact 
+with him/her). The corridor was 28~m $\times$ 22~m with periodic boundary 
+conditions and $v_d=1$. (a) corresponds to a simulation without body force and 
+(b) corresponds to a simulation with $k_n=1.2$~E5. The friction coefficient and 
+the other SFM parameters are the same as in Section \ref{bottleneck}. Color 
+online only.}
 \label{network_corridor}
@@
 
-We find these topological magnitudes useful for comparing the 
-pedestrian behavior in the 
-corridor geometry with respect to the bottleneck geometry. A re-examination of 
-Fig.~\ref{degree_dens} (corridor) and Fig.~\ref{degree_vd} (bottleneck) reveal 
-that the pedestrian stiffness $k_n$ affects differently the way they contact 
-each other. The mean degree increases for ``stiff'' pedestrians moving along 
-the corridor as the density increased with a sharp increase at
- $5\,$p/m$^2$. Conversely, the mean degree 
-increases for ``soft'' pedestrians in the bottleneck situation.\\
-
-Fig.~\ref{network_bottleneck} and 
-Fig.~\ref{network_corridor} illustrate the connectivity differences between 
-the bottleneck and the corridor situation. The bulk in 
-Fig.~\ref{network_bottleneck} appears more heavily connected among ``soft'' 
-pedestrians than among ``stiff'' pedestrians (see both snapshots at $v_d=10$). 
-The opposite occurs in Fig.~\ref{network_corridor}. This discrepancy seems to 
-be related to the boundary conditions, since the same SFM parameters were 
-applied on both situations. We may speculate that this phenomenon occurs 
-because, in the corridor, the lateral walls act like a 
-confining barrier that 
+We find these topological magnitudes useful for comparing the  pedestrian
+behavior in the  corridor geometry with respect to the bottleneck geometry. A
+re-examination of  Fig.~\ref{degree_dens} (corridor) and Fig.~\ref{degree_vd}
+(bottleneck) reveal  that the pedestrian stiffness $k_n$ affects differently the
+way they contact  each other. The mean degree increases for ``stiff''
+pedestrians moving along  the corridor as the density increased with a sharp
+increase at  $5\,$p/m$^2$. Conversely, the mean degree  increases for ``soft''
+pedestrians in the bottleneck situation.\\
+
+Fig.~\ref{network_bottleneck} and  Fig.~\ref{network_corridor} illustrate the
+connectivity differences between  the bottleneck and the corridor situation. The
+bulk in  Fig.~\ref{network_bottleneck} appears more heavily connected among
+``soft''  pedestrians than among ``stiff'' pedestrians (see both snapshots at
+$v_d=10$).  The opposite occurs in Fig.~\ref{network_corridor}. This discrepancy
+seems to  be related to the boundary conditions, since the same SFM parameters
+were  applied on both situations. We may speculate that this phenomenon occurs
+because, in the corridor, the lateral walls act like a  confining barrier that
 forces the ``stiff'' pedestrian to increase his (her) contacts. On the contrary,
@@
 
-The above results represent an important step in the 
-investigation. The inter-pedestrian connectivity differences between the bottleneck geometry 
-and the corridor geometry were not expected and opens two major questions:
- how do the pedestrians interact with the walls as
-a function of the body stiffness, and consequently, how does 
-this affect the flux across the corridor.\\
+The above results represent an important step in the  investigation. The inter-
+pedestrian connectivity differences between the bottleneck geometry  and the
+corridor geometry were not expected and opens two major questions:  how do the
+pedestrians interact with the walls as a function of the body stiffness, and
+consequently, how does  this affect the flux across the corridor.\\
 
@@
 \includegraphics[width=0.7\columnwidth]{./kn_vs_vx_corridor.eps}
-\caption{\label{kn_vs_vx_corridor} Mean velocity in the longitudinal coordinate $(v_x)$
- as a function of the stiffness $k_n$ for three different global densities (see label in the plot). 
- The measurements correspond to a corridor of 28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$.
- The average was taken along the corridor and along the simulated time. Color online only.      }
+\caption{\label{kn_vs_vx_corridor} Mean velocity in the longitudinal coordinate
+$(v_x)$ as a function of the stiffness $k_n$ for three different global 
+densities (see label in the plot). The measurements correspond to a corridor of 
+28~m $\times$ 22~m with periodic boundary conditions and $v_d=1$. The average 
+was taken along the corridor and along the simulated time. Color online only.}
 \end{figure}
 
-The $\langle v_x\rangle$ values in Fig.~\ref{kn_vs_vx_corridor} 
-were computed at densities $\rho\geq 5.5$. According to 
-Fig.~\ref{overlap_dens},
-at these densities, the overlaps among pedestrians attain significant values. Furthermore, 
-stiffness values $k_n\geq 10^4$ move the system to a more heavily connected 
-stage, and thus, pedestrians have no choice but to walk at 
-(almost) the same speed as his (her) neighbors. This 
-behavior may be envisaged as the passage from a ``free'' 
-walking movement to a  constrained movement as the stiffness increases. A more 
-physical picture would assimilate the former as a ``fluid-like 
-state'' and the latter as a ``solid-like state''. When the stiffness is 
-very high (say $k_n=$1.2~E6), all the pedestrians 
-are expected to walk at a common velocity. The 
-pedestrians that walk in physical contact with the wall are the ones who 
-determine the velocity of the whole crowd, as discussed 
-below.\\
-
-Fig.~\ref{vx_profile} shows the velocity profile ($\langle v_x \rangle$ vs.
-the transversal coordinate $y$) for different $k_n$ values.
-For $k_n=0$, we can see a parabolic-like velocity profile which means that the friction with the walls reduces the speed of pedestrians.
-The velocity profile resembles the Poiseuille flow (similar to Newtonian and incompressible fluids in a laminar regime).
-This behavior was also observed in empirical measurements of crowd dynamics reported in Ref.~\cite{zhang2013empirical}.
-But as $k_n$ increases the velocity profile flattens until becoming (almost) uniform (see Fig.~\ref{vx_profile} for $k_n=1.2\,$E6).
-In this scenario, $v_x$ attains a much lower  value  than in the case of soft pedestrians ($k_n=$0).\\
-
-From the results displayed above, we realize that the crowd behaves like a solid for very stiff pedestrians.
-This means that the crowd can not be easily ``deformed''.
-In this context, deformation means that parts of the crowd may be allowed to move faster than other parts of the crowd.
-\\
-
-The strain rate tensor displays the rate of change of the deformation of a body in the vicinity of a given point.
- We consider the following discrete definition of the strain rate:
+The $\langle v_x\rangle$ values in Fig.~\ref{kn_vs_vx_corridor}  were computed
+at densities $\rho\geq 5.5$. According to  Fig.~\ref{overlap_dens}, at these
+densities, the overlaps among pedestrians attain significant values.
+Furthermore,  stiffness values $k_n\geq 10^4$ move the system to a more heavily
+connected  stage, and thus, pedestrians have no choice but to walk at  (almost)
+the same speed as his (her) neighbors. This  behavior may be envisaged as the
+passage from a ``free''  walking movement to a  constrained movement as the
+stiffness increases. A more  physical picture would assimilate the former as a
+``fluid-like  state'' and the latter as a ``solid-like state''. When the
+stiffness is  very high (say $k_n=$1.2~E6), all the pedestrians  are expected to
+walk at a common velocity. The  pedestrians that walk in physical contact with
+the wall are the ones who  determine the velocity of the whole crowd, as
+discussed  below.\\
+
+Fig.~\ref{vx_profile} shows the velocity profile ($\langle v_x \rangle$ vs. the
+transversal coordinate $y$) for different $k_n$ values. For $k_n=0$, we can see
+a parabolic-like velocity profile which means that the friction with the walls
+reduces the speed of pedestrians. The velocity profile resembles the Poiseuille
+flow (similar to Newtonian and incompressible fluids in a laminar regime). This
+behavior was also observed in empirical measurements of crowd dynamics reported
+in Ref.~\cite{zhang2013empirical}. But as $k_n$ increases the velocity profile
+flattens until becoming (almost) uniform (see Fig.~\ref{vx_profile} for
+$k_n=1.2\,$E6). In this scenario, $v_x$ attains a much lower  value  than in the
+case of soft pedestrians ($k_n=$0).\\
+
+From the results displayed above, we realize that the crowd behaves like a solid
+for very stiff pedestrians. This means that the crowd can not be easily
+``deformed''. In this context, deformation means that parts of the crowd may be
+allowed to move faster than other parts of the crowd. \\
+
+The strain rate tensor displays the rate of change of the deformation of a body
+in the vicinity of a given point.  We consider the following discrete definition
+of the strain rate:
 
 \begin{equation}
-\dot{\gamma} = \frac{\langle v_x(\mathrm{center})\rangle - \langle v_x(\mathrm{boundary})\rangle }{\left | y(\mathrm{center}) - y(\mathrm{boundary}) \right |} 
+\dot{\gamma} = \frac{\langle v_x(\mathrm{center})\rangle
+ - \langle v_x(\mathrm{boundary})\rangle }{\left | y(\mathrm{center}) 
+ - y(\mathrm{boundary}) \right |} 
 \end{equation}
@@
 \centering
-    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./vx_profile.eps}\label{vx_profile}}\ 
-    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./strain_rate_vs_kn.eps}\label{strain_rate_vs_kn}}\\
-\caption[width=0.47\columnwidth]{(a) Mean velocity in the $x$ coordinate as a function of the transversal coordinate $y$ for three different stiffness values $k_n$ (see the label).
-(b) Strain rate as a function of the stiffness level $k_n$ for three different global density values (see label).
-Data correspond to a corridor of 28$\,$m $\times$ 22$\,$m with periodic boundary conditions and $v_d=1$.
-The global density was $\rho=7 p\,$m$^{-2}$.
-Color online only.
-}
+\subfloat[]{\includegraphics[width=0.49\columnwidth]
+{./vx_profile.eps}\label{vx_profile}}\ 
+\subfloat[]{\includegraphics[width=0.49\columnwidth]
+{./strain_rate_vs_kn.eps}\label{strain_rate_vs_kn}}\\
+
+\caption[width=0.47\columnwidth]{(a) Mean velocity in the $x$ coordinate as a 
+function of the transversal coordinate $y$ for three different stiffness values 
+$k_n$ (see the label). (b) Strain rate as a function of the stiffness level 
+$k_n$ for three different global density values (see label). Data correspond to 
+a corridor of 28$\,$m $\times$ 22$\,$m with periodic boundary conditions and 
+$v_d=1$. The global density was $\rho=7 p\,$m$^{-2}$. Color online only. }
 \label{profile_strain}
@@
 
-Where $\langle \cdot \rangle$ means the average taken over time.
-This definition compares the velocity of the pedestrians close to the wall (boundary) with respect to the velocity of the pedestrians at the center of the corridor (center).
-Thus, $\dot{\gamma}$ vanishes (no deformation) as the stiffness level increases.
-This phenomenon is shown in Fig.~\ref{strain_rate_vs_kn} where we can see that the strain rate drops for high values of $k_n$.
-\\
-
-We conclude this Section by stressing, once again, that stiffer pedestrians attain opposite results in corridors with respect to bottlenecks.
-The walls in the corridors play a critical role that prevents pedestrians from detaching from each other.
-This effect has can be observed as an increment in the connectivity of the contact network and the flattening of the velocity profile (thus reducing the strain rate).
-Very high enough stiffness values stuck the pedestrians leading to a ``solidification'' of the crowd.
-All the pedestrians walk at almost the same velocity at this stage.
-The pedestrians that are in contact with the walls are the ones that determine the velocity of the whole crowd.
-We already analyzed this situation in Ref~\cite{dorso_2019}.
-\\
+Where $\langle \cdot \rangle$ means the average taken over time. This definition
+compares the velocity of the pedestrians close to the wall (boundary) with
+respect to the velocity of the pedestrians at the center of the corridor
+(center). Thus, $\dot{\gamma}$ vanishes (no deformation) as the stiffness level
+increases. This phenomenon is shown in Fig.~\ref{strain_rate_vs_kn} where we can
+see that the strain rate drops for high values of $k_n$. \\
+
+We conclude this Section by stressing, once again, that stiffer pedestrians
+attain opposite results in corridors with respect to bottlenecks. The walls in
+the corridors play a critical role that prevents pedestrians from detaching from
+each other. This effect has can be observed as an increment in the connectivity
+of the contact network and the flattening of the velocity profile (thus reducing
+the strain rate). Very high enough stiffness values stuck the pedestrians
+leading to a ``solidification'' of the crowd. All the pedestrians walk at almost
+the same velocity at this stage. The pedestrians that are in contact with the
+walls are the ones that determine the velocity of the whole crowd. We already
+analyzed this situation in Ref~\cite{dorso_2019}. \\
 
@@
 
-The final stage of our investigation deals with the plausible values of the dimensionless numbers $\mathcal{K}_c$ and $\mathcal{K}$, in comparison to the empirical measurements.
-We vary the body force coefficient ($k_n$) and the friction coefficient ($k_t$) to explore different values of $\mathcal{K}_c$ and $\mathcal{K}$, respectively.\\
-
-We consider the empirical measurements from Ref.~\cite{helbing_2007} corresponding to the fundamental diagram obtained at the entrance of the Jamaraat bridge (see the inset in Fig.~\ref{flow_density_no_body_force}).
-Our aim is to reproduce the qualitative behavior of these measurements.\\
-
-Figs.
-\ref{flow_density} show the pedestrian flow as a function of the global density (fundamental diagram).
-Fig.~\ref{flow_density_no_body_force} corresponds to $\mathcal{K}_c=$ 0 (this is \textit{i.e.} $k_n=0$) while Fig.~\ref{flow_density_body_force} corresponds to $\mathcal{K}_c=$68 corresponding to the original SFM with $k_n=1.2\,$E5.
-Each curve represents different friction values (see the caption for details).\\
-
-According to the empirical measurements at Jamaraat, the flow slows down for high enough densities due to jamming.
-Notice that the original SFM (corresponding to $\mathcal{K}=$137) does not produce the expected slowing down for null body force ($\mathcal{K}_c=$0).
-However, when the body force is present (the original SFM) an ``U'' shape behavior occcurs for densities above 5 p$^{-2}$.\\
-
-The increase in $\mathcal{K}$ to $\mathcal{K} = $ 685 (five times the original SFM value) slows down  the flux for densities above 5 p m$^{-2}$, regardless of the presence of the body force.
-Including the body force, however, produces a subtle increment in the flow for densities higher than 7 p m$^{-2}$ (see orange curve from Fig.~\ref{flow_density_no_body_force}).
-\\
-
-A further increment of $\mathcal{K}$ to $\mathcal{K}=$137 (ten times the original SFM value) attains a plateau ($\rho>5$ p m$^{-2}$) before vanishing at very high densities.
-This occurs on either $\mathcal{K}_c=$ 0 and $\mathcal{K}_c = $ 68.\\
-
-%It is worth mentioning that the SFM contemplates the possibility of overlapping between pedestrians (unlike the models stated in Refs.~\cite{kabalan_2017,jebrane_2019}).
-Despite this hard-to-interpret feature, the SFM can reproduce empirical behaviors of collective pedestrian dynamics.\\
-
-These results suggest that although increasing $\mathcal{K}_c$ slows down the flux, it is still necessary to increase $\mathcal{K}$ (by increasing the friction coefficient $k_t$) to avoid an ``U'' shape behavior for extremely high densities.
-It is still a challenge to find the optimal dimensionless numbers  $(\mathcal{A},\mathcal{K},\mathcal{K}_c)$ for the fundamental diagram.
-Our inspection into the parameter set is a first approach to narrow down the search.\\
+The final stage of our investigation deals with the plausible values of the
+dimensionless numbers $\mathcal{K}_c$ and $\mathcal{K}$, in comparison to the
+empirical measurements. We vary the body force coefficient ($k_n$) and the
+friction coefficient ($k_t$) to explore different values of $\mathcal{K}_c$ and
+$\mathcal{K}$, respectively.\\
+
+We consider the empirical measurements from Ref.~\cite{helbing_2007}
+corresponding to the fundamental diagram obtained at the entrance of the
+Jamaraat bridge (see the inset in Fig.~\ref{flow_density_no_body_force}). Our
+aim is to reproduce the qualitative behavior of these measurements.\\
+
+Figs. \ref{flow_density} show the pedestrian flow as a function of the global
+density (fundamental diagram). Fig.~\ref{flow_density_no_body_force} corresponds
+to $\mathcal{K}_c=$ 0 (this is \textit{i.e.} $k_n=0$) while
+Fig.~\ref{flow_density_body_force} corresponds to $\mathcal{K}_c=$68
+corresponding to the original SFM with $k_n=1.2\,$E5. Each curve represents
+different friction values (see the caption for details).\\
+
+According to the empirical measurements at Jamaraat, the flow slows down for
+high enough densities due to jamming. Notice that the original SFM
+(corresponding to $\mathcal{K}=$137) does not produce the expected slowing down
+for null body force ($\mathcal{K}_c=$0). However, when the body force is present
+(the original SFM) an ``U'' shape behavior occcurs for densities above 5
+p$^{-2}$.\\
+
+The increase in $\mathcal{K}$ to $\mathcal{K} = $ 685 (five times the original
+SFM value) slows down  the flux for densities above 5 p m$^{-2}$, regardless of
+the presence of the body force. Including the body force, however, produces a
+subtle increment in the flow for densities higher than 7 p m$^{-2}$ (see orange
+curve from Fig.~\ref{flow_density_no_body_force}). \\
+
+A further increment of $\mathcal{K}$ to $\mathcal{K}=$137 (ten times the 
+original SFM value) attains a plateau ($\rho>5$ p m$^{-2}$) before vanishing at 
+very high densities. This occurs on either $\mathcal{K}_c=$ 0 and 
+$\mathcal{K}_c = $ 68.\\
+
+%It is worth mentioning that the SFM contemplates the possibility of overlapping
+%between pedestrians (unlike the models stated in
+%Refs.~\cite{kabalan_2017,jebrane_2019}). Despite this hard-to-interpret
+%feature, the SFM can reproduce empirical behaviors of collective pedestrian
+%dynamics.\\
+
+These results suggest that although increasing $\mathcal{K}_c$ slows down the
+flux, it is still necessary to increase $\mathcal{K}$ (by increasing the
+friction coefficient $k_t$) to avoid an ``U'' shape behavior for extremely high
+densities. It is still a challenge to find the optimal dimensionless numbers
+$(\mathcal{A},\mathcal{K},\mathcal{K}_c)$ for the fundamental diagram. Our
+inspection into the parameter set is a first approach to narrow down the
+search.\\
 
 \begin{comment}
-Fig.
-\ref{flow_density} shows the flow as a function of the global density (fundamental diagram).
-\ref{flow_density_no_body_force} corresponds to zero body force (\textit{i.e.} $k_n=0$), Fig.~\ref{flow_density_body_force} corresponds to a body force with $k_n=1.2\,$E5.
-Each curve correspond to a different friction value (see the caption).\\
-
-According to most of the empirical measurements, the flow decreases for high enough values of density because the crowd becomes jammed.
-Notice that the original friction does not produce a reduction of the flow when there is zero body force but when the body force is included (with the original SFM value), the flow reduces from  5 p m$^{-2}$ to 7 p m$^{-2}$ and increases for higher values of density.
-When the friction is five times the original value, the flow reduces for densities higher than 5 p m$^{-2}$ in both cases (with body force and without body force).
-The main qualitative difference is that including the body force produces a subtle increment in the flow for densities higher than 7 p m$^{-2}$.
-When the friction is increased by a factor of ten, the flow reduces or remains constant when the density is higher than 5 p m$^{-2}$ for both cases (with body force and without body force).
-This result suggests that even including the body force, the original SFM requires an increment of the friction in order to reproduce the flow reduction reported in empirical measurements.\\
+Fig. \ref{flow_density} shows the flow as a function of the global density 
+(fundamental diagram). \ref{flow_density_no_body_force} corresponds to zero body
+ force (\textit{i.e.} $k_n=0$), Fig.~\ref{flow_density_body_force} corresponds 
+ to a body force with $k_n=1.2\,$E5. Each curve correspond to a different 
+ friction value (see the caption).\\
+
+According to most of the empirical measurements, the flow decreases for high 
+enough values of density because the crowd becomes jammed. Notice that the 
+original friction does not produce a reduction of the flow when there is zero 
+body force but when the body force is included (with the original SFM value), 
+the flow reduces from  5 p m$^{-2}$ to 7 p m$^{-2}$ and increases for higher 
+values of density. When the friction is five times the original value, the flow 
+reduces for densities higher than 5 p m$^{-2}$ in both cases (with body force 
+and without body force). The main qualitative difference is that including the 
+body force produces a subtle increment in the flow for densities higher than 
+7 p m$^{-2}$. When the friction is increased by a factor of ten, the flow 
+reduces or remains constant when the density is higher than 5 p m$^{-2}$ for 
+both cases (with body force and without body force). This result suggests that 
+even including the body force, the original SFM requires an increment of the 
+friction in order to reproduce the flow reduction reported in empirical 
+measurements.\\
 \end{comment}
@@
 \centering
-    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./flow-density_multifric_nobodyforce.eps}\label{flow_density_no_body_force}}\ 
-    \subfloat[]{\includegraphics[width=0.49\columnwidth]{./flow-density_multifric_bodyforce.eps}\label{flow_density_body_force}}\\
-\caption[width=0.47\columnwidth]{Flow vs.
-global density.
-The flow is calculated in a circular area of $R=1\,$m at the center of the corridor.
-The circular markers correspond to the original friction of the SFM, the "+" symbol corresponds to the friction increased by a factor of five and the triangles correspond to the friction increased by a factor of ten.
-The desired velocity was $v_d=1$ in all the cases.
-(a) corresponds to simulations without body force ($\mathcal{K}_c =$0) and (b) corresponds to a body force with the original value of the body stiffness ($\mathcal{K}_c =$68).
-Color online only.}
+\subfloat[]{\includegraphics[width=0.49\columnwidth]
+{./flow-density_multifric_nobodyforce.eps}\label{flow_density_no_body_force}}\ 
+\subfloat[]{\includegraphics[width=0.49\columnwidth]
+{./flow-density_multifric_bodyforce.eps}\label{flow_density_body_force}}\\
+\caption[width=0.47\columnwidth]{Flow vs. global density. The flow is calculated
+in a circular area of $R=1\,$m at the center of the corridor. The circular 
+markers correspond to the original friction of the SFM, the "+" symbol 
+corresponds to the friction increased by a factor of five and the triangles 
+correspond to the friction increased by a factor of ten. The desired velocity 
+was $v_d=1$ in all the cases. (a) corresponds to simulations without body force 
+($\mathcal{K}_c =$0) and (b) corresponds to a body force with the original value
+ of the body stiffness ($\mathcal{K}_c =$68). Color online only.}
 \label{flow_density}
@@
 
-Having adopted as fundamental philosophy of work that the parameters of the SFM should be properly determined by requiring that the model properly reproduces well established experimental data, we explored the effect on the pedestrians dynamics of the (sometimes neglected) body force in the framework of the SFM.
-We showed that the stiffness coefficient ($k_n$) has a significant impact on the evacuation dynamics (bottleneck) and also in the dynamics of pedestrians walking along a straight corridor.\\
-
-In the bottleneck geometry, the evacuation time diminishes (pedestrians move faster) as pedestrians become stiffer along the explored desired velocities.
-This phenomenon occurs because stiffer pedestrians reduce the overlapping and hence the sliding friction intensity.
-This scenario releases more easily the pedestrians and reduces the probability of producing a cluster of pedestrians blocking the exit (blocking cluster).
-This leads to a more efficient evacuation dynamics.
-\\
-
-The opposite behavior is obtained in the corridor geometry with respect to the bottleneck geometry.
-The major difference is that pedestrians are limited to the available space between walls in the corridor geometry.
-Walls are not relevant in the bottleneck geometry.
-Thus, the overlap between pedestrians is controlled by the available space.
-But, stiffer pedestrians are more likely to get stuck.
-The whole crowd can be compared to a granular material.
-Granular materials can be disordered (amorphous) or ordered depending on how particles interact with each other.
-In the present context, at low stiffness levels, the crowd appears disordered attaining a parabolic velocity profile.
-If the stiffness level is high, the whole crowd appears ordered into a lattice (like a crystalline solid) with a uniform velocity profile that depends on the friction interaction with the walls.\\
-
-Our efforts to ``tune'' the original SFM to reproduce empirical data (say, the fundamental diagram) moved us to explore the dimensionless parameter space.
-We found that  we can qualitatively reproduce the empirical data if the parameters are close to $\mathcal{K}_c < 68$, $\mathcal{K} = 685$ and $\mathcal{A}=14$.
-Nevertheless, this is a first attempt to arrive at suitable parameters, although we do not claim these to be optimal.
-We encourage further research to find dimensionless numbers that may better fit experimental data.\\
+Having adopted as fundamental philosophy of work that the parameters of the SFM
+should be properly determined by requiring that the model properly reproduces
+well established experimental data, we explored the effect on the pedestrians
+dynamics of the (sometimes neglected) body force in the framework of the SFM. We
+showed that the stiffness coefficient ($k_n$) has a significant impact on the
+evacuation dynamics (bottleneck) and also in the dynamics of pedestrians walking
+along a straight corridor.\\
+
+In the bottleneck geometry, the evacuation time diminishes (pedestrians move
+faster) as pedestrians become stiffer along the explored desired velocities.
+This phenomenon occurs because stiffer pedestrians reduce the overlapping and
+hence the sliding friction intensity. This scenario releases more easily the
+pedestrians and reduces the probability of producing a cluster of pedestrians
+blocking the exit (blocking cluster). This leads to a more efficient evacuation
+dynamics. \\
+
+The opposite behavior is obtained in the corridor geometry with respect to the
+bottleneck geometry. The major difference is that pedestrians are limited to the
+available space between walls in the corridor geometry.  Walls are not relevant
+in the bottleneck geometry. Thus, the overlap between pedestrians is controlled
+by the available space. But, stiffer pedestrians are more likely to get stuck.
+The whole crowd can be compared to a granular material. Granular materials can
+be disordered (amorphous) or ordered depending on how particles interact with
+each other. In the present context, at low stiffness levels, the crowd appears
+disordered attaining a parabolic velocity profile. If the stiffness level is
+high, the whole crowd appears ordered into a lattice (like a crystalline solid)
+with a uniform velocity profile that depends on the friction interaction with
+the walls.\\
+
+Our efforts to ``tune'' the original SFM to reproduce empirical data (say, the 
+fundamental diagram) moved us to explore the dimensionless parameter space.  We 
+found that  we can qualitatively reproduce the empirical data if the parameters 
+are close to $\mathcal{K}_c < 68$, $\mathcal{K} = 685$ and $\mathcal{A}=14$. 
+Nevertheless, this is a first attempt to arrive at suitable parameters, although
+ we do not claim these to be optimal. We encourage further research to find 
+ dimensionless numbers that may better fit experimental data.\\
 
@@
 Research Council (spanish: Consejo Nacional de Investigaciones Cient\'\i ficas 
-y T\'ecnicas - CONICET, Argentina) grant Programaci\'on Cient\'\i fica 2018 (UBACYT) Number 20020170100628BA.\\
-
-The authors want to thanks the degree students Josefina Catoni and Ayelen Santos for providing data acquired at 
-the subway in Buenos Aires, Argentina. \\
+y T\'ecnicas - CONICET, Argentina) grant Programaci\'on Cient\'\i fica 2018 
+(UBACYT) Number 20020170100628BA.\\
+
+The authors want to thanks the degree students Josefina Catoni and Ayelen Santos
+ for providing data acquired at the subway in Buenos Aires, Argentina. \\
 

### 2020-03-04 paper.tex
pequeñas correcciones de ortografia

@@
 a complete set of experimental parameters is still not available (to our
-konwledge). We are aware, though, of the drawbacks of this choice, say, the
+knowledge). We are aware, though, of the drawbacks of this choice, say, the
 unrealistic meanings for the length $B$ and the compressibility $k_n$ (see
@@
 room. These collide with the bulk, providing some kind of overlap during very
-short time. We will not analize this regime.\\
+short time. We will not analyze this regime.\\
 
@@
 for null body force ($\mathcal{K}_c=$0). However, when the body force is present
-(the original SFM) an ``U'' shape behavior occcurs for densities above 5
+(the original SFM) an ``U'' shape behavior occurs for densities above 5
 p$^{-2}$.\\

### 2020-03-04 paper.tex
algunas correcciones de ortografia

@@
 reflects the fact that an increase in the stiffness reduces the overlap
-between pedestrians and, as a consequence, the sliding friction is reduced.
+between pedestrians and, as a consequence, the sliding friction is diminished.
 This phenomenon reduces the number of blocking clusters close to the exit
@@
 The Social Force Model (SFM) models the crowd dynamics  considering three kinds
-of force: desired forces, social forces, and physical forces. In its original
+of forces: desired forces, social forces, and physical forces. In its original
 version, the SFM, addresses two physical forces as essential:   the ``body
@@
 
-The existence of a ``body force'' in the context of highly dense crowds (say, 5
-to 10$\,$people/m$^2$) is a commonsense matter \cite{henein_2007,fruin_1993}.
-Researchers, however, question the numerical setting for this force in  the SFM
-context \cite{lakoba_2005}. As a matter of fact, the usual   set of parameters
-provided by  Helbing prevents the excessive overlapping among pedestrians, but
-it is known to  accomplish artificially high force levels
-\cite{helbing_2000,lakoba_2005,langston_2006,lin_2017}. The force estimates from
-the SFM appear to be remarkably higher with respect to the reported real life
-data (say, an order of magnitude). The crowd motion simulations, however,
-present realistic results \cite{lakoba_2005,langston_2006,dorso_2017}.  The
-point seems to be that the SFM focuses on the ``collective behavior'' due  to
-clogging, missing the ``individualistic'' perspective  of single pedestrians  or
-very small groups \cite{helbing_2000,henein_2007,narain_2009}.  \\
+The existence of a ``body force'' in the context of highly dense crowds (say,
+more than 5$\,$people/m$^2$) is a commonsense matter
+\cite{henein_2007,fruin_1993}. Researchers, however, question the numerical
+setting for this force in  the SFM context \cite{lakoba_2005}. As a matter of
+fact, the usual   set of parameters provided by  Helbing prevents the excessive
+overlapping among pedestrians, but it is known to  accomplish artificially high
+force levels \cite{helbing_2000,lakoba_2005,langston_2006,lin_2017}. The force
+estimates from the SFM appear to be remarkably higher with respect to the
+reported real life data (say, an order of magnitude). The crowd motion
+simulations, however, present realistic results
+\cite{lakoba_2005,langston_2006,dorso_2017}.  The point seems to be that the SFM
+focuses on the ``collective behavior'' due  to clogging, missing the
+``individualistic'' perspective  of single pedestrians  or very small groups
+\cite{helbing_2000,henein_2007,narain_2009}.  \\
 
@@
 two body interactions). In the second case, crowds experience a flux  slowing
-down, but other behaviors are also possible \cite{helbing_2007,lohner_2018}.
-We may suspect that the  modeling of the  ``flux slowing down'' within the
-context of the SFM will require the proper  setting of the (dimensionless)
-controlling parameters. We have already examined this working hypothesis in
-Ref.~\cite{dorso_2019}, but limiting the parameter exploration to  the sliding
-friction, disregarding the body force.  We now widen the investigation on the
-set of parameters to include the one  associated to the body force. We will
-explore   the complex interplay between  the body force and the sliding friction
-among pedestrians. Recall that the  interplay dynamics is not directly
-controlled by the set of parameters, but  through dimensionless ``numbers'',
-where the model parameters appear mixed  between each other. Thus, this step up
-offers a challenge to the  ``individualistic'' meaning of the parameter's set.
-\\
+down, but other behaviors are also possible \cite{helbing_2007,lohner_2018}. We
+may suspect that the  modeling of the  ``flux slowing down'' within the context
+of the SFM will require the proper  setting of the (dimensionless) controlling
+parameters. This working hypothesis was already examined in
+Ref.~\cite{dorso_2019}, but the parameter exploration was limited to  the
+sliding friction, disregarding the body force. In this paper, we widen the
+investigation on the set of parameters to include the one  associated to the
+body force. We will explore   the complex interplay between  the body force and
+the sliding friction among pedestrians. Recall that the  interplay dynamics is
+not directly controlled by the set of parameters, but  through dimensionless
+``numbers'', where the model parameters appear mixed  between each other. Thus,
+this step up offers a challenge to the  ``individualistic'' meaning of the
+parameter's set. \\
 
@@
 \ref{background}). We present our numerical simulations in Section
-\ref{results}. For the sake of clarity, this Section is  separated into two
-major parts: the bottleneck scenario and the corridor  scenario in Sections
-\ref{bottleneck} and \ref{corridor}, respectively.  Section \ref{conclusions}
-opens a detailed discussion from results in Section \ref{results} and resumes
-our main conclusions.
+\ref{results}. For the sake of clarity, this Section is  separated into three
+major parts: the bottleneck scenario, the corridor scenario and the comparison
+with empirical data in Sections: \ref{bottleneck}, \ref{corridor} and
+\ref{Dimensionless}, respectively.  Section \ref{conclusions} opens a detailed
+discussion from results in Section \ref{results} and resumes our main
+conclusions.
 
@@
 $k_n$ assesses either the clothes and the body compressibility. The  final
-value, though, is linearly related to the compression $x$. \\
+value, though, is linearly related to the compression (overlap) $x$. \\
 
@@
 
-The maximum (realistic) compressions may be computed from the Hooke's relation
+The maximum (realistic) overlap may be computed from the Hooke's relation
 $F(x)=k_n(x)\,x$ and the compressibility $k_n(x)$ reported in
 Table~\ref{table_data}.  An ``uncomfortable'' body force  $10\,$N $-$ $30\,$N
-can address compressions in the  range of $0.030-0.055\,$m. Also, a ``hitting''
-force of $60\,$N can address  compressions between $0.045$ and $0.065\,$m.
-Besides, no reliable values for the sliding friction $k_t$ appears to be
-available in the literature (to our knowledge).\\
+can address overlap values in the  range of $0.030-0.055\,$m. Also, a
+``hitting'' force of $60\,$N can address  overlap values between $0.045$ and
+$0.065\,$m. Besides, no reliable values for the sliding friction $k_t$ appears
+to be available in the literature (to our knowledge).\\
 
@@
 The Social Force Model (SFM) provides a necessary framework for simulating  the
-collective dynamics of self-driven particles (\textit{i.e.} pedestrians).  The
+collective dynamics of pedestrians (\textit{i.e.} self-driven particles). The
 pedestrians are considered to follow an equation of motion involving  either
@@
 makes him (her) appear more or less ``assertive''. As  mentioned in
-Section~\ref{experimental}, the reaction time $\tau$ reflects for  this
+Section~\ref{experimental}, the reaction time $\tau$ reflects this
 attitude. Thus, the desire force is modeled as follows
@@
 
-\subsection{Dimensionless numbers and comparison with empirical data}
+\subsection{\label{Dimensionless}Dimensionless numbers and comparison
+ with empirical data}
 

### 2020-03-05 paper.tex
agregue la palabra set en la linea 412
borre comentarios que no voy a usar en el tex

@@
 \usepackage{amssymb} 
-
 \usepackage{mathtools}
-
 \usepackage{lineno}
-
 \usepackage{tikz}        %permite rellenar las figuras (circulos)
 \usepackage{etoolbox}
-%\usepackage[backend=biber,citestyle=authoryear]{biblatex}
 \usepackage{ulem}         %permite el tachado de texto.
-
-%\usepackage{epstopdf}
-
 \usepackage[caption=false]{subfig}
@@
 
-The numerical of the parameters may affect the dynamics of the  pedestrians.
+The numerical set of parameters may affect the dynamics of the  pedestrians.
 Some values, however, yield similar collective dynamics. We introduce
@@
 
-%It is worth mentioning that the SFM contemplates the possibility of overlapping
-%between pedestrians (unlike the models stated in
-%Refs.~\cite{kabalan_2017,jebrane_2019}). Despite this hard-to-interpret
-%feature, the SFM can reproduce empirical behaviors of collective pedestrian
-%dynamics.\\
-
 These results suggest that although increasing $\mathcal{K}_c$ slows down the
@@
 search.\\
-
-\begin{comment}
-Fig. \ref{flow_density} shows the flow as a function of the global density 
-(fundamental diagram). \ref{flow_density_no_body_force} corresponds to zero body
- force (\textit{i.e.} $k_n=0$), Fig.~\ref{flow_density_body_force} corresponds 
- to a body force with $k_n=1.2\,$E5. Each curve correspond to a different 
- friction value (see the caption).\\
-
-According to most of the empirical measurements, the flow decreases for high 
-enough values of density because the crowd becomes jammed. Notice that the 
-original friction does not produce a reduction of the flow when there is zero 
-body force but when the body force is included (with the original SFM value), 
-the flow reduces from  5 p m$^{-2}$ to 7 p m$^{-2}$ and increases for higher 
-values of density. When the friction is five times the original value, the flow 
-reduces for densities higher than 5 p m$^{-2}$ in both cases (with body force 
-and without body force). The main qualitative difference is that including the 
-body force produces a subtle increment in the flow for densities higher than 
-7 p m$^{-2}$. When the friction is increased by a factor of ten, the flow 
-reduces or remains constant when the density is higher than 5 p m$^{-2}$ for 
-both cases (with body force and without body force). This result suggests that 
-even including the body force, the original SFM requires an increment of the 
-friction in order to reproduce the flow reduction reported in empirical 
-measurements.\\
-\end{comment}
 

### 2020-03-05 paper.tex
correcciones chicas de ortografia

@@
 
-\item[(c)] We will explore crowd densities allowing body compressions up to
-$0.1\,$m. This corresponds to remarkably high densities, since our own  (real-
-life) estimates do not surpass $0.065\,$m (see  Section~\ref{experimental}).
-Therefore, the extremely high density  scenarios (say, above $0.065\,$m) will be
-considered for the purpose of a  tendency, but not as a common real-life
-situation. No casualties due to high  pressures will be further considered.
+\item[(c)] We will explore crowd densities allowing body compressions (overlaps)
+up to $0.1\,$m. This corresponds to remarkably high densities, since our own
+(real- life) estimates do not surpass $0.065\,$m (see
+Section~\ref{experimental}). Therefore, the extremely high density  scenarios
+(say, above $0.065\,$m) will be considered for the purpose of a  tendency, but
+not as a common real-life situation. No casualties due to high  pressures will
+be further considered.
 
@@
 crowded environments. We will work on the hypothesis that any ``reasonable''
-parameter set should reproduce the collective behavior (say, the slowing down
-in the fundamental diagram; see Section~\ref{corridor}). We will not attempt to
-optimize parameters from other objective functions. \\
+parameter set should reproduce the collective behavior (say, the slowing down in
+the fundamental diagram; see Section~\ref{Dimensionless}). We will not attempt
+to optimize parameters from other objective functions. \\
 
@@
 environments. The body compression and the sliding friction parameters are
-supposed to be connected in some way under this hypothesis. However, we will
-not introduce any direct link between $\mathcal{K}$ and $\mathcal{K}_c$. We
-will investigate the interplay between both in Section~\ref{corridor}.  \\
+supposed to be connected in some way under this hypothesis. However, we will not
+introduce any direct link between $\mathcal{K}$ and $\mathcal{K}_c$. We will
+investigate the interplay between both in Section~\ref{Dimensionless}.\\
 
@@
 velocities $v_d>1.2\,$m/s. The  evacuation time attains a FIS+FIF pattern for
-compression coefficients below  $k=1.2\,$E5. This means that ``soft''
+compression coefficients below  $k_n=1.2\,$E5. This means that ``soft''
 individuals can attain this  behavioral pattern.  Notice that higher values of
@@
 \caption[width=0.47\columnwidth]{(a) Mean degree as a function of the
-pedestrian’s desired velocity (m/s). (b) Mean overlap as a function of the
+pedestrian’s desired velocity. (b) Mean overlap as a function of the
 pedestrians desired velocity. Each symbol indicates the $k_n$ value
@@
 degree approaches the asymptotic value  of six. Degree six corresponds to the
-maximum packing density for identical  hard circles.\\
+maximum packing density for identical hard disks.\\
 
@@
 corridor at time $t=50\,$s. The global density was $\rho=6$.  The lines that 
-connect the nodes (pedestrians) represent the contact between them. The colors 
+connect the nodes (pedestrians) represent the contacts between them. The colors 
 stand for the degree of the node (the number of pedestrians that are in contact 
@@
 forces the ``stiff'' pedestrian to increase his (her) contacts. On the contrary,
-no real containment walls exist in the bottleneck situation (regardless the side
+no real confining walls exist in the bottleneck situation (regardless the side
 walls). \\
@@
 Fig.~\ref{overlap_vd}, however, do not meet each other as in  
-Fig.~\ref{overlap_dens}. All the curves meet each other at
+Fig.~\ref{overlap_dens} where all the curves meet each other at
 high-density values. This phenomenon occurs due to space limitations
@@
 
-The above results represent an important step in the  investigation. The inter-
-pedestrian connectivity differences between the bottleneck geometry  and the
-corridor geometry were not expected and opens two major questions:  how do the
-pedestrians interact with the walls as a function of the body stiffness, and
-consequently, how does  this affect the flux across the corridor.\\
+The above results represent an important step in the  investigation.
+The inter-pedestrian connectivity differences between the bottleneck geometry
+and the corridor geometry were not expected and opens two major questions:  how
+do the pedestrians interact with the walls as a function of the body stiffness,
+and consequently, how does  this affect the flux across the corridor.\\
 
@@
 the same speed as his (her) neighbors. This  behavior may be envisaged as the
-passage from a ``free''  walking movement to a  constrained movement as the
-stiffness increases. A more  physical picture would assimilate the former as a
-``fluid-like  state'' and the latter as a ``solid-like state''. When the
+passage from a ``free''  walking movement to a constrained walking movement as
+the stiffness increases. A more  physical picture would assimilate the former as
+a ``fluid-like  state'' and the latter as a ``solid-like state''. When the
 stiffness is  very high (say $k_n=$1.2~E6), all the pedestrians  are expected to
@@
 for very stiff pedestrians. This means that the crowd can not be easily
-``deformed''. In this context, deformation means that parts of the crowd may be
-allowed to move faster than other parts of the crowd. \\
+``deformed''. In this context, deformation means that some parts of the crowd
+may be allowed to move faster than other parts of the crowd. \\
 
@@
 respect to the velocity of the pedestrians at the center of the corridor
-(center). Thus, $\dot{\gamma}$ vanishes (no deformation) as the stiffness level
-increases. This phenomenon is shown in Fig.~\ref{strain_rate_vs_kn} where we can
-see that the strain rate drops for high values of $k_n$. \\
+(center). Thus, the strain rate $\dot{\gamma}$ vanishes (no deformation) as the
+stiffness level increases. This phenomenon is shown in
+Fig.~\ref{strain_rate_vs_kn} where we can see that the strain rate drops for
+high values of $k_n$. \\
 
@@
 the corridors play a critical role that prevents pedestrians from detaching from
-each other. This effect has can be observed as an increment in the connectivity
+each other. This effect can be observed as an increment in the connectivity
 of the contact network and the flattening of the velocity profile (thus reducing
-the strain rate). Very high enough stiffness values stuck the pedestrians
+the strain rate). High enough stiffness values stuck the pedestrians
 leading to a ``solidification'' of the crowd. All the pedestrians walk at almost
@@
 
-A further increment of $\mathcal{K}$ to $\mathcal{K}=$137 (ten times the 
+A further increment of $\mathcal{K}$ to $\mathcal{K}=$1371 (ten times the 
 original SFM value) attains a plateau ($\rho>5$ p m$^{-2}$) before vanishing at 
@@
 Having adopted as fundamental philosophy of work that the parameters of the SFM
-should be properly determined by requiring that the model properly reproduces
+should be properly determined by requiring that the model reproduces
 well established experimental data, we explored the effect on the pedestrians
@@
 
-The authors want to thanks the degree students Josefina Catoni and Ayelen Santos
+The authors want to thank the degree students Josefina Catoni and Ayelen Santos
  for providing data acquired at the subway in Buenos Aires, Argentina. \\

### 2020-03-05 paper.tex
correcciones ortograficas minimas

@@
 significant intrusion. This (partially) supports the argument that the sliding
-friction should weaken for stiffer pedestrians (say increasing $k_n$ values). \\
+friction should weaken for stiffer pedestrians (say increasing $k_n$ values).\\
 
@@
 to $\mathcal{K}_c=$ 0 (this is \textit{i.e.} $k_n=0$) while
-Fig.~\ref{flow_density_body_force} corresponds to $\mathcal{K}_c=$68
+Fig.~\ref{flow_density_body_force} corresponds to $\mathcal{K}_c=$ 68
 corresponding to the original SFM with $k_n=1.2\,$E5. Each curve represents
@@
 high enough densities due to jamming. Notice that the original SFM
-(corresponding to $\mathcal{K}=$137) does not produce the expected slowing down
-for null body force ($\mathcal{K}_c=$0). However, when the body force is present
-(the original SFM) an ``U'' shape behavior occurs for densities above 5
+(corresponding to $\mathcal{K}=$ 137) does not produce the expected slowing down
+for null body force ($\mathcal{K}_c=$ 0). However, when the body force is
+present (the original SFM) an ``U'' shape behavior occurs for densities above 5
 p$^{-2}$.\\
@@
 
-A further increment of $\mathcal{K}$ to $\mathcal{K}=$1371 (ten times the 
+A further increment of $\mathcal{K}$ to $\mathcal{K}=$ 1371 (ten times the 
 original SFM value) attains a plateau ($\rho>5$ p m$^{-2}$) before vanishing at 
@@
 should be properly determined by requiring that the model reproduces
-well established experimental data, we explored the effect on the pedestrians
+well established experimental data; we explored the effect on the pedestrians
 dynamics of the (sometimes neglected) body force in the framework of the SFM. We

### 2020-03-05 plots/bottleneck/network_config/plot_config_graph.py
agregue dibujo de la puerta en bottleneck

@@ -7,6 +7,7 @@ import numpy as np
 import networkx as nx
 import matplotlib.pyplot as plt
 import matplotlib.colors as mcolors
+import matplotlib.patches as patches
 import pylab
 import math
 
@@ -130,6 +131,8 @@ def plot_network(G,output_filename,title):
      nodes = G.nodes()
      n_color = np.asarray([degrees[n] for n in nodes])
      fig, ax = plt.subplots()
+     rect = patches.Rectangle((20,10),0.3,1,linewidth=2,edgecolor='k',clip_on=False,facecolor='k')
+     ax.add_patch(rect)
      pos = nx.get_node_attributes(G,'pos')
      sc = nx.draw(G,pos,width=0.5,cmap='jet',vmax=6,node_color=n_color,node_size=5,with_labels=False,edge_color='black')
      plt.axis([13,20,4,16])
@@ -150,6 +153,9 @@ def plot_network(G,output_filename,title):
      plt.text(21.5, 11.5, "4", fontsize=12,color="k")
      plt.text(21.5, 13, "5", fontsize=12,color="k")
      plt.text(21.5, 15, "6", fontsize=12,color="k")
+
+
+
      pylab.savefig('{}.png'.format(output_filename), format='png', dpi=300, bbox_inches='tight')
      pylab.savefig('{}.eps'.format(output_filename), format='eps', dpi=300, bbox_inches='tight')
 
@@ -160,9 +166,9 @@ def main():
 
      ############# PARAMETERS #############
      #1200000
-     input_filename = 'config_bottleneck_vd2_k1200000'
-     output_filename = 'network_vd2_kn1200000'
-     title = "$v_d=$2 m~s$^{-1}$ \hspace{0.5cm} $k_n=$1.2~E6"
+     input_filename = 'config_bottleneck_vd2_k0'
+     output_filename = 'network_vd2_kn0'
+     title = "$v_d=$2 m~s$^{-1}$ \hspace{0.5cm} $k_n=$0"
      time = 100
      sum_rads = 0.46
      ######################################

### 2020-03-05 paper.tex
agregue dibujo de la puerta en bottleneck
agregue parrafo de unidades

@@
 
+We warn the reader that, for simplicity, we will not include the units
+corresponding to the numerical results. Remember that the friction coefficient
+has units $\left [ k_t \right]=$Kg~m$^{-1}$~s$^{-1}$, 
+the body stiffness coefficient $\left [ k_n \right]=$Kg~s$^{-2}$, 
+the density $\left [ \rho \right]=$p~m$^{-2}$ and the flow $\left [ J \right
+]=$p~m$^{-1}$~s$^{-1}$.\\
+
 \section{\label{results}Results}
@@
 respectively. (c) and (d) correspond to simulations with $k_n=1.2\,$E6 with
-$v_d=$2 and $v_d=$10 respectively. Color online only.}
+$v_d=$2 and $v_d=$10 respectively. The black rectangle at the right
+represents the exit door. Color online only.}
 \label{network_bottleneck}
